### 2022-04-16 Publish Paper/manuscript_main.tex
Update Publish Paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%The Need of Medical Engioneering

%The Need of Medical Engineering in Skin Lesion Clasification

%The Success in AI - especially in CNN - some model based CNN

%Related Work

%My Approach

\section{The Model}

\section{Data}

\section{Results}

\section{Conclusion}
\cite{08332}
\clearpage
\pagebreak

### 2022-04-17 Publish Paper/manuscript_title_etc.tex
Update Publish Paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 1. Define Keywords, JEL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERKEYWORDS}{\textbf{Keywords}: AI-enabled computer-aid diagnosis, Diagnosis, Skin Sancer, Skin Lesion Classification, Artificial Intelligence, Deep Learning, Machine Learning}
\newcommand{\PAPERJEL}{\textbf{JEL}: I15, D8, D9, O15}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2. Define Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERTITLE}{Skin Cancer Classification using Soft Attention and Metadata Concatenance}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 3. Define Authors contact information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\AUTHORWANG}{Hoang Khoi Do \\ khoi.dh200322@sis.hust.edu.vn \\ Ha Noi University of Science and Technology}
%\newcommand{\AUTHORWANGINFO}{\AUTHORWANG: Ha Noi University of Science and Technology (email: khoi.dh200322@sis.hust.edu.vn)}
\newcommand{\AUTHOREMAIL}{khoi.dh200322@sis.hust.edu.vn}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 4. Define Thanks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ACKNOWLEDGMENTS}{
We thank \blindtext}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Recent estimates are that about 150 million children under five years of age are stunted, with substantial negative consequences for their schooling, cognitive skills, health, and economic productivity. Therefore, understanding what determines such growth retardation is significant for designing public policies that aim to address this issue. We build a model for nutritional choices and health with reference-dependent preferences. Parents care about the health of their children relative to some reference population. In our empirical model, we use height as the health outcome that parents target. Reference height is an equilibrium object determined by earlier cohorts' parents' nutritional choices in the same village. We explore the exogenous variation in reference height produced by a protein-supplementation experiment in Guatemala to estimate our model’s parameters. We use our model to decompose the impact of the protein intervention on height into price and reference-point effects. We find that the changes in reference points account for 65\% of the height difference between two-year-old children in experimental and control villages in the sixth annual cohort born after the initiation of the intervention.}

### 2022-04-20 Publish Paper/manuscript_main.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textbf{ACKNOWLEDGMENT} \\ 
+I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung() who gave me the golden support to do this wonderful project.
+He gave a chance to use High GPU computing computer for AI Training.
+Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.
 \section{Introduction}
+%The Need of AI-enabled computer-aided diagnostics
+Skin cancer is one of the most common cancer leading causes of death worldwide.
+Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer.
+Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year.
+According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}.
+In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}.
+On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%.
+However, once disease progresses beyond the skin, survival is poor\cite{11872}.
+Moreover, with the increasing
+incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need of effective solution. \newline
+%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
+Recently, deep learning particularly, and machine learning in generally algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks.
+AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis and Medical Treatment.
+Medical imaging, including ultrasound, computed tomography, and magnetic resonance imaging, and X-ray image is used extensively in clinical practice.
+In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosed results are considered by a doctor.
+In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history medical data.
+In Medical Treatment, AI models are applied for building solution for a specific disease, medicine revolutionize is an example.
+In various studies, AI algorithms has provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.
+\newline
+%The Success in AI - especially in CNN - some model based CNN
+In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance.
+Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{11946}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, VGG\cite{1556}, and Xception\cite{02357}.
+Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section.
 
-%The Need of Medical Engioneering
+\section{Related Work}
 
-%The Need of Medical Engineering in Skin Lesion Clasification
+\section{Objective}
+In this paper, my objectives are: \newline
+- Building a model that has ability to classify in a balanced way between classes instead of specifying almost classes except one or two classes. \newline
+- Investigate the performance of the combination of different backbone model and SoftAttention. \\
+- Identifying whether the metadata can make the performance of model better. \\
 
-%The Success in AI - especially in CNN - some model based CNN
+\section{Implementation}
 
-%Related Work
+\subsection{Data}
+The dataset used in this paper is the HAM10000 dataset published by Havard University Dataverse\cite{10417}.
+There are total 7 classes in this dataset containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses and lichen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
+The distribution of the dataset is shown in the table below:
+\begin{center}
+	\begin{tabular}{|c c c c c c c c c|} 
+		\hline
+		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
+		\hline
+		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
+		\hline
+	\end{tabular}
+\end{center}
+More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL).
+\subsection{Model Schema}
+\subsubsection{Input Schema}
+\subsubsection{Backbone Model}
+\subsubsection{SoftAttention}
+\subsubsection{Output Schema}
+\subsubsection{Model}
 
-%My Approach
-
-\section{The Model}
-
-\section{Data}
-
+\subsection{Training}
+\subsubsection{Data Division}
+\subsubsection{Loss Function}
+The loss function used in this paper is categorical cross-entropy.
+Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $W = [w_1, w_2, \dots, w_n]$.
+Let $n$ is the number of class in the dataset.
+The categorical cross-entropy loss is presented as:
+\[L(w, x_i) = -\sum_{i=1}^{n}y_i\log(\hat{y}_i)\]
+where $\hat{y}_i$  is the output of model and $y_i$ is the target that the model should return. \\
+Since the dataset face the imbalanced problem then I applied the class weight for the loss. This formula below is used to calculate the class weight:
+\[CLassWeight = N \odot D\]
+\[D = [\frac{1}{C \times  N_1}  \frac{1}{C \times  N_2}  \dots \frac{1}{C \times  N_n}]\]
+where $N$ is the number of sample in dataset, $C$ is the number of class in the dataset, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.
+\subsubsection{Optimizer}
 \section{Results}

### 2022-04-23 Publish Paper/manuscript_main.tex
Update Diagram and Paper

@@
 In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance.
-Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{11946}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, VGG\cite{1556}, and Xception\cite{02357}.
+Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{11946}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, VGG\cite{1556}.
 Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section.
@@
 
-\section{Implementation}
-
-\subsection{Data}
+\section{Data}
 The dataset used in this paper is the HAM10000 dataset published by Havard University Dataverse\cite{10417}.
-There are total 7 classes in this dataset containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses and lichen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
+There are total 7 classes in this dataset containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
 The distribution of the dataset is shown in the table below:
@@
 More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL).
-\subsection{Model Schema}
-\subsubsection{Input Schema}
-\subsubsection{Backbone Model}
-\subsubsection{SoftAttention}
-\subsubsection{Output Schema}
-\subsubsection{Model}
+On the other hand, before being used for training the whole data is shuffled then split into two part.
+$90$ percent and $10$ percent of the data is used for training and validating respectively.
+Besides, the label of the whole data is preprocessed into one-hot vector.
+Each backbone need the different input size of image as well as the range of pixel value.
+DenseNet201\cite{06993} require the input pixels values are converted to type float32 scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet dataset.
+In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet dataset, without scaling.
+InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$.
 
-\subsection{Training}
-\subsubsection{Data Division}
-\subsubsection{Loss Function}
+\section{Model Schema}
+\subsection{Input Schema}
+\subsection{Soft-Attention}
+\subsection{Backbone Model Architecture}
+\subsection{Output Schema}
+\subsection{Model}
+
+\section{Training}
+\subsection{Loss Function}
 The loss function used in this paper is categorical cross-entropy.
@@
 where $N$ is the number of sample in dataset, $C$ is the number of class in the dataset, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.
-\subsubsection{Optimizer}
+\subsection{Evaluation Metric}
+
 \section{Results}
-
+All the model in this paper is trained with Adam Optimizer\cite{6980}.
+The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$.
+Otherwise, the epsilon argument of the optimizer is set to $0.1$.
+The performance of all model is presented in the figure below:
 \section{Conclusion}

### 2022-05-02 Publish Paper/manuscript_main.tex
Update Paper

@@
 In various studies, AI algorithms has provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.
-\newline
+\\
 %The Success in AI - especially in CNN - some model based CNN
 In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance.
-Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{11946}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, VGG\cite{1556}.
+Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, NasNet\cite{07012}.
 Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section.
+\\
+In this paper, I will analyze the effect of the metadata on classifying skin disease.
+On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has ability to classify in a balanced way between classes instead of well identifying the majority of classes.
 
@@
 
-\section{Objective}
-In this paper, my objectives are: \newline
-- Building a model that has ability to classify in a balanced way between classes instead of specifying almost classes except one or two classes. \newline
-- Investigate the performance of the combination of different backbone model and SoftAttention. \\
-- Identifying whether the metadata can make the performance of model better. \\
-
 \section{Data}
+\subsection{Image Data}
 The dataset used in this paper is the HAM10000 dataset published by Havard University Dataverse\cite{10417}.
@@
 \end{center}
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/DataDistribution}
+	\caption{Example image of each class}
+	\label{fig:datadistribution}
+\end{figure}
 More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL).
 On the other hand, before being used for training the whole data is shuffled then split into two part.
-$90$ percent and $10$ percent of the data is used for training and validating respectively.
-Besides, the label of the whole data is preprocessed into one-hot vector.
-Each backbone need the different input size of image as well as the range of pixel value.
-DenseNet201\cite{06993} require the input pixels values are converted to type float32 scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet dataset.
+$90$ percent and $10$ percent of the data is used for training and validating respectively.\\
+In the previous paper\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images.
+Since, this data is imbalanced, using augmented data may cause the problem of well classify on the majority of class.
+In this paper, instead of augmenting data, metadata is used.
+The way of processing metadata is discuss in MetaData section.
+Images in this dataset has the type of $RGB$ and shape of (450, 600).
+However, Each backbone need the different input size of image as well as the range of pixel value.
+DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet dataset.
 In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet dataset, without scaling.
 InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$.
-
+Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.
+\subsection{Metadata}
+The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position.
+During the data exploration term, I found out that the age category miss 57 data point, then I decided to remove this 57 samples.
+In the gender and capturing position category contain some samples of unknown.
+Instead of removing, these unknowns data point is kept and considered as "prefer not to say".
+Besides, the label of the whole data is preprocessed into one-hot vector.
 \section{Model Schema}
 \subsection{Input Schema}
+%Other preprocessed input%
+Using metadata as another input is not new.
+In paper\cite{03910}, they decide to keep the missing value and set its value to $0$.
+The sex and anatomical site are categorical encoded.
+The age, on the other hand is numerical normalized.
+After processing, the metadata is fed into a two-layer neural network with 256 neurons each.
+Each layer contains batch normalization, a ReLU\cite{08375} activation and dropout with $p = 0.4$.
+The network’s output is concatenated with the CNN’s feature vector after global average pooling.
+Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata.
+During training, they randomly encode each property as missing with a probability of $p = 0.1$.
+\\
+%My proprocessed input%
+In this paper, the unknowns is kept as a type as discussed in Metadata section.
+Sex, anatomical site and age are also category encoded and numerical normalized, respectively.
+After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons.
+Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section.
+\\
+%Figure%
+The Input schema is described as follow:
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{"Diagram/Input Schema"}
+	\caption{Input Schema}
+	\label{fig:input-schema}
+\end{figure}
+
 \subsection{Soft-Attention}
+Applying Soft-Attention layer in deep learning is not a new approach.
+Soft-Attention have been used in various application: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively.
+In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}.
+Soft-Attention has ability to ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights.
+The function below describe the flow of Soft-Attention module:
+\[
+	f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
+\]
+In order to apply Soft-Attention, there are two main steps.
+Firstly, the input tensor is put in a grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}.
+This feature map called $t \in R^{h \times w \times d}$ where $h, w, and d$ is the shape of tensor generate by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$.
+The output of this convolution is normalized using softmax function to generate K = 16 attention maps.
+These $16$ attention maps are aggregated to produce a weight function called $\alpha$.
+This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar.
+Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{Diagram/SoftAttention}
+	\caption{Soft-Attention Module}
+	\label{fig:softattention}
+\end{figure}
+In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{Diagram/SoftAttentionBlock}
+	\caption{Soft-Attention Module}
+	\label{fig:softattentionblock}
+\end{figure}
+
 \subsection{Backbone Model Architecture}
@@
 The loss function used in this paper is categorical cross-entropy.
-Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $W = [w_1, w_2, \dots, w_n]$.
-Let $n$ is the number of class in the dataset.
+Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$.
+Let $N$, and $C$ is the number of training examples and number of class respectively.
 The categorical cross-entropy loss is presented as:
-\[L(w, x_i) = -\sum_{i=1}^{n}y_i\log(\hat{y}_i)\]
-where $\hat{y}_i$  is the output of model and $y_i$ is the target that the model should return. \\
+\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}y^c_n\log(\hat{y}^c_i)\]
+where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return. \\
 Since the dataset face the imbalanced problem then I applied the class weight for the loss. This formula below is used to calculate the class weight:
-\[CLassWeight = N \odot D\]
-\[D = [\frac{1}{C \times  N_1}  \frac{1}{C \times  N_2}  \dots \frac{1}{C \times  N_n}]\]
-where $N$ is the number of sample in dataset, $C$ is the number of class in the dataset, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.
-\subsection{Evaluation Metric}
-
+\[W = N \odot D\]
+\[D = \begin{bmatrix}
+	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
+\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
+\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
+\end{bmatrix}\]
+where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$.
+$D$ is the matrix contain the inverse of $C \times N_i$.
+The overall loss function is then become\cite{8943952}:
+\[
+	L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N} W_c \times y^c_n \times \log(h_\theta(x_n, \theta, c))
+\]
+where $W_c$ is the weight of class $c$, $y^c_n$ is the expected output of class $c$ at training example $n$. Otherwise, $h_\theta$ is the model with weight $\theta$.
+\subsection{Evaluation Metrics}
+\begin{figure}[!htb]
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=1.1\linewidth]{img/Confusion-matrix}
+		\caption{Confusion Matrix}\label{Fig:Data1}
+	\end{minipage}\hfill
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=.7\linewidth]{img/AUC}
+		\caption{Area Under the Curve}\label{Fig:Data2}
+	\end{minipage}
+\end{figure}
+In this paper, the model is evaluated by using the confusion matrix and related metrics.
+The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class.
+Consider a confusion matrix $A$ with $C$ number of class.
+Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively.
+\[
+	A = \begin{bmatrix}
+		a_{11} & a_{12} & \dots & a_{1j} \\
+		a_{21} & a_{22} & \dots & a_{2j} \\
+		\vdots & \vdots	&  & \vdots\\
+		a_{i1} & a_{i2} & \dots & a_{ij} 
+	\end{bmatrix}
+\]
+The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$.
+The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
+\[
+	FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
+\]
+\[
+	TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
+		TN_1 & TN_2 & \dots & TN_c
+	\end{bmatrix}
+\]
+Then, the model is evaluated by the following metrics:
+\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
+\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
+\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
+The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
 \section{Results}

### 2022-05-04 Publish Paper/manuscript_main.tex
Update paper

@@
 In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance.
-Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, NasNet\cite{07012}.
+Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
 Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section.
@@
 %Figure%
-The Input schema is described as follow:
+The Input schema is described as follow:\\
 \begin{figure}[h]
@@
 	\label{fig:input-schema}
-\end{figure}
-
+\end{figure}\\
+Image data, on the other hand after being preprocessed, is fed directly into the backbone model. 
 \subsection{Soft-Attention}
@@
 	\label{fig:softattentionblock}
-\end{figure}
+\end{figure}\\
 
 \subsection{Backbone Model Architecture}
-\subsection{Output Schema}
+In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
+The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both test by the previous paper\cite{03358} with a great performance.
+Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated.
+Therefore, in this paper, I will analyze the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth.
+On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.
+\begin{center}
+	\begin{tabular}{|c | c c c|} 
+		\hline
+		Model & Size(MB) & Parameters & Depth \\ 
+		\hline
+		Resnet50 & 98 & 25.6M & 107 \\ 
+		\hline
+		Resnet152 & 232 & 60.4M & 311 \\ 
+		\hline
+		DenseNet201 & 80 & 20.2M & 402 \\
+		\hline
+		InceptionResNetV2 & 215 & 55.9M & 449 \\
+		\hline
+		MobileNet & 16 & 4.3M & 55 \\ 
+		\hline
+		MobileNetV2 & 14 & 3.5M & 105 \\ 
+		\hline
+		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
+		\hline
+		MobileNetV3Large & Unknown & 5.5M & 118 \\
+		\hline
+		NasnetMobile & 23 & 5.3M & 308 \\
+		\hline
+		NasnetLarge & 343 & 88.9M & 533 \\ 
+		\hline
+	\end{tabular}
+\end{center}
+
 \subsection{Model}
+The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}.
+Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.
+It is described in the figure below:
 
@@
 The categorical cross-entropy loss is presented as:
-\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}y^c_n\log(\hat{y}^c_i)\]
+\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}y^c_n\log(\hat{y}^c_n)\]
 where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return. \\
@@
 \[
-	L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N} W_c \times y^c_n \times \log(h_\theta(x_n, \theta, c))
+	L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N} W_c \times y^c_n \times \log(h_\theta(x_n, c))
 \]

### 2022-05-10 Publish Paper/manuscript_main.tex
Update Reference

@@
 It is described in the figure below:
-
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{Diagram/MainModel}
+	\caption{Overall Model}
+	\label{fig:mainmodel}
+\end{figure}
 \section{Training}
@@
 The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
-\section{Results}
+\section{Experiment}
 All the model in this paper is trained with Adam Optimizer\cite{6980}.
@@
 \section{Conclusion}
-\cite{08332}
 \clearpage

### 2022-05-13 Publish Paper/manuscript_main.tex
update mail teacher

@@
 \textbf{ACKNOWLEDGMENT} \\ 
-I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung() who gave me the golden support to do this wonderful project.
+I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project.
 He gave a chance to use High GPU computing computer for AI Training.

### 2022-05-17 Publish Paper/manuscript_title_etc.tex
Update Paper
Update Publish Paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\PAPERTITLE}{Skin Cancer Classification using Soft Attention and Metadata Concatenance}
+\newcommand{\PAPERTITLE}{Skin Cancer Classification using Soft Attention and Metadata}
 
@@
 \newcommand{\PAPERABSTRACT}{
-Recent estimates are that about 150 million children under five years of age are stunted, with substantial negative consequences for their schooling, cognitive skills, health, and economic productivity.
-Therefore, understanding what determines such growth retardation is significant for designing public policies that aim to address this issue.
-We build a model for nutritional choices and health with reference-dependent preferences.
-Parents care about the health of their children relative to some reference population.
-In our empirical model, we use height as the health outcome that parents target.
-Reference height is an equilibrium object determined by earlier cohorts' parents' nutritional choices in the same village.
-We explore the exogenous variation in reference height produced by a protein-supplementation experiment in Guatemala to estimate our model’s parameters.
-We use our model to decompose the impact of the protein intervention on height into price and reference-point effects.
-We find that the changes in reference points account for 65\% of the height difference between two-year-old children in experimental and control villages in the sixth annual cohort born after the initiation of the intervention.}
+Nowadays, the dramatic development of the big city and industrial field leads to a higher rate of skin disease because of polluted air.
+Moreover, in many developing countries, the hospital is being overloaded every single day by the huge number of the patient.
+They need a fast and accurate solution to diagnose skin disease before meeting the doctor or how to create an optimized and balanced model for skin lesion classification.
+After the literature review process, I found that there are many outstanding papers on both Deep Learning and Machine Learning.
+In Deep Learning, they often use transfer learning.
+Some new approaches are GradCam, Kernel Shap, Student and Teacher model.
+In Machine Learning, Random Forest, and Support Vector Machine are applied.
+The main focus of this research is to analyze the effect of metadata on the combination of the backbone model and the Soft-Attention layer.
+The soft-Attention layer is tested in a previous paper that improve the model performance.
+I also try some other combinations to construct an optimized model that can use on mobile phone.
+After the experiment process, I found out that metadata makes the performance of the model more balanced than in the previous paper.
+I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with a bit lower accuracy but thirty times as fast as other combinations.
+}

### 2022-05-17 Publish Paper/manuscript_main.tex
Update publish paper

--- 2022-05-10 Publish Paper/manuscript_main.tex
@@
 \textbf{ACKNOWLEDGMENT} \\ 
-I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung() who gave me the golden support to do this wonderful project.
+I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project.
 He gave a chance to use High GPU computing computer for AI Training.
 Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.
+I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung(dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project.
+He gave me a chance to use High GPU computing computers for AI Training.
+Furthermore, he also gave me recommendations on how to implement experiments to make a good conclusion such as what I should focus on, what I need to investigate, and which metrics I should consider.
 \section{Introduction}
 %The Need of AI-enabled computer-aided diagnostics
-Skin cancer is one of the most common cancer leading causes of death worldwide.
+Skin cancer is one of the most common cancers leading to worldwide death.
 Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer.
@@
 On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%.
-However, once disease progresses beyond the skin, survival is poor\cite{11872}.
-Moreover, with the increasing
-incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need of effective solution. \newline
+However, once the disease progresses beyond the skin, survival is poor\cite{11872}.
+Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.
+\newline
 %The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
-Recently, deep learning particularly, and machine learning in generally algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks.
-AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis and Medical Treatment.
-Medical imaging, including ultrasound, computed tomography, and magnetic resonance imaging, and X-ray image is used extensively in clinical practice.
-In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosed results are considered by a doctor.
-In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history medical data.
-In Medical Treatment, AI models are applied for building solution for a specific disease, medicine revolutionize is an example.
-In various studies, AI algorithms has provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.
+Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks.
+AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment.
+Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice.
+In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor.
+In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data.
+In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example.
+In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.
 \\
@@
 \\
-In this paper, I will analyze the effect of the metadata on classifying skin disease.
-On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has ability to classify in a balanced way between classes instead of well identifying the majority of classes.
+In this paper, I will analyze the effect of metadata on classifying skin disease.
+On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
 
-\section{Related Work}
-
+\section{Literature Review}
+Skin lesion classification is not a new area, since there are many great performance models constructed.
+One of the most cutting-edge technologies that have been used is Soft-Attention as stated in\cite{03358}.
+Soumyya and his team construct several models formed by the combination of a backbone model including DenseNet201\cite{06993}, InceptionResNetV2\cite{00567}, ResNet50\cite{03385}\cite{05027}, VGG16\cite{1556} and Soft-Attention layer.
+Using those above backbones has been tried by many previous papers including \cite{03798} which uses transfer learning approach with CNN based model, \cite{10348} which does not only use those above backbone model but also used InceptionV3\cite{00567} model.
+Another paper that uses the backbone models is \cite{09418}.
+Hemanth and his team decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating
+holes of different sizes on the images i.e.
+technically making a random portion of image inactive during data augmentation process.
+\cite{01284} also used Deep Convolution Neural Network.
+However, that paper used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative
+Learning Strategy which can more effectively balance representation learning and
+classifier learning without additional computational cost.
+Another state of the art is GradCam and Kernel SHAP\cite{06612}, which are both model agnostic, local interpretability methods that can highlight pixels that the trained network deems
+relevant for the final classification.\\
+Otherwise, the Student and Teacher Model is also a state of the art in 2021\cite{03225}.
+The student and teacher model is the combination of two-mode which share the memory with each other.
+Therefore, they can take full advantage of what others learn.
+SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem.
+Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910}.
+\\
+On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning.
+Random Forest, XGBoost, and Support Vector Machines are tested by \cite{03798}.
+Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348}.
+Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045}.
 \section{Data}
@@
 The distribution of the dataset is shown in the table below:
-\begin{center}
+\begin{table}
+	\centering
 	\begin{tabular}{|c c c c c c c c c|} 
@@
 	\end{tabular}
-\end{center}
-\begin{figure}
+	\caption{Data Distribution in HAM10000}
+	\label{table:1}
+\end{table}
+\begin{figure}[h]
 	\centering
@@
 \subsection{Soft-Attention}
-Applying Soft-Attention layer in deep learning is not a new approach.
-Soft-Attention have been used in various application: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively.
+Applying the Soft-Attention layer in deep learning is not a new approach.
+Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively.
 In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}.
-Soft-Attention has ability to ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights.
-The function below describe the flow of Soft-Attention module:
+Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights.
+The function below describes the flow of the Soft-Attention module:
 \[
@@
 In order to apply Soft-Attention, there are two main steps.
-Firstly, the input tensor is put in a grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}.
-This feature map called $t \in R^{h \times w \times d}$ where $h, w, and d$ is the shape of tensor generate by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$.
-The output of this convolution is normalized using softmax function to generate K = 16 attention maps.
+Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}.
+This feature map called $t \in R^{h \times w \times d}$ where $h, w, and d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$.
+The output of this convolution is normalized using the softmax function to generate K = 16 attention maps.
 These $16$ attention maps are aggregated to produce a weight function called $\alpha$.
@@
 In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
-The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both test by the previous paper\cite{03358} with a great performance.
+The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance.
 Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated.
@@
 On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.
-\begin{center}
+\begin{table}
+	\centering
 	\begin{tabular}{|c | c c c|} 
@@
 	\end{tabular}
-\end{center}
+\caption{Size and Parameters and Depth of backbone model used in this paper}
+\label{table:2}
+\end{table}
 
@@
 	\includegraphics[width=1\linewidth]{Diagram/MainModel}
-	\caption{Overall Model}
+	\caption{Overall Model Architecture}
 	\label{fig:mainmodel}
@@
 Otherwise, the epsilon argument of the optimizer is set to $0.1$.
-The performance of all model is presented in the figure below:
+The accuracy of all model is presented in the figure below:\\
+\begin{table}[h]
+	\centering
+	\begin{tabular}{| c | c | c | c |}
+		\hline
+		InceptionResNetV2 & DenseNet201 & ResNet50 & VGG16 \\
+		\hline
+		0.93 & 0.91 & 0.92 & 0.88\\
+		\hline
+	\end{tabular}
+\caption{Accuracy of the model with augmented data}
+\label{table:3}
+\end{table}
+\begin{table}[h]
+	\centering
+	\begin{tabular}{| c | c | c | c | c |}
+		\hline
+		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
+		\hline
+		0.89 & 0.89 & 0.70 & 0.57 & 0.81\\
+		\hline
+	\end{tabular}
+\end{table}
+\begin{table}[h]
+	\centering
+	\begin{tabular}{| c | c | c | c |}
+		\hline
+		MobileNetV3Large & MobileNetV3Small & NasNetLarge & NasNetMobile\\
+		0.84 & 0.78 & 0.86 & 0.86\\
+		\hline
+	\end{tabular}
+\caption{Accuracy of the model with metadata}
+\label{table:4}
+\end{table}\\
+According to the Table 3 and 4, it is clear that the model trained with augmented data has a higher accuracy than the model trained with metadata only.
+While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.93$ and $0.91$ respectively, their training with metadata has both the accuracy of $0.89$.
+Furthermore, Resnet50 trained with augmented data has the accuracy that outperform the Resnet50 and is twice as high as Resnet152 trained with metadata.
+On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, although has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively.
+This term will be discussed later on.
+Although, the model trained with augmented data have high accuracy, when I analyzed the f1-score and the recall score of models, it turns out that models trained with augmented data have imbalanced f1-scores according to table 5.
+As a results, augmented data model dose not classify well on all class as InceptionRtesNetV2 trained on augmented data have 0.29 f1-score on class df while InceptionRtesNetV2 trained on metadata can classify well by a balanced way.
+This may cause by the augmented data.
+\\
+However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class. The others still face the
+the imbalanced term.
+Since this dataset is not balanced, therefore using augmented data can make the model bias to the class which has large sample.
+Using the metadata instead make the model less bias, though it still make the model imbalanced due to the high variance of model which has the number of depth much less than 400.\\
+This problem is also true with the recall score according to table 6.
+DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has recall standard deviation of $0.189$, $0.275$, $0.209$, $0.191$, respectively.
+On the other hand, other models have recall standard deviation which is close to $0.1$.
+Especially, inceptionResnetV2 train on metadata has recall standard deviation of approximately $0.09$.
+\\
+As the results, metadata does not make the model more balanced and improve the model performance.
+The reason why the model become much more balanced is the weighted loss function.
+Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class.
+Therefore, DenseNet201, InceptionResNetV2 trained with weighted loss function have recall in akiec of $0.85$.
+$0.82$, respectively, as opposed to their training in akiec without weighted loss function.
+MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|l | c | c | c | c | c | c | c | c|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & $\sigma$ \\
+		\hline
+		DenseNet201 + Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.128 \\ 
+		\hline
+		InceptionResNetV2 + Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.225\\
+		\hline
+		Resnet50 + Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.165\\
+		\hline 	
+		VGG16 + Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.197\\ 
+		\hline		
+		DenseNet201 + Metadata & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.088}\\
+		\hline
+		InceptionResNetV2 + Metadata & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.09}\\
+		\hline
+		Resnet50 + Metadata & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.162\\
+		\hline
+		Resnet152 + Metadata & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.199\\
+		\hline
+		MobileNetV2 + Metadata & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & 0.9 & 0.122\\
+		\hline
+		MobileNetV3Large + Metadata & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & 0.92 & 0.12\\
+		\hline
+		MobileNetV3Small + Metadata & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & 0.89 & 0.144\\
+		\hline
+		NasNetLarge + Metadata & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.088}\\
+		\hline
+		NasNetMobile + Metadata & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & 0.93 & 0.101\\
+		\hline
+	\end{tabular}
+	\caption{F1-Score of each class and the standard deviation of each model}
+	\label{table:5}
+\end{table}\\
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|l | c | c | c | c | c | c | c | c|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & $\sigma$ \\
+		\hline
+		DenseNet201 + Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & \textbf{0.189}\\ 
+		\hline
+		InceptionResNetV2 + Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & \textbf{0.275}\\
+		\hline
+		Resnet50 + Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & \textbf{0.209}\\
+		\hline 	
+		VGG16 + Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 	\textbf{0.191}\\ 
+		\hline		
+		DenseNet201 + Metadata & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & 0.116\\
+		\hline
+		InceptionResNetV2 + Metadata & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 	0.93 & \textbf{0.097}\\
+		\hline
+		Resnet50 + Metadata & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.107\\
+		\hline
+		Resnet152 + Metadata & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.121\\
+		\hline
+		MobileNetV2 + Metadata & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.126\\
+		\hline
+		MobileNetV3Large + Metadata & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & 0.12\\
+		\hline
+		MobileNetV3Small + Metadata & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.147\\
+		\hline
+		NasNetLarge + Metadata & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & 0.119\\
+		\hline
+		NasNetMobile + Metadata & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & 0.134\\
+		\hline
+	\end{tabular}
+	\caption{Recall score of each class and the standard deviation of each model}
+	\label{table:6}
+\end{table}\\
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|l | c | c | c | c | c | c | c|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc \\
+		\hline
+		DenseNet201 + Augmented Data & 0.96 & 0.98 & 0.9 & 0.80 & 0.95 & 0.95 & 0.999\\ 
+		\hline
+		InceptionResNetV2 + Augmented Data & 0.96 & 0.99 & 0.96 & 0.92 & 0.97 & 0.976 & 0.999\\
+		\hline
+		Resnet50 + Augmented Data & 0.97 & 0.99 & 0.91 & 0.94 & 0.95 & 0.95 & 0.99\\
+		\hline 	
+		VGG16 + Augmented Data & 0.98 & 0.99 & 0.96 & 0.97 & 0.97 & 0.97 & 0.99\\ 
+		\hline		
+		DenseNet201 + Metadata & 0.99 & 0.99 & 0.97 & 0.99 & 0.92 & 0.96 & 0.99\\
+		\hline
+		InceptionResNetV2 + Metadata & 0.98 & 0.98 & 0.98 & 0.98 & 0.95 & 0.96 & 0.99\\
+		\hline
+		Resnet50 + Metadata & 0.97 & 0.95 & 0.88 & 0.99 & 0.85 & 0.92 & 0.98\\
+		\hline
+		Resnet152 + Metadata & 0.95 & 0.9 & 0.84 & 0.92 & 0.82 & 0.89 & 0.8\\
+		\hline
+		MobileNetV2 + Metadata & 0.97 & 0.98 & 0.94 & 0.99 & 0.9 & 0.95 & 0.99\\
+		\hline
+		MobileNetV3Large + Metadata & 0.99 & 0.98 & 0.96 & 0.99 & 0.92 & 0.95 & 0.99\\
+		\hline
+		MobileNetV3Small + Metadata & 0.97 & 0.97 & 0.93 & 0.99 & 0.87 & 0.94 & 0.99\\
+		\hline
+		NasNetLarge + Metadata & 0.95 & 0.98 & 0.97 & 1 & 0.92 & 0.95 & 1\\
+		\hline
+		NasNetMobile + Metadata & 0.98 & 0.99 & 0.97 & 1 & 0.9 & 0.96 & 1\\
+		\hline
+	\end{tabular}
+	\caption{ROC AUC Score of each model}
+	\label{table:7}
+\end{table}\\
+Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
+The table 8 illustrates the deeper analyzing of the three models.\\
+\begin{table}
+	\centering	
+	\begin{tabular}{l | c | c | c | c|}
+		\hline
+		Model & MobileNetV2 & MobileNetV3Smal & MobileNetV3Large & NasNetMobile\\
+		\hline
+		Accuracy(avg)\\
+		\hline
+		Balanced Accuracy(avg)\\ 
+		\hline
+		Precision(avg)\\
+		\hline
+		F1-score(avg)\\
+		\hline
+		Sensitivity(avg)\\ 
+		\hline
+		Specificity(avg)\\
+		\hline
+		ROC-AUC-score(avg)\\
+		\hline
+	\end{tabular}
+\end{table}
 \section{Conclusion}
+
 \clearpage

### 2022-05-17 Publish Paper/manuscript_main.tex
Update publish paper

@@
 Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
-The table 8 illustrates the deeper analyzing of the three models.\\
+The table 8 illustrates the deeper analyzing of the three models.
+It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.
+Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.At the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model.
+The result of this experiment is illustrated in table 9.\\
 \begin{table}
 	\centering	
-	\begin{tabular}{l | c | c | c | c|}
+	\begin{tabular}{|l | c | c | c | c|}
 		\hline
-		Model & MobileNetV2 & MobileNetV3Smal & MobileNetV3Large & NasNetMobile\\
+		Model & MobileNetV2 & MobileNetV3Small & MobileNetV3Large & NasNetMobile\\
 		\hline
-		Accuracy(avg)\\
+		Accuracy(avg) & 0.81 & 0.78 & 0.84 & \textbf{0.86}\\
 		\hline
-		Balanced Accuracy(avg)\\ 
+		Balanced Accuracy(avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
 		\hline
-		Precision(avg)\\
+		Precision(avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
 		\hline
-		F1-score(avg)\\
+		F1-score(avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
 		\hline
-		Sensitivity(avg)\\ 
+		Sensitivity(avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
 		\hline
-		Specificity(avg)\\
+		Specificity(avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
 		\hline
-		ROC-AUC-score(avg)\\
+		ROC-AUC-score(avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
 		\hline
+	\end{tabular}
+\caption{Deeper analyzing of mobile model}
+\label{table:8}
+\end{table}
+\begin{table}
+	\centering
+	\begin{tabular}{|l | c |}
+		Model & Accuracy\\
+		\hline
+		MobileNetV3Large-Layer[:270] + Soft-Attention & 0.71 \\
+		\hline
+		MobileNetV3Large-Layer[:266] + Soft-Attention & 0.73 \\
+		\hline
+		MobileNetV3Large-Layer[:260] + Soft-Attention & 0.77 \\
+		\hline
+		MobileNetV3Large-Layer[:251] + Soft-Attention & 0.79 \\
+		\hline
+		MobileNetV3Large-Layer[:246] + Soft-Attention & 0.84 \\
+		\hline
+		MobileNetV3Large-Layer[:246] + Soft-Attention + Dense(512)& 1 \\
 	\end{tabular}
@@
 \section{Conclusion}
-
+In this paper, my objective is to analyze the effect of metadata on the performance of model as well as identifying whether metadata can make the model less imbalanced or not.
+In case it is not, what factor make the model imbalanced.
+On the other hand, I also try to construct an optimized and balanced model that can be used on mobile phone or electronic devices.
+The experiment shown that metadata make the model less imbalanced, the factor that make the model much more imbalanced is the augmented data.
+This problem can be solve quite absolutely by using weighted loss function.
+Using weighted loss function make the standard deviation of model f1-score less than $0.1$.
+At the end of the experiment, mobile model is found that can achieve great performance without the large number of parameters or depth.
+Therefore, MobileNetV3Large is configured to construct an optimized and balanced model.
 \clearpage

### 2022-05-18 Publish Paper/manuscript_main.tex
Update Publish Paper

@@
 \label{table:8}
-\end{table}
+\end{table}\\
 \begin{table}
@@
 	\begin{tabular}{|l | c |}
+		\hline
 		Model & Accuracy\\
 		\hline
-		MobileNetV3Large-Layer[:270] + Soft-Attention & 0.71 \\
+		MobileNetV3Large-Layer[:270] + Soft-Attention + Metadata & 0.71 \\
 		\hline
-		MobileNetV3Large-Layer[:266] + Soft-Attention & 0.73 \\
+		MobileNetV3Large-Layer[:266] + Soft-Attention + Metadata  & 0.73 \\
 		\hline
-		MobileNetV3Large-Layer[:260] + Soft-Attention & 0.77 \\
+		MobileNetV3Large-Layer[:260] + Soft-Attention + Metadata  & 0.77 \\
 		\hline
-		MobileNetV3Large-Layer[:251] + Soft-Attention & 0.79 \\
+		MobileNetV3Large-Layer[:251] + Soft-Attention + Metadata  & 0.79 \\
 		\hline
-		MobileNetV3Large-Layer[:246] + Soft-Attention & 0.84 \\
+		MobileNetV3Large-Layer[:246] + Soft-Attention + Metadata  & 0.84 \\
 		\hline
-		MobileNetV3Large-Layer[:246] + Soft-Attention + Dense(512)& 1 \\
+		MobileNetV3Large-Layer[:246] + Soft-Attention + Dense(512) + Metadata & 0.85 \\
+		\hline
+		MobileNetV3Large-Layer[:240] + Soft-Attention + Metadata  & \textbf{0.86}\\
+		\hline
+		MobileNetV3Large-Layer[:230] + Soft-Attention + Metadata  & 0.84 \\
+		\hline
+		MobileNetV3Large-Layer[:230] + Soft-Attention + Metadata  & 0.81 \\
+		\hline
+		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 
+		\hline
+		MobileNetV3Large & 0.85 \\ 
+		\hline
 	\end{tabular}
+\caption{Deeper analyzing of MobileNetV3Large Model}
+\label{table:9}
+\end{table}
+In the MobileNetV3Large experiment, the model architecture is constructed by replacing the layers after the $28^th$ layer from the last layer by the Soft-Attention.
+The Table 9 demonstrate that, the Soft-Attention and the metadata have a good effect on the model.
+Otherwise, Adding a dense layer does not increase the model performance.
+The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^th$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of 0.86 accuracy rate.
+This is an optimized and balanced model, the parameters of model is indicated in Table 10.\\
+\begin{table}
+	\centering
+	\begin{tabular}{| l | c |}
+		\hline
+		Accuracy & 0.86\\
+		\hline
+		Precision(avg) & 0.86\\
+		\hline
+		F1-score(avg) & 0.86\\
+		\hline
+		Sensitivity(avg) & 0.86\\
+		\hline
+		Specificity(avg) & 0.95\\
+		\hline
+		ROC AUC Score(avg) & 0.98\\
+		\hline
+	\end{tabular}
+\caption{Performance of MobileNetV3Large}
+\label{table:10}
 \end{table}

### 2022-05-20 Publish Paper/manuscript_main.tex
Update

@@
 Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.
-I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung(dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project.
-He gave me a chance to use High GPU computing computers for AI Training.
-Furthermore, he also gave me recommendations on how to implement experiments to make a good conclusion such as what I should focus on, what I need to investigate, and which metrics I should consider.
 \section{Introduction}
@@
 The categorical cross-entropy loss is presented as:
-\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}y^c_n\log(\hat{y}^c_n)\]
+\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
 where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return. \\
@@
 It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.
-Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.At the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model.
-The result of this experiment is illustrated in table 9.\\
+Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.\\
 \begin{table}
@@
 	\label{table:8}
-\end{table}\\
+\end{table}
+At the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model. The result of this experiment is illustrated in table 9.
 \begin{table}
@@
 \end{table}
-In the MobileNetV3Large experiment, the model architecture is constructed by replacing the layers after the $28^th$ layer from the last layer by the Soft-Attention.
+In the MobileNetV3Large experiment, the model architecture is constructed by replacing the layers after the $28^{th}$ layer from the last layer by the Soft-Attention.
 The Table 9 demonstrate that, the Soft-Attention and the metadata have a good effect on the model.
 Otherwise, Adding a dense layer does not increase the model performance.
-The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^th$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of 0.86 accuracy rate.
-This is an optimized and balanced model, the parameters of model is indicated in Table 10.\\
+The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^{th}$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of 0.86 accuracy rate.
+This is an optimized and balanced model, the parameters of model is indicated in Table 10 and Table 11.
 \begin{table}
@@
 \end{table}
+\begin{table}
+	\centering
+	\begin{tabular}{| l | c | c | c |}
+		\hline
+		Model & MobileNetV3Large & DenseNet201 & InceptionResnetV2\\
+		\hline
+		No. Parameters & \textbf{5.5M} & 20.2M & 55.9M\\
+		\hline
+		Depth & \textbf{118} & 402 & 449\\
+		\hline
+		Accuracy & 0.86 & 0.89 & 0.90\\
+		\hline
+		Time Prediction(s/epochs) & \textbf{116} & 1000 & 3500 \\
+		\hline
+	\end{tabular}
+\caption{How Performance of MobileNetV3Large be optimized}
+\label{table:11}
+\end{table}
 \section{Conclusion}

### 2022-05-21 Publish Paper/manuscript_main.tex
Update publish paper

@@
 The distribution of the dataset is shown in the table below:
-\begin{table}
+\FloatBarrier
+\begin{table}[ht]
 	\centering
@@
 \end{table}
+\FloatBarrier
 \begin{figure}[h]
@@
 Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
 On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.
-\begin{table}
+\FloatBarrier
+\begin{table}[ht]
 	\centering
@@
 \end{table}
-
+\FloatBarrier
 \subsection{Model}
@@
 Otherwise, the epsilon argument of the optimizer is set to $0.1$.
-The accuracy of all model is presented in the figure below:\\
+The accuracy of all model is presented in the figure below:
+\FloatBarrier
 \begin{table}[h]
@@
 \end{table}
+\FloatBarrier
+\FloatBarrier
 \begin{table}[h]
@@
 \label{table:4}
-\end{table}\\
+\end{table}
+\FloatBarrier
 According to the Table 3 and 4, it is clear that the model trained with augmented data has a higher accuracy than the model trained with metadata only.
@@
 \\
-As the results, metadata does not make the model more balanced and improve the model performance.
-The reason why the model become much more balanced is the weighted loss function.
+As the results, metadata does make the model less imbalanced and improve the model performance by reducing the amount of data needed for achieving nearly the expected results.On the other hand, the reason why the model become much more balanced is the weighted loss function.
 Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class.
@@
 $0.82$, respectively, as opposed to their training in akiec without weighted loss function.
-MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.
+MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.\\
+\FloatBarrier
 \begin{table}[h]
@@
 	\label{table:5}
-\end{table}\\
+\end{table}
+\FloatBarrier
+\FloatBarrier
 \begin{table}[h]
@@
 	\label{table:6}
-\end{table}\\
-\begin{table}[h]
+\end{table}
+\FloatBarrier
+\FloatBarrier
+\begin{table}[ht]
 	\centering
@@
 	\label{table:7}
-\end{table}\\
+\end{table}
+\FloatBarrier
 Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
@@
 It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.
-Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.\\
-\begin{table}
+\FloatBarrier
+\begin{table}[ht]
 	\centering	
@@
 		\hline
-		Model & MobileNetV2 & MobileNetV3Small & MobileNetV3Large & NasNetMobile\\
+		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\
 		\hline
@@
 \end{table}
-At the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model. The result of this experiment is illustrated in table 9.
-\begin{table}
+\FloatBarrier
+Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.
+Therefore, at the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model.
+The result of this experiment is illustrated in table 9.
+\FloatBarrier
+\begin{table}[ht]
 	\centering
@@
 		\hline
-		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 
+		MobileNetV3Large-Layer[:230] + Soft-Attention & s0.85 \\ 
 		\hline
@@
 \end{table}
+\FloatBarrier
 In the MobileNetV3Large experiment, the model architecture is constructed by replacing the layers after the $28^{th}$ layer from the last layer by the Soft-Attention.
@@
 This is an optimized and balanced model, the parameters of model is indicated in Table 10 and Table 11.
-\begin{table}
+\FloatBarrier
+\begin{table}[ht]
 	\centering
@@
 \end{table}
-\begin{table}
+\FloatBarrier
+\begin{table}[ht]
 	\centering
@@
 \end{table}
+\FloatBarrier
 \section{Conclusion}

### 2022-05-21 Publish Paper/manuscript_title_etc.tex
Update
Update publish paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\PAPERTITLE}{Skin Cancer Classification using Soft Attention and Metadata}
+\newcommand{\PAPERTITLE}{Balanced and Optimized Skin Cancer Classification Model using Soft Attention and Metadata}
 
@@
 The main focus of this research is to analyze the effect of metadata on the combination of the backbone model and the Soft-Attention layer.
-The soft-Attention layer is tested in a previous paper that improve the model performance.
+The soft-Attention layer is tested in a previous paper that improve the model performance to 92 percent accuracy.
 I also try some other combinations to construct an optimized model that can use on mobile phone.
-After the experiment process, I found out that metadata makes the performance of the model more balanced than in the previous paper.
-I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with a bit lower accuracy but thirty times as fast as other combinations.
+After the experiment process, I found out that metadata and weighted loss function makes the performance of the model less imbalanced with 90 percent accuracy but its f1-score and recall score standard deviation is 0.08 and 0.09, respectively.
+I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with 86 percent accuracy but thirty times as fast as the highest performance model.
 }

### 2022-05-21 Publish Paper/manuscript_title_etc.tex
Update

@@
 \newcommand{\PAPERABSTRACT}{
-Nowadays, the dramatic development of the big city and industrial field leads to a higher rate of skin disease because of polluted air.
+Nowadays, the dramatic development of the big city and industrial zones leads to a higher rate of skin disease because of polluted air.
 Moreover, in many developing countries, the hospital is being overloaded every single day by the huge number of the patient.

### 2022-05-27 Publish Paper/manuscript_main.tex
Update Published Paper
+ VN abstract
+ Eng paper

@@
 Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
-Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section.
+Some of these models wich have been used as a backbone model in this paper will be discuss more in the Related Work section.
 \\
-In this paper, I will analyze the effect of metadata on classifying skin disease.
-On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
+In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
 
@@
 \cite{01284} also used Deep Convolution Neural Network.
-However, that paper used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative
-Learning Strategy which can more effectively balance representation learning and
-classifier learning without additional computational cost.
-Another state of the art is GradCam and Kernel SHAP\cite{06612}, which are both model agnostic, local interpretability methods that can highlight pixels that the trained network deems
-relevant for the final classification.\\
+Moreover, that paper used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.
+Another state of the art is GradCam and Kernel SHAP\cite{06612}, which are both model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.\\
 Otherwise, the Student and Teacher Model is also a state of the art in 2021\cite{03225}.
@@
 The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position.
-During the data exploration term, I found out that the age category miss 57 data point, then I decided to remove this 57 samples.
+During the data exploration term, the age category miss 57 data point, which is decided to remove this 57 samples.
 In the gender and capturing position category contain some samples of unknown.
@@
 Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated.
-Therefore, in this paper, I will analyze the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth.
+Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed.
 On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.

### 2022-05-27 Publish Paper/manuscript_title_etc.tex
Update Published Paper
+ VN abstract
+ Eng paper

@@
 \newcommand{\PAPERABSTRACT}{
-Nowadays, the dramatic development of the big city and industrial zones leads to a higher rate of skin disease because of polluted air.
-Moreover, in many developing countries, the hospital is being overloaded every single day by the huge number of the patient.
-They need a fast and accurate solution to diagnose skin disease before meeting the doctor or how to create an optimized and balanced model for skin lesion classification.
-After the literature review process, I found that there are many outstanding papers on both Deep Learning and Machine Learning.
-In Deep Learning, they often use transfer learning.
-Some new approaches are GradCam, Kernel Shap, Student and Teacher model.
-In Machine Learning, Random Forest, and Support Vector Machine are applied.
-The main focus of this research is to analyze the effect of metadata on the combination of the backbone model and the Soft-Attention layer.
-The soft-Attention layer is tested in a previous paper that improve the model performance to 92 percent accuracy.
-I also try some other combinations to construct an optimized model that can use on mobile phone.
-After the experiment process, I found out that metadata and weighted loss function makes the performance of the model less imbalanced with 90 percent accuracy but its f1-score and recall score standard deviation is 0.08 and 0.09, respectively.
-I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with 86 percent accuracy but thirty times as fast as the highest performance model.
+Today, the rapid development of big cities and industrial zones leads to an increasing incidence of skin diseases because of air pollution.
+According to a survey by the American Cancer Society, there are about 100,000 people with skin cancer and more than 7,600 people are predicted to not survive by 2022.
+Therefore, a tool to support the diagnosis of skin cancer quickly and accurately is needed in the context of hospitals being overwhelmed every day by the large number of patients in many developing countries.
+In the past half-decade, technologies belonging to the 4.0 technology group are rapidly changing our lives, including Artificial Intelligence, Machine Learning and Deep Learning.
+Deep Learning and Machine Learning have also been applied to build diagnostic models of skin pathologies.
+Some of the new approaches are GradCam, Kernel Shap and the Student-Teacher model.
+In Machine Learning, Random Forest and Support Vector Machine are applied.
+The data used in this study is HAM10000 which is an imbalanced dataset.
+Several methods have been applied including data augmentation, Soft-Attention, and balanced resampling.
+In this study, the models DenseNet201, InceptionResNetV2, ResNet50, ResNet152, NasNetLarge are combined with Soft Attetion by replacing the last 2 CNN blocks with Soft-Attetnion.
+Moreover, metadata is used as a sub input layer in the model.
+Besides, weight loss function is applied, the way of calculating weight will be shown in this paper.
+Soft Attention was tested in an earlier paper to improve the model's performance with 92 percent accuracy.
+In addition, MobileNetV2, MobileNetV3 and NasNetMobile models are also studied to deploy solutions on phones.
+After testing, the performance of DenseNet201 model combined with Soft-Attetion using baseline data and weighted loss function reached 90 percent accuracy but standard deviation of f1 score and recall score of it is 0.08 and 0.09, respectively, compared to the standard deviation of the f1 index and the recall index of 0.22 and 0.27 of the previous paper, respectively.A model with combination of MobileNetV3Large and Soft-Attention layer with baseline data and image input have been constructed that achieve 86 percent accuracy but training time takes 116 seconds per training session.
 }

### 2022-05-27 Publish Paper/manuscript_main.tex
Update publish paper
- VN paper: abstract
- Eng paper: change std to mean, rewrite all

@@
 \section{Introduction}
-%The Need of AI-enabled computer-aided diagnostics
 Skin cancer is one of the most common cancers leading to worldwide death.
@@
 In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}.
-On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%.
+On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent.
 However, once the disease progresses beyond the skin, survival is poor\cite{11872}.
 Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.
-\newline
-%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
+\\
 Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks.
@@
 \\
-%The Success in AI - especially in CNN - some model based CNN
 In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance.
@@
 \subsection{Input Schema}
-%Other preprocessed input%
 Using metadata as another input is not new.
@@
 \\
-%My proprocessed input%
 In this paper, the unknowns is kept as a type as discussed in Metadata section.
@@
 \\
-%Figure%
 The Input schema is described as follow:\\
@@
 \\
-However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class. The others still face the
-the imbalanced term.
+However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
+The others still face the imbalanced term.
 Since this dataset is not balanced, therefore using augmented data can make the model bias to the class which has large sample.
@@
 		\hline
-		Model & akiec & bcc & bkl & df & mel & nv & vasc & $\sigma$ \\
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
 		\hline
-		DenseNet201 + Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.128 \\ 
+		DenseNet201 + Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
 		\hline
-		InceptionResNetV2 + Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.225\\
+		InceptionResNetV2 + Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
 		\hline
-		Resnet50 + Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.165\\
+		Resnet50 + Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
 		\hline 	
-		VGG16 + Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.197\\ 
+		VGG16 + Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
 		\hline		
-		DenseNet201 + Metadata & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.088}\\
+		DenseNet201 + WeightLoss & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
 		\hline
-		InceptionResNetV2 + Metadata & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.09}\\
+		InceptionResNetV2 + WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
 		\hline
-		Resnet50 + Metadata & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.162\\
+		Resnet50 + WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
 		\hline
-		Resnet152 + Metadata & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.199\\
+		Resnet152 + WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
 		\hline
-		MobileNetV2 + Metadata & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & 0.9 & 0.122\\
+		MobileNetV2 + WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
 		\hline
-		MobileNetV3Large + Metadata & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & 0.92 & 0.12\\
+		MobileNetV3Large + WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
 		\hline
-		MobileNetV3Small + Metadata & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & 0.89 & 0.144\\
+		MobileNetV3Small + WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
 		\hline
-		NasNetLarge + Metadata & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.088}\\
+		NasNetLarge + WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
 		\hline
-		NasNetMobile + Metadata & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & 0.93 & 0.101\\
+		NasNetMobile + WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
 		\hline
 	\end{tabular}
-	\caption{F1-Score of each class and the standard deviation of each model}
+	\caption{F1-Score of each class and the mean f1-score of each model}
 	\label{table:5}
@@
 		\hline
-		Model & akiec & bcc & bkl & df & mel & nv & vasc & $\sigma$ \\
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
 		\hline
-		DenseNet201 + Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & \textbf{0.189}\\ 
+		DenseNet201 + Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
 		\hline
-		InceptionResNetV2 + Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & \textbf{0.275}\\
+		InceptionResNetV2 + Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
 		\hline
-		Resnet50 + Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & \textbf{0.209}\\
+		Resnet50 + Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
 		\hline 	
-		VGG16 + Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 	\textbf{0.191}\\ 
+		VGG16 + Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
 		\hline		
-		DenseNet201 + Metadata & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & 0.116\\
+		DenseNet201 + Weight Loss & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
 		\hline
-		InceptionResNetV2 + Metadata & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 	0.93 & \textbf{0.097}\\
+		InceptionResNetV2 + Metadata & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 	0.93 & \textbf{0.81}\\
 		\hline
-		Resnet50 + Metadata & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.107\\
+		Resnet50 + Weight Loss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
 		\hline
-		Resnet152 + Metadata & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.121\\
+		Resnet152 + Weight Loss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
 		\hline
-		MobileNetV2 + Metadata & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.126\\
+		MobileNetV2 + Weight Loss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
 		\hline
-		MobileNetV3Large + Metadata & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & 0.12\\
+		MobileNetV3Large + Weight Loss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
 		\hline
-		MobileNetV3Small + Metadata & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.147\\
+		MobileNetV3Small + Weight Loss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
 		\hline
-		NasNetLarge + Metadata & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & 0.119\\
+		NasNetLarge + Weight Loss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
 		\hline
-		NasNetMobile + Metadata & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & 0.134\\
+		NasNetMobile + Weight Loss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
 		\hline
 	\end{tabular}
-	\caption{Recall score of each class and the standard deviation of each model}
+	\caption{Recall score of each class and the mean recall score of each model}
 	\label{table:6}
@@
 		\hline
-		MobileNetV3Large-Layer[:230] + Soft-Attention & s0.85 \\ 
+		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 
 		\hline

### 2022-05-27 Publish Paper/manuscript_title_etc.tex
Update eng paper

--- 2022-05-21 Publish Paper/manuscript_title_etc.tex
@@
 \newcommand{\PAPERABSTRACT}{
-Nowadays, the dramatic development of the big city and industrial zones leads to a higher rate of skin disease because of polluted air.
-Moreover, in many developing countries, the hospital is being overloaded every single day by the huge number of the patient.
-They need a fast and accurate solution to diagnose skin disease before meeting the doctor or how to create an optimized and balanced model for skin lesion classification.
-After the literature review process, I found that there are many outstanding papers on both Deep Learning and Machine Learning.
-In Deep Learning, they often use transfer learning.
-Some new approaches are GradCam, Kernel Shap, Student and Teacher model.
-In Machine Learning, Random Forest, and Support Vector Machine are applied.
-The main focus of this research is to analyze the effect of metadata on the combination of the backbone model and the Soft-Attention layer.
-The soft-Attention layer is tested in a previous paper that improve the model performance to 92 percent accuracy.
-I also try some other combinations to construct an optimized model that can use on mobile phone.
-After the experiment process, I found out that metadata and weighted loss function makes the performance of the model less imbalanced with 90 percent accuracy but its f1-score and recall score standard deviation is 0.08 and 0.09, respectively.
-I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with 86 percent accuracy but thirty times as fast as the highest performance model.
+Today, the rapid development of industrial zones leads to an increasing incidence of skin diseases because of polluted air.
+According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffered from skin cancer and more than 7600 of these people will not survive.
+In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels have lack of experience, having a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential.
+Along with the strong development of artificial intelligence technologies, many solutions and tools to support the diagnosis of skin diseases have been researched and developed.
+These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet, VGGNet.
+In this study, another approach to build tools to aid in the diagnosis of skin pathologies is proposed.
+SOTA (state of the art) models DenseNet, InceptionNet, ResNet, NasNet, MobileNet combined with Soft-Attention are used as backbone.
+In addition, personal information such as age and gender are also used.
+In addition, a new loss function that takes into account the imbalance of the data is also proposed.
+Experimental results on dataset HAM10000 show that using InceptionResNetV2 with Soft-Attetion and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and auc- scores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published indexes.
+Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of floors is 4 times less, it achieves 86 percent accuracy and 30 times faster diagnosis.
 }

### 2022-05-30 Publish Paper/manuscript_main.tex
Update Eng Paper

@@
 \[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
-where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return. \\
+where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$.\\
 Since the dataset face the imbalanced problem then I applied the class weight for the loss. This formula below is used to calculate the class weight:
@@
 \end{bmatrix}\]
-where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$.
-$D$ is the matrix contain the inverse of $C \times N_i$.
-The overall loss function is then become\cite{8943952}:
-\[
-	L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N} W_c \times y^c_n \times \log(h_\theta(x_n, c))
-\]
-where $W_c$ is the weight of class $c$, $y^c_n$ is the expected output of class $c$ at training example $n$. Otherwise, $h_\theta$ is the model with weight $\theta$.
+where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$. 
 \subsection{Evaluation Metrics}
@@
 Furthermore, Resnet50 trained with augmented data has the accuracy that outperform the Resnet50 and is twice as high as Resnet152 trained with metadata.
-On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, although has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively.
+On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively.
 This term will be discussed later on.
-Although, the model trained with augmented data have high accuracy, when I analyzed the f1-score and the recall score of models, it turns out that models trained with augmented data have imbalanced f1-scores according to table 5.
-As a results, augmented data model dose not classify well on all class as InceptionRtesNetV2 trained on augmented data have 0.29 f1-score on class df while InceptionRtesNetV2 trained on metadata can classify well by a balanced way.
-This may cause by the augmented data.
+Since, the model trained with augmented data have high accuracy, when their f1-score and the recall score of models are analyzed, it turns out that models trained with augmented data have imbalanced f1-scores according to table 5.
+As a results, augmented data model dose not classify well on all class as InceptionResNetV2 trained on augmented data have $0.29$ f1-score on class df while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way.
 \\
+\FloatBarrier
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c | c | c | c | c | c | c | c | c|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
+		\hline
+		\thead{DenseNet201 +\\ Augmented Data} & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
+		\hline
+		\thead{InceptionResNetV2 +\\ Augmented Data} & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
+		\hline
+		\thead{Resnet50 +\\ Augmented Data} & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
+		\hline 	
+		\thead{VGG16 +\\ Augmented Data} & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
+		\hline		
+		\thead{DenseNet201 +\\Metadata and WeightLoss} & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
+		\hline
+		\thead{InceptionResNetV2 +\\Metadata and WeightLoss} & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
+		\hline
+		\thead{Resnet50 +\\Metadata and WeightLoss} & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
+		\hline
+		\thead{Resnet152 +\\Metadata and WeightLoss} & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
+		\hline
+		\thead{MobileNetV2 +\\Metadata and WeightLoss} & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
+		\hline
+		\thead{MobileNetV3Large +\\Metadata and WeightLoss} & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
+		\hline
+		\thead{MobileNetV3Small +\\Metadata and WeightLoss} & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
+		\hline
+		\thead{NasNetLarge +\\Metadata and WeightLoss} & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
+		\hline
+		\thead{NasNetMobile +\\Metadata and WeightLoss} & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
+		\hline
+	\end{tabular}
+	\caption{F1-Score of each class and the mean f1-score of each model}
+	\label{table:5}
+\end{table}
+\FloatBarrier
 However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
 The others still face the imbalanced term.
-Since this dataset is not balanced, therefore using augmented data can make the model bias to the class which has large sample.
-Using the metadata instead make the model less bias, though it still make the model imbalanced due to the high variance of model which has the number of depth much less than 400.\\
-This problem is also true with the recall score according to table 6.
-DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has recall standard deviation of $0.189$, $0.275$, $0.209$, $0.191$, respectively.
-On the other hand, other models have recall standard deviation which is close to $0.1$.
-Especially, inceptionResnetV2 train on metadata has recall standard deviation of approximately $0.09$.
-\\
-As the results, metadata does make the model less imbalanced and improve the model performance by reducing the amount of data needed for achieving nearly the expected results.On the other hand, the reason why the model become much more balanced is the weighted loss function.
-Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class.
-Therefore, DenseNet201, InceptionResNetV2 trained with weighted loss function have recall in akiec of $0.85$.
-$0.82$, respectively, as opposed to their training in akiec without weighted loss function.
-MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.\\
+Since this dataset is not balanced, therefore using augmented data can make the model more  bias to the class which has larger sample.
+Using the metadata, though still make the model bias, it dose contributes to the improvement of  the performance of the model.\\
 \FloatBarrier
@@
 		\hline
-		DenseNet201 + Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
+		\thead{DenseNet201 +\\ Augmented Data} & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
 		\hline
-		InceptionResNetV2 + Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
+		\thead{InceptionResNetV2 +\\ Augmented Data} & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
 		\hline
-		Resnet50 + Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
+		\thead{Resnet50 +\\ Augmented Data} & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
 		\hline 	
-		VGG16 + Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
+		\thead{VGG16 +\\ Augmented Data} & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
 		\hline		
-		DenseNet201 + WeightLoss & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
+		\thead{DenseNet201 +\\Metadata and WeightLoss} & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
 		\hline
-		InceptionResNetV2 + WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
+		\thead{InceptionResNetV2 +\\Metadata and WeightLoss} & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
 		\hline
-		Resnet50 + WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
+		\thead{Resnet50 +\\Metadata and WeightLoss} & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
 		\hline
-		Resnet152 + WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
+		\thead{Resnet152 +\\Metadata and WeightLoss} & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
 		\hline
-		MobileNetV2 + WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
+		\thead{MobileNetV2 +\\Metadata and WeightLoss} & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
 		\hline
-		MobileNetV3Large + WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
+		\thead{MobileNetV3Large +\\Metadata and WeightLoss} & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
 		\hline
-		MobileNetV3Small + WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
+		\thead{MobileNetV3Small +\\Metadata and WeightLoss} & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
 		\hline
-		NasNetLarge + WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
+		\thead{NasNetLarge +\\Metadata and WeightLoss} & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
 		\hline
-		NasNetMobile + WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
-		\hline
-	\end{tabular}
-	\caption{F1-Score of each class and the mean f1-score of each model}
-	\label{table:5}
-\end{table}
-\FloatBarrier
-\FloatBarrier
-\begin{table}[h]
-	\centering
-	\begin{tabular}{|l | c | c | c | c | c | c | c | c|} 
-		\hline
-		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
-		\hline
-		DenseNet201 + Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
-		\hline
-		InceptionResNetV2 + Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
-		\hline
-		Resnet50 + Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
-		\hline 	
-		VGG16 + Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
-		\hline		
-		DenseNet201 + Weight Loss & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
-		\hline
-		InceptionResNetV2 + Metadata & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 	0.93 & \textbf{0.81}\\
-		\hline
-		Resnet50 + Weight Loss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
-		\hline
-		Resnet152 + Weight Loss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
-		\hline
-		MobileNetV2 + Weight Loss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
-		\hline
-		MobileNetV3Large + Weight Loss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
-		\hline
-		MobileNetV3Small + Weight Loss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
-		\hline
-		NasNetLarge + Weight Loss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
-		\hline
-		NasNetMobile + Weight Loss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
+		\thead{NasNetMobile +\\Metadata and WeightLoss} & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
 		\hline
@@
 \FloatBarrier
+This problem is also true with the recall score according to table 6.
+DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has expected value of recall of $0.72$, $0.71$, $0.69$, $0.69$, respectively, while the combination of InceptionResNetV2, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
+As the results, metadata does improve the model performance by reducing the amount of data needed for achieving nearly the expected results.
+On the other hand, the reason why the model become much more balanced is the weighted loss function.
+Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class.
+Therefore, DenseNet201, InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$.
+$0.82$, respectively, as opposed to their training in akiec without weighted loss function.
+MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.\\
+\begin{comment}
 \FloatBarrier
@@
 \FloatBarrier
+\end{comment}
 Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
@@
 		\hline
-		MobileNetV3Large-Layer[:230] + Soft-Attention + Metadata  & 0.81 \\
-		\hline
 		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 
@@
 \FloatBarrier
-In the MobileNetV3Large experiment, the model architecture is constructed by replacing the layers after the $28^{th}$ layer from the last layer by the Soft-Attention.
-The Table 9 demonstrate that, the Soft-Attention and the metadata have a good effect on the model.
+The Table 9 demonstrate that the Soft-Attention and the metadata have a good effect on the model.
 Otherwise, Adding a dense layer does not increase the model performance.
-The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^{th}$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of 0.86 accuracy rate.
-This is an optimized and balanced model, the parameters of model is indicated in Table 10 and Table 11.
+The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^{th}$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of $0.86$ accuracy rate.
 \FloatBarrier
@@
 In this paper, my objective is to analyze the effect of metadata on the performance of model as well as identifying whether metadata can make the model less imbalanced or not.
-In case it is not, what factor make the model imbalanced.
 On the other hand, I also try to construct an optimized and balanced model that can be used on mobile phone or electronic devices.
-The experiment shown that metadata make the model less imbalanced, the factor that make the model much more imbalanced is the augmented data.
-This problem can be solve quite absolutely by using weighted loss function.
-Using weighted loss function make the standard deviation of model f1-score less than $0.1$.
-At the end of the experiment, mobile model is found that can achieve great performance without the large number of parameters or depth.
-Therefore, MobileNetV3Large is configured to construct an optimized and balanced model.
+The experiment shown that metadata improve the model performance, the factor that make the model much more imbalanced is the augmented data.
+This problem can be solve quite absolutely by using aforementioned weighted loss function.
+Using weighted loss function make the expected value of model f1-score increase.
+At the end of the experiment, mobile model is found that can achieve great performance without either the large number of parameters or depth.
 \clearpage

### 2022-05-31 Publish Paper/manuscript_main.tex
Update Eng Paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \textbf{ACKNOWLEDGMENT} \\ 
@@
 He gave a chance to use High GPU computing computer for AI Training.
-Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.
+Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.\\
+
+\textbf{ABSTRACT} \\
+Today, the rapid development of industrial zones leads to an increasing incidence of skin diseases because of polluted air.
+According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffered from skin cancer and more than 7600 of these people will not survive.
+In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels have lack of experience, having a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential.
+Along with the strong development of artificial intelligence technologies, many solutions and tools to support the diagnosis of skin diseases have been researched and developed.
+These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet, VGGNet.
+In this study, another approach to build tools to aid in the diagnosis of skin pathologies is proposed.
+SOTA (state of the art) models DenseNet, InceptionNet, ResNet, NasNet, MobileNet combined with Soft-Attention are used as backbone.
+In addition, personal information such as age and gender are also used.
+In addition, a new loss function that takes into account the imbalance of the data is also proposed.
+Experimental results on dataset HAM10000 show that using InceptionResNetV2 with Soft-Attetion and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and auc- scores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published indexes.
+Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of floors is 4 times less, it achieves 86 percent accuracy and 30 times faster diagnosis.\\
+
 \section{Introduction}
+\subsection{Problem Statement}
 Skin cancer is one of the most common cancers leading to worldwide death.
@@
 \\
-In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance.
+In order to adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance.
 Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
-Some of these models wich have been used as a backbone model in this paper will be discuss more in the Related Work section.
+Some of these models wich have been used as a backbone model in this paper will be discussed in the Related Work section.
 \\
-In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
 
-\section{Literature Review}
+\subsection{Literature Review}
 Skin lesion classification is not a new area, since there are many great performance models constructed.
@@
 Another paper that uses the backbone models is \cite{09418}.
-Hemanth and his team decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating
-holes of different sizes on the images i.e.
+Hemanth and his team decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating holes of different sizes on the images i.e.
 technically making a random portion of image inactive during data augmentation process.
@@
 Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045}.
-\section{Data}
-\subsection{Image Data}
+
+\subsection{Objectives}
+In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
+
+\section{Research Result}
+\subsection{Data}
+\subsubsection{Image Data}
 The dataset used in this paper is the HAM10000 dataset published by Havard University Dataverse\cite{10417}.
@@
 Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.
-\subsection{Metadata}
+\subsubsection{Metadata}
 The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position.
@@
 Besides, the label of the whole data is preprocessed into one-hot vector.
-\section{Model Schema}
-\subsection{Input Schema}
+\subsection{Model Schema}
+\subsubsection{Input Schema}
 Using metadata as another input is not new.
@@
 Image data, on the other hand after being preprocessed, is fed directly into the backbone model. 
-\subsection{Soft-Attention}
+\subsubsection{Soft-Attention}
 Applying the Soft-Attention layer in deep learning is not a new approach.
@@
 
-\subsection{Backbone Model Architecture}
+\subsubsection{Backbone Model Architecture}
 In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
@@
 \FloatBarrier
-\subsection{Model}
+
+\subsubsection{Model}
 The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}.
@@
 \end{figure}
-\section{Training}
+
 \subsection{Loss Function}
@@
 The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
-\section{Experiment}
+\subsection{Experiment Setup}
 All the model in this paper is trained with Adam Optimizer\cite{6980}.
@@
 Otherwise, the epsilon argument of the optimizer is set to $0.1$.
+\subsection{Results and Discusstion}
 The accuracy of all model is presented in the figure below:

### 2022-06-01 Publish Paper/manuscript_main.tex
Update Paper

@@
 The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
-\subsection{Experiment Setup}
+\subsection{Traning}
+Before training, the dataset is split into three sub datasets including training, validation, and testing. In this paper, the graphic card that is used to train is Nvidia RTX TitanV.\\
 All the model in this paper is trained with Adam Optimizer\cite{6980}.
-The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$.
-Otherwise, the epsilon argument of the optimizer is set to $0.1$.
+The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$, the epsilon argument of the optimizer is set to $0.1$.
+On the other hand, Early Stopping is also set up, if the accuracy of validation set dose not increase after 25 epochs, the training will stop.
 \subsection{Results and Discusstion}

### 2022-06-24 MDPI/Sensor Paper/template.tex
Update Paper MDPI

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{} 
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{DIAGNOSTIC SUPPORT OF SKIN LESION
	CLASSIFICATION USING CNN AND SOFT
	ATTENTION}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Khoi Do $^{1,\dagger,\ddagger}$\orcidA{}*}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Khoi Do}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Do, K.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: khoido8899@gmail.com; Tel.: +84-9360-192-58}

% Current address and/or shared authorship
\firstnote{Current address: 1st Dai Co Viet Street, Ha Noi, Viet Nam} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Today, the rapid development of industrial zones leads to an increasing incidence of skin
	diseases because of polluted air. According to a report by the American Cancer Society, it is
	estimated that in 2022 there will be about 100,000 people suffered from skin cancer and more
	than 7600 of these people will not survive. In the context that doctors at provincial hospitals
	and health facilities are overloaded, doctors at lower levels have lack of experience, having
	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately
	is essential. Along with the strong development of artificial intelligence technologies, many
	solutions and tools to support the diagnosis of skin diseases have been researched and
	developed. These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet,
	VGGNet. In this study, another approach to build tools to aid in the diagnosis of skin
	pathologies is proposed. SOTA (state of the art) models DenseNet, InceptionNet, ResNet,
	NasNet, MobileNet combined with Soft-Attention are used as backbone. In addition,
	personal information such as age and gender are also used. In addition, a new loss function
	that takes into account the imbalance of the data is also proposed. Experimental results
	on dataset HAM10000 show that using InceptionResNetV2 with Soft-Attetion and new
	loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and aucscores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published
	indexes. Besides, using MobileNetV3Large combined with Soft-Attention and new loss
	function, even though the number of parameters is 11 times less, the number of floors is 4
	times less, it achieves 86 percent accuracy and 30 times faster diagnosis.}

% Keywords
\keyword{AI-enabled computer-aid diagnosis, Diagnosis, Skin Sancer, Skin Lesion
	Classification, Artificial Intelligence, Deep Learning, Machine Learning)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.

% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}
\unskip

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
			Entry 1		& Data			& Data			& Data\\
			Entry 2		& Data			& Data			& Data \textsuperscript{1}\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=13.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans. OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals. OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. If the study did not report any data, you might add ``Not applicable'' here.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the~results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\sampleavailability{Samples of the compounds ... are available from the authors.}

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}
\subsection[\appendixname~\thesubsection]{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{table}[H] 
\caption{This is a table caption.\label{tab5}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}

\section[\appendixname~\thesection]{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{adjustwidth}
\end{document}

### 2022-06-24 MDPI/Sensor Paper/template.tex
Update MDPI

@@
 \begin{thebibliography}{999}
-% Reference 1
-\bibitem[Author1(year)]{ref-journal}
-Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% Reference 2
-\bibitem[Author2(year)]{ref-book1}
-Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% Reference 3
-\bibitem[Author3(year)]{ref-book2}
-Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-% Reference 4
-\bibitem[Author4(year)]{ref-unpublish}
-Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
-% Reference 5
-\bibitem[Author5(year)]{ref-communication}
-Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-% Reference 6
-\bibitem[Author6(year)]{ref-proceeding}
-Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of presentation.
-In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
-% Reference 7
-\bibitem[Author7(year)]{ref-thesis}
-Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
-% Reference 8
-\bibitem[Author8(year)]{ref-url}
-Title of Site. Available online: URL (accessed on Day Month Year).
+
+\bibitem[Author1(year)]{08332}
+Katherine M. Li and Evelyn C. Li. Skin Lesion Analysis Towards Melanoma Detection via End-to-end Deep Learning of Convolutional Neural Networks. {\em Journal Abbreviation} {\bf 2018}.
+
+\bibitem[Author2(year)]{03225}
+Xiaohan Xing and Yuenan Hou and  Hang Li and Yixuan Yuan and Hongsheng Li and Max Q.-H.
+Meng Categorical Relation-Preserving Contrastive Knowledge Distillation for Medical Image Classification.
+{\em Journal Abbreviation} {\bf 2021}.
+
+\bibitem[Author2(year)]{03798}
+Rishu Garg and Saumil Maheshwari and Anupam Shukla Decision Support System for Detection and Classification of Skin Cancer using CNN. {\em Journal Abbreviation} {\bf 2019}.
+
+\bibitem[Author2(year)]{09365}
+Amirreza Rezvantalab and Habib Safigholi and Somayeh Karimijeshni Dermatologist Level Dermoscopy Skin Cancer Classification Using Different Deep Learning Convolutional Neural Networks Algorithms.
+{\em Journal Abbreviation} {\bf 2020}.
+
+\bibitem[Author2(year)]{10348}
+Amirreza Rezvantalab and Habib Safigholi and Somayeh Karimijeshni Dermatologist Level Dermoscopy Skin Cancer Classification Using Different Deep Learning Convolutional Neural Networks Algorithms.
+{\em Journal Abbreviation} {\bf 2021}.
+
+\bibitem[Author2(year)]{06612}
+Kyle Young and Gareth Booth and Becks Simpson and Reuben Dutton and Sally Shrapnel Dermatologist Level Dermoscopy Deep neural network or dermatologist?. {\em Journal Abbreviation} {\bf 2021}.
+
 \end{thebibliography}

### 2022-06-29 MDPI/Sensor Paper/template.tex
Update

@@
 %=================================================================
-\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
+\documentclass[sensors,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
 % For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
@@
 The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
+\usepackage{makecell}
+\usepackage{placeins}
+\usepackage{amsmath}
+\usepackage{comment}
 
@@
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Title}
+\TitleCitation{DIAGNOSTIC SUPPORT OF SKIN LESION
+	CLASSIFICATION USING CNN AND SOFT
+	ATTENTION}
 
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorA}{0000-0002-2566-5637} % Add \orcidA{} behind the author's name
 %\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
@@
 % Authors, for the paper (add full first names)
-\Author{Khoi Do $^{1,\dagger,\ddagger}$\orcidA{}*}
+\Author{Khoi Do Hoang$^{
+		1,\dagger,%\ddagger
+	}$\orcidA{}*}
 
@@
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+
 \address{
-$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
-$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
+$^{1}$ \quad Viet Dung Nguyen; dung.nguyenviet1@hust.edu.vn\\
+$^{2}$ \quad Khoi Do Hoang; khoi.dh200332@sis.hust.edu.vn}
 
@@
 \firstnote{Current address: 1st Dai Co Viet Street, Ha Noi, Viet Nam} 
-\secondnote{These authors contributed equally to this work.}
+\secondnote{}
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Today, the rapid development of industrial zones leads to an increasing incidence of skin
-	diseases because of polluted air. According to a report by the American Cancer Society, it is
-	estimated that in 2022 there will be about 100,000 people suffered from skin cancer and more
-	than 7600 of these people will not survive. In the context that doctors at provincial hospitals
-	and health facilities are overloaded, doctors at lower levels have lack of experience, having
-	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately
-	is essential. Along with the strong development of artificial intelligence technologies, many
-	solutions and tools to support the diagnosis of skin diseases have been researched and
-	developed. These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet,
-	VGGNet. In this study, another approach to build tools to aid in the diagnosis of skin
-	pathologies is proposed. SOTA (state of the art) models DenseNet, InceptionNet, ResNet,
-	NasNet, MobileNet combined with Soft-Attention are used as backbone. In addition,
-	personal information such as age and gender are also used. In addition, a new loss function
-	that takes into account the imbalance of the data is also proposed. Experimental results
-	on dataset HAM10000 show that using InceptionResNetV2 with Soft-Attetion and new
-	loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and aucscores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published
-	indexes. Besides, using MobileNetV3Large combined with Soft-Attention and new loss
-	function, even though the number of parameters is 11 times less, the number of floors is 4
-	times less, it achieves 86 percent accuracy and 30 times faster diagnosis.}
+\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air.
+According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive.
+In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential.
+Along with the strong development of artificial intelligence technologies, many solutions and tools to support the diagnosis of skin diseases have been researched and developed.
+These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet, VGGNet.
+In this study, another approach to building tools to aid in the diagnosis of skin pathologies is proposed.
+SOTA (state of the art) models DenseNet, InceptionNet, ResNet, NasNet, MobileNet combined with Soft-Attention are used as backbone.
+In addition, personal information such as age and gender are also used.
+In addition, a new loss function	that takes into account the imbalance of the data is also proposed.
+Experimental results on dataset HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published indexes.
+Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of floors is 4 times less, it achieves 86 percent accuracy and 30 times faster diagnosis.}
 
 % Keywords
-\keyword{AI-enabled computer-aid diagnosis, Diagnosis, Skin Sancer, Skin Lesion
-	Classification, Artificial Intelligence, Deep Learning, Machine Learning)}
+\keyword{AI Diagnosis, Skin Sancer, Skin Lesion
+	Classification, Deep Learning, Machine Learning)}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setcounter{section}{-1} %% Remove this when starting to work on the template.
+\setcounter{section}{0} %% Remove this when starting to work on the template.
+\begin{comment}
 	\section{How to Use this Template}
@@
 	% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
+\end{comment}
 
 \section{Introduction} 
+\subsection{Problem Statement}
+Skin cancer is one of the most common cancers leading to worldwide death.
+Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer.
+Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year.
+According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}.
+In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}.
+On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent.
+However, once the disease progresses beyond the skin, survival is poor\cite{11872}.
+Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
+Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks.
+AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment.
+Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice.
+In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor.
+In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data.
+In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example.
+In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.
+
+In order to adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance.
+Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
+Some of these models wich have been used as a backbone model in this paper will be discussed in the Related Work section.
+
+\subsection{Related Works}
+Skin lesion classification is not a new area, since there are many great performance models constructed.
+One of the most cutting-edge technologies that have been used is Soft-Attention as stated in\cite{03358}.
+Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201\cite{06993}, InceptionResNetV2\cite{00567}, ResNet50\cite{03385}\cite{05027}, VGG16\cite{1556} and Soft-Attention layer.
+Using those above backbones has been tried by many previous papers.
+Rishu Garg et al \cite{03798} uses transfer learning approach with CNN based model.
+Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3\cite{00567} model.
+Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating holes of different sizes on the images i.e.
+technically making a random portion of image inactive during data augmentation process.
+\cite{01284} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.
+Another state of the art is GradCam and Kernel SHAP\cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.
+
+Otherwise, the Student and Teacher Model is also a state of the art in 2021\cite{03225}.
+The student and teacher model is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
+Therefore, they can take full advantage of what others learn.
+SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively.
+Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al.
+
+On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning.
+Random Forest, XGBoost, and Support Vector Machines are tested by \cite{03798} of Rishu Garg et al.
+Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348} by Amirreza Rezvantalab et al.
+Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al.
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|c c c c c c c c c|} 
+		\hline
+		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
+		\hline
+		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
+		\hline
+	\end{tabular}
+	\caption{Data Distribution in HAM10000}
+	\label{table:1}
+\end{table}
+
+\subsection{Objectives}
+In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Materials and Methods}
+\subsection{Data}
+\subsubsection{Image Data}
+The dataset used in this paper is the HAM10000 dataset published by Havard University Dataverse\cite{10417}.
+There are total 7 classes in this dataset containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
+The distribution of the dataset is shown in the table below:
+\FloatBarrier
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|c c c c c c c c c|} 
+		\hline
+		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
+		\hline
+		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
+		\hline
+	\end{tabular}
+	\caption{Data Distribution in HAM10000}
+	\label{table:1}
+\end{table}
+\FloatBarrier
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/DataDistribution}
+	\caption{Example image of each class}
+	\label{fig:datadistribution}
+\end{figure}
+More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL).
+On the other hand, before being used for training the whole data is shuffled then split into two part.
+$90$ percent and $10$ percent of the data is used for training and validating respectively.
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+In the previous paper\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images.
+Since, this data is imbalanced, using augmented data may cause the problem of well classify on the majority of class.
+In this paper, instead of augmenting data, metadata is used.
+The way of processing metadata is discuss in MetaData section.
+Images in this dataset has the type of $RGB$ and shape of (450, 600).
+However, Each backbone need the different input size of image as well as the range of pixel value.
+DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet dataset.
+In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet dataset, without scaling.
+InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$.
+Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.
+\subsubsection{Metadata}
+The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position.
+During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples.
+In the gender and capturing position category contain some samples of unknown.
+Instead of removing, these "unknowns" data points is kept and considered as "prefer not to say".
+Besides, the label of the whole data is preprocessed into one-hot vector.
+\subsection{Model Schema}
+\subsubsection{Input Schema}
+Using metadata as another input is not new.
+In paper\cite{03910}, they decide to keep the missing value and set its value to $0$.
+The sex and anatomical site are categorical encoded.
+The age, on the other hand is numerical normalized.
+After processing, the metadata is fed into a two-layer neural network with 256 neurons each.
+Each layer contains batch normalization, a ReLU\cite{08375} activation and dropout with $p = 0.4$.
+The network’s output is concatenated with the CNN’s feature vector after global average pooling.
+Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata.
+During training, they randomly encode each property as missing with a probability of $p = 0.1$.
 
-Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+In this paper, the unknowns is kept as a type as discussed in Metadata section.
+Sex, anatomical site and age are also category encoded and numerical normalized, respectively.
+After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons.
+Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section.
+The Input schema is described as follow:\\
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{"Definitions/Input Schema"}
+	\caption{Input Schema}
+	\label{fig:input-schema}
+\end{figure}\\
+Image data, on the other hand after being preprocessed, is fed directly into the backbone model. 
+\subsubsection{Soft-Attention}
+Applying the Soft-Attention layer in deep learning is not a new approach.
+Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively.
+In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}.
+Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights.
+The function below describes the flow of the Soft-Attention module:
+\[
+f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
+\]
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-\begin{quote}
-This is an example of a quote.
-\end{quote}
+In order to apply Soft-Attention, there are two main steps.
+Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}.
+This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$.
+The output of this convolution is normalized using the softmax function to generate K = 16 attention maps.
+These $16$ attention maps are aggregated to produce a weight function called $\alpha$.
+This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar.
+Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/SoftAttention}
+	\caption{Soft-Attention Module}
+	\label{fig:softattention}
+\end{figure}
+In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
+\FloatBarrier
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{Definitions/SoftAttentionBlock}
+	\caption{Soft-Attention Module}
+	\label{fig:softattentionblock}
+\end{figure}
+\FloatBarrier
+\subsubsection{Backbone Model Architecture}
+In this paper, the backbone models used in this paper are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
+The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance.
+Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated.
+Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed.
+On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.
+\FloatBarrier
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|c | c c c|} 
+		\hline
+		Model & Size(MB) & Parameters & Depth \\ 
+		\hline
+		Resnet50 & 98 & 25.6M & 107 \\ 
+		\hline
+		Resnet152 & 232 & 60.4M & 311 \\ 
+		\hline
+		DenseNet201 & 80 & 20.2M & 402 \\
+		\hline
+		InceptionResNetV2 & 215 & 55.9M & 449 \\
+		\hline
+		MobileNet & 16 & 4.3M & 55 \\ 
+		\hline
+		MobileNetV2 & 14 & 3.5M & 105 \\ 
+		\hline
+		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
+		\hline
+		MobileNetV3Large & Unknown & 5.5M & 118 \\
+		\hline
+		NasnetMobile & 23 & 5.3M & 308 \\
+		\hline
+		NasnetLarge & 343 & 88.9M & 533 \\ 
+		\hline
+	\end{tabular}
+	\caption{Size and Parameters and Depth of backbone model used in this paper}
+	\label{table:2}
+\end{table}
+\FloatBarrier
+
+\subsubsection{Model}
+The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}.
+Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.
+It is described in the figure below:
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/MainModel}
+	\caption{Overall Model Architecture}
+	\label{fig:mainmodel}
+\end{figure}
+
+\subsection{Loss Function}
+The loss function used in this paper is categorical cross-entropy.
+Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$.
+Let $N$, and $C$ is the number of training examples and number of class respectively.
+The categorical cross-entropy loss is presented as:
+\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
+where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$.
+Since the dataset face the imbalanced problem then I applied the class weight for the loss.
+This formula below is used to calculate the class weight:
+\[W = N \odot D\]
+\[D = \begin{bmatrix}
+	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
+\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
+	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
+\end{bmatrix}\]
+where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$. 
+\subsection{Evaluation Metrics}
+\begin{figure}[!htb]
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
+		\caption{Confusion Matrix}\label{Fig:Data1}
+	\end{minipage}\hfill
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=.7\linewidth]{Definitions/AUC}
+		\caption{Area Under the Curve}\label{Fig:Data2}
+	\end{minipage}
+\end{figure}
+In this paper, the model is evaluated by using the confusion matrix and related metrics.
+The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class.
+Consider a confusion matrix $A$ with $C$ number of class.
+Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively.
+\[
+A = \begin{bmatrix}
+	a_{11} & a_{12} & \dots & a_{1j} \\
+	a_{21} & a_{22} & \dots & a_{2j} \\
+	\vdots & \vdots	&  & \vdots\\
+	a_{i1} & a_{i2} & \dots & a_{ij} 
+\end{bmatrix}
+\]
+
+The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$.
+The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
+\[
+FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
+\]
+\[
+TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
+	TN_1 & TN_2 & \dots & TN_c
+\end{bmatrix}
+\]
+Then, the model is evaluated by the following metrics:
+\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
+\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
+\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
+The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
+\subsection{Traning}
+Before training, the dataset is split into three sub datasets including training, validation, and testing. In this paper, the graphic card that is used to train is Nvidia RTX TitanV.\\
+All the model in this paper is trained with Adam Optimizer\cite{6980}.
+The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$, the epsilon argument of the optimizer is set to $0.1$.
+On the other hand, Early Stopping is also set up, if the accuracy of validation set dose not increase after 25 epochs, the training will stop.
 
@@
 \section{Results}
-
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\subsection{Subsection}
-\subsubsection{Subsubsection}
-
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
-
-Numbered lists can be added as follows:
-\begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
-\end{enumerate}
-
-The text continues here.
-
-\subsection{Figures, Tables and Schemes}
-
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
-\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
-\end{figure}   
-\unskip
-
-\begin{table}[H] 
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabularx}
+The accuracy of all model is presented in the figure below:
+\begin{table}[h]
+	\centering
+	\begin{tabular}{| c | c | c | c |}
+		\hline
+		InceptionResNetV2 & DenseNet201 & ResNet50 & VGG16 \\
+		\hline
+		0.93 & 0.91 & 0.92 & 0.88\\
+		\hline
+	\end{tabular}
+	\caption{Accuracy of the model with augmented data}
+	\label{table:3}
 \end{table}
-\unskip
-
-\begin{table}[H]
-\caption{This is a wide table.\label{tab2}}
-	\begin{adjustwidth}{-\extralength}{0cm}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\fulllength}{CCCC}
-			\toprule
-			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
-			\midrule
-			Entry 1		& Data			& Data			& Data\\
-			Entry 2		& Data			& Data			& Data \textsuperscript{1}\\
-			\bottomrule
-		\end{tabularx}
-	\end{adjustwidth}
-	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
+\begin{table}[h]
+	\centering
+	\begin{tabular}{| c | c | c | c | c |}
+		\hline
+		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
+		\hline
+		0.89 & 0.89 & 0.70 & 0.57 & 0.81\\
+		\hline
+	\end{tabular}
+\end{table}
+\begin{table}[h]
+	\centering
+	\begin{tabular}{| c | c | c | c |}
+		\hline
+		MobileNetV3Large & MobileNetV3Small & NasNetLarge & NasNetMobile\\
+		0.84 & 0.78 & 0.86 & 0.86\\
+		\hline
+	\end{tabular}
+	\caption{Accuracy of the model with metadata}
+	\label{table:4}
+\end{table}
+According to the Table 3 and 4, it is clear that the model trained with augmented data has a higher accuracy than the model trained with metadata only.
+While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.93$ and $0.91$ respectively, their training with metadata has both the accuracy of $0.89$.
+Furthermore, Resnet50 trained with augmented data has the accuracy that outperform the Resnet50 and is twice as high as Resnet152 trained with metadata.
+On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively.
+This term will be discussed later on.
+Since, the model trained with augmented data have high accuracy, when their f1-score and the recall score of models are analyzed, it turns out that models trained with augmented data have imbalanced f1-scores according to table 5.
+As a results, augmented data model dose not classify well on all class as InceptionResNetV2 trained on augmented data have $0.29$ f1-score on class df while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way.
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c | c | c | c | c | c | c | c | c|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
+		\hline
+		\thead{DenseNet201 +\\ Augmented Data} & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
+		\hline
+		\thead{InceptionResNetV2 +\\ Augmented Data} & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
+		\hline
+		\thead{Resnet50 +\\ Augmented Data} & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
+		\hline 	
+		\thead{VGG16 +\\ Augmented Data} & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
+		\hline		
+		\thead{DenseNet201 +\\Metadata and WeightLoss} & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
+		\hline
+		\thead{InceptionResNetV2 +\\Metadata and WeightLoss} & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
+		\hline
+		\thead{Resnet50 +\\Metadata and WeightLoss} & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
+		\hline
+		\thead{Resnet152 +\\Metadata and WeightLoss} & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
+		\hline
+		\thead{NasNetLarge +\\Metadata and WeightLoss} & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
+		\hline
+		\thead{MobileNetV2 +\\Metadata and WeightLoss} & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
+		\hline
+		\thead{MobileNetV3Large +\\Metadata and WeightLoss} & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
+		\hline
+		\thead{MobileNetV3Small +\\Metadata and WeightLoss} & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
+		\hline
+		\thead{NasNetMobile +\\Metadata and WeightLoss} & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
+		\hline
+	\end{tabular}
+	\caption{F1-Score of each class and the mean f1-score of each model}
+	\label{table:5}
 \end{table}
 
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\columnwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\columnwidth}{1pt}
-%\end{listing}
+However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
+The others still face the imbalanced term.
+Since this dataset is not balanced, therefore using augmented data can make the model more  bias to the class which has larger sample.
+Using the metadata, though still make the model bias, it dose contributes to the improvement of  the performance of the model.
 
-Text.
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|l | c | c | c | c | c | c | c | c|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
+		\hline
+		\thead{DenseNet201 +\\ Augmented Data} & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
+		\hline
+		\thead{InceptionResNetV2 +\\ Augmented Data} & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
+		\hline
+		\thead{Resnet50 +\\ Augmented Data} & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
+		\hline 	
+		\thead{VGG16 +\\ Augmented Data} & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
+		\hline		
+		\thead{DenseNet201 +\\Metadata and WeightLoss} & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
+		\hline
+		\thead{InceptionResNetV2 +\\Metadata and WeightLoss} & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
+		\hline
+		\thead{Resnet50 +\\Metadata and WeightLoss} & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
+		\hline
+		\thead{Resnet152 +\\Metadata and WeightLoss} & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
+		\hline
+		\thead{NasNetLarge +\\Metadata and WeightLoss} & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
+		\hline
+		\thead{MobileNetV2 +\\Metadata and WeightLoss} & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
+		\hline
+		\thead{MobileNetV3Large +\\Metadata and WeightLoss} & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
+		\hline
+		\thead{MobileNetV3Small +\\Metadata and WeightLoss} & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
+		\hline
+		\thead{NasNetMobile +\\Metadata and WeightLoss} & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
+		\hline
+	\end{tabular}
+	\caption{Recall score of each class and the mean recall score of each model}
+	\label{table:6}
+\end{table}
 
-Text.
+This problem is also true with the recall score according to table 6.
+DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has expected value of recall of $0.72$, $0.71$, $0.69$, $0.69$, respectively, while the combination of InceptionResNetV2, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
 
-\subsection{Formatting of Mathematical Components}
+As the results, metadata does improve the model performance by reducing the amount of data needed for achieving nearly the expected results.
+On the other hand, the reason why the model become much more balanced is the weighted loss function.
+Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class.
+Therefore, DenseNet201, InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$.
+$0.82$, respectively, as opposed to their training in akiec without weighted loss function.
+MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.
 
-This is the example 1 of equation:
-\begin{linenomath}
-\begin{equation}
-a = 1,
-\end{equation}
-\end{linenomath}
-the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
+Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
+The table 8 illustrates the deeper analyzing of the three models.
+It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.
+\FloatBarrier
+\begin{table}[ht]
+	\centering	
+	\begin{tabular}{|l | c | c | c | c|} 
+		\hline
+		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\
+		\hline
+		Accuracy(avg) & 0.81 & 0.78 & 0.84 & \textbf{0.86}\\
+		\hline
+		Balanced Accuracy(avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
+		\hline
+		Precision(avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
+		\hline
+		F1-score(avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
+		\hline
+		Sensitivity(avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
+		\hline
+		Specificity(avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
+		\hline
+		ROC-AUC-score(avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
+		\hline
+	\end{tabular}
+	\caption{Deeper analyzing of mobile model}
+	\label{table:7}
+\end{table}
+\FloatBarrier
+Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.
+Therefore, at the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model.
+The result of this experiment is illustrated in table 9.
+\FloatBarrier
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|l | c |}
+		\hline
+		Model & Accuracy\\
+		\hline
+		MobileNetV3Large-Layer[:270] + Soft-Attention + Metadata & 0.71 \\
+		\hline
+		MobileNetV3Large-Layer[:266] + Soft-Attention + Metadata  & 0.73 \\
+		\hline
+		MobileNetV3Large-Layer[:260] + Soft-Attention + Metadata  & 0.77 \\
+		\hline
+		MobileNetV3Large-Layer[:251] + Soft-Attention + Metadata  & 0.79 \\
+		\hline
+		MobileNetV3Large-Layer[:246] + Soft-Attention + Metadata  & 0.84 \\
+		\hline
+		MobileNetV3Large-Layer[:246] + Soft-Attention + Dense(512) + Metadata & 0.85 \\
+		\hline
+		MobileNetV3Large-Layer[:240] + Soft-Attention + Metadata  & \textbf{0.86}\\
+		\hline
+		MobileNetV3Large-Layer[:230] + Soft-Attention + Metadata  & 0.84 \\
+		\hline
+		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 
+		\hline
+		MobileNetV3Large & 0.85 \\ 
+		\hline
+	\end{tabular}
+	\caption{Deeper analyzing of MobileNetV3Large Model}
+	\label{table:8}
+\end{table}
+\FloatBarrier
+The Table 9 demonstrate that the Soft-Attention and the metadata have a good effect on the model.
+Otherwise, Adding a dense layer does not increase the model performance.
+The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^{th}$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of $0.86$ accuracy rate.
+\FloatBarrier
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{| l | c |}
+		\hline
+		Accuracy & 0.86\\
+		\hline
+		Precision(avg) & 0.86\\
+		\hline
+		F1-score(avg) & 0.86\\
+		\hline
+		Sensitivity(avg) & 0.86\\
+		\hline
+		Specificity(avg) & 0.95\\
+		\hline
+		ROC AUC Score(avg) & 0.98\\
+		\hline
+	\end{tabular}
+	\caption{Performance of MobileNetV3Large}
+	\label{table:9}
+\end{table}
+\FloatBarrier
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{| l | c | c | c |}
+		\hline
+		Model & MobileNetV3Large & DenseNet201 & InceptionResnetV2\\
+		\hline
+		No. Parameters & \textbf{5.5M} & 20.2M & 55.9M\\
+		\hline
+		Depth & \textbf{118} & 402 & 449\\
+		\hline
+		Accuracy & 0.86 & 0.89 & 0.90\\
+		\hline
+		Time Prediction(s/epochs) & \textbf{116} & 1000 & 3500 \\
+		\hline
+	\end{tabular}
+	\caption{How Performance of MobileNetV3Large be optimized}
+	\label{table:11}
+\end{table}
+\FloatBarrier
+\section{Conclusions}
+In this paper, my objective is to analyze the effect of metadata on the performance of model as well as identifying whether metadata can make the model less imbalanced or not.
+On the other hand, I also try to construct an optimized and balanced model that can be used on mobile phone or electronic devices.
+The experiment shown that metadata improve the model performance, the factor that make the model much more imbalanced is the augmented data.
+This problem can be solve quite absolutely by using aforementioned weighted loss function.
+Using weighted loss function make the expected value of model f1-score increase.
+At the end of the experiment, mobile model is found that can achieve great performance without either the large number of parameters or depth.
 
-This is the example 2 of equation:
-\begin{adjustwidth}{-\extralength}{0cm}
-\begin{equation}
-a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-\end{equation}
-\end{adjustwidth}
-
-% Example of a page in landscape format (with table and table footnote).
-%\startlandscape
-%\begin{table}[H] %% Table in wide page
-%\caption{This is a very wide table.\label{tab3}}
-%	\begin{tabularx}{\textwidth}{CCCC}
-%		\toprule
-%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
-%		\midrule
-%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
-%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
-%		\bottomrule
-%	\end{tabularx}
-%	\begin{adjustwidth}{+\extralength}{0cm}
-%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
-%	\end{adjustwidth}
-%\end{table}
-%\finishlandscape
-
-% Example of a figure that spans the whole page width. The same concept works for tables, too.
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=13.5cm]{Definitions/logo-mdpi}
-\end{adjustwidth}
-\caption{This is a wide figure.\label{fig2}}
-\end{figure}
-
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-
-The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \vspace{6pt}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
+\authorcontributions{In this paper, I am the only author, therefore I need to do all things including research, implementation, analyze data, writing draft resolution}
 
-\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''.
-Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
+\funding{This research received no external funding}
 
-\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study.
-You might choose to exclude this statement if the study did not require ethical approval.
-Please note that the Editorial Office might ask you for further information.
-Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans.
-OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals.
-OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}
+\institutionalreview{Not applicable}
 
-\informedconsent{Any research article describing a study involving humans should contain this statement.
-Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
-You might also choose to exclude this statement if the study did not involve humans.
-
-Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
-Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
+\informedconsent{Not applicable}
 
@@
 
-\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
+\acknowledgments{I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project.
+He gave a chance to use High GPU computing computer for AI Training.
+Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.}
 
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the~results''.}
+\conflictsofinterest{The authors declare no conflict of interest.}
 
@@
 \begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute\\
-DOAJ & Directory of open access journals\\
-TLA & Three letter acronym\\
-LD & Linear dichroism
+CAD & Computer aided diagnosis\\
+AI & Artificial Intelligence\\
+AKIEC & Actinic keratoses and intraepithelial carcinoma or Bowen's disease\\
+BCC & Basal Cell Carcinoma\\
+BKL & Benign Keratosis-like Lesions\\
+DF & Dermatofibroma\\
+MEL & Melanoma\\
+NV & Melanocytic Nevi\\
+VASC & Vascular Lesions\\
+HISTO & Histopathology\\
+FOLLOWUP & Follow-up examination\\
+CONSENSUS & Expert Consensus\\
+CONFOCAL & Confocal Microscopy\\
+RGB & Red Green Blue\\
+BGR & Blue Green Red\\
+TP & True Positives\\
+FN & False Negatives\\
+TN & True Negatives\\
+FP & False Positives\\
+Sens & Sensitivity\\
+Spec & Specificity\\
+AUC & Area Under the Curve\\
+ROC & Receiver Operating Curve\\
 \end{tabular}
@@
 %% Optional
-\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+\begin{comment}
+	\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
+If the appendix sections contain a heading then change the argument to "yes".
 	\appendixstart
@@
 	\bottomrule
-\end{tabularx}
-\end{table}
+	%\end{tabularx}
+	%\end{table}
 
@@
 	All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
+\end{comment}
 
@@
 \bibitem[Author1(year)]{08332}
-Katherine M. Li and Evelyn C. Li. Skin Lesion Analysis Towards Melanoma Detection via End-to-end Deep Learning of Convolutional Neural Networks. {\em Journal Abbreviation} {\bf 2018}.
+Katherine M. Li and Evelyn C. Li. Skin Lesion Analysis Towards Melanoma Detection via End-to-end Deep Learning of Convolutional Neural Networks. 
+{\em Journal Abbreviation} 
+{\bf 2018}.
 
 \bibitem[Author2(year)]{03225}
-Xiaohan Xing and Yuenan Hou and  Hang Li and Yixuan Yuan and Hongsheng Li and Max Q.-H.
-Meng Categorical Relation-Preserving Contrastive Knowledge Distillation for Medical Image Classification.
-{\em Journal Abbreviation} {\bf 2021}.
+Xiaohan Xing and Yuenan Hou and  Hang Li and Yixuan Yuan and Hongsheng Li and Max Q.-H. Meng Categorical Relation-Preserving Contrastive Knowledge Distillation for Medical Image Classification. 
+{\em Journal Abbreviation} 
+{\bf 2021}.
 
@@
 \bibitem[Author2(year)]{09365}
-Amirreza Rezvantalab and Habib Safigholi and Somayeh Karimijeshni Dermatologist Level Dermoscopy Skin Cancer Classification Using Different Deep Learning Convolutional Neural Networks Algorithms.
-{\em Journal Abbreviation} {\bf 2020}.
+Xuan Li and Yuchen Lu and Christian Desrosiers and Xue Liu Out-of-Distribution Detection for Skin Lesion Images with Deep Isolation Forest. 
+{\em Journal Abbreviation} 
+{\bf 2020}.
 
@@
 Amirreza Rezvantalab and Habib Safigholi and Somayeh Karimijeshni Dermatologist Level Dermoscopy Skin Cancer Classification Using Different Deep Learning Convolutional Neural Networks Algorithms. 
-{\em Journal Abbreviation} {\bf 2021}.
+{\em Journal Abbreviation} 
+{\bf 2021}.
 
 \bibitem[Author2(year)]{06612}
-Kyle Young and Gareth Booth and Becks Simpson and Reuben Dutton and Sally Shrapnel Dermatologist Level Dermoscopy Deep neural network or dermatologist?. {\em Journal Abbreviation} {\bf 2021}.
+Kyle Young and Gareth Booth and Becks Simpson and Reuben Dutton and Sally Shrapnel Dermatologist Level Dermoscopy Deep neural network or dermatologist?. {\em Journal Abbreviation} 
+{\bf 2021}.
+
+\bibitem[Author2(year)]{10417}
+Philipp Tschandl and Cliff Rosendahl and Harald Kittler The HAM10000 dataset, a large collection of multi-source dermatoscopic images of common pigmented skin lesions. 
+{\em Journal Abbreviation} 
+{\bf 2018}.
+
+\bibitem[Author2(year)]{05045}
+Michele Alberti and Angela Botros and Narayan Schuez and Rolf Ingold and Marcus Liwicki and Mathias Seuret Trainable Spectrally Initializable Matrix Transformations in Convolutional Neural Networks. 
+{\em Journal Abbreviation} 
+{\bf 2019}.
+
+\bibitem[Author2(year)]{09418}
+Hemanth Nadipineni Method to Classify Skin Lesions using Dermoscopic images. {\em Journal Abbreviation} 
+{\bf 2020}.
+
+\bibitem[Author2(year)]{03910}
+Nils Gessert and Maximilian Nielsen and Mohsin Shaikh and René Werner and Alexander Schlaefer Skin Lesion Classification Using Ensembles of Multi-Resolution EfficientNets with Meta Data. 
+{\em Journal Abbreviation} 
+{\bf 2020}.
+
+\bibitem[Author2(year)]{11797}
+Pranav Poduval and Hrushikesh Loya and Amit Sethi Functional Space Variational Inference for Uncertainty Estimation in Computer Aided Diagnosis. 
+{\em Journal Abbreviation} 
+{\bf 2020}.
+
+\bibitem[Author2(year)]{01284}
+Peng Yao and Shuwei Shen, Mengjuan Xu and Peng Liu and Fan Zhang and Jinyu Xing and Pengfei Shao and Benjamin Kaffenberger and Ronald X.
+Xu Single Model Deep Learning on Imbalanced Small Datasets for Skin Lesion Classification.
+{\em Journal Abbreviation} 
+{\bf 2022}.
+
+\bibitem[Author2(year)]{11872}
+Manu Goyal and Thomas Knackstedt and Shaofeng Yan and Saeed Hassanpour Artificial Intelligence-Based Image Classification for Diagnosis of Skin Cancer: Challenges and Opportunities. 
+{\em Journal Abbreviation} 
+{\bf 2020}.
+
+\bibitem[Author2(year)]{03358}
+Soumyya Kanti Datta and  Mohammad Abuzar Shaikh and Sargur N. Srihari and Mingchen Gao Soft-Attention Improves Skin Cancer Classification Performance. {\em Journal Abbreviation} 
+{\bf 2021}.
+
+\bibitem[Author2(year)]{12602}
+Amirreza Mahbod and Philipp Tschandl and Georg Langs and Rupert Ecker and Isabella Ellinger The Effects of Skin Lesion Segmentation on the	Performance of Dermatoscopic Image Classification
+{\em Journal Abbreviation} 
+{\bf 2020}.
+
+\bibitem[Author2(year)]{03426}
+Yeong Chan Lee and Sang-Hyuk Jung and Hong-Hee Won WonDerM: Skin Lesion Classification with Fine-tuned Neural Networks
+{\em Journal Abbreviation} 
+{\bf 2019}.
+
+\bibitem[Author2(year)]{04803}
+Zihang Dai and Hanxiao Liu and Quoc V. Le and Mingxing Tan: CoAtNet Marrying Convolution and Attention for All Data Sizes
+{\em Journal Abbreviation} 
+{\bf 2021}.
+
+\bibitem[Author2(year)]{06993}
+Gao Huang and Zhuang Liu and Laurens van der Maaten and Kilian Q. Weinberger: Densely Connected Convolutional Network
+{\em Journal Abbreviation} 
+{\bf 2018}.
+
+\bibitem[Author2(year)]{11946}
+Mingxing Tan and Quoc V. Le EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks
+{\em Journal Abbreviation} 
+{\bf 2020}.
+
+\bibitem[Author2(year)]{00567}
+Christian Szegedy and Vincent Vanhoucke and Sergey Ioffe and Jonathon Shlens and Zbigniew Wojna Rethinking the Inception Architecture for Computer Vision
+{\em Journal Abbreviation} 
+{\bf 2015}.
+
+\bibitem[Author2(year)]{04861}
+Andrew G.
+Howard and Menglong Zhu and Bo Chen and Dmitry Kalenichenko and Weijun Wang and Tobias Weyand and Marco Andreetto and Hartwig Adam MobileNets: Efficient Convolutional Neural Networks for Mobile Vision Applications
+{\em Journal Abbreviation} 
+{\bf 2017}.
+
+\bibitem[Author2(year)]{04381}
+Mark Sandler and Andrew Howard and Menglong Zhu and Andrey Zhmoginov and Liang-Chieh Chen MobileNetV2: Inverted Residuals and Linear Bottlenecks
+{\em Journal Abbreviation} 
+{\bf 2018}.
+
+\bibitem[Author2(year)]{02244}
+Andrew Howard and Mark Sandler and Grace Chu and Liang-Chieh Chen and Bo Chen and Mingxing Tan and Weijun Wang and Yukun Zhu and Ruoming Pang and Vijay Vasudevan and Quoc V.
+Le and Hartwig Adam Searching for MobileNetV3
+{\em Journal Abbreviation} 
+{\bf 2019}.
+
+\bibitem[Author2(year)]{03385}
+Kaiming He and Xiangyu Zhang and Shaoqing Ren and Jian Sun Deep Residual Learning for Image Recognition
+{\em Journal Abbreviation} 
+{\bf 2015}.
+
+\bibitem[Author2(year)]{05027}
+Kaiming He and Xiangyu Zhang and Shaoqing Ren and Jian Sun Identity Mappings in Deep Residual Networks
+{\em Journal Abbreviation} 
+{\bf 2016}.
+
+\bibitem[Author2(year)]{1556}
+Karen Simonyan and Andrew Zisserman Very Deep Convolutional Networks for Large-Scale Image Recognition
+{\em Journal Abbreviation} 
+{\bf 2016}.
+
+\bibitem[Author2(year)]{02357}
+François Chollet Xception: Deep Learning with Depthwise Separable Convolutions
+{\em Journal Abbreviation} 
+{\bf 2017}.
+
+\bibitem[Author2(year)]{6980}
+Diederik P. Kingma, Jimmy Ba Adam: A Method for Stochastic Optimization
+{\em Journal Abbreviation} 
+{\bf 2017}.
+
+\bibitem[Author2(year)]{03044}
+Kelvin Xu and Jimmy Ba and Ryan Kiros and Kyunghyun Cho and Aaron Courville and Ruslan Salakhutdinov and Richard Zemel and Yoshua Bengio Show, Attend and Tell: Neural Image Caption Generation with Visual Attention 2020 17th International Conference on Frontiers in Handwriting Recognition
+{\em Journal Abbreviation} 
+{\bf 2016}.
+
+\bibitem[Author2(year)]{08513}
+Naofumi Tomita and Behnaz Abdollahi and Jason Wei and Bing Ren and Arief Suriawinata and Saeed Hassanpour.
+Attention-Based Deep Neural Networks for Detection of Cancerous and Precancerous Esophagus Tissue on Histopathological Slides
+{\em Journal Abbreviation} 
+{\bf 2020}.
+
+\bibitem[Author2(year)]{02357}
+Mohammad Abuzar Shaikh and Tiehang Duan and Mihir Chauhan and Sargur N. Srihari. 2020 17th International Conference on Frontiers in Handwriting Recognition
+{\em Journal Abbreviation} 
+{\bf 2019}.
+
+\bibitem[Author2(year)]{8943952}
+Srihari. YAOSHIANG HO AND SAMUEL WOOKEY The Real-World-Weight Cross-Entropy Loss Function: Modeling the Costs of Mislabeling 
+{\em Journal Abbreviation} 
+{\bf 2020}.
+
+\bibitem[Author2(year)]{07012}
+Barret Zoph, Vijay Vasudevan, Jonathon Shlens, Quoc V. Le Learning Transferable Architectures for Scalable Image Recognition 
+{\em Journal Abbreviation} 
+{\bf 2017}.
+
+\bibitem[Author2(year)]{08375}
+Abien Fred Agarap Deep Learning using Rectified Linear Units (ReLU) 
+{\em Journal Abbreviation} 
+{\bf 2019}.
+
+\bibitem[Author2(year)]{01507}
+Jie Hu, Li Shen, Samuel Albanie, Gang Sun, Enhua Wu Squeeze-and-Excitation Networks 
+{\em Journal Abbreviation} 
+{\bf 2019}.
+
+\bibitem[Author2(year)]{04552v2}
+Improved Regularization of Convolutional Neural Networks with Cutout Improved Regularization of Convolutional Neural Networks with Cutout 
+{\em Journal Abbreviation} 
+{\bf 2017}.
 

### 2022-06-29 MDPI/Sensor Paper/template.tex
Update Ver 4 MDPI Sensor Paper

@@
 Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
-Some of these models wich have been used as a backbone model in this paper will be discussed in the Related Work section.
+Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.
 
@@
 SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively.
+In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600).
+In SkinLinkNet, instead resize the image down to (448, 448).
+Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively.
 Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al.
@@
 	\centering
-	\begin{tabular}{|c c c c c c c c c|} 
-		\hline
-		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
-		\hline
-		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
-		\hline
-	\end{tabular}
-	\caption{Data Distribution in HAM10000}
-	\label{table:1}
+	\begin{tabular}{|p{1cm}|p{12.5cm}|}
+		\hline
+		Work & Approach \\ 
+		\hline
+		\cite{03358} & Combination of Backbone Model and Soft Attention. Backbone model includes DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34\\
+		\hline
+		\cite{03798} & Transfer Learning with CNN based model\\
+		\hline
+		\cite{10348} & Transfer Learning with CNN based model including DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34, and InceptionNetV3\\
+		\hline
+		\cite{09418} & Transfer Learning with CNN based model including EfficientNet and SeNet.
+Data augmentation process used CutOut to create random sized hole considered as an inactive portion of image.\\
+		\hline
+		\cite{01284} & Transfer Learning with CNN based model.
+Data augmentation process uses RandArgument to split picture into several pictures which is used to train.
+DropBlock and Multi-Weight Loss Function are used to deal with the imbalanced.\\
+		\hline
+		\cite{06612} & GradCam and Kernel SHAP, two model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.\\
+		\hline
+		\cite{03225} & Student and Teacher Model is the combination of two model which share the memory learned with others. \\
+		\hline
+		\cite{12602} & SkinLinkNet uses the image whose shape is (448,488) for training. Unet and EfficientNetB0 are used for segmentation and classification task respectively.\\
+		\hline
+		\cite{03426} & WonderM uses the image whose shape is (600,600) created by padding for training. Unet and DenseNet are used for segmentation and classification task respectively.\\
+		\hline
+		\cite{03910} & MetaData including age, gender, and capture position are used to gain higher performance of the model. The models used in this paper are CNN-based model \\
+		\hline
+		\cite{03798} & Traditional Machine Learning Algorithms are applied including Random Forest, XGBoost, and Support Vector Machine \\
+		\hline
+		\cite{10348} & Matrix Factorization are applied before the softmax activation function \\
+		\hline
+		\cite{05045} & Isolation Forest are applied distribution skin lesion images before fedding into the softmax activation function. \\
+		\hline
+		\cite{10348} & Matrix Factorization are applied before the softmax activation function. \\
+		\hline
+	\end{tabular}
+	\caption{Related Works Summary}
+	\label{table:0}
 \end{table}

### 2022-07-07 MDPI/Sensor Paper/template.tex
Update

@@
 In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data.
-In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example.
-In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.
+In Medical Treatment, AI models are applied to build solutions to a specific disease, medicine revolution is an example.
+In various studies, AI algorithms have provided various end-to-end solutions to the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.
 
@@
 
-Otherwise, the Student and Teacher Model is also a state of the art in 2021\cite{03225}.
-The student and teacher model is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
+Otherwise, there are also many state of the art whose great performance on skin lesion classification.
+The Student and Teacher Model is also a high performance model in 2021\cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
 Therefore, they can take full advantage of what others learn.
@@
 Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al.
+\FloatBarrier
 \begin{table}[ht]
@@
 \end{table}
-
+\FloatBarrier
 \subsection{Objectives}
-In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
+In this paper, the effect of metadata on classifying skin disease will be analyzed.
+On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\caption{Example image of each class}
-	\label{fig:datadistribution}
+	\label{fig:dataexample}
 \end{figure}
+\FloatBarrier
 More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL).
@@
 After processing, the metadata is fed into a two-layer neural network with 256 neurons each.
-Each layer contains batch normalization, a ReLU\cite{08375} activation and dropout with $p = 0.4$.
+Each layer contains batch normalization, a ReLU\cite{08375} activation, and dropout with $p = 0.4$.
 The network’s output is concatenated with the CNN’s feature vector after global average pooling.
@@
 Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section.
-The Input schema is described as follow:\\
+The Input schema is described as follow:
+\FloatBarrier
 \begin{figure}[h]
 	\centering
-	\includegraphics[width=0.7\linewidth]{"Definitions/Input Schema"}
+	\includegraphics[width=1\linewidth]{"Definitions/Input Schema"}
 	\caption{Input Schema}
 	\label{fig:input-schema}
-\end{figure}\\
+\end{figure}
+\FloatBarrier
 Image data, on the other hand after being preprocessed, is fed directly into the backbone model. 
@@
 \]
-
 In order to apply Soft-Attention, there are two main steps.
@@
 This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar.
-Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.
+Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.
+\FloatBarrier
 \begin{figure}[h]
@@
 \end{figure}
+\FloatBarrier
 In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
@@
 	\centering
-	\begin{tabular}{|c | c c c|} 
+	\begin{tabular}{|l | c c c|} 
 		\hline
@@
 		\hline
-		InceptionResNetV2 & 215 & 55.9M & 449 \\
+		InceptionResNetV2\cite{07261} & 215 & 55.9M & 449 \\
 		\hline
@@
 It is described in the figure below:
+\FloatBarrier
 \begin{figure}[h]
 	\centering
-	\includegraphics[width=1\linewidth]{Definitions/MainModel}
+	\includegraphics[width=0.7\linewidth]{Definitions/MainModel - Model Form}
 	\caption{Overall Model Architecture}
@@
 \end{figure}
+\FloatBarrier
+
+\begin{table}[H]
+	\begin{adjustwidth}{-\extralength}{0cm}
+		%\newcolumntype{C}{>{\centering\arraybackslash}X}
+		\begin{tabularx}{\fulllength}{p{1.4cm} | p{1.4cm} | p{1.4cm} | p{1.4cm} | p{1.4cm} | p{1.4cm} | p{1.4cm} | p{1.4cm} | p{1.4cm} | p{1.4cm}}
+			\toprule
+			\textbf{DenseNet-201} & \textbf{DenseNet-201 + SA} & \textbf{Inception-ResNetV2} & \textbf{Inception-ResNetV2 + SA} & \textbf{ResNet-50} & \textbf{ResNet-50 + SA} & \textbf{ResNet-152} & \textbf{ResNet-152 + SA} & \textbf{NasNet-Large} & \textbf{NasNet-Large + SA}\\
+			\midrule
+			Conv2D 7x7 & Conv2D 7x7 & STEM& STEM& Conv2D 7x7& Conv2D 7x7& Conv2D 7x7& Conv2D 7x7& Conv2D 3x3& Conv2D 3x3\\ \hline
+			Pooling 3x3 & Pooling 3x3 & & & Pooling 3x3& Pooling  3x3& Pooling  3x3& Pooling  3x3& Pooling& Pooling\\ \hline		
+			DenseBlock x 6 & DenseBlock x 6 & Inception ResNet A x 10& Inception ResNet A x 10& Residual Block x 3& Residual Block x 3& Residual Block x 3& Residual Block x 3& Reduction Cell x 2& Reduction Cell x 2\\  \hline
+			Conv2D 1x1 & Conv2D 1x1 & Reduction A & Reduction A & & & & & Normal Cell x N& Normal Cell x N\\	\hline			
+			Average pool 2x2 & Average pool 2x2 & & & & & & & & \\ \hline			
+			DenseBlock x 12 & DenseBlock x 12 & Inception ResNet B x 20& Inception ResNet B x 20& Residual Block x 4& Residual Block x 4& Residual Block x 8& Residual Block x 8& Reduction Cell& Reduction Cell\\ \hline
+			Conv2D 1x1 & Conv2D 1x1 & Reduction B & Reduction B & & & & & Normal Cell x N& Normal Cell x N\\			\hline
+			Average pool 2x2 & Average pool 2x2 & & & & & & & & \\ \hline
+			DenseBlock x 48 & DenseBlock x 12 & Inception ResNet C x 5& Inception ResNet C x 5& Residual Block x 6& Residual Block x 6& Residual Block x 36& Residual Block x 36& Reduction Cell& Reduction Cell\\ \hline
+			Conv2D 1x1 & Conv2D 1x1 & & & & & & & Normal Cell x N& Normal Cell x N-2\\			\hline
+			Average pool 2x2 & Average pool 2x2 & & & & & & & & \\ \hline
+			DenseBlock x 29 & DenseBlock x 29 & & & Residual Block x 3& & Residual Block x 3& & & \\ \hline
+			DenseBlock x 3 & \textbf{SA Module} & & \textbf{SA Module}& & \textbf{SA Module}& & \textbf{SA Module}& & \textbf{SA Module}\\	\hline
+			GAP 7x7 & & Average pool& & GAP 7x7& & GAP 7x7& & & \\			\hline
+			FC 1000D & & Dropout (0.8)& & FC 1000D& & FC 1000D& & & \\ \hline
+			SoftMax & SoftMax & SoftMax& SoftMax& SoftMax& SoftMax& SoftMax& SoftMax& SoftMax& SoftMax\\ 			
+			\bottomrule
+		\end{tabularx}
+	\end{adjustwidth}
+	\caption{Details Structure of Models except Mobile models.
+SA stands for Soft-Attention, SA Module denotes whether that model use Soft-Attention Module.
+GAP stands for Global Average Pooling.
+FC stands for Fully-Connected Layer\label{detailed structure model}}
+\end{table}
+
+The table 4 and table 5 illustrate the detailed structure of the models in original form and its combination with Soft-Attention which is used in this research.
+In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module.
+Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module.
+InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module.
+Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.
+
+\begin{table}[H]
+	\begin{adjustwidth}{-\extralength}{0cm}
+		%\newcolumntype{C}{>{\centering\arraybackslash}X}
+		\begin{tabularx}{\fulllength}{p{1.8cm} | p{1.8cm} | p{1.9cm} | p{1.9cm} | p{1.9cm} | p{1.8cm} | p{1.8cm} | p{1.9cm}}
+			\toprule
+			\textbf{MobileNetV2} & \textbf{MobileNetV2 + SA} & \textbf{MobileNetV3 Small} & \textbf{MobileNetV3 Small + SA} & \textbf{MobileNetV3 Large} & \textbf{MobileNetV3 Large + SA} & \textbf{NasNet Mobile} & \textbf{NasNetMobile + SA}\\
+			\midrule
+			Conv2D & Conv2D& Conv2D 3x3& Conv2D 3x3& Conv2D 3x3& Conv2D 3x3 & Normal Cell & Normal Cell\\	\hline		
+			bottleneck & bottleneck & bottleneck 3x3 SE& bottleneck 3x3 SE& bottleneck 3x3 3 repeated& bottleneck 3x3 3 repeated& Reduction Cell& Reduction Cell\\ \hline					
+			bottleneck 2 repeated& bottleneck 2 repeated& bottleneck 3x3& bottleneck 3x3& bottleneck 5x5 SE 3 repeated& bottleneck 5x5 SE 3 repeated & Normal Cell & Normal Cell\\ \hline	
+			bottleneck 3 repeated& bottleneck 3 repeated& bottleneck 5x5 SE 8 repeated& bottleneck 5x5 SE 8 repeated& bottleneck 3x3 4 repeated& bottleneck 3x3 4 repeated& Reduction Cell & Reduction Cell\\ \hline
+			bottleneck 4 repeated& bottleneck 4 repeated& & & bottleneck 3x3 SE 2 repeated& bottleneck 3x3 SE 2 repeated & Normal Cell\\ \hline	
+			bottleneck 3 repeated& bottleneck 3 repeated& & & bottleneck 5x5 SE 3 repeated& bottleneck 5x5 SE 3 repeated& \\ \hline	
+			bottleneck 3 repeated& bottleneck & & & & & \\ \hline	
+			bottleneck & & & & & & \\ \hline
+			Conv2D 1x1 & & Conv2D 1x1 SE & Conv2D 1x1 SE& Conv2D 1x1& Conv2D 1x1 & & \\ \hline
+			AP 7x7 & & Pool 7x7& Pool 7x7& Pool 7x7& Pool 7x7& &\\ \hline
+			Conv2D 1x1 & \textbf{SA Module}& Conv2D 1x1 2 repeated& \textbf{SA Module}& Conv2D 1x1 2 repeated& \textbf{SA Module}& &\textbf{SA Module}\\ \hline
+			Softmax & Softmax& Softmax& Softmax& Softmax& Softmax& Softmax & Softmax\\ 
+			\bottomrule
+		\end{tabularx}
+	\end{adjustwidth}
+	\caption{Details Structure of Mobile based Models.
+SA stands for Soft-Attention, SA Module denotes whether that model use Soft-Attention Module.
+SE which stands for Squeeze-And-Excite shows whether that block has Squeeze-And-Excite.
+\label{detailed mobile model structure}}
+\end{table}
+
+The table 5, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
+All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module.
+The NasNetMObile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell.
 
@@
 The accuracy of all model is presented in the figure below:
+
 \begin{table}[h]
@@
 		\hline
-		InceptionResNetV2 & DenseNet201 & ResNet50 & VGG16 \\
+		InceptionResNetV2\cite{03358} & DenseNet201\cite{03358} & ResNet50\cite{03358} & VGG16\cite{bibid} \\
 		\hline
@@
 \end{table}
+
 According to the Table 3 and 4, it is clear that the model trained with augmented data has a higher accuracy than the model trained with metadata only.
@@
 As a results, augmented data model dose not classify well on all class as InceptionResNetV2 trained on augmented data have $0.29$ f1-score on class df while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way.
-\begin{table}[h]
-	\centering
-	\begin{tabular}{|c | c | c | c | c | c | c | c | c|} 
-		\hline
-		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
-		\hline
-		\thead{DenseNet201 +\\ Augmented Data} & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
-		\hline
-		\thead{InceptionResNetV2 +\\ Augmented Data} & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
-		\hline
-		\thead{Resnet50 +\\ Augmented Data} & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
-		\hline 	
-		\thead{VGG16 +\\ Augmented Data} & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
-		\hline		
-		\thead{DenseNet201 +\\Metadata and WeightLoss} & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
-		\hline
-		\thead{InceptionResNetV2 +\\Metadata and WeightLoss} & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
-		\hline
-		\thead{Resnet50 +\\Metadata and WeightLoss} & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
-		\hline
-		\thead{Resnet152 +\\Metadata and WeightLoss} & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
-		\hline
-		\thead{NasNetLarge +\\Metadata and WeightLoss} & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
-		\hline
-		\thead{MobileNetV2 +\\Metadata and WeightLoss} & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
-		\hline
-		\thead{MobileNetV3Large +\\Metadata and WeightLoss} & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
-		\hline
-		\thead{MobileNetV3Small +\\Metadata and WeightLoss} & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
-		\hline
-		\thead{NasNetMobile +\\Metadata and WeightLoss} & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
-		\hline
-	\end{tabular}
-	\caption{F1-Score of each class and the mean f1-score of each model}
-	\label{table:5}
-\end{table}
-
 However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
@@
 	\centering
-	\begin{tabular}{|l | c | c | c | c | c | c | c | c|} 
+	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
 		\hline
@@
 		\hline
-		\thead{DenseNet201 +\\ Augmented Data} & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
-		\hline
-		\thead{InceptionResNetV2 +\\ Augmented Data} & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
-		\hline
-		\thead{Resnet50 +\\ Augmented Data} & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
-		\hline 	
-		\thead{VGG16 +\\ Augmented Data} & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
-		\hline		
-		\thead{DenseNet201 +\\Metadata and WeightLoss} & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
-		\hline
-		\thead{InceptionResNetV2 +\\Metadata and WeightLoss} & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
-		\hline
-		\thead{Resnet50 +\\Metadata and WeightLoss} & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
-		\hline
-		\thead{Resnet152 +\\Metadata and WeightLoss} & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
-		\hline
-		\thead{NasNetLarge +\\Metadata and WeightLoss} & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
-		\hline
-		\thead{MobileNetV2 +\\Metadata and WeightLoss} & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
-		\hline
-		\thead{MobileNetV3Large +\\Metadata and WeightLoss} & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
-		\hline
-		\thead{MobileNetV3Small +\\Metadata and WeightLoss} & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
-		\hline
-		\thead{NasNetMobile +\\Metadata and WeightLoss} & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
+		DenseNet201 with Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
+		\hline
+		InceptionResNetV2 with Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
+		\hline
+		Resnet50 with Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
+		\hline 	
+		VGG16 with Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
+		\hline		
+		DenseNet201 with Metadata and WeightLoss & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
+		\hline
+		InceptionResNetV2 with Metadata and WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
+		\hline
+		Resnet50 with Metadata and WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
+		\hline
+		Resnet152 with Metadata and WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
+		\hline
+		NasNetLarge with Metadata and WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
+		\hline
+		MobileNetV2 with Metadata and WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
+		\hline
+		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
+		\hline
+		MobileNetV3Small with Metadata and WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
+		\hline
+		NasNetMobile with Metadata and WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
+		\hline
+	\end{tabular}
+	\caption{F1-Score of each class and the mean f1-score of each model}
+	\label{table:5}
+\end{table}
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
+		\hline
+		DenseNet201 with Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
+		\hline
+		InceptionResNetV2 with Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
+		\hline
+		Resnet50 with Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
+		\hline 	
+		VGG16 with Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
+		\hline		
+		DenseNet201 with Metadata and WeightLoss & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
+		\hline
+		InceptionResNetV2 with Metadata and WeightLoss & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
+		\hline
+		Resnet50 with Metadata and WeightLoss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
+		\hline
+		Resnet152 with Metadata and WeightLoss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
+		\hline
+		NasNetLarge with Metadata and WeightLoss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
+		\hline
+		MobileNetV2 with Metadata and WeightLoss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
+		\hline
+		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
+		\hline
+		MobileNetV3Small with Metadata and WeightLoss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
+		\hline
+		NasNetMobile with Metadata and WeightLoss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
 		\hline
@@
 
-This problem is also true with the recall score according to table 6.
+This problem is also true with the recall score according to table 7.
 DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has expected value of recall of $0.72$, $0.71$, $0.69$, $0.69$, respectively, while the combination of InceptionResNetV2, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
-
-As the results, metadata does improve the model performance by reducing the amount of data needed for achieving nearly the expected results.
+Therefore, metadata does improve the model performance by reducing the amount of data needed for achieving nearly the expected results.
 On the other hand, the reason why the model become much more balanced is the weighted loss function.
@@
 It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.
-\FloatBarrier
-\begin{table}[ht]
-	\centering	
-	\begin{tabular}{|l | c | c | c | c|} 
-		\hline
-		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\
-		\hline
-		Accuracy(avg) & 0.81 & 0.78 & 0.84 & \textbf{0.86}\\
-		\hline
-		Balanced Accuracy(avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
-		\hline
-		Precision(avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
-		\hline
-		F1-score(avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
-		\hline
-		Sensitivity(avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
-		\hline
-		Specificity(avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
-		\hline
-		ROC-AUC-score(avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
-		\hline
-	\end{tabular}
-	\caption{Deeper analyzing of mobile model}
-	\label{table:7}
-\end{table}
-\FloatBarrier
 Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.
@@
 The result of this experiment is illustrated in table 9.
-\FloatBarrier
+
 \begin{table}[ht]
 	\centering	
-	\begin{tabular}{|l | c |}
+	\begin{tabular}{|l | c | c | c | c|} 
+		\hline
+		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\
+		\hline
+		Accuracy(avg) & 0.81 & 0.78 & 0.84 & \textbf{0.86}\\
+		\hline
+		Balanced Accuracy(avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
+		\hline
+		Precision(avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
+		\hline
+		F1-score(avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
+		\hline
+		Sensitivity(avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
+		\hline
+		Specificity(avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
+		\hline
+		ROC-AUC-score(avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
+		\hline
+	\end{tabular}
+	\caption{Deeper analyzing of mobile model}
+	\label{table:7}
+\end{table}
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|p{11cm} | c |}
 		\hline
@@
 		\hline
-		MobileNetV3Large-Layer[:270] + Soft-Attention + Metadata & 0.71 \\
-		\hline
-		MobileNetV3Large-Layer[:266] + Soft-Attention + Metadata  & 0.73 \\
-		\hline
-		MobileNetV3Large-Layer[:260] + Soft-Attention + Metadata  & 0.77 \\
+		MobileNetV3Large + Soft-Attention + Metadata & 0.71 \\
+		\hline
+		MobileNetV3Large without Logits + Soft-Attention + Metadata  & 0.73 \\
+		\hline
+		MobileNetV3Large - Layer[:260] + Soft-Attention + Metadata  & 0.77 \\
 		\hline
@@
 \end{table}
-\FloatBarrier
+
 The Table 9 demonstrate that the Soft-Attention and the metadata have a good effect on the model.
@@
 The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^{th}$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of $0.86$ accuracy rate.
-\FloatBarrier
+
 \begin{table}[ht]
@@
 \end{table}
-\FloatBarrier
+
 \begin{table}[ht]
@@
 \end{table}
-\FloatBarrier
+
 \section{Conclusions}
@@
 
-\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
-Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.
-If the study did not report any data, you might add ``Not applicable'' here.}
+\dataavailability{The code and the data analysis report can be found here: \\https://github.com/KhoiDOO/Skin-Disease-Detection-HAM100000.git}
 
@@
 Katherine M. Li and Evelyn C. Li. Skin Lesion Analysis Towards Melanoma Detection via End-to-end Deep Learning of Convolutional Neural Networks. 
-{\em Journal Abbreviation} 
+{\em Sensors} 
 {\bf 2018}.
@@
 Xiaohan Xing and Yuenan Hou and  Hang Li and Yixuan Yuan and Hongsheng Li and Max Q.-H. Meng Categorical Relation-Preserving Contrastive Knowledge Distillation for Medical Image Classification. 
-{\em Journal Abbreviation} 
+{\em Springer Link} 
 {\bf 2021}.
@@
 \bibitem[Author2(year)]{03798}
-Rishu Garg and Saumil Maheshwari and Anupam Shukla Decision Support System for Detection and Classification of Skin Cancer using CNN. {\em Journal Abbreviation} {\bf 2019}.
+Rishu Garg and Saumil Maheshwari and Anupam Shukla Decision Support System for Detection and Classification of Skin Cancer using CNN. {\em Springer Link} {\bf 2019}.
 
@@
 Xuan Li and Yuchen Lu and Christian Desrosiers and Xue Liu Out-of-Distribution Detection for Skin Lesion Images with Deep Isolation Forest. 
-{\em Journal Abbreviation} 
+{\em Springer Link} 
 {\bf 2020}.
@@
 Amirreza Rezvantalab and Habib Safigholi and Somayeh Karimijeshni Dermatologist Level Dermoscopy Skin Cancer Classification Using Different Deep Learning Convolutional Neural Networks Algorithms. 
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2021}.
@@
 \bibitem[Author2(year)]{06612}
-Kyle Young and Gareth Booth and Becks Simpson and Reuben Dutton and Sally Shrapnel Dermatologist Level Dermoscopy Deep neural network or dermatologist?. {\em Journal Abbreviation} 
+Kyle Young and Gareth Booth and Becks Simpson and Reuben Dutton and Sally Shrapnel Dermatologist Level Dermoscopy Deep neural network or dermatologist?. {\em Nature} 
 {\bf 2021}.
@@
 Philipp Tschandl and Cliff Rosendahl and Harald Kittler The HAM10000 dataset, a large collection of multi-source dermatoscopic images of common pigmented skin lesions. 
-{\em Journal Abbreviation} 
+{\em Nature} 
 {\bf 2018}.
@@
 Michele Alberti and Angela Botros and Narayan Schuez and Rolf Ingold and Marcus Liwicki and Mathias Seuret Trainable Spectrally Initializable Matrix Transformations in Convolutional Neural Networks. 
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2019}.
@@
 \bibitem[Author2(year)]{09418}
-Hemanth Nadipineni Method to Classify Skin Lesions using Dermoscopic images. {\em Journal Abbreviation} 
+Hemanth Nadipineni Method to Classify Skin Lesions using Dermoscopic images. {\em Arxiv} 
 {\bf 2020}.
@@
 Nils Gessert and Maximilian Nielsen and Mohsin Shaikh and René Werner and Alexander Schlaefer Skin Lesion Classification Using Ensembles of Multi-Resolution EfficientNets with Meta Data. 
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2020}.
@@
 Pranav Poduval and Hrushikesh Loya and Amit Sethi Functional Space Variational Inference for Uncertainty Estimation in Computer Aided Diagnosis. 
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2020}.
@@
 Xu Single Model Deep Learning on Imbalanced Small Datasets for Skin Lesion Classification.
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2022}.
@@
 Manu Goyal and Thomas Knackstedt and Shaofeng Yan and Saeed Hassanpour Artificial Intelligence-Based Image Classification for Diagnosis of Skin Cancer: Challenges and Opportunities. 
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2020}.
@@
 \bibitem[Author2(year)]{03358}
-Soumyya Kanti Datta and  Mohammad Abuzar Shaikh and Sargur N. Srihari and Mingchen Gao Soft-Attention Improves Skin Cancer Classification Performance. {\em Journal Abbreviation} 
+Soumyya Kanti Datta and  Mohammad Abuzar Shaikh and Sargur N. Srihari and Mingchen Gao Soft-Attention Improves Skin Cancer Classification Performance. {\em SpringerLink} 
 {\bf 2021}.
@@
 Amirreza Mahbod and Philipp Tschandl and Georg Langs and Rupert Ecker and Isabella Ellinger The Effects of Skin Lesion Segmentation on the Performance of Dermatoscopic Image Classification
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2020}.
@@
 Yeong Chan Lee and Sang-Hyuk Jung and Hong-Hee Won WonDerM: Skin Lesion Classification with Fine-tuned Neural Networks
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2019}.
-
-\bibitem[Author2(year)]{04803}
-Zihang Dai and Hanxiao Liu and Quoc V. Le and Mingxing Tan: CoAtNet Marrying Convolution and Attention for All Data Sizes
-{\em Journal Abbreviation} 
-{\bf 2021}.
 
@@
 Gao Huang and Zhuang Liu and Laurens van der Maaten and Kilian Q. Weinberger: Densely Connected Convolutional Network
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2018}.
@@
 Mingxing Tan and Quoc V. Le EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2020}.
@@
 Christian Szegedy and Vincent Vanhoucke and Sergey Ioffe and Jonathon Shlens and Zbigniew Wojna Rethinking the Inception Architecture for Computer Vision
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2015}.
@@
 Howard and Menglong Zhu and Bo Chen and Dmitry Kalenichenko and Weijun Wang and Tobias Weyand and Marco Andreetto and Hartwig Adam MobileNets: Efficient Convolutional Neural Networks for Mobile Vision Applications
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2017}.
@@
 Mark Sandler and Andrew Howard and Menglong Zhu and Andrey Zhmoginov and Liang-Chieh Chen MobileNetV2: Inverted Residuals and Linear Bottlenecks
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2018}.
@@
 Le and Hartwig Adam Searching for MobileNetV3
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2019}.
@@
 Kaiming He and Xiangyu Zhang and Shaoqing Ren and Jian Sun Deep Residual Learning for Image Recognition
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2015}.
@@
 Kaiming He and Xiangyu Zhang and Shaoqing Ren and Jian Sun Identity Mappings in Deep Residual Networks
-{\em Journal Abbreviation} 
+{\em Springer Link} 
 {\bf 2016}.
@@
 Karen Simonyan and Andrew Zisserman Very Deep Convolutional Networks for Large-Scale Image Recognition
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2016}.
@@
 François Chollet Xception: Deep Learning with Depthwise Separable Convolutions
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2017}.
@@
 Diederik P. Kingma, Jimmy Ba Adam: A Method for Stochastic Optimization
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2017}.
@@
 Kelvin Xu and Jimmy Ba and Ryan Kiros and Kyunghyun Cho and Aaron Courville and Ruslan Salakhutdinov and Richard Zemel and Yoshua Bengio Show, Attend and Tell: Neural Image Caption Generation with Visual Attention 2020 17th International Conference on Frontiers in Handwriting Recognition
-{\em Journal Abbreviation} 
+{\em PMLR} 
 {\bf 2016}.
+
+\bibitem[Author2(year)]{202017}
+Mohammad Abuzar Shaikh and Tiehang Duan and Mihir Chauhan and Sargur N. Srihari. 2020 17th International Conference on Frontiers in Handwriting Recognition
+{\em IEEE Xplore} 
+{\bf 2020}.
 
@@
 Attention-Based Deep Neural Networks for Detection of Cancerous and Precancerous Esophagus Tissue on Histopathological Slides
-{\em Journal Abbreviation} 
+{\em Jama Network} 
 {\bf 2020}.
@@
 Mohammad Abuzar Shaikh and Tiehang Duan and Mihir Chauhan and Sargur N. Srihari. 2020 17th International Conference on Frontiers in Handwriting Recognition
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2019}.
@@
 Srihari. YAOSHIANG HO AND SAMUEL WOOKEY The Real-World-Weight Cross-Entropy Loss Function: Modeling the Costs of Mislabeling 
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2020}.
@@
 Barret Zoph, Vijay Vasudevan, Jonathon Shlens, Quoc V. Le Learning Transferable Architectures for Scalable Image Recognition 
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2017}.
@@
 Abien Fred Agarap Deep Learning using Rectified Linear Units (ReLU) 
-{\em Journal Abbreviation} 
+{\em Arxiv} 
 {\bf 2019}.
@@
 Jie Hu, Li Shen, Samuel Albanie, Gang Sun, Enhua Wu Squeeze-and-Excitation Networks 
-{\em Journal Abbreviation} 
+{\em IEEE Xplore} 
 {\bf 2019}.
@@
 \bibitem[Author2(year)]{04552v2}
-Improved Regularization of Convolutional Neural Networks with Cutout Improved Regularization of Convolutional Neural Networks with Cutout 
-{\em Journal Abbreviation} 
+Terrance DeVries, Graham W. Taylor Improved Regularization of Convolutional Neural Networks with Cutout 
+{\em Arxiv} 
 {\bf 2017}.
+
+\bibitem[Author2(year)]{07261}
+Christian Szegedy, Sergey Ioffe, Vincent Vanhoucke, Alex Alemi Inception-v4, Inception-ResNet and the Impact of Residual Connections on Learning
+{\em AAAI Conference} 
+{\bf 2018}.
 

### 2022-07-09 MDPI/Sensor Paper/template.tex
Update Ver 6 of research paper
- Update the Structure of all Models
- Remove Strategy of MBNV3
- Update explanation for all tables and figures

@@
 \Author{Khoi Do Hoang$^{
-		1,\dagger,%\ddagger
+		2,\dagger,%\ddagger
 	}$\orcidA{}*}
@@
 \address{
-$^{1}$ \quad Viet Dung Nguyen; dung.nguyenviet1@hust.edu.vn\\
-$^{2}$ \quad Khoi Do Hoang; khoi.dh200332@sis.hust.edu.vn}
+$^{1}$ \quad Lecturer: Viet Dung Nguyen; dung.nguyenviet1@hust.edu.vn\\
+$^{2}$ \quad Author: Khoi Do Hoang; khoi.dh200332@sis.hust.edu.vn}
 
@@
 In addition, a new loss function	that takes into account the imbalance of the data is also proposed.
-Experimental results on dataset HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published indexes.
+Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published indexes.
 Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of floors is 4 times less, it achieves 86 percent accuracy and 30 times faster diagnosis.}
@@
 	\end{tabular}
-	\caption{Related Works Summary}
-	\label{table:0}
+	\caption{Related Works Summary.
+This table is a summary of the approach to skin lesion classification and segmentation.
+The first column illustrate the cite to the paper research.
+Column 2 shows a brief summary of the method that is stated in the associated paper.}
+	\label{table:related-work-summary}
 \end{table}
@@
 \subsubsection{Image Data}
-The dataset used in this paper is the HAM10000 dataset published by Havard University Dataverse\cite{10417}.
-There are total 7 classes in this dataset containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
-The distribution of the dataset is shown in the table below:
-\FloatBarrier
-\begin{table}[ht]
+The data set used in this paper is the HAM10000 data set published by Havard University Dataverse\cite{10417}.
+There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
+The distribution of the data set is shown in the table below:
+
+\begin{table}[H]
 	\centering
@@
 	\end{tabular}
-	\caption{Data Distribution in HAM10000}
-	\label{table:1}
+	\caption{Data Distribution in HAM10000. This table illustrate the distribution of all class in the data set. The detail name of the skin disease in the data set can be found at the Abbreviations}
+	\label{table:data-distribution}
 \end{table}
-\FloatBarrier
-\begin{figure}[h]
+
+\begin{figure}[H]
 	\centering
@@
 	\caption{Example image of each class}
-	\label{fig:dataexample}
+	\label{fig:data-sample}
 \end{figure}
-\FloatBarrier
+
 More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL).
@@
 In this paper, instead of augmenting data, metadata is used.
-The way of processing metadata is discuss in MetaData section.
-Images in this dataset has the type of $RGB$ and shape of (450, 600).
+The way of processing metadata is discussed in MetaData section.
+Images in this data set has the type of $RGB$ and shape of (450, 600).
 However, Each backbone need the different input size of image as well as the range of pixel value.
-DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet dataset.
-In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet dataset, without scaling.
+DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set.
+In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling.
 InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$.
 Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.
+
 \subsubsection{Metadata}
-The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position.
+The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position.
 During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples.
@@
 The Input schema is described as follow:
-\FloatBarrier
-\begin{figure}[h]
+
+\begin{figure}[H]
 	\centering
@@
 \end{figure}
-\FloatBarrier
-Image data, on the other hand after being preprocessed, is fed directly into the backbone model. 
+
 \subsubsection{Soft-Attention}
@@
 Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.
-\FloatBarrier
-\begin{figure}[h]
+
+\begin{figure}[H]
 	\centering
@@
 	\caption{Soft-Attention Module}
-	\label{fig:softattention}
+	\label{fig:soft-attention}
 \end{figure}
-\FloatBarrier
+
 In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
-\FloatBarrier
-\begin{figure}[h]
+
+\begin{figure}[H]
 	\centering
@@
 	\caption{Soft-Attention Module}
-	\label{fig:softattentionblock}
+	\label{fig:soft-attention-block}
 \end{figure}
-\FloatBarrier
+
+After feeding into ReLU function layer, the feature map is processed in two paths.
+The first path is the 2-dimensional Max Pooling.
+In the second path, the feature map, on the other hand is fed into the Soft-Attention Layer before the 2-dimensional Max Pooling.
+After all, these two paths are then concatenated, fed into a ReLU layer, and a Dropout with the probability of $0.5$.
 \subsubsection{Backbone Model Architecture}
@@
 On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.
-\FloatBarrier
-\begin{table}[ht]
+
+\begin{table}[H]
 	\centering
@@
 	\end{tabular}
-	\caption{Size and Parameters and Depth of backbone model used in this paper}
-	\label{table:2}
+	\caption{Size and Parameters and Depth of backbone model used in this paper.
+This table summarizes the properties of the backbone models.
+The size column illustrates how many space need to store the model in megabyte.
+The parameters column demonstrate the number of parameters in the associated model.
+The last column, depth show the number of hidden layers in that model.
+Parameters and Depth are two crucial element to evaluate the optimized model stated in the Objective section.}
+	\label{table:model-summary}
 \end{table}
-\FloatBarrier
 
@@
 It is described in the figure below:
-\FloatBarrier
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.7\linewidth]{Definitions/MainModel - Model Form}
-	\caption{Overall Model Architecture}
-	\label{fig:mainmodel}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\linewidth]{Definitions/MainModel - Model Form}
+	\caption{Overall Mobile-based Model Architecture}
+	\label{fig:main-model}
 \end{figure}
-\FloatBarrier
+
+The figure 6 illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research.
+In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module.
+Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module.
+InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module.
+Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/Model Structure}
+	\caption{Overall Model Architecture.
+This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge.
+The detail structure and information can be found at the Apendix A}
+	\label{fig:model-structure}
+\end{figure}
+The figure 7, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
+All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module.
+The NasNetMobile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
+	\caption{Overall Mobile-based Model Architecture.
+This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
+The detail structure and information can be found at the Apendix B}
+	\label{fig:mobile-model-structure}
+\end{figure}
+
+\subsection{Loss Function}
+The loss function used in this paper is categorical cross-entropy.
+Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$.
+Let $N$, and $C$ is the number of training examples and number of class respectively.
+The categorical cross-entropy loss is presented as:
+\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
+where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$.
+Since the data set face the imbalanced problem then I applied the class weight for the loss.
+This formula below is used to calculate the class weight:
+\[W = N \odot D\]
+\[D = \begin{bmatrix}
+	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
+\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
+	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
+\end{bmatrix}\]
+where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$. 
+\subsection{Evaluation Metrics}
+\begin{figure}[!htb]
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
+		\caption{Confusion Matrix}\label{fig:confusion-matrix}
+	\end{minipage}\hfill
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=.7\linewidth]{Definitions/AUC}
+		\caption{Area Under the Curve}\label{fig:AUC}
+	\end{minipage}
+\end{figure}
+In this paper, the model is evaluated by using the confusion matrix and related metrics.
+The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class.
+Consider a confusion matrix $A$ with $C$ number of class.
+Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively.
+\[
+A = \begin{bmatrix}
+	a_{11} & a_{12} & \dots & a_{1j} \\
+	a_{21} & a_{22} & \dots & a_{2j} \\
+	\vdots & \vdots	&  & \vdots\\
+	a_{i1} & a_{i2} & \dots & a_{ij} 
+\end{bmatrix}
+\]
+
+The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$.
+The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
+\[
+FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
+\]
+\[
+TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
+	TN_1 & TN_2 & \dots & TN_c
+\end{bmatrix}
+\]
+Then, the model is evaluated by the following metrics:
+\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
+\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
+\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
+The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
+\subsection{Traning}
+Before training, the data set is split into three sub datasets including training, validation, and testing.
+In this paper, the graphic card that is used to train is Nvidia RTX TitanV.
+In order to make the comparison fair, all the model in this paper is trained with Adam Optimizer\cite{6980}.
+The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$, the epsilon argument of the optimizer is set to $0.1$.
+On the other hand, Early Stopping is also set up, if the accuracy of validation set dose not increase after 25 epochs, the training will stop.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+The accuracy of all model is presented in the figure below:
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{| c | c | c | c |}
+		\hline
+		InceptionResNetV2 & DenseNet201 & ResNet50 & VGG16 \\
+		\hline
+		0.93 & 0.91 & 0.92 & 0.88\\
+		\hline
+	\end{tabular}
+	\caption{Accuracy of the model with augmented data}
+	\label{table:Acc-Augment-Model}
+\end{table}
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{| c | c | c | c | c |}
+		\hline
+		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
+		\hline
+		0.89 & 0.89 & 0.70 & 0.57 & 0.81\\
+		\hline
+	\end{tabular}
+\end{table}
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{| c | c | c | c |}
+		\hline
+		MobileNetV3Large & MobileNetV3Small & NasNetLarge & NasNetMobile\\
+		0.84 & 0.78 & 0.86 & 0.86\\
+		\hline
+	\end{tabular}
+	\caption{Accuracy of the model with metadata}
+	\label{table:Acc-Metadata-Model}
+\end{table}
+
+According to the Table 3 and 4, it is clear that the model trained with augmented data has a higher accuracy than the model trained with metadata only.
+While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.93$ and $0.91$ respectively, their training with metadata has both the accuracy of $0.89$.
+Furthermore, Resnet50 trained with augmented data has the accuracy that outperform the Resnet50 and is twice as high as Resnet152 trained with metadata.
+On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively.
+This term will be discussed later on.
+Since, the model trained with augmented data have high accuracy, when their f1-score and the recall score of models are analyzed, it turns out that models trained with augmented data have imbalanced f1-scores according to table 5.
+As a results, augmented data model dose not classify well on all class as InceptionResNetV2 trained on augmented data have $0.29$ f1-score on class df while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way.
+However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
+The others still face the imbalanced term.
+Since this data set is not balanced, therefore using augmented data can make the model more  bias to the class which has larger sample.
+Using the metadata, though still make the model bias, it dose contributes to the improvement of  the performance of the model.
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
+		\hline
+		DenseNet201 with Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
+		\hline
+		InceptionResNetV2 with Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
+		\hline
+		Resnet50 with Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
+		\hline 	
+		VGG16 with Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
+		\hline		
+		DenseNet201 with Metadata and WeightLoss & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
+		\hline
+		InceptionResNetV2 with Metadata and WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
+		\hline
+		Resnet50 with Metadata and WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
+		\hline
+		Resnet152 with Metadata and WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
+		\hline
+		NasNetLarge with Metadata and WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
+		\hline
+		MobileNetV2 with Metadata and WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
+		\hline
+		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
+		\hline
+		MobileNetV3Small with Metadata and WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
+		\hline
+		NasNetMobile with Metadata and WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
+		\hline
+	\end{tabular}
+	\caption{F1-Score of each class and the mean f1-score of each model}
+	\label{table:F1-score-summary}
+\end{table}
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
+		\hline
+		DenseNet201 with Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
+		\hline
+		InceptionResNetV2 with Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
+		\hline
+		Resnet50 with Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
+		\hline 	
+		VGG16 with Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
+		\hline		
+		DenseNet201 with Metadata and WeightLoss & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
+		\hline
+		InceptionResNetV2 with Metadata and WeightLoss & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
+		\hline
+		Resnet50 with Metadata and WeightLoss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
+		\hline
+		Resnet152 with Metadata and WeightLoss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
+		\hline
+		NasNetLarge with Metadata and WeightLoss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
+		\hline
+		MobileNetV2 with Metadata and WeightLoss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
+		\hline
+		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
+		\hline
+		MobileNetV3Small with Metadata and WeightLoss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
+		\hline
+		NasNetMobile with Metadata and WeightLoss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
+		\hline
+	\end{tabular}
+	\caption{Recall score of each class and the mean recall score of each model}
+	\label{table:recall-score-summary}
+\end{table}
+
+This problem is also true with the recall score according to table 7.
+DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has expected value of recall of $0.72$, $0.71$, $0.69$, $0.69$, respectively, while the combination of InceptionResNetV2, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
+Therefore, metadata does improve the model performance by reducing the amount of data needed for achieving nearly the expected results.
+On the other hand, the reason why the model become much more balanced is the weighted loss function.
+Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class.
+DenseNet201, InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$.
+$0.82$, respectively, as opposed to their training in akiec without weighted loss function.
+MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.
+
+\begin{table}[H]
+	\centering	
+	\begin{tabular}{|l | c | c | c | c|} 
+		\hline
+		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\
+		\hline
+		Accuracy(avg) & 0.81 & 0.78 & 0.86 & \textbf{0.86}\\
+		\hline
+		Balanced Accuracy(avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
+		\hline
+		Precision(avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
+		\hline
+		F1-score(avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
+		\hline
+		Sensitivity(avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
+		\hline
+		Specificity(avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
+		\hline
+		ROC-AUC-score(avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
+		\hline
+	\end{tabular}
+	\caption{Deeper analyzing of mobile model.
+This table illustrate the other indicators of the four mobile-based models including MobileNetV2, MobileNetV3Small, MobileNetV3Large, NasNetMobile.
+The indicators are Accuracy, Balanced Accuracy, Precision, F1-score, Sensitivity, Specificity, and ROC - AUC score.
+All of them are average indicator}
+	\label{table:mobile-performance}
+\end{table}
+
+Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
+The table 8 illustrates the deeper analyzing of the three models.
+It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.
+Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{| l | c | c | c |}
+		\hline
+		Model & MobileNetV3Large & DenseNet201 & InceptionResnetV2\\
+		\hline
+		No. Parameters & \textbf{5.5M} & 20.2M & 55.9M\\
+		\hline
+		Depth & \textbf{118} & 402 & 449\\
+		\hline
+		Accuracy & 0.86 & 0.89 & 0.90\\
+		\hline
+		Time Prediction(s/epochs) & \textbf{116} & 1000 & 3500 \\
+		\hline
+	\end{tabular}
+	\caption{How Performance of MobileNetV3Large be optimized}
+	\label{table:optimized-performance-mobile-model}
+\end{table}
+
+The table 9 shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others.
+In detail, MobileNetV3Large whose the number of parameters is 5.5 millions which is four and ten times less than DenseNet201 and InceptionResNetV2, respectively.
+The depth of MobileNetV3Large, on the other hand, is four times less than DenseNet201, InceptionResNetV2 which are 118 hidden layers as opposed to 402, 449 of DenseNet201 and InceptionResNetV2, separately.
+Although, the MobileNetV3Larege only achieve the accuracy of 0.86 the time need for prediction is 10 and 30 times less than the other opponents.
+If the MobileNetV3Large need a harder process of parameter hyper-tuning to achieve a better result, which is also the future target of this research.
+
+\section{Conclusions}
+In this paper, my objective is to analyze the effect of metadata on the performance of model as well as identifying whether metadata can make the model less imbalanced or not.
+On the other hand, I also try to construct an optimized and balanced model that can be used on mobile phone or electronic devices.
+The experiment shown that metadata improve the model performance, the factor that make the model much more imbalanced is the augmented data.
+This problem can be solve quite absolutely by using aforementioned weighted loss function.
+Using weighted loss function make the expected value of model f1-score increase.
+At the end of the experiment, mobile model is found that can achieve great performance without either the large number of parameters or depth.
+
+\vspace{6pt}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
+
+% Only for the journal Methods and Protocols:
+% If you wish to submit a video article, please do so with any other supplementary material.
+% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
+A supporting video article is available at doi: link.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{In this paper, I am the only author, therefore I need to do all things including research, implementation, analyze data, writing draft resolution}
+
+\funding{This research received no external funding}
+
+\institutionalreview{Not applicable}
+
+\informedconsent{Not applicable}
+
+\dataavailability{The code and the data analysis report can be found here: \\https://github.com/KhoiDOO/Skin-Disease-Detection-HAM100000.git}
+
+\acknowledgments{I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project.
+He gave a chance to use High GPU computing computer for AI Training.
+Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.}
+
+\conflictsofinterest{The authors declare no conflict of interest.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Optional
+\sampleavailability{Samples of the compounds ... are available from the authors.}
+
+%% Only for journal Encyclopedia
+%\entrylink{The Link to this entry published on the encyclopedia platform.}
+
+\abbreviations{Abbreviations}{
+The following abbreviations are used in this manuscript:\\
+
+\noindent 
+\begin{tabular}{@{}ll}
+CAD & Computer aided diagnosis\\
+AI & Artificial Intelligence\\
+AKIEC & Actinic keratoses and intraepithelial carcinoma or Bowen's disease\\
+BCC & Basal Cell Carcinoma\\
+BKL & Benign Keratosis-like Lesions\\
+DF & Dermatofibroma\\
+MEL & Melanoma\\
+NV & Melanocytic Nevi\\
+VASC & Vascular Lesions\\
+HISTO & Histopathology\\
+FOLLOWUP & Follow-up examination\\
+CONSENSUS & Expert Consensus\\
+CONFOCAL & Confocal Microscopy\\
+RGB & Red Green Blue\\
+BGR & Blue Green Red\\
+TP & True Positives\\
+FN & False Negatives\\
+TN & True Negatives\\
+FP & False Positives\\
+Sens & Sensitivity\\
+Spec & Specificity\\
+AUC & Area Under the Curve\\
+ROC & Receiver Operating Curve\\
+\end{tabular}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Optional
+
+%\appendixtitles{no} 
+\appendixstart
+\appendix
+\section[\appendixname~\thesection]{Detailed Model Structure}
 
@@
 GAP stands for Global Average Pooling.
-FC stands for Fully-Connected Layer\label{detailed structure model}}
+FC stands for Fully-Connected Layer\label{appendix-table:detailed structure model}}
 \end{table}
 
-The table 4 and table 5 illustrate the detailed structure of the models in original form and its combination with Soft-Attention which is used in this research.
-In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module.
-Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module.
-InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module.
-Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.
+\section[\appendixname~\thesection]{Detailed Mobile-based Model Structure}
 
@@
 SE which stands for Squeeze-And-Excite shows whether that block has Squeeze-And-Excite.
-\label{detailed mobile model structure}}
+\label{appendix-table:detailed mobile model structure}}
 \end{table}
-
-The table 5, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
-All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module.
-The NasNetMObile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell.
-
-\subsection{Loss Function}
-The loss function used in this paper is categorical cross-entropy.
-Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$.
-Let $N$, and $C$ is the number of training examples and number of class respectively.
-The categorical cross-entropy loss is presented as:
-\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
-where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$.
-Since the dataset face the imbalanced problem then I applied the class weight for the loss.
-This formula below is used to calculate the class weight:
-\[W = N \odot D\]
-\[D = \begin{bmatrix}
-	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
-\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
-	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
-\end{bmatrix}\]
-where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$. 
-\subsection{Evaluation Metrics}
-\begin{figure}[!htb]
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
-		\caption{Confusion Matrix}\label{Fig:Data1}
-	\end{minipage}\hfill
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=.7\linewidth]{Definitions/AUC}
-		\caption{Area Under the Curve}\label{Fig:Data2}
-	\end{minipage}
-\end{figure}
-In this paper, the model is evaluated by using the confusion matrix and related metrics.
-The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class.
-Consider a confusion matrix $A$ with $C$ number of class.
-Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively.
-\[
-A = \begin{bmatrix}
-	a_{11} & a_{12} & \dots & a_{1j} \\
-	a_{21} & a_{22} & \dots & a_{2j} \\
-	\vdots & \vdots	&  & \vdots\\
-	a_{i1} & a_{i2} & \dots & a_{ij} 
-\end{bmatrix}
-\]
-
-The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$.
-The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
-\[
-FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
-\]
-\[
-TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
-	TN_1 & TN_2 & \dots & TN_c
-\end{bmatrix}
-\]
-Then, the model is evaluated by the following metrics:
-\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
-\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
-\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
-The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
-\subsection{Traning}
-Before training, the dataset is split into three sub datasets including training, validation, and testing. In this paper, the graphic card that is used to train is Nvidia RTX TitanV.\\
-All the model in this paper is trained with Adam Optimizer\cite{6980}.
-The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$, the epsilon argument of the optimizer is set to $0.1$.
-On the other hand, Early Stopping is also set up, if the accuracy of validation set dose not increase after 25 epochs, the training will stop.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-The accuracy of all model is presented in the figure below:
-
-\begin{table}[h]
-	\centering
-	\begin{tabular}{| c | c | c | c |}
-		\hline
-		InceptionResNetV2\cite{03358} & DenseNet201\cite{03358} & ResNet50\cite{03358} & VGG16\cite{bibid} \\
-		\hline
-		0.93 & 0.91 & 0.92 & 0.88\\
-		\hline
-	\end{tabular}
-	\caption{Accuracy of the model with augmented data}
-	\label{table:3}
-\end{table}
-\begin{table}[h]
-	\centering
-	\begin{tabular}{| c | c | c | c | c |}
-		\hline
-		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
-		\hline
-		0.89 & 0.89 & 0.70 & 0.57 & 0.81\\
-		\hline
-	\end{tabular}
-\end{table}
-\begin{table}[h]
-	\centering
-	\begin{tabular}{| c | c | c | c |}
-		\hline
-		MobileNetV3Large & MobileNetV3Small & NasNetLarge & NasNetMobile\\
-		0.84 & 0.78 & 0.86 & 0.86\\
-		\hline
-	\end{tabular}
-	\caption{Accuracy of the model with metadata}
-	\label{table:4}
-\end{table}
-
-According to the Table 3 and 4, it is clear that the model trained with augmented data has a higher accuracy than the model trained with metadata only.
-While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.93$ and $0.91$ respectively, their training with metadata has both the accuracy of $0.89$.
-Furthermore, Resnet50 trained with augmented data has the accuracy that outperform the Resnet50 and is twice as high as Resnet152 trained with metadata.
-On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively.
-This term will be discussed later on.
-Since, the model trained with augmented data have high accuracy, when their f1-score and the recall score of models are analyzed, it turns out that models trained with augmented data have imbalanced f1-scores according to table 5.
-As a results, augmented data model dose not classify well on all class as InceptionResNetV2 trained on augmented data have $0.29$ f1-score on class df while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way.
-However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
-The others still face the imbalanced term.
-Since this dataset is not balanced, therefore using augmented data can make the model more  bias to the class which has larger sample.
-Using the metadata, though still make the model bias, it dose contributes to the improvement of  the performance of the model.
-
-\begin{table}[h]
-	\centering
-	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
-		\hline
-		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
-		\hline
-		DenseNet201 with Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
-		\hline
-		InceptionResNetV2 with Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
-		\hline
-		Resnet50 with Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
-		\hline 	
-		VGG16 with Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
-		\hline		
-		DenseNet201 with Metadata and WeightLoss & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
-		\hline
-		InceptionResNetV2 with Metadata and WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
-		\hline
-		Resnet50 with Metadata and WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
-		\hline
-		Resnet152 with Metadata and WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
-		\hline
-		NasNetLarge with Metadata and WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
-		\hline
-		MobileNetV2 with Metadata and WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
-		\hline
-		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
-		\hline
-		MobileNetV3Small with Metadata and WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
-		\hline
-		NasNetMobile with Metadata and WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
-		\hline
-	\end{tabular}
-	\caption{F1-Score of each class and the mean f1-score of each model}
-	\label{table:5}
-\end{table}
-
-\begin{table}[h]
-	\centering
-	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
-		\hline
-		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
-		\hline
-		DenseNet201 with Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
-		\hline
-		InceptionResNetV2 with Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
-		\hline
-		Resnet50 with Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
-		\hline 	
-		VGG16 with Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
-		\hline		
-		DenseNet201 with Metadata and WeightLoss & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
-		\hline
-		InceptionResNetV2 with Metadata and WeightLoss & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
-		\hline
-		Resnet50 with Metadata and WeightLoss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
-		\hline
-		Resnet152 with Metadata and WeightLoss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
-		\hline
-		NasNetLarge with Metadata and WeightLoss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
-		\hline
-		MobileNetV2 with Metadata and WeightLoss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
-		\hline
-		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
-		\hline
-		MobileNetV3Small with Metadata and WeightLoss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
-		\hline
-		NasNetMobile with Metadata and WeightLoss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
-		\hline
-	\end{tabular}
-	\caption{Recall score of each class and the mean recall score of each model}
-	\label{table:6}
-\end{table}
-
-This problem is also true with the recall score according to table 7.
-DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has expected value of recall of $0.72$, $0.71$, $0.69$, $0.69$, respectively, while the combination of InceptionResNetV2, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
-Therefore, metadata does improve the model performance by reducing the amount of data needed for achieving nearly the expected results.
-On the other hand, the reason why the model become much more balanced is the weighted loss function.
-Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class.
-Therefore, DenseNet201, InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$.
-$0.82$, respectively, as opposed to their training in akiec without weighted loss function.
-MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile whose standard deviation is less than $0.15$ outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.
-
-Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
-The table 8 illustrates the deeper analyzing of the three models.
-It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.
-Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.
-Therefore, at the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model.
-The result of this experiment is illustrated in table 9.
-
-\begin{table}[ht]
-	\centering	
-	\begin{tabular}{|l | c | c | c | c|} 
-		\hline
-		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\
-		\hline
-		Accuracy(avg) & 0.81 & 0.78 & 0.84 & \textbf{0.86}\\
-		\hline
-		Balanced Accuracy(avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
-		\hline
-		Precision(avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
-		\hline
-		F1-score(avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
-		\hline
-		Sensitivity(avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
-		\hline
-		Specificity(avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
-		\hline
-		ROC-AUC-score(avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
-		\hline
-	\end{tabular}
-	\caption{Deeper analyzing of mobile model}
-	\label{table:7}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{|p{11cm} | c |}
-		\hline
-		Model & Accuracy\\
-		\hline
-		MobileNetV3Large + Soft-Attention + Metadata & 0.71 \\
-		\hline
-		MobileNetV3Large without Logits + Soft-Attention + Metadata  & 0.73 \\
-		\hline
-		MobileNetV3Large - Layer[:260] + Soft-Attention + Metadata  & 0.77 \\
-		\hline
-		MobileNetV3Large-Layer[:251] + Soft-Attention + Metadata  & 0.79 \\
-		\hline
-		MobileNetV3Large-Layer[:246] + Soft-Attention + Metadata  & 0.84 \\
-		\hline
-		MobileNetV3Large-Layer[:246] + Soft-Attention + Dense(512) + Metadata & 0.85 \\
-		\hline
-		MobileNetV3Large-Layer[:240] + Soft-Attention + Metadata  & \textbf{0.86}\\
-		\hline
-		MobileNetV3Large-Layer[:230] + Soft-Attention + Metadata  & 0.84 \\
-		\hline
-		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 
-		\hline
-		MobileNetV3Large & 0.85 \\ 
-		\hline
-	\end{tabular}
-	\caption{Deeper analyzing of MobileNetV3Large Model}
-	\label{table:8}
-\end{table}
-
-The Table 9 demonstrate that the Soft-Attention and the metadata have a good effect on the model.
-Otherwise, Adding a dense layer does not increase the model performance.
-The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^{th}$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of $0.86$ accuracy rate.
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{| l | c |}
-		\hline
-		Accuracy & 0.86\\
-		\hline
-		Precision(avg) & 0.86\\
-		\hline
-		F1-score(avg) & 0.86\\
-		\hline
-		Sensitivity(avg) & 0.86\\
-		\hline
-		Specificity(avg) & 0.95\\
-		\hline
-		ROC AUC Score(avg) & 0.98\\
-		\hline
-	\end{tabular}
-	\caption{Performance of MobileNetV3Large}
-	\label{table:9}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{| l | c | c | c |}
-		\hline
-		Model & MobileNetV3Large & DenseNet201 & InceptionResnetV2\\
-		\hline
-		No. Parameters & \textbf{5.5M} & 20.2M & 55.9M\\
-		\hline
-		Depth & \textbf{118} & 402 & 449\\
-		\hline
-		Accuracy & 0.86 & 0.89 & 0.90\\
-		\hline
-		Time Prediction(s/epochs) & \textbf{116} & 1000 & 3500 \\
-		\hline
-	\end{tabular}
-	\caption{How Performance of MobileNetV3Large be optimized}
-	\label{table:11}
-\end{table}
-
-\section{Conclusions}
-In this paper, my objective is to analyze the effect of metadata on the performance of model as well as identifying whether metadata can make the model less imbalanced or not.
-On the other hand, I also try to construct an optimized and balanced model that can be used on mobile phone or electronic devices.
-The experiment shown that metadata improve the model performance, the factor that make the model much more imbalanced is the augmented data.
-This problem can be solve quite absolutely by using aforementioned weighted loss function.
-Using weighted loss function make the expected value of model f1-score increase.
-At the end of the experiment, mobile model is found that can achieve great performance without either the large number of parameters or depth.
-
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
-
-% Only for the journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
-A supporting video article is available at doi: link.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{In this paper, I am the only author, therefore I need to do all things including research, implementation, analyze data, writing draft resolution}
-
-\funding{This research received no external funding}
-
-\institutionalreview{Not applicable}
-
-\informedconsent{Not applicable}
-
-\dataavailability{The code and the data analysis report can be found here: \\https://github.com/KhoiDOO/Skin-Disease-Detection-HAM100000.git}
-
-\acknowledgments{I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project.
-He gave a chance to use High GPU computing computer for AI Training.
-Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.}
-
-\conflictsofinterest{The authors declare no conflict of interest.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\sampleavailability{Samples of the compounds ... are available from the authors.}
-
-%% Only for journal Encyclopedia
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-
-\abbreviations{Abbreviations}{
-The following abbreviations are used in this manuscript:\\
-
-\noindent 
-\begin{tabular}{@{}ll}
-CAD & Computer aided diagnosis\\
-AI & Artificial Intelligence\\
-AKIEC & Actinic keratoses and intraepithelial carcinoma or Bowen's disease\\
-BCC & Basal Cell Carcinoma\\
-BKL & Benign Keratosis-like Lesions\\
-DF & Dermatofibroma\\
-MEL & Melanoma\\
-NV & Melanocytic Nevi\\
-VASC & Vascular Lesions\\
-HISTO & Histopathology\\
-FOLLOWUP & Follow-up examination\\
-CONSENSUS & Expert Consensus\\
-CONFOCAL & Confocal Microscopy\\
-RGB & Red Green Blue\\
-BGR & Blue Green Red\\
-TP & True Positives\\
-FN & False Negatives\\
-TN & True Negatives\\
-FP & False Positives\\
-Sens & Sensitivity\\
-Spec & Specificity\\
-AUC & Area Under the Curve\\
-ROC & Receiver Operating Curve\\
-\end{tabular}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\begin{comment}
-	\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
-If the appendix sections contain a heading then change the argument to "yes".
-	\appendixstart
-	\appendix
-	\section[\appendixname~\thesection]{}
-	\subsection[\appendixname~\thesubsection]{}
-	The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
-
-	\begin{table}[H] 
-	\caption{This is a table caption.\label{tab5}}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{CCC}
-	\toprule
-	\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-	\midrule
-	Entry 1		& Data			& Data\\
-	Entry 2		& Data			& Data\\
-	\bottomrule
-	%\end{tabularx}
-	%\end{table}
-
-	\section[\appendixname~\thesection]{}
-	All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
-\end{comment}
 
@@
 \bibitem[Author2(year)]{10417}
-Philipp Tschandl and Cliff Rosendahl and Harald Kittler The HAM10000 dataset, a large collection of multi-source dermatoscopic images of common pigmented skin lesions. 
+Philipp Tschandl and Cliff Rosendahl and Harald Kittler The HAM10000 data set, a large collection of multi-source dermatoscopic images of common pigmented skin lesions. 
 {\em Nature} 

### 2022-08-11 MDPI/Sensor Paper/template.tex
Update Research Paper

@@
 
-In the previous paper\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images.
-Since, this data is imbalanced, using augmented data may cause the problem of well classify on the majority of class.
+In the previous research\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images.
+Since, this data is imbalanced, using augmented data may cause the problem of well classify on the classes almostly taking the number of samples.
 In this paper, instead of augmenting data, metadata is used.
@@
 \subsubsection{Metadata}
-The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position.
+The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position as well as the test data set containing 857 images.
 During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples.

### 2022-08-13 MDPI/Sensor Paper/template.tex

@@
 The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$, the epsilon argument of the optimizer is set to $0.1$.
-On the other hand, Early Stopping is also set up, if the accuracy of validation set dose not increase after 25 epochs, the training will stop.
+On the other hand, Early Stopping is also set up, if the accuracy of validation set does not increase after 25 epochs, the training will stop.
 
@@
 		\hline
-		0.93 & 0.91 & 0.92 & 0.88\\
+		0.79 & 0.84 & 0.76 & 0.77\\
 		\hline
@@
 
-According to the Table 3 and 4, it is clear that the model trained with augmented data has a higher accuracy than the model trained with metadata only.
-While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.93$ and $0.91$ respectively, their training with metadata has both the accuracy of $0.89$.
+According to the Table 4 and 5, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only.
+While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.79$ and $0.84$ respectively, their training with metadata has both the accuracy of $0.89$.
 Furthermore, Resnet50 trained with augmented data has the accuracy that outperform the Resnet50 and is twice as high as Resnet152 trained with metadata.
 On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively.
-This term will be discussed later on.
-Since, the model trained with augmented data have high accuracy, when their f1-score and the recall score of models are analyzed, it turns out that models trained with augmented data have imbalanced f1-scores according to table 5.
-As a results, augmented data model dose not classify well on all class as InceptionResNetV2 trained on augmented data have $0.29$ f1-score on class df while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way.
+
+Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to figure 10.
+As a results, augmented data model does not classify well on all class as InceptionResNetV2 trained on augmented data have f1-score on class df and akiec is just above $0.3$ and $0.4$, separately while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way arcoding to the figure 11.
 However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
@@
 Since this data set is not balanced, therefore using augmented data can make the model more  bias to the class which has larger sample.
-Using the metadata, though still make the model bias, it dose contributes to the improvement of  the performance of the model.
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
-		\hline
-		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
-		\hline
-		DenseNet201 with Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 
-		\hline
-		InceptionResNetV2 with Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\
-		\hline
-		Resnet50 with Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\
-		\hline 	
-		VGG16 with Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 
-		\hline		
-		DenseNet201 with Metadata and WeightLoss & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
-		\hline
-		InceptionResNetV2 with Metadata and WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
-		\hline
-		Resnet50 with Metadata and WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
-		\hline
-		Resnet152 with Metadata and WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
-		\hline
-		NasNetLarge with Metadata and WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
-		\hline
-		MobileNetV2 with Metadata and WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
-		\hline
-		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
-		\hline
-		MobileNetV3Small with Metadata and WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
-		\hline
-		NasNetMobile with Metadata and WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
-		\hline
-	\end{tabular}
-	\caption{F1-Score of each class and the mean f1-score of each model}
-	\label{table:F1-score-summary}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
-		\hline
-		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
-		\hline
-		DenseNet201 with Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 
-		\hline
-		InceptionResNetV2 with Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\
-		\hline
-		Resnet50 with Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\
-		\hline 	
-		VGG16 with Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 
-		\hline		
-		DenseNet201 with Metadata and WeightLoss & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
-		\hline
-		InceptionResNetV2 with Metadata and WeightLoss & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
-		\hline
-		Resnet50 with Metadata and WeightLoss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
-		\hline
-		Resnet152 with Metadata and WeightLoss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
-		\hline
-		NasNetLarge with Metadata and WeightLoss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
-		\hline
-		MobileNetV2 with Metadata and WeightLoss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
-		\hline
-		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
-		\hline
-		MobileNetV3Small with Metadata and WeightLoss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
-		\hline
-		NasNetMobile with Metadata and WeightLoss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
-		\hline
-	\end{tabular}
-	\caption{Recall score of each class and the mean recall score of each model}
-	\label{table:recall-score-summary}
-\end{table}
+Using the metadata, though still make the model bias, it does contributes to the improvement of  the performance of the model.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\linewidth]{Definitions/f1 AD}
+	\caption{F1 Score on each class of each model.
+The class contain AKIEC, BCC, BKL, DF, MEL, NV, VASC which is denoted in the abbreviation section.
+The models showed in the above bar chart include DenseNet201 and InceoptionResNetV2 which are the two best model after hyper tuning.
+AD means the two models are trained with augmented data created during the training, there is neither no metadata nor weight loss contribution.
+}
+	\label{fig:f1 AD}
+\end{figure}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\linewidth]{Definitions/f1 MD WL}
+	\caption{The f1-score on each class of two models: DenseNet201 and InceptionResNetV2 which are trained with the MetaData (MD) and the Weight Loss (WL) function.
+In this case, there is no contribution from the augmented data.The detail architecture of the model can be seen at the appendix section A.
+The f1-score performance results of other models can be seen at appendix section C.1}
+	\label{fig:f1 MD WL}
+\end{figure}
 
 This problem is also true with the recall score according to table 7.
-DenseNet201, InceptionResNetV2, ResNet50, VGG16 trained with augmented data has expected value of recall of $0.72$, $0.71$, $0.69$, $0.69$, respectively, while the combination of InceptionResNetV2, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
-Therefore, metadata does improve the model performance by reducing the amount of data needed for achieving nearly the expected results.
+DenseNet201, InceptionResNetV2, trained with augmented data has expected value of recall of $0.56$, $0.69$, respectively, while the combination of DenseNet201, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
+Therefore, metadata does improve the model performance by reducing the amount of data needed for achieving higher results.
 On the other hand, the reason why the model become much more balanced is the weighted loss function.
@@
 DenseNet201, InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$.
-$0.82$, respectively, as opposed to their training in akiec without weighted loss function.
-MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately.
-
-\begin{table}[H]
-	\centering	
-	\begin{tabular}{|l | c | c | c | c|} 
-		\hline
-		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\
-		\hline
-		Accuracy(avg) & 0.81 & 0.78 & 0.86 & \textbf{0.86}\\
-		\hline
-		Balanced Accuracy(avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
-		\hline
-		Precision(avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
-		\hline
-		F1-score(avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
-		\hline
-		Sensitivity(avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
-		\hline
-		Specificity(avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
-		\hline
-		ROC-AUC-score(avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
-		\hline
-	\end{tabular}
-	\caption{Deeper analyzing of mobile model.
-This table illustrate the other indicators of the four mobile-based models including MobileNetV2, MobileNetV3Small, MobileNetV3Large, NasNetMobile.
-The indicators are Accuracy, Balanced Accuracy, Precision, F1-score, Sensitivity, Specificity, and ROC - AUC score.
-All of them are average indicator}
-	\label{table:mobile-performance}
-\end{table}
+$0.82$, respectively, as opposed to their training in akiec without weighted loss function: $0.65$ and $0.37$.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\linewidth]{Definitions/re AD}
+	\caption{Recall score on each class of each model.
+The class contain AKIEC, BCC, BKL, DF, MEL, NV, VASC which is denoted in the abbreviation section.
+The models showed in the above bar chart include DenseNet201 and InceoptionResNetV2 which are the two best model after hyper tuning.
+AD means the two models are trained with augmented data created during the training, there is neither no metadata nor weight loss contribution.
+The detail architecture of the model can be seen at the appendix section A.
+The f1-score performance results of other models can be seen at appendix section C.2}
+	\label{fig:re AD}
+\end{figure}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\linewidth]{Definitions/re MD WL}
+	\caption{The recall score on each class of two models: DenseNet201 and InceptionResNetV2 which are trained with the MetaData (MD) and the Weight Loss (WL) function.
+In this case, there is no contribution from the augmented data.The detail architecture of the model can be seen at the appendix section A.
+The f1-score performance results of other models can be seen at appendix section C.2}
+	\label{fig:re MD WL}
+\end{figure}
 
 Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
-The table 8 illustrates the deeper analyzing of the three models.
-It's clear that MobileNetV3Large and NasNetMobile are the two best performance model.
-Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.
+MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately according to the  table A4 appendix C.2.
+It's transparent that MobileNetV3Large and NasNetMobile are the two best performance model.
+Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile.
 
@@
 \begin{adjustwidth}{-\extralength}{0cm}
+
+\section[\appendixname~\thesection]{Detailed Model Performance}
+\subsection[\appendixname~\thesection]{F1-Score Model Performance}
+\begin{table}[H]
+	\centering
+	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
+		\hline
+		DenseNet201 with Augmented Data & 0.56 & 0.75 & 0.64 & 0.62 & 0.60 & 0.93 & 0.85 & 0.70 \\ 
+		\hline
+		InceptionResNetV2 with Augmented Data & 0.42 &	0.63 & 0.51 & 0.35 & 0.57 & 0.9 & 0.7 & 0.58\\
+		\hline
+		Resnet50 with Augmented Data & 0.39 & 0.59 & 0.42 & 0.6 & 0.42 & 0.88 & 0.79 & 0.58\\
+		\hline 	
+		VGG16 with Augmented Data & 0.35 & 0.62 & 0.42 & 0.32 & 0.47 & 0.89 & 0.77 & 0.54\\ 
+		\hline		
+		DenseNet201 with Metadata and WeightLoss & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
+		\hline
+		InceptionResNetV2 with Metadata and WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
+		\hline
+		Resnet50 with Metadata and WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
+		\hline
+		Resnet152 with Metadata and WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
+		\hline
+		NasNetLarge with Metadata and WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
+		\hline
+		MobileNetV2 with Metadata and WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
+		\hline
+		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
+		\hline
+		MobileNetV3Small with Metadata and WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
+		\hline
+		NasNetMobile with Metadata and WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
+		\hline
+	\end{tabular}
+	\caption{F1-Score of each class: akiec, bcc, bkl, df, mel, nv, vasc which are denoted in the abbreviation.
+The last column is the expected value of f1-score from each model.
+All model in the first column is the models trained in this research.
+The term "with Augmented Data" means that model is trained with data augmenting during the training, there is no metadata or weight loss contribution.
+The term "with Metadata and WeightLoss" means that the model is trained with metadata including age, gender, localization and the weight loss function, there is no augmented data contribution}
+	\label{table:F1-score-summary}
+\end{table}
+
+\subsection[\appendixname~\thesection]{Recall Model Performance}
+\begin{table}[H]
+	\centering
+	\begin{tabular}{|p{5cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.6cm} | p{0.7cm}|} 
+		\hline
+		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\
+		\hline
+		DenseNet201 with Augmented Data & 0.65 & 0.75 & 0.59 & 0.53 & 0.54 & 0.93 & 0.85 & 0.69\\ 
+		\hline
+		InceptionResNetV2 with Augmented Data & 0.37 & 0.60 & 0.55 & 0.24 & 0.59 & 0.9 & 0.67 & 0.56\\
+		\hline
+		Resnet50 with Augmented Data & 0.33 & 0.56 & 0.38 & 0.53 & 0.40 & 0.92 & 0.81 & 0.56\\
+		\hline 	
+		VGG16 with Augmented Data & 0.31 & 0.66 & 0.37 & 0.24 & 0.40 & 0.94 & 0.71 & 0.51\\ 
+		\hline		
+		DenseNet201 with Metadata and WeightLoss & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
+		\hline
+		InceptionResNetV2 with Metadata and WeightLoss & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
+		\hline
+		Resnet50 with Metadata and WeightLoss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
+		\hline
+		Resnet152 with Metadata and WeightLoss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
+		\hline
+		NasNetLarge with Metadata and WeightLoss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
+		\hline
+		MobileNetV2 with Metadata and WeightLoss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
+		\hline
+		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
+		\hline
+		MobileNetV3Small with Metadata and WeightLoss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
+		\hline
+		NasNetMobile with Metadata and WeightLoss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
+		\hline
+	\end{tabular}
+	\caption{Recall score of each class and the expected value of recall score from each model}
+	\label{table:recall-score-summary}
+\end{table}
+
+\subsection[\appendixname~\thesection]{Detailed Mobile Model Perform}
+\begin{table}[H]
+	\centering	
+	\begin{tabular}{|l | c | c | c | c|} 
+		\hline
+		Model & \cite{04381} & \cite{02244}Small & \cite{02244}Large & \cite{07012}Mobile\\
+		\hline
+		Accuracy(avg) & 0.81 & 0.78 & 0.86 & \textbf{0.86}\\
+		\hline
+		Balanced Accuracy(avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
+		\hline
+		Precision(avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
+		\hline
+		F1-score(avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
+		\hline
+		Sensitivity(avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
+		\hline
+		Specificity(avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
+		\hline
+		ROC-AUC-score(avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
+		\hline
+	\end{tabular}
+	\caption{Deeper analyzing of mobile model.
+This table illustrate the other indicators of the four mobile-based models including MobileNetV2, MobileNetV3Small, MobileNetV3Large, NasNetMobile.
+The indicators are Accuracy, Balanced Accuracy, Precision, F1-score, Sensitivity, Specificity, and ROC - AUC score.
+All of them are average indicator}
+	\label{table:mobile-performance}
+\end{table}
+
 %\printendnotes[custom] % Un-comment to print a list of endnotes

### 2022-08-15 MDPI/Sensor Paper/template.tex
Update Paper

@@
 Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201\cite{06993}, InceptionResNetV2\cite{00567}, ResNet50\cite{03385}\cite{05027}, VGG16\cite{1556} and Soft-Attention layer.
+Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model.
+For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively.
+DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer.
+
 Using those above backbones has been tried by many previous papers.
-Rishu Garg et al \cite{03798} uses transfer learning approach with CNN based model.
+Rishu Garg et al \cite{03798} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set.
+Besides, they also use data augmentation to avoid the imbalance of the data set.
+Histogram Equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, Support Vector Machine.
+
 Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3\cite{00567} model.
+In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set.
+Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3.
+
 Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating holes of different sizes on the images i.e.
 technically making a random portion of image inactive during data augmentation process.
-\cite{01284} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.
+
+Otherwise, \cite{01284} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.
+
 Another state of the art is GradCam and Kernel SHAP\cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.
-
-Otherwise, there are also many state of the art whose great performance on skin lesion classification.
+In that research they use three data sets containing HAM10000, BCN-20000 and MSK.
+Before feeding into the models, the images are preprocessed by binarized with a very low threshold to find the center of mass.
+
+On the other hand, there are also many state of the art whose great performance on skin lesion classification.
 The Student and Teacher Model is also a high performance model in 2021\cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
 Therefore, they can take full advantage of what others learn.
+
 SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively.
@@
 Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively.
+
 Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al.
+The metadata is fed into fully connected neural network after being encoded into one-hot vector.
+All missing data point of age is set to 0.
+In order to overcome the missing data problem, the research apply one-hot encoding to the group but the initial validation is poor performance then numerical encoding is applied.
 
@@
 Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al.
-\FloatBarrier
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{|p{1cm}|p{12.5cm}|}
-		\hline
-		Work & Approach \\ 
-		\hline
-		\cite{03358} & Combination of Backbone Model and Soft Attention. Backbone model includes DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34\\
-		\hline
-		\cite{03798} & Transfer Learning with CNN based model\\
-		\hline
-		\cite{10348} & Transfer Learning with CNN based model including DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34, and InceptionNetV3\\
-		\hline
-		\cite{09418} & Transfer Learning with CNN based model including EfficientNet and SeNet.
-Data augmentation process used CutOut to create random sized hole considered as an inactive portion of image.\\
-		\hline
-		\cite{01284} & Transfer Learning with CNN based model.
-Data augmentation process uses RandArgument to split picture into several pictures which is used to train.
-DropBlock and Multi-Weight Loss Function are used to deal with the imbalanced.\\
-		\hline
-		\cite{06612} & GradCam and Kernel SHAP, two model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.\\
-		\hline
-		\cite{03225} & Student and Teacher Model is the combination of two model which share the memory learned with others. \\
-		\hline
-		\cite{12602} & SkinLinkNet uses the image whose shape is (448,488) for training. Unet and EfficientNetB0 are used for segmentation and classification task respectively.\\
-		\hline
-		\cite{03426} & WonderM uses the image whose shape is (600,600) created by padding for training. Unet and DenseNet are used for segmentation and classification task respectively.\\
-		\hline
-		\cite{03910} & MetaData including age, gender, and capture position are used to gain higher performance of the model. The models used in this paper are CNN-based model \\
-		\hline
-		\cite{03798} & Traditional Machine Learning Algorithms are applied including Random Forest, XGBoost, and Support Vector Machine \\
-		\hline
-		\cite{10348} & Matrix Factorization are applied before the softmax activation function \\
-		\hline
-		\cite{05045} & Isolation Forest are applied distribution skin lesion images before fedding into the softmax activation function. \\
-		\hline
-		\cite{10348} & Matrix Factorization are applied before the softmax activation function. \\
+
+\begin{table}
+	\centering
+	\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
+		\hline
+		Research & Deep Learning & Machine Learning & Data 
+		Augmentation & Feture Extraction & Data set\\
+		\hline
+		\cite{03358} & x & & x & & HAM10000\\
+		\hline
+		\cite{03798} & x & x & x & x & HAM10000\\
+		\hline
+		\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
+		\hline
+		\cite{09418} & x & & x & & HAM10000\\
+		\hline
+		\cite{01284} & x & & x & & HAM10000\\
+		\hline
+		\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
+		\hline
+		\cite{03225} & x & & x & & HAM10000\\
+		\hline
+		\cite{12602} & x & & x & & HAM10000\\
+		\hline
+		\cite{03426} & x & & x & & HAM10000\\
+		\hline
+		\cite{03910} & x & & x & & HAM10000\\
+		\hline
+		\cite{05045} & & x & x & x & HAM10000\\
 		\hline
@@
 \end{table}
-\FloatBarrier
-\subsection{Objectives}
-In this paper, the effect of metadata on classifying skin disease will be analyzed.
-On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
+\subsection{Proposed Method}
+In this research, a new model is constructed from the combination of:\\
+- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
+- Using metadata including age, gender, localization as another input of the model\\
+- Using Soft-Attention as a feature extractor of the model\\
+- A new weight loss function
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Materials and Methods}
-\subsection{Data}
+\subsection{Materials}
 \subsubsection{Image Data}
@@
 $90$ percent and $10$ percent of the data is used for training and validating respectively.
-
-In the previous research\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images.
-Since, this data is imbalanced, using augmented data may cause the problem of well classify on the classes almostly taking the number of samples.
-In this paper, instead of augmenting data, metadata is used.
-The way of processing metadata is discussed in MetaData section.
 Images in this data set has the type of $RGB$ and shape of (450, 600).
 However, Each backbone need the different input size of image as well as the range of pixel value.
+
+\subsubsection{Metadata}
+The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position 
+\begin{table}[H]
+	\centering
+	\begin{tabular}{|c c c c |} 
+		\hline
+		ID & Age & Gender & Local\\ 
+		\hline
+		ISIC-00001 & 15 & Male & back\\
+		\hline
+		ISIC-00002 & 85 & Female & elbow\\
+		\hline
+	\end{tabular}
+	\caption{Metadata example in the data set}
+	\label{table:metadata sample}
+\end{table}
+\subsection{Methodology}
+\subsubsection{Overall Architecture}
+The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}.
+Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.
+It is described in the figure below:
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/MainModel - Model Form}
+	\caption{Overall Model Architecture}
+	\label{fig:main-model}
+\end{figure}
+
+The figure 6 illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research.
+In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module.
+Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module.
+InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module.
+Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/Model Structure}
+	\caption{Overall Model Architecture.
+This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge.
+The detail structure and information can be found at the Apendix A}
+	\label{fig:model-structure}
+\end{figure}
+The figure 7, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
+All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module.
+The NasNetMobile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
+	\caption{Overall Mobile-based Model Architecture.
+This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
+The detail structure and information can be found at the Apendix B}
+	\label{fig:mobile-model-structure}
+\end{figure}
+
+\subsubsection{Input Schema}
+In this research, the image data is both augmented for all class, the number of image increase to 18015 images and keep original form.
+Before feeding into the backbone model, the images is pre-processed by the input requirement of each model.
 DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set.
@@
 
-\subsubsection{Metadata}
-The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position as well as the test data set containing 857 images.
-During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples.
-In the gender and capturing position category contain some samples of unknown.
-Instead of removing, these "unknowns" data points is kept and considered as "prefer not to say".
-Besides, the label of the whole data is preprocessed into one-hot vector.
-\subsection{Model Schema}
-\subsubsection{Input Schema}
-Using metadata as another input is not new.
+On the other hand, the metadata is also used as another input.
 In paper\cite{03910}, they decide to keep the missing value and set its value to $0$.
@@
 \end{figure}
+
+\subsubsection{Backbone Model}
+In this paper, the backbone models used in this paper are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
+The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance.
+Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated.
+Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed.
+On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{|l | c c c|} 
+		\hline
+		Model & Size(MB) & Parameters & Depth \\ 
+		\hline
+		Resnet50 & 98 & 25.6M & 107 \\ 
+		\hline
+		Resnet152 & 232 & 60.4M & 311 \\ 
+		\hline
+		DenseNet201 & 80 & 20.2M & 402 \\
+		\hline
+		InceptionResNetV2\cite{07261} & 215 & 55.9M & 449 \\
+		\hline
+		MobileNet & 16 & 4.3M & 55 \\ 
+		\hline
+		MobileNetV2 & 14 & 3.5M & 105 \\ 
+		\hline
+		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
+		\hline
+		MobileNetV3Large & Unknown & 5.5M & 118 \\
+		\hline
+		NasnetMobile & 23 & 5.3M & 308 \\
+		\hline
+		NasnetLarge & 343 & 88.9M & 533 \\ 
+		\hline
+	\end{tabular}
+	\caption{Size and Parameters and Depth of backbone model used in this paper.
+This table summarizes the properties of the backbone models.
+The size column illustrates how many space need to store the model in megabyte.
+The parameters column demonstrate the number of parameters in the associated model.
+The last column, depth show the number of hidden layers in that model.
+Parameters and Depth are two crucial element to evaluate the optimized model stated in the Objective section.}
+	\label{table:model-summary}
+\end{table}
 
@@
 This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$.
-The output of this convolution is normalized using the softmax function to generate K = 16 attention maps.
-These $16$ attention maps are aggregated to produce a weight function called $\alpha$.
+The output of this convolution is normalized using the softmax function to generate K (a constant value) attention maps.
+These $K$ attention maps are aggregated to produce a weight function called $\alpha$.
 This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar.
@@
 After all, these two paths are then concatenated, fed into a ReLU layer, and a Dropout with the probability of $0.5$.
-\subsubsection{Backbone Model Architecture}
-In this paper, the backbone models used in this paper are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
-The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance.
-Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated.
-Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed.
-On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{|l | c c c|} 
-		\hline
-		Model & Size(MB) & Parameters & Depth \\ 
-		\hline
-		Resnet50 & 98 & 25.6M & 107 \\ 
-		\hline
-		Resnet152 & 232 & 60.4M & 311 \\ 
-		\hline
-		DenseNet201 & 80 & 20.2M & 402 \\
-		\hline
-		InceptionResNetV2\cite{07261} & 215 & 55.9M & 449 \\
-		\hline
-		MobileNet & 16 & 4.3M & 55 \\ 
-		\hline
-		MobileNetV2 & 14 & 3.5M & 105 \\ 
-		\hline
-		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
-		\hline
-		MobileNetV3Large & Unknown & 5.5M & 118 \\
-		\hline
-		NasnetMobile & 23 & 5.3M & 308 \\
-		\hline
-		NasnetLarge & 343 & 88.9M & 533 \\ 
-		\hline
-	\end{tabular}
-	\caption{Size and Parameters and Depth of backbone model used in this paper.
-This table summarizes the properties of the backbone models.
-The size column illustrates how many space need to store the model in megabyte.
-The parameters column demonstrate the number of parameters in the associated model.
-The last column, depth show the number of hidden layers in that model.
-Parameters and Depth are two crucial element to evaluate the optimized model stated in the Objective section.}
-	\label{table:model-summary}
-\end{table}
-
-\subsubsection{Model}
-The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}.
-Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.
-It is described in the figure below:
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.5\linewidth]{Definitions/MainModel - Model Form}
-	\caption{Overall Mobile-based Model Architecture}
-	\label{fig:main-model}
-\end{figure}
-
-The figure 6 illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research.
-In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module.
-Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module.
-InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module.
-Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1\linewidth]{Definitions/Model Structure}
-	\caption{Overall Model Architecture.
-This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge.
-The detail structure and information can be found at the Apendix A}
-	\label{fig:model-structure}
-\end{figure}
-The figure 7, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
-All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module.
-The NasNetMobile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell.
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
-	\caption{Overall Mobile-based Model Architecture.
-This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
-The detail structure and information can be found at the Apendix B}
-	\label{fig:mobile-model-structure}
-\end{figure}
-
-\subsection{Loss Function}
+
+\subsubsection{Loss Function}
 The loss function used in this paper is categorical cross-entropy.
@@
 where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.
-\subsection{Evaluation Metrics}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+\subsection{Experimental Setup}
+\subsubsection{Training}
+Before training, the data set is split into two sub set for training (90 percent) and validation (90 percent).
+Test set, otherwise is provided by the HAM10000 data set, contains 857 images.
+In order to analyze the effect of augmented data on the model, during the training the image data is augmented by the following technique:\\
+- Rotation Range: rotate the image in a fixed angle. \\
+- Width and height shift range: Shift the image horizontally and vertically, respectively. \\
+- Zoom Range: zoom in the image to create new image. \\
+- Horizontal and vertical flipping: flipping the image horizontally and vertically to create new form of image.\\
+Otherwise, all of models is trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$.
+The initial epochs is set to 250 epochs and the Early Stopping is also applied to stop the training as the accuracy of validation set does not increase after $25$ epochs.
+Besides, the batch size is set to $32$.
+
+\subsubsection{Tools}
+In order to build and train the model, Keras and TensorFlow library are applied.
+In detail, Keras is used to build, clone the backbone model which is pre-trained with the image-net data set.
+Soft-Attention, on the other hand is coded by inheriting the Layer class of TensorFlow.
+Therefore, the Soft-Attention layer can be combined with the functional API model.
+Otherwise, the models are trained by NVIDIA RTX TitanV and the data set is pre-processed with the CPU Intel I5 32 processors, RAM 32GB.
+In detail, the GPU is setup with CUDA 11.6, cuDNN 8.3 and ChipSRT as the requirement of TensorFlow.
+\subsubsection{Evaluation Metrics}
 \begin{figure}[!htb]
@@
 Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively.
-\[
-A = \begin{bmatrix}
-	a_{11} & a_{12} & \dots & a_{1j} \\
-	a_{21} & a_{22} & \dots & a_{2j} \\
-	\vdots & \vdots	&  & \vdots\\
-	a_{i1} & a_{i2} & \dots & a_{ij} 
-\end{bmatrix}
-\]
-
+%\[
+%A = \begin{bmatrix}
+%	a_{11} & a_{12} & \dots & a_{1j} \\
+%	a_{21} & a_{22} & \dots & a_{2j} \\
+%	\vdots & \vdots	&  & \vdots\\
+%	a_{i1} & a_{i2} & \dots & a_{ij} 
+%\end{bmatrix}
+%\]
 The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$.
@@
 \[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
+where Sensitivity and specificity mathematically describe the accuracy of a test which reports the presence or absence of a condition.
+Individuals for which the condition is satisfied are considered "positive" and those for which it is not are considered "negative".
+Sensitivity or true positive rate refers to the probability of a positive test, conditioned on truly being positive while Specificity  or true negative rate refers to the probability of a negative test, conditioned on truly being negative.
 \[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
+Precision or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative.
+F1-score, on the other hand refers the harmonic mean of precision and recall which mean the higher the f1-score is, the higher both precision and recall is.
+Besides, the expected value of precision, f1-score and recall-score are also applied because of the multi-class problem.
 \[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
-The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
-\subsection{Traning}
-Before training, the data set is split into three sub datasets including training, validation, and testing.
-In this paper, the graphic card that is used to train is Nvidia RTX TitanV.
-In order to make the comparison fair, all the model in this paper is trained with Adam Optimizer\cite{6980}.
-The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$, the epsilon argument of the optimizer is set to $0.1$.
-On the other hand, Early Stopping is also set up, if the accuracy of validation set does not increase after 25 epochs, the training will stop.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicate the probability of TP versus the probability of FP.
+
+\subsection{Discussion} 
 The accuracy of all model is presented in the figure below:
@@
 		\hline
-		0.89 & 0.89 & 0.70 & 0.57 & 0.81\\
+		0.90 & 0.89 & 0.70 & 0.57 & 0.81\\
 		\hline

### 2022-08-15 MDPI/Sensor Paper/template.tex
Update Paper

@@
 
-The table 9 shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others.
+The table 7 shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others.
 In detail, MobileNetV3Large whose the number of parameters is 5.5 millions which is four and ten times less than DenseNet201 and InceptionResNetV2, respectively.
@@
 If the MobileNetV3Large need a harder process of parameter hyper-tuning to achieve a better result, which is also the future target of this research.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/ADvsMD}
+	\caption{ROC AUC Score. This figure illustrate the AUC score associated with models including models trained with augmented data and models trained with metadata}
+	\label{fig:ADvsDC-AUC}
+\end{figure}
+
+The figure 14 shows the AUC score of the three models InceptionResNetV2, Densenet201, and ResNet50 which is trained with only augmented data or metadata.
+It's transparent that the InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: 0.974 and 0.971 as opposed to 0.972 and 0.93, respectively.
+ResNet50 trained with augmented data, on the other hand have higher auc-score: 0.95 as compared to 0.93 of ResNet50 trained with metadata.
+Overall, InceptionResNetV2 trained with metadata reach the peak with the auc-score of 0.974.
+The InceptionResNetV2 trained with metadata is also compared with the others to find out the best models trained.
+According to the figure 15, the InceptionResNetV2 still hit the peak of 0.974 auc-score.
+ResNet152, otherwise is the worst model with the auc-score of 0.87.
+Other models, on the other hand have the approximately same of auc-score.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/vsALL}
+	\caption{ROC AUC Score of all model trained in this paper.}
+	\label{fig:vsallAUC}
+\end{figure}
+
+After the experiment, the InceptionResNetV2 is chose to compare with the other SOTA models.
+
+\begin{table}
+	\begin{tabular}{| p{3cm} | c | c | c | c | c |}
+		\hline
+		Model & Accuracy & Precision & f1-score & recall & auc-score\\
+		\hline
+		s
+	\end{tabular}
+\end{table}
 

### 2022-08-19 MDPI/Sensor Paper/template.tex
Update

@@
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0002-2566-5637} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorC}{0000-0002-2566-5637} % Add \orcidC{} behind the author's name
 
 % Authors, for the paper (add full first names)
-\Author{Khoi Do Hoang$^{
-		2,\dagger,%\ddagger
-	}$\orcidA{}*}
+\Author{Viet Dung Nguyen $^{1,\dagger}$\orcidA{}, Ngoc Dung Bui $^{2,\dagger}$\orcidB{} and Khoi Do Hoang $^{3,\dagger}$\orcidC{}}
 
@@
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Khoi Do}
+\AuthorNames{Dung Viet Nguyen, Ngoc Dung Bui and Khoi Do Hoang}
 
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Do, K.}
+\AuthorCitation{Nguyen, D.; Bui, D.; Khoi, D.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 \address{
-$^{1}$ \quad Lecturer: Viet Dung Nguyen; dung.nguyenviet1@hust.edu.vn\\
-$^{2}$ \quad Author: Khoi Do Hoang; khoi.dh200332@sis.hust.edu.vn}
+$^{1}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam \\
+$^{2}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam\\
+$^{3}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam}
 
 % Contact information of the corresponding author
-\corres{Correspondence: khoido8899@gmail.com; Tel.: +84-9360-192-58}
+\corres{Correspondence: dung.nguyenviet1@hust.edu.vn; Tel.:  +84-9834-443-22 (D.N.)}
 
@@
 \firstnote{Current address: 1st Dai Co Viet Street, Ha Noi, Viet Nam} 
-\secondnote{}
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 Skin cancer is one of the most common cancers leading to worldwide death.
-Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer.
-Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year.
-According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}.
-In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}.
+Every day, more than 9500 \cite{03358} people in the United States are diagnosed with skin cancer.
+Otherwise, 3.6 \cite{03358} million people are diagnosed with basal cell skin cancer each year.
+According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase \cite{11872}.
+In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States \cite{11872}.
 On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent.
-However, once the disease progresses beyond the skin, survival is poor\cite{11872}.
+However, once the disease progresses beyond the skin, survival is poor \cite{11872}.
 Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.
@@
 In Medical Treatment, AI models are applied to build solutions to a specific disease, medicine revolution is an example.
-In various studies, AI algorithms have provided various end-to-end solutions to the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.
+In various studies, AI algorithms have provided various end-to-end solutions to the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging \cite{11872}.
 
 In order to adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance.
-Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
+Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet \cite{04861}, Inception \cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet \cite{03385} \cite{05027}, and NasNet \cite{07012}.
 Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.
@@
 Skin lesion classification is not a new area, since there are many great performance models constructed.
-One of the most cutting-edge technologies that have been used is Soft-Attention as stated in\cite{03358}.
-Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201\cite{06993}, InceptionResNetV2\cite{00567}, ResNet50\cite{03385}\cite{05027}, VGG16\cite{1556} and Soft-Attention layer.
+One of the most cutting-edge technologies that have been used is Soft-Attention as stated in \cite{03358}.
+Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \cite{06993}, InceptionResNetV2 \cite{00567}, ResNet50 \cite{03385} \cite{05027}, VGG16 \cite{1556} and Soft-Attention layer.
 Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model.
@@
 
-Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3\cite{00567} model.
+Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3 \cite{00567} model.
 In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set.
@@
 
-Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating holes of different sizes on the images i.e.
+Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet \cite{11946} and SeNET \cite{01507} instead and CutOut \cite{04552v2} method which involves creating holes of different sizes on the images i.e.
 technically making a random portion of image inactive during data augmentation process.
@@
 
-Another state of the art is GradCam and Kernel SHAP\cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.
+Another state of the art is GradCam and Kernel SHAP \cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.
 In that research they use three data sets containing HAM10000, BCN-20000 and MSK.
@@
 On the other hand, there are also many state of the art whose great performance on skin lesion classification.
-The Student and Teacher Model is also a high performance model in 2021\cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
+The Student and Teacher Model is also a high performance model in 2021 \cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
 Therefore, they can take full advantage of what others learn.
 
-SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively.
+SkinLinkNet \cite{12602} and WonderM \cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively.
 In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600).
@@
 Random Forest, XGBoost, and Support Vector Machines are tested by  \cite{03798} of Rishu Garg et al.
-Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348} by Amirreza Rezvantalab et al.
+Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \cite{10348} by Amirreza Rezvantalab et al.
 Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al.
@@
 \subsubsection{Image Data}
-The data set used in this paper is the HAM10000 data set published by Havard University Dataverse\cite{10417}.
+The data set used in this paper is the HAM10000 data set published by Havard University Dataverse \cite{10417}.
 There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
-The distribution of the data set is shown in the table below:
+The distribution of the data set is shown in the table \ref{table:data-distribution} below:
 
@@
 \subsubsection{Metadata}
-The HAM10000 data set\cite{10417} also contain the metadata of patient including gender, age, and the capturing position 
+The HAM10000 data set \cite{10417} also contain the metadata of patient including gender, age, and the capturing position illustrated in table \ref{table:metadata sample}
 \begin{table}[H]
@@
 \subsubsection{Overall Architecture}
-The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}.
+The whole architecture of the model is represented in the figure \ref{fig:main-model}.
+The model takes two input including Image data and Metadata.
 Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.
-It is described in the figure below:
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1\linewidth]{Definitions/MainModel - Model Form}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\linewidth]{Definitions/MainModel - Model Form}
 	\caption{Overall Model Architecture}
@@
 
-The figure 6 illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research.
+The figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research.
 In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module.
@@
 Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.
+
 \begin{figure}[H]
@@
 	\includegraphics[width=1\linewidth]{Definitions/Model Structure}
-	\caption{Overall Model Architecture.
+	\caption{Overall Original Model Architecture.
 This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge.
-The detail structure and information can be found at the Apendix A}
+The detail structure and information can be found at the Apendix \ref{appendix-table:detailed structure model}}
 	\label{fig:model-structure}
 \end{figure}
-The figure 7, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
+
+The figure \ref{fig:mobile-model-structure}, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
 All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module.
@@
 This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
-The detail structure and information can be found at the Apendix B}
+The detail structure and information can be found at the Apendix \ref{appendix-table:detailed mobile model structure}}
 	\label{fig:mobile-model-structure}
@@
 Before feeding into the backbone model, the images is pre-processed by the input requirement of each model.
-DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set.
-In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling.
+DenseNet201 \cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set.
+In Resnet50 and Resnet152 \cite{03385} \cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling.
 InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$.
-Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$.
+Similarly, three versions of MobileNet \cite{04861} \cite{04381} \cite{02244}, NasNetMobile and NasNetLarge \cite{07012} require the input pixel is in range of $-1$ and $1$.
 
 On the other hand, the metadata is also used as another input.
-In paper\cite{03910}, they decide to keep the missing value and set its value to $0$.
+In the research \cite{03910}, they decide to keep the missing value and set its value to $0$.
 The sex and anatomical site are categorical encoded.
@@
 After processing, the metadata is fed into a two-layer neural network with 256 neurons each.
-Each layer contains batch normalization, a ReLU\cite{08375} activation, and dropout with $p = 0.4$.
+Each layer contains batch normalization, a ReLU \cite{08375} activation, and dropout with $p = 0.4$.
 The network’s output is concatenated with the CNN’s feature vector after global average pooling.
@@
 Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section.
-The Input schema is described as follow:
+The Input schema is described in the table \ref{fig:input-schema}
 
@@
 \subsubsection{Backbone Model}
-In this paper, the backbone models used in this paper are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}.
-The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance.
+In this paper, the backbone models used in this paper are DenseNet201 \cite{06993}, Inception \cite{00567}, MobileNets \cite{04861} \cite{04381} \cite{02244}, ResNet \cite{03385} \cite{05027}, and NasNet \cite{07012}.
+The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance.
 Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated.
@@
 		\hline
-		InceptionResNetV2\cite{07261} & 215 & 55.9M & 449 \\
+		InceptionResNetV2 & 215 & 55.9M & 449 \\
 		\hline
@@
 
-\subsubsection{Soft-Attention}
+\subsubsection{Soft-Attention Module}
 Applying the Soft-Attention layer in deep learning is not a new approach.
@@
 In order to apply Soft-Attention, there are two main steps.
-Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}.
+Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map \cite{08513}.
 This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$.
-The output of this convolution is normalized using the softmax function to generate K (a constant value) attention maps.
+The output of this convolution is normalized using the soft-max function to generate K (a constant value) attention maps.
 These $K$ attention maps are aggregated to produce a weight function called $\alpha$.
@@
 
-In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
+In this paper, the Soft-Attention layer is applied in the same way in this paper \cite{03358}. The Soft-Attention module is described in the following diagram:
 
@@
 
-After feeding into ReLU function layer, the feature map is processed in two paths.
+After feeding into ReLU function layer, the heat feature map is processed in two paths.
 The first path is the 2-dimensional Max Pooling.
@@
 where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$.
-Since the data set face the imbalanced problem then I applied the class weight for the loss.
+Since the data set face the imbalanced problem then class weight for the loss is applied.
 This formula below is used to calculate the class weight:
@@
 \subsubsection{Training}
-Before training, the data set is split into two sub set for training (90 percent) and validation (90 percent).
+Before training, the data set is split into two sub set for training (90 percent) and validation (10 percent).
 Test set, otherwise is provided by the HAM10000 data set, contains 857 images.
@@
 - Width and height shift range: Shift the image horizontally and vertically, respectively. \\
-- Zoom Range: zoom in the image to create new image. \\
-- Horizontal and vertical flipping: flipping the image horizontally and vertically to create new form of image.\\
+- Zoom Range:  image to create new image. \\
+- Horizontal and vertical flipping: flipping the image horizontally and vertically to create new fzoom in theorm of image.\\
 Otherwise, all of models is trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$.
@@
 \subsubsection{Tools}
-In order to build and train the model, Keras and TensorFlow library are applied.
-In detail, Keras is used to build, clone the backbone model which is pre-trained with the image-net data set.
-Soft-Attention, on the other hand is coded by inheriting the Layer class of TensorFlow.
-Therefore, the Soft-Attention layer can be combined with the functional API model.
+TensorFlow and Keras are two of the most popular framework to build deep learning model.
+In this research, Keras based on TensorFlow is used to build, clone the backbone model which is pre-trained with the image-net data set.
 Otherwise, the models are trained by NVIDIA RTX TitanV and the data set is pre-processed with the CPU Intel I5 32 processors, RAM 32GB.
-In detail, the GPU is setup with CUDA 11.6, cuDNN 8.3 and ChipSRT as the requirement of TensorFlow.
+In detail, the GPU is setup with CUDA 11.6, cuDNN 8.3 and ChipSRT as the requirement of TensorFlow version 2.7.0.
 \subsubsection{Evaluation Metrics}
@@
 \end{figure}
-In this paper, the model is evaluated by using the confusion matrix and related metrics.
+The model is evaluated by using the confusion matrix and related metrics.
 The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class.
 Consider a confusion matrix $A$ with $C$ number of class.
-Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively.
-%\[
-%A = \begin{bmatrix}
-%	a_{11} & a_{12} & \dots & a_{1j} \\
-%	a_{21} & a_{22} & \dots & a_{2j} \\
-%	\vdots & \vdots	&  & \vdots\\
-%	a_{i1} & a_{i2} & \dots & a_{ij} 
-%\end{bmatrix}
-%\]
+Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively, therefore $A^i_k$ is the element at row i and column k
+\[
+A = \begin{bmatrix}
+	a_{11} & a_{12} & \dots & a_{1j} \\
+	a_{21} & a_{22} & \dots & a_{2j} \\
+	\vdots & \vdots	&  & \vdots\\
+	a_{i1} & a_{i2} & \dots & a_{ij} 
+\end{bmatrix}
+\]
 The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$.
@@
 \subsection{Discussion} 
-The accuracy of all model is presented in the figure below:
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{| c | c | c | c |}
-		\hline
-		InceptionResNetV2 & DenseNet201 & ResNet50 & VGG16 \\
-		\hline
-		0.79 & 0.84 & 0.76 & 0.77\\
-		\hline
-	\end{tabular}
-	\caption{Accuracy of the model with augmented data}
-	\label{table:Acc-Augment-Model}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{| c | c | c | c | c |}
-		\hline
-		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
-		\hline
-		0.90 & 0.89 & 0.70 & 0.57 & 0.81\\
-		\hline
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{| c | c | c | c |}
-		\hline
-		MobileNetV3Large & MobileNetV3Small & NasNetLarge & NasNetMobile\\
-		0.84 & 0.78 & 0.86 & 0.86\\
-		\hline
-	\end{tabular}
-	\caption{Accuracy of the model with metadata}
-	\label{table:Acc-Metadata-Model}
-\end{table}
-
-According to the Table 4 and 5, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only.
-While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.79$ and $0.84$ respectively, their training with metadata has both the accuracy of $0.89$.
-Furthermore, Resnet50 trained with augmented data has the accuracy that outperform the Resnet50 and is twice as high as Resnet152 trained with metadata.
-On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.84$, $0.86$, respectively.
-
-Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to figure 10.
-As a results, augmented data model does not classify well on all class as InceptionResNetV2 trained on augmented data have f1-score on class df and akiec is just above $0.3$ and $0.4$, separately while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way arcoding to the figure 11.
+\begin{comment}
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=1\linewidth]{Definitions/ACCALL}
+		\caption{Accuracy of all models trained in this research}
+		\label{fig:accall}
+	\end{figure}
+\end{comment}
+
+According to the Figure 10, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only.
+While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.79$ and $0.84$ respectively, their training with metadata are $0.90$ and $0.89$, respectively.
+Furthermore, Resnet50 trained with metadata data has the accuracy that outperform the Resnet50 trained with augmented data and is twice as high as Resnet152 trained with metadata.
+On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.86$, $0.86$, respectively.
+
+Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to figure 10, 11, 12, 13.
+As a results, augmented data model does not classify well on all class as InceptionResNetV2 trained on augmented data have f1-score on class df and akiec is just above $0.3$ and $0.4$, separately while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way arcoding to the figure 12.
 However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{Definitions/f1 AD}
-	\caption{F1 Score on each class of each model.
-The class contain AKIEC, BCC, BKL, DF, MEL, NV, VASC which is denoted in the abbreviation section.
-The models showed in the above bar chart include DenseNet201 and InceoptionResNetV2 which are the two best model after hyper tuning.
-AD means the two models are trained with augmented data created during the training, there is neither no metadata nor weight loss contribution.
-}
-	\label{fig:f1 AD}
-\end{figure}
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.7\linewidth]{Definitions/f1 MD WL}
-	\caption{The f1-score on each class of two models: DenseNet201 and InceptionResNetV2 which are trained with the MetaData (MD) and the Weight Loss (WL) function.
-In this case, there is no contribution from the augmented data.The detail architecture of the model can be seen at the appendix section A.
-The f1-score performance results of other models can be seen at appendix section C.1}
-	\label{fig:f1 MD WL}
-\end{figure}
-
-This problem is also true with the recall score according to table 7.
+	\includegraphics[width=1\linewidth]{Definitions/den f1}
+	\caption{The comparison between f1 scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss}
+	\label{fig:den f1}
+\end{figure}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/in f1}
+	\caption{The comparison between f1 scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss}
+	\label{fig:incep f1}
+\end{figure}
+
+This problem is also true with the recall score according to fugure 13.
 DenseNet201, InceptionResNetV2, trained with augmented data has expected value of recall of $0.56$, $0.69$, respectively, while the combination of DenseNet201, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{Definitions/re AD}
-	\caption{Recall score on each class of each model.
-The class contain AKIEC, BCC, BKL, DF, MEL, NV, VASC which is denoted in the abbreviation section.
-The models showed in the above bar chart include DenseNet201 and InceoptionResNetV2 which are the two best model after hyper tuning.
-AD means the two models are trained with augmented data created during the training, there is neither no metadata nor weight loss contribution.
-The detail architecture of the model can be seen at the appendix section A.
-The f1-score performance results of other models can be seen at appendix section C.2}
-	\label{fig:re AD}
-\end{figure}
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.7\linewidth]{Definitions/re MD WL}
-	\caption{The recall score on each class of two models: DenseNet201 and InceptionResNetV2 which are trained with the MetaData (MD) and the Weight Loss (WL) function.
-In this case, there is no contribution from the augmented data.The detail architecture of the model can be seen at the appendix section A.
-The f1-score performance results of other models can be seen at appendix section C.2}
-	\label{fig:re MD WL}
+	\includegraphics[width=1\linewidth]{Definitions/den re}
+	\caption{The comparison between recal scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss}
+	\label{fig:den recall}
+\end{figure}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/in re}
+	\caption{The comparison between recall scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss}
+	\label{fig:incep recall}
 \end{figure}
@@
 
-The table 7 shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others.
+The table 5 shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others.
 In detail, MobileNetV3Large whose the number of parameters is 5.5 millions which is four and ten times less than DenseNet201 and InceptionResNetV2, respectively.
@@
 
-The figure 14 shows the AUC score of the three models InceptionResNetV2, Densenet201, and ResNet50 which is trained with only augmented data or metadata.
+The figure 15 shows the AUC score of the three models InceptionResNetV2, Densenet201, and ResNet50 which is trained with only augmented data or metadata.
 It's transparent that the InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: 0.974 and 0.971 as opposed to 0.972 and 0.93, respectively.
@@
 
-After the experiment, the InceptionResNetV2 is chose to compare with the other SOTA models.
-
-\begin{table}
-	\begin{tabular}{| p{3cm} | c | c | c | c | c |}
+After reviewing, the InceptionResNetV2 is found to be the best model trained.
+Futhermore, the InceptionResNetV2 is compared with the other state of the art researched model.
+According to the table 8, there are six research that use the same data set: HAM10000 but different approaches.
+These models used in that research are also SOTA models sorted in ascending order.
+The table shows that the accuracy of the combination of InceptionResNetV2 with Soft-Attention, metadata and weight loss in this research is less than the InceptionResNetV2 with Soft-Attention and augmented data: 0.90 compared to 0.93 respectively.
+However, since Soumyyak et al use data augmentation for all class of an imbalanced data set, the f1-score and recall score are much lower.
+This is because the model in that research can only classify well on NV and VASC class which have the highest number of samples.
+On the other hand, the InceptionResNetV2 in this research also outperform the other model according to 5 indicator: accuracy, precision, f1-score, recall score, and auc score.
+\FloatBarrier
+\begin{table}[H]
+	\begin{tabular}{| p{4cm} | c | c | c | c | c |}
 		\hline
@@
 		\hline
-		s
+		Our Proposed & 0.9	& 0.86 &\textbf{0.86} & \textbf{0.81} & 0.974\\
+		\hline
+		InceptionResNetV2\cite{03358} & 0.93 & 0.89 & 0.75 & 0.71 & 0.97\\
+		\hline
+		\cite{03798} & - & 0.88 & 0.77 & 0.74 & - \\
+		\hline
+		\cite{09418} & 0.88 & - & - & - & - \\
+		\hline
+		\cite{01284} & 0.86 & - & - & - & - \\
+		\hline
+		GradCam and Kernel SHAP\cite{06612} & 0.88 & - & - & - & - \\
+		\hline
+		Student and Teacher\cite{03225} & 0.85 & 0.76 & 0.76 & - & - \\
+		\hline
 	\end{tabular}
+	\caption{Comparative Analysis}
+	\label{table:comparative-analysis}
 \end{table}
@@
 In this paper, my objective is to analyze the effect of metadata on the performance of model as well as identifying whether metadata can make the model less imbalanced or not.
-On the other hand, I also try to construct an optimized and balanced model that can be used on mobile phone or electronic devices.
+On the other hand, an optimized and balanced model that can be used on mobile phone or electronic devices is also constructed.
 The experiment shown that metadata improve the model performance, the factor that make the model much more imbalanced is the augmented data.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{In this paper, I am the only author, therefore I need to do all things including research, implementation, analyze data, writing draft resolution}
+\authorcontributions{Conceptualization, D.N.
+and K.D.; methodology, D.N.
+and K.D.; software, K.D.; validation, D.N., D.B.
+and K.D.; formal analysis, D.N.
+and K.D.; investigation, D.N., D.B.
+and K.D.; resources, D.N.; data curation, K.D.; writing---original draft preparation, K.D.; writing---review and editing, D.N.
+and D.B.; visualization, K.D.; supervision, D.N.
+and D.B.; project administration, D.N.
+All authors have read and agreed to the published version of the manuscript.}
 

### 2022-08-20 MDPI/Sensor Paper/template.tex
Update

@@
 \address{
-$^{1}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam \\
-$^{2}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam\\
-$^{3}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam}
+$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam\\
+$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, Vietnam\\
+$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam}
 
@@
 In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential.
-Along with the strong development of artificial intelligence technologies, many solutions and tools to support the diagnosis of skin diseases have been researched and developed.
-These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet, VGGNet.
-In this study, another approach to building tools to aid in the diagnosis of skin pathologies is proposed.
-SOTA (state of the art) models DenseNet, InceptionNet, ResNet, NasNet, MobileNet combined with Soft-Attention are used as backbone.
-In addition, personal information such as age and gender are also used.
-In addition, a new loss function	that takes into account the imbalance of the data is also proposed.
-Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published indexes.
-Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of floors is 4 times less, it achieves 86 percent accuracy and 30 times faster diagnosis.}
+Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed.
+In this paper, a combination of SOTA model such as DenseNet, InceptionNet, ResNet, NasNet, and MobileNet and Soft-Attention is proposed.
+Furthermore, personal information including age and gender are also used.
+It is worth to note that a new loss function	that takes into account the data imbalance is also proposed.
+Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively.
+Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than DenseNet201.
+}
 
@@
 	\end{tabular}
-	\caption{Related Works Summary.
-This table is a summary of the approach to skin lesion classification and segmentation.
-The first column illustrate the cite to the paper research.
-Column 2 shows a brief summary of the method that is stated in the associated paper.}
+	\caption{Related Works Summary.}
 	\label{table:related-work-summary}
@@
 There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
-The distribution of the data set is shown in the table \ref{table:data-distribution} below:
+The distribution of the data set is shown in the Table \ref{table:data-distribution} below:
 
@@
 	\end{tabular}
-	\caption{Data Distribution in HAM10000. This table illustrate the distribution of all class in the data set. The detail name of the skin disease in the data set can be found at the Abbreviations}
+	\caption{Data Distribution in HAM10000.}
 	\label{table:data-distribution}
@@
 \subsubsection{Metadata}
-The HAM10000 data set \cite{10417} also contain the metadata of patient including gender, age, and the capturing position illustrated in table \ref{table:metadata sample}
+The HAM10000 data set \cite{10417} also contain the metadata of patient including gender, age, and the capturing position illustrated in Table \ref{table:metadata sample}
 \begin{table}[H]
@@
 \subsubsection{Overall Architecture}
-The whole architecture of the model is represented in the figure \ref{fig:main-model}.
+The whole architecture of the model is represented in the Figure \ref{fig:main-model}.
 The model takes two input including Image data and Metadata.
@@
 
-The figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research.
+The Figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research.
 In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module.
@@
 
-The figure \ref{fig:mobile-model-structure}, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
+The Figure \ref{fig:mobile-model-structure}, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
 All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module.
@@
 
-In this paper, the unknowns is kept as a type as discussed in Metadata section.
+In this research, the unknowns is kept as a type as discussed in Metadata section.
 Sex, anatomical site and age are also category encoded and numerical normalized, respectively.
@@
 Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section.
-The Input schema is described in the table \ref{fig:input-schema}
+The Input schema is described in the Table \ref{fig:input-schema}
 
@@
 	\end{tabular}
-	\caption{Size and Parameters and Depth of backbone model used in this paper.
-This table summarizes the properties of the backbone models.
-The size column illustrates how many space need to store the model in megabyte.
-The parameters column demonstrate the number of parameters in the associated model.
-The last column, depth show the number of hidden layers in that model.
-Parameters and Depth are two crucial element to evaluate the optimized model stated in the Objective section.}
+	\caption{Size and Parameters and Depth of backbone model used in this paper.}
 	\label{table:model-summary}
@@
 
-In this paper, the Soft-Attention layer is applied in the same way in this paper \cite{03358}. The Soft-Attention module is described in the following diagram:
+In this research, the Soft-Attention layer is applied in the same way in this research \cite{03358}. The Soft-Attention module is described in the figure \ref{fig:soft-attention-block}
 
@@
 The model is evaluated by using the confusion matrix and related metrics.
-The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class.
+The Figure \ref{fig:confusion-matrix} illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class.
 Consider a confusion matrix $A$ with $C$ number of class.
@@
 
-According to the Figure 10, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only.
+According to the Table \ref{table:overall-acc}, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only.
 While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.79$ and $0.84$ respectively, their training with metadata are $0.90$ and $0.89$, respectively.
@@
 
-Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to figure 10, 11, 12, 13.
-As a results, augmented data model does not classify well on all class as InceptionResNetV2 trained on augmented data have f1-score on class df and akiec is just above $0.3$ and $0.4$, separately while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way arcoding to the figure 12.
+\begin{table}[H]
+	\centering
+	\begin{tabular}{| l | c  c | }
+		\hline
+		Model & ACC(AD) & ACC(MD)\\ 
+		\hline
+		InceptionResNetV2 & 0.79 & \textbf{0.90}\\
+		\hline
+		DenseNet201 & 0.84 & \textbf{0.89}\\
+		\hline
+		ResNet50 & 0.76 & 0.70 \\
+		\hline
+		ResNet152 & - & 0.57\\
+		\hline
+		NasNetLarge & - & 0.84\\
+		\hline
+		MobileNetV2 & - & 0.81\\
+		\hline
+		MobileNetV3Small & - & 0.78\\
+		\hline
+		MobileNetV3Large & - & \textbf{0.86}\\
+		\hline
+		NasNetMobile & - & \textbf{0.86}\\
+		\hline
+	\end{tabular}
+	\caption{Accuracy of all models.
+ACC stands for accuracy.
+AD stands for augmented data, this indicate that the model is trained with augmented data.
+MD stands for Metadata which indicate that the model is trained with Metadata}
+	\label{table:overall-acc}
+\end{table}
+
+Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to Figure \ref{fig:den f1}, \ref{fig:incep f1}, \ref{fig:den recall}, and \ref{fig:incep recall}.
+As a results, augmented data model does not classify well on all class as InceptionResNetV2 trained on augmented data have f1-score on class df and akiec is just above $0.3$ and $0.4$, separately while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way arcoding to the Figure \ref{fig:incep f1}.
 However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
@@
 
-This problem is also true with the recall score according to fugure 13.
+This problem is also true with the recall score according to Figure \ref{fig:den recall} and \ref{fig:incep recall}.
 DenseNet201, InceptionResNetV2, trained with augmented data has expected value of recall of $0.56$, $0.69$, respectively, while the combination of DenseNet201, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
@@
 \end{figure}
+
 \begin{figure}[H]
@@
 Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
-MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately according to the  table A4 appendix C.2.
+MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately according to the Table \ref{appendix-table:mobile-performance}.
 It's transparent that MobileNetV3Large and NasNetMobile are the two best performance model.
@@
 
-The table 5 shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others.
+The Table \ref{table:optimized-performance-mobile-model} shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others.
 In detail, MobileNetV3Large whose the number of parameters is 5.5 millions which is four and ten times less than DenseNet201 and InceptionResNetV2, respectively.
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1\linewidth]{Definitions/ADvsMD}
-	\caption{ROC AUC Score. This figure illustrate the AUC score associated with models including models trained with augmented data and models trained with metadata}
-	\label{fig:ADvsDC-AUC}
-\end{figure}
-
-The figure 15 shows the AUC score of the three models InceptionResNetV2, Densenet201, and ResNet50 which is trained with only augmented data or metadata.
+The Table \ref{table:overall-auc} shows the AUC score of the three models InceptionResNetV2, Densenet201, and ResNet50 which is trained with only augmented data or metadata.
 It's transparent that the InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: 0.974 and 0.971 as opposed to 0.972 and 0.93, respectively.
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1\linewidth]{Definitions/vsALL}
-	\caption{ROC AUC Score of all model trained in this paper.}
-	\label{fig:vsallAUC}
-\end{figure}
+\begin{table}[H]
+	\centering
+	\begin{tabular}{| l | c  c | }
+		\hline
+		Model & AUC(AD) & AUC(MD)\\ 
+		\hline
+		InceptionResNetV2 & 0.971 & \textbf{0.974}\\
+		\hline
+		DenseNet201 & 0.93 & \textbf{0.97}\\
+		\hline
+		ResNet50 & \textbf{0.95} & 0.93 \\
+		\hline
+		ResNet152 & - & 0.87\\
+		\hline
+		NasNetLarge & - & \textbf{0.96}\\
+		\hline
+		MobileNetV2 & - & \textbf{0.97}\\
+		\hline
+		MobileNetV3Small & - & \textbf{0.96}\\
+		\hline
+		MobileNetV3Large & - & \textbf{0.97}\\
+		\hline
+		NasNetMobile & - & \textbf{0.97}\\
+		\hline
+	\end{tabular}
+	\caption{AUC(area under the curve) of all models.
+AD stands for augmented data, this indicate that the model is trained with augmented data.
+MD stands for Metadata which indicate that the model is trained with Metadata}
+	\label{table:overall-auc}
+\end{table}
 
@@
 Futhermore, the InceptionResNetV2 is compared with the other state of the art researched model.
-According to the table 8, there are six research that use the same data set: HAM10000 but different approaches.
+According to the Table \ref{table:comparative-analysis}, there are six research that use the same data set: HAM10000 but different approaches.
 These models used in that research are also SOTA models sorted in ascending order.
-The table shows that the accuracy of the combination of InceptionResNetV2 with Soft-Attention, metadata and weight loss in this research is less than the InceptionResNetV2 with Soft-Attention and augmented data: 0.90 compared to 0.93 respectively.
+The Table shows that the accuracy of the combination of InceptionResNetV2 with Soft-Attention, metadata and weight loss in this research is less than the InceptionResNetV2 with Soft-Attention and augmented data: 0.90 compared to 0.93 respectively.
 However, since Soumyyak et al use data augmentation for all class of an imbalanced data set, the f1-score and recall score are much lower.
@@
 \begin{table}[H]
+	\centering
 	\begin{tabular}{| p{4cm} | c | c | c | c | c |}
@@
 
+However, there is still some drawbacks of the model that the InceptionResNetV2 cannot well classify the melanoma and the nevus.
+According to Figure \ref{fig:nevusVSmela} the model sometime classify the black nevus as the melanoma because of the same color between them.
+However, this problem is not true for the hard black or big melanoma or the red black nevus.
+Some future approach that can be proposed are change the type of color to other to fix the same color problem.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/img_class_nevus_mela}
+	\caption{Model ability to classify melanoma and nevus}
+	\label{fig:nevusVSmela}
+\end{figure}
+
 \section{Conclusions}
-In this paper, my objective is to analyze the effect of metadata on the performance of model as well as identifying whether metadata can make the model less imbalanced or not.
-On the other hand, an optimized and balanced model that can be used on mobile phone or electronic devices is also constructed.
-The experiment shown that metadata improve the model performance, the factor that make the model much more imbalanced is the augmented data.
-This problem can be solve quite absolutely by using aforementioned weighted loss function.
-Using weighted loss function make the expected value of model f1-score increase.
-At the end of the experiment, mobile model is found that can achieve great performance without either the large number of parameters or depth.
-
+In this research, our proposed is to construct a model as a combination of backbone models and Soft-Attention.
+Moreover, the model takes two inputs including image data and metadata.
+besides, a new weight loss function is applied to figure out the data imbalance problem.
+Finally, the combination of InceptionResNetV2, Soft-Attention, and Metadata is the best model.
+Although the accuracy and the precision of the model are not the highest, the f1-score, recall, and AUC-score is the highest and the most balanced indicator.
+Therefore, InceptionResnetV2 can classify well in all classes including low samples classes.
+Otherwise, during the experiment, the combination of MobileNetV3, Soft-Attention, and Metadata achieve an accuracy that is nearly the same as InceptionResNetV2, though with fewer number parameters and depth.
+Therefore the infer time is much less than the InceptionResNetV2.
+This result opens the door to constructing a great performance model that can be applied to mobile, IoT devices.
 \vspace{6pt}
@@
 
-\acknowledgments{I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project.
-He gave a chance to use High GPU computing computer for AI Training.
-Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.}
+\acknowledgments{}
 
@@
 %% Optional
-\sampleavailability{Samples of the compounds ... are available from the authors.}
+\sampleavailability{}
 
@@
 The term "with Metadata and WeightLoss" means that the model is trained with metadata including age, gender, localization and the weight loss function, there is no augmented data contribution}
-	\label{table:F1-score-summary}
+	\label{appendix-table:F1-score-summary}
 \end{table}
@@
 	\caption{Recall score of each class and the expected value of recall score from each model}
-	\label{table:recall-score-summary}
+	\label{appendix-table:recall-score-summary}
 \end{table}
@@
 All of them are average indicator}
-	\label{table:mobile-performance}
+	\label{appendix-table:mobile-performance}
 \end{table}
@@
 \end{adjustwidth}
+
 \end{document}

### 2022-08-20 MDPI/Sensor Paper/template.tex
update

@@
 % Full title of the paper (Capitalized)
-\Title{DIAGNOSTIC SUPPORT OF SKIN LESION
-	CLASSIFICATION USING CNN AND SOFT
-	ATTENTION}
+\Title{SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION}
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{DIAGNOSTIC SUPPORT OF SKIN LESION
-	CLASSIFICATION USING CNN AND SOFT
-	ATTENTION}
+\TitleCitation{SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION}
 
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
-\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorA}{0000-0001-7152-0191} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0001-9934-7474} % Add \orcidB{} behind the author's name
 \newcommand{\orcidauthorC}{0000-0002-2566-5637} % Add \orcidC{} behind the author's name
@@
 % Authors, for the paper (add full first names)
-\Author{Viet Dung Nguyen $^{1,\dagger}$\orcidA{}, Ngoc Dung Bui $^{2,\dagger}$\orcidB{} and Khoi Do Hoang $^{3,\dagger}$\orcidC{}}
+\Author{Viet Dung Nguyen $^{1,\dagger, *}$\orcidA{}, Ngoc Dung Bui $^{2,\dagger}$\orcidB and Hoang Khoi Do  $^{1,\dagger}$\orcidC{}}
 
@@
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Dung Viet Nguyen, Ngoc Dung Bui and Khoi Do Hoang}
+\AuthorNames{Viet Dung Nguyen, Ngoc Dung Bui and Hoang Khoi Do}
 
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Nguyen, D.; Bui, D.; Khoi, D.}
+\AuthorCitation{Nguyen, V.D.; Bui, N.D.; Do, H.K.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 % Contact information of the corresponding author
-\corres{Correspondence: dung.nguyenviet1@hust.edu.vn; Tel.:  +84-9834-443-22 (D.N.)}
+\corres{Correspondence: dung.nguyenviet1@hust.edu.vn; Tel.:  +84-9834-443-22 (N.V.D.)}
 
 % Current address and/or shared authorship
-\firstnote{Current address: 1st Dai Co Viet Street, Ha Noi, Viet Nam} 
+\firstnote{Current address: 1st Dai Co Viet Street, Ha Noi, Vietnam} 
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 
-% Abstract (Do not insert blank lines, i.e. \\) 
+% Abstract (Do not insert blank lines, i.e. \\) s
 \abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air.
@@
 Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively.
-Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than DenseNet201.
-}
+Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than InceptionResNetV2.}
 
 % Keywords
-\keyword{AI Diagnosis, Skin Sancer, Skin Lesion
-	Classification, Deep Learning, Machine Learning)}
+\keyword{Skin Lesions, Classification, Deep Learning, Soft-Attention, Imbalance)}
 
@@
 
-In order to adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance.
+To adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance.
 Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet \cite{04861}, Inception \cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet \cite{03385} \cite{05027}, and NasNet \cite{07012}.
@@
 SkinLinkNet \cite{12602} and WonderM \cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively.
-In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600).
+In WonderM, the method used is padding the image so that the image has the shape increased from (450, 600) to (600, 600).
 In SkinLinkNet, instead resize the image down to (448, 448).
@@
 All missing data point of age is set to 0.
-In order to overcome the missing data problem, the research apply one-hot encoding to the group but the initial validation is poor performance then numerical encoding is applied.
+To overcome the missing data problem, the research apply one-hot encoding to the group but the initial validation is poor performance then numerical encoding is applied.
 
@@
 	\centering
-	\includegraphics[width=0.5\linewidth]{Definitions/MainModel - Model Form}
+	\includegraphics[width=0.8\linewidth]{Definitions/MainModel - Model Form}
 	\caption{Overall Model Architecture}
@@
 \subsubsection{Soft-Attention Module}
-Applying the Soft-Attention layer in deep learning is not a new approach.
-Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively.
-In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}.
+Soft-Attention has been used in various applications: image caption generation such as \cite{03044} or handwriting verification \cite{202017}.
 Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights.
-The function below describes the flow of the Soft-Attention module:
+Soft-Attention is described in below equation:
 \[
@@
 \]
-In order to apply Soft-Attention, there are two main steps.
+The Figure \ref{fig:soft-attention} shows the two main steps of applying Soft-Attention is applied in two main steps.
 Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map \cite{08513}.
-This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$.
+This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network (CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$.
 The output of this convolution is normalized using the soft-max function to generate K (a constant value) attention maps.
@@
 	\includegraphics[width=1\linewidth]{Definitions/SoftAttention}
-	\caption{Soft-Attention Module}
+	\caption{Soft-Attention Layer}
 	\label{fig:soft-attention}
@@
 Test set, otherwise is provided by the HAM10000 data set, contains 857 images.
-In order to analyze the effect of augmented data on the model, during the training the image data is augmented by the following technique:\\
+To analyze the effect of augmented data on the model, during the training the image data is augmented by the following technique:\\
 - Rotation Range: rotate the image in a fixed angle. \\
 - Width and height shift range: Shift the image horizontally and vertically, respectively. \\
-- Zoom Range:  image to create new image. \\
-- Horizontal and vertical flipping: flipping the image horizontally and vertically to create new fzoom in theorm of image.\\
+- Zoom Range:  Zoom in or zoom out the image to create new image. \\
+- Horizontal and vertical flipping: Flipping the image horizontally and vertically to create new image.\\
 Otherwise, all of models is trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$.
@@
 \[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
-where Sensitivity and specificity mathematically describe the accuracy of a test which reports the presence or absence of a condition.
+where Sensitivity and Specificity mathematically describe the accuracy of a test which reports the presence or absence of a condition.
 Individuals for which the condition is satisfied are considered "positive" and those for which it is not are considered "negative".
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Conceptualization, D.N.
-and K.D.; methodology, D.N.
-and K.D.; software, K.D.; validation, D.N., D.B.
-and K.D.; formal analysis, D.N.
-and K.D.; investigation, D.N., D.B.
-and K.D.; resources, D.N.; data curation, K.D.; writing---original draft preparation, K.D.; writing---review and editing, D.N.
-and D.B.; visualization, K.D.; supervision, D.N.
-and D.B.; project administration, D.N.
+\authorcontributions{Conceptualization, V.D.N.
+and H.K.D.; methodology, V.D.N.
+and H.K.D.; software, K.D.; validation, V.D.N., N.D.B.
+and H.K.D.; formal analysis, V.D.N.
+and H.K.D.; investigation, V.D.N., N.D.B.
+and H.K.D.; resources, V.D.N.; data curation, H.K.D.; writing---original draft preparation, H.K.D.; writing---review and editing, V.D.N.
+and N.D.B.; visualization, H.K.D.; supervision, V.D.N.
+and N.D.B.; project administration, V.D.N.
 All authors have read and agreed to the published version of the manuscript.}

### 2022-08-20 MDPI/Sensor Paper/template.tex
Update Paper Ver 12

@@
 % Keywords
-\keyword{Skin Lesions, Classification, Deep Learning, Soft-Attention, Imbalance)}
+\keyword{Skin Lesions, Classification, Deep Learning, Soft-Attention, Imbalance}
 
@@
 Since the data set face the imbalanced problem then class weight for the loss is applied.
-This formula below is used to calculate the class weight:
+In this research, both of the original weight and a new weight formula is implementation.
+Originally, the weight is calculated by taking the inverse of percentage that each class accounts for.
+The new weight formula is described as follow:
 \[W = N \odot D\]
@@
 
+Besides the comparison between original weight loss based model and the new weight loss based model is also conducted on the three best performance model including InceptionResNetV2, DenseNet201, MobileNetV3.
+After the experiment, it is found out that the new weight loss function dose not only contribute to the model to overcome the data imbalance problem but it also make the accuracy increase.
+The performance of models is described in the Table \ref{table:loss-comparision}
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{| l | c | c |}
+		\hline
+		Model & Original Loss Accuracy & New Loss Accuracy\\
+		\hline
+		InceptionResNetV2 & 0.74 & 0.90\\
+		DenseNet201 & 0.81 & 0.89\\
+		MobileNetV3 & 0.80 & 0.86\\
+		\hline
+	\end{tabular}
+	\caption{Loss based model accuracy comparison}
+	\label{table:loss-comparision}
+\end{table}
+
 After reviewing, the InceptionResNetV2 is found to be the best model trained.

### 2022-08-25 MDPI/Sensor Paper/template.tex
Update

@@
 \address{
-$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam\\
-$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, Vietnam\\
-$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam}
+$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam; dung.nguyenviet1@hust.edu.vn\\
+$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, Vietnam; dnbui@utc.edu.vn\\
+$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam; khoi.dh200322@sis.hust.edu.vn}
 
@@
 
-Besides the comparison between original weight loss based model and the new weight loss based model is also conducted on the three best performance model including InceptionResNetV2, DenseNet201, MobileNetV3.
+Besides the comparison between original weight loss calculated by the sample percentage of each class model and the new weight loss based model is also conducted on the three best performance model including InceptionResNetV2, DenseNet201, MobileNetV3.
 After the experiment, it is found out that the new weight loss function dose not only contribute to the model to overcome the data imbalance problem but it also make the accuracy increase.
@@
 	\centering
-	\begin{tabular}{| l | c | c |}
-		\hline
-		Model & Original Loss Accuracy & New Loss Accuracy\\
-		\hline
-		InceptionResNetV2 & 0.74 & 0.90\\
-		DenseNet201 & 0.81 & 0.89\\
-		MobileNetV3 & 0.80 & 0.86\\
+	\begin{tabular}{| l | c | c | c |}
+		\hline
+		Model & No Weight & Original Loss Accuracy & New Loss Accuracy\\
+		\hline
+		InceptionResNetV2 & 0.74 & 0.79 & 0.90\\
+		DenseNet201 & 0.81 & 0.84 & 0.89\\
+		MobileNetV3 & 0.79 & 0.80 & 0.86\\
 		\hline

### 2022-09-03 MDPI/Sensor Paper/template.tex
Update

@@
 \address{
-$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam; dung.nguyenviet1@hust.edu.vn\\
+$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi University of Science and Technology, Vietnam; dung.nguyenviet1@hust.edu.vn\\
 $^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, Vietnam; dnbui@utc.edu.vn\\
-$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam; khoi.dh200322@sis.hust.edu.vn}
+$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi University of Science and Technology, Vietnam; khoi.dh200322@sis.hust.edu.vn}
 
@@
 Test set, otherwise is provided by the HAM10000 data set, contains 857 images.
-To analyze the effect of augmented data on the model, during the training the image data is augmented by the following technique:\\
+To analyze the effect of augmented data on the model, before the training the image data is augmented to 53573 images by the following technique:\\
 - Rotation Range: rotate the image in a fixed angle. \\
@@
 		\hline
-		ResNet50 & 0.76 & 0.70 \\
-		\hline
-		ResNet152 & - & 0.57\\
+		ResNet50 & 0.76 & 0.70\\
+		\hline
+		ResNet152 & 0.81 & 0.57\\
 		\hline
@@
 		\hline
-		MobileNetV3Large & - & \textbf{0.86}\\
-		\hline
-		NasNetMobile & - & \textbf{0.86}\\
+		MobileNetV3Large & 0.85 & \textbf{0.86}\\
+		\hline
+		NasNetMobile & 0.84 & \textbf{0.86}\\
 		\hline

### 2022-09-11 MDPI/sensors-1915564/template.tex
Update Paper Review 1

--- 2022-09-03 MDPI/Sensor Paper/template.tex
@@
 \usepackage{comment}
+\usepackage{soulutf8}
+\usepackage[adjustmargins]{LatexPackage/trackchanges}
+\addeditor{H.K.D}
 
@@
 Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed.
-In this paper, a combination of SOTA model such as DenseNet, InceptionNet, ResNet, NasNet, and MobileNet and Soft-Attention is proposed.
+In this paper, a combination of \add[H.K.D]{one} SOTA model \change[H.K.D]{such as}{including} DenseNet, InceptionNet, ResNet, NasNet,  MobileNet and Soft-Attention is proposed.
 Furthermore, personal information including age and gender are also used.
@@
 \subsection{Problem Statement}
-Skin cancer is one of the most common cancers leading to worldwide death.
-Every day, more than 9500 \cite{03358} people in the United States are diagnosed with skin cancer.
-Otherwise, 3.6 \cite{03358} million people are diagnosed with basal cell skin cancer each year.
-According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase \cite{11872}.
-In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States \cite{11872}.
+\change[H.K.D]{One of the most common malignancies that cause death globally is skin cancer.
+In the United States, more than 9500 persons receive a skin cancer diagnosis each day \mbox{\cite{03358}}.
+The Skin Cancer Foundation reports that there is an ongoing rise in the incidence of skin cancer worldwide \mbox{\cite{11872}}.
+In the United States, 192,310 new cases of melanoma are anticipated to be detected in 2019.
+On the other hand, if patients receive an early diagnosis, their chances of survival are 99 percent.
+Survival is, however, generally poor after the illness has spread beyond the skin \mbox{\cite{11872}}.
+Additionally, there is a need for an efficient solution because to the rising prevalence of skin malignancies, low awareness among a population that is expanding, and a lack of sufficient clinical competence and services.}{Skin cancer is one of the most common cancers leading to worldwide death.
+Every day, more than 9500 \mbox{\cite{03358}} people in the United States are diagnosed with skin cancer.
+Otherwise, 3.6 \mbox{\cite{03358}} million people are diagnosed with basal cell skin cancer each year.
+According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase \mbox{\cite{11872}}.
+In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States \mbox{\cite{11872}}.
 On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent.
-However, once the disease progresses beyond the skin, survival is poor \cite{11872}.
-Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.
+However, once the disease progresses beyond the skin, survival is poor \mbox{\cite{11872}}.
+Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.}
 
@@
 \subsection{Related Works}
-Skin lesion classification is not a new area, since there are many great performance models constructed.
-One of the most cutting-edge technologies that have been used is Soft-Attention as stated in \cite{03358}.
-Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \cite{06993}, InceptionResNetV2 \cite{00567}, ResNet50 \cite{03385} \cite{05027}, VGG16 \cite{1556} and Soft-Attention layer.
+\change[H.K.D]{Skin lesion classification is not a new area, since there are many great performance models constructed.
+One of the most cutting-edge technologies that have been used is Soft-Attention as stated in \mbox{\cite{03358}}.
+Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \mbox{\cite{06993}}, InceptionResNetV2 \mbox{\cite{00567}}, ResNet50 \mbox{\cite{03385} \cite{05027}}, VGG16 \mbox{\cite{1556}} and Soft-Attention layer.
 Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model.
@@
 Using those above backbones has been tried by many previous papers.
-Rishu Garg et al   \cite{03798} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set.
+Rishu Garg et al \mbox{\cite{03798}} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set.
 Besides, they also use data augmentation to avoid the imbalance of the data set.
@@
 
-Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3 \cite{00567} model.
+Amirreaza et al \mbox{\cite{10348}} do not only use those above backbone model but also used InceptionV3 \mbox{\cite{00567}} model.
 In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set.
@@
 
-Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet \cite{11946} and SeNET \cite{01507} instead and CutOut \cite{04552v2} method which involves creating holes of different sizes on the images i.e.
+Another paper that uses the backbone models is \mbox{\cite{09418}}, Hemanth et al decide to use EfficientNet \mbox{\cite{11946}} and SeNET \mbox{\cite{01507}} instead and CutOut \mbox{\cite{04552v2}} method which involves creating holes of different sizes on the images i.e.
 technically making a random portion of image inactive during data augmentation process.
 
-Otherwise, \cite{01284} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.
-
-Another state of the art is GradCam and Kernel SHAP \cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.
+Otherwise, \mbox{\cite{01284}} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.
+
+Another state of the art is GradCam and Kernel SHAP \mbox{\cite{06612}}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.
 In that research they use three data sets containing HAM10000, BCN-20000 and MSK.
@@
 On the other hand, there are also many state of the art whose great performance on skin lesion classification.
-The Student and Teacher Model is also a high performance model in 2021 \cite{03225}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
+The Student and Teacher Model is also a high performance model in 2021 \mbox{\cite{03225}}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
 Therefore, they can take full advantage of what others learn.
 
-SkinLinkNet \cite{12602} and WonderM \cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively.
+SkinLinkNet \mbox{\cite{12602}} and WonderM \mbox{\cite{03426}} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively.
 In WonderM, the method used is padding the image so that the image has the shape increased from (450, 600) to (600, 600).
@@
 
-Another approach is using metadata including gender, age, and capturing position as stated in  \cite{03910} by Nil Gessert et al.
+Another approach is using metadata including gender, age, and capturing position as stated in \mbox{\cite{03910}} by Nil Gessert et al.
 The metadata is fed into fully connected neural network after being encoded into one-hot vector.
@@
 On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning.
-Random Forest, XGBoost, and Support Vector Machines are tested by  \cite{03798} of Rishu Garg et al.
-Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \cite{10348} by Amirreza Rezvantalab et al.
-Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al.
-
-\begin{table}
+Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al.
+Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \mbox{\cite{10348}} by Amirreza Rezvantalab et al.
+Matrix Transformation, besides is also applied before the soft-max activation function in \mbox{\cite{05045}} by Michele Alberti et al.}
+
+{Skin lesion classification is not a new area, since there are many great performance models constructed, recent years.
+The skin classification approaches can be divided into two main approaches: Deep Learning and Machine Learning.
+Both approaches gain great performance.
+Data Augmentation and Feature Extractor, otherwise are two main supporters that make the model better.
+	\begin{table}[H]
 		\centering
@@
 	\end{table}
+\subsubsection{Deep Learning Approach}
+In Deep Learning, one of the most cutting-edge technologies that have been used is Soft-Attention as stated in \mbox{\cite{03358}}.
+Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \mbox{\cite{06993}}, InceptionResNetV2 \mbox{\cite{00567}}, ResNet50 \mbox{\cite{03385} \cite{05027}}, VGG16 \mbox{\cite{1556}} and Soft-Attention layer.
+Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model.
+For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively.
+DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer.
+Soumyyak et al proposed method gain a greate performance and also outperform many other studies with the accuracy of 0.93 and the precision of 0.92.
+However using the Data Augmentation on an imbalanced data set make the model cannot classify well on all of the classes, therefore their model got the recall and f1-score of 0.71 and 0.75, respectively.
+In this research, our proposed method also consider this problem and solve it.
+
+Using those above backbones has been tried by many previous papers.
+Rishu Garg et al \mbox{\cite{03798}} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set.
+Besides, they also use data augmentation to avoid the imbalance of the data set.
+Histogram Equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, Support Vector Machine.	Histogram Equalization can be consider as a heat map that takes the main feature as the number of occurrences of the same value pixel.
+This approach also gain great performance with the accuracy of 0.90 and the precision of 0.88.
+However this approach can be bias since the one skin image of the data set contain the skin lesion at the center and the background skin so that histogram may treat background with more number of occurrence of the same pixel value.
+In this research, our proposed method use the Soft-Attention which can create a heat map feature of the lesion.
+Otherwise, Rishu Garg et al proposed method also face the problem of imbalanced classifying due to the imbalanced data set with the f1-score and recall is 0.77 and 0.74, respectively.
+
+Amirreaza et al \mbox{\cite{10348}} do not only use those above backbone model but also used InceptionV3 \mbox{\cite{00567}} model.
+In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set.
+Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3.
+The best ROC AUC values for melanoma and basal
+cell carcinoma are 0.94 (ResNet152) and 0.93 (DenseNet201).
+
+Another paper that uses the backbone models is \mbox{\cite{09418}}, Hemanth et al decide to use EfficientNet \mbox{\cite{11946}} and SeNET \mbox{\cite{01507}} instead and CutOut \mbox{\cite{04552v2}} method which involves creating holes of different sizes on the images i.e.
+technically making a random portion of image inactive during data augmentation process.
+Although this approach get the accuracy of 0.88, it may be bias due to the CutOut method since this method can create a hole overlap the skin lesion field.
+The method accuracy is also low due to the data augmentation process.
+
+Otherwise, \mbox{\cite{01284}} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.
+This approach get the accuracy of 0.86.
+Although, this approach figure out the data imbalance problem, got a low accuracy may due to the RandArgument.
+If the skin lesion part of the image is quite big or quite small the cropped image may contain only skin or the lesion spread out the whole image.
+
+Another state of the art is GradCam and Kernel SHAP \mbox{\cite{06612}}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.
+In that research they use three data sets containing HAM10000, BCN-20000 and MSK.
+Before feeding into the models, the images are preprocessed by binarized with a very low threshold to find the center of mass.
+This approach got the AUC score of 0.85.
+
+On the other hand, there are also many state of the art whose great performance on skin lesion classification.
+The Student and Teacher Model is also a high performance model in 2021 \mbox{\cite{03225}}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
+Therefore, they can take full advantage of what others learn.
+The Student and Teacher model get the accuracy of 0.85, however the precision and f1-score are quite low 0.76.
+
+SkinLinkNet \mbox{\cite{12602}} and WonderM \mbox{\cite{03426}} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively.
+In WonderM, the method used is padding the image so that the image has the shape increased from (450, 600) to (600, 600).
+In SkinLinkNet, instead resize the image down to (448, 448).
+Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively.
+This approach get the AUC score of 0.92.
+
+Another approach is using metadata including gender, age, and capturing position as stated in \mbox{\cite{03910}} by Nil Gessert et al.
+The metadata is fed into fully connected neural network after being encoded into one-hot vector.
+All missing data point of age is set to 0.
+To overcome the missing data problem, the research apply one-hot encoding to the group but the initial validation is poor performance then numerical encoding is applied.
+The metadata is then fed into two block networks, each one containing a Dense Layer, a Batch Normalization, a ReLU activation function, and a Dropout.
+After all the feature vector extract from image is then concatenate with the feature vector extracted from metadata.
+Otherwise, the data augmentation is also applied.
+This approach got the recall score of 0.74.
+The low recall score may be due to the imbalanced data set.
+
+\subsubsection{Machine Learning Approach}
+In Machine Learning, there are also many approaches.
+Since the image data is quite complex for Machine Learning algorithm, therefore using feature extractor or feature preprocessing to another form of data is recommended.
+
+Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al.
+In this approach, the data is fed directly into the Machine Learning algorithm and show out no promising result, therefore Rishu Garg et al dose not show the result of the Machine Learning algorithm.
+
+Besides, Deep Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \mbox{\cite{09365}} by Amirreza Rezvantalab et al.
+In the Deep Isolation Forest, an feature extractor is applied by using CNN to learn the main pattern of the image.
+After that, the feature map is then fed into K isolation forest estimators using bagging algorithm.
+The Deep Isolation Forest got the accuracy of 0.9 and the confidence of 0.86.
+However, the AUC score is just 0.74, this may due to the limitation of Machine Learning algorithm.
+
+Matrix Transformation, otherwise is also applied before the soft-max activation function in \mbox{\cite{05045}} by Michele Alberti et al.
+In this approach the image is fed into a general model using sequence of residual block.
+The feature maps created from those above residual block is then fed into an Global Average Pooling to create a feature vector.
+This feature vector is then extracted by CNN-1D and transformed by Discrete Fourier Transformation (DFT) as a filter before going to the soft-max layer.
+}
+
 \subsection{Proposed Method}
@@
 \subsubsection{Input Schema}
+\add[H.K.D]{Image preprocessing is an essential part before the training process because of the ability to extract main pattern of an image.
+In this stage, the image can be changed the color channel so that the main feature is separated from the useless part.
+Image Retrieval, otherwise has significantly create a vector that represent the main feature of an image.
+Those image retrieval techniques can be energy compaction, primitive pattern units, etc.
+Shervan Fekri-Ershad et al create an feature vector by calculating the element wise product of histogram vector in each channel of an image \mbox{\cite{2012.4305}}.
+Then comparing the Euclidean distance between this feature vector and the average feature vector of the whole data set with a thresh hold, they can extract the skin part of the image.}
+
 In this research, the image data is both augmented for all class, the number of image increase to 18015 images and keep original form.
@@
 Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights.
-Soft-Attention is described in below equation:
-\[
+Soft-Attention is described in the Equation \ref{eqn:softatt}.
+\begin{equation}
+	\label{eqn:softatt}
 	f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
-\]
+\end{equation}
+
 The Figure \ref{fig:soft-attention} shows the two main steps of applying Soft-Attention is applied in two main steps.
@@
 
-In this research, the Soft-Attention layer is applied in the same way in this research \cite{03358}. The Soft-Attention module is described in the figure \ref{fig:soft-attention-block}
+In this research, the Soft-Attention layer is applied in the same way in this research \cite{03358}. The Soft-Attention module is described in the figure \ref{fig:soft-attention-block}.
 
@@
 Let $N$, and $C$ is the number of training examples and number of class respectively.
-The categorical cross-entropy loss is presented as:
-\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
+The categorical cross-entropy loss is presented in the Equation \ref{eqn:weightlossfunction}.
+\begin{equation}
+	\label{eqn:weightlossfunction}
+	L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)
+\end{equation}
+
 where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$.
@@
 Originally, the weight is calculated by taking the inverse of percentage that each class accounts for.
-The new weight formula is described as follow:
-\[W = N \odot D\]
-\[D = \begin{bmatrix}
+The new weight formula is described in the Equation \ref{eqn:weightformula} and \ref{eqn:vector-inverse-percent}.
+\add{This weight formula is the original weight multiplies with the inverse of number of class in the data set which make the training more balanced.
+It is inspired by the “balanced” heuristic proposed by Gary King et al\mbox{\cite{WV006-01}}}
+
+\begin{equation}
+	\label{eqn:weightformula}
+	W = N \odot D
+\end{equation}
+
+\begin{equation}
+	\label{eqn:vector-inverse-percent}
+	D = \begin{bmatrix}
 		\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
@@
 		\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
-\end{bmatrix}\]
+	\end{bmatrix}
+\end{equation}
+
 where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.
@@
 Test set, otherwise is provided by the HAM10000 data set, contains 857 images.
-To analyze the effect of augmented data on the model, before the training the image data is augmented to 53573 images by the following technique:\\
-- Rotation Range: rotate the image in a fixed angle. \\
-- Width and height shift range: Shift the image horizontally and vertically, respectively. \\
-- Zoom Range:  Zoom in or zoom out the image to create new image. \\
+To analyze the effect of augmented data on the model, before the training the image data is augmented to $53573$ images by the following technique:\\
+- Rotation Range: rotate the image in an \add[H.K.D]{angle range of 180}. \\
+- Width and height shift range: Shift the image horizontally and vertically \add[H.K.D]{in a range of 0.1}, respectively. \\
+- Zoom Range:  Zoom in or zoom out the image \add[H.K.D]{in a range of 0.1} to create new image. \\
 - Horizontal and vertical flipping: Flipping the image horizontally and vertically to create new image.\\
@@
 The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
-\[
-FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
-\]
-\[
+
+\begin{equation}
+	\label{eqn:FP}
+	FP = -TP + \sum_{k=1}^{i}A^i_k
+\end{equation}
+
+\begin{equation}
+	\label{eqn:FN}
+	FN = -TP + \sum_{k=1}^{j}A^j_k
+\end{equation}
+
+\begin{equation}
+	\label{eqn:TN}
 	TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
@@
 	\end{bmatrix}
-\]
+\end{equation}
+
 Then, the model is evaluated by the following metrics:
-\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
-where Sensitivity and Specificity mathematically describe the accuracy of a test which reports the presence or absence of a condition.
+
+\begin{equation}
+	\label{eqn:sens}
+	\text{Sensitivity (Sens)} = \frac{TP}{TP + FN}
+\end{equation}
+
+\begin{equation}
+	\label{eqn:spec}
+	\text{Specificity (Spec)} = \frac{TN}{TN + FP}
+\end{equation}
+
+\change[H.K.D]{Sensitivity  and Specificity  mathematically describe the accuracy of a test which reports the presence or absence of a condition.
 Individuals for which the condition is satisfied are considered "positive" and those for which it is not are considered "negative".
-Sensitivity or true positive rate refers to the probability of a positive test, conditioned on truly being positive while Specificity  or true negative rate refers to the probability of a negative test, conditioned on truly being negative.
-\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
-Precision or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative.
-F1-score, on the other hand refers the harmonic mean of precision and recall which mean the higher the f1-score is, the higher both precision and recall is.
+Sensitivity or true positive rate refers to the probability of a positive test, conditioned on truly being positive while Specificity  or true negative rate refers to the probability of a negative test, conditioned on truly being negative.}{Sensitivity (Equation \mbox{\ref{eqn:sens}}) and Specificity (Equation \mbox{\ref{eqn:spec}}) mathematically describe the accuracy of a test that identifies a condition's presence or absence. Sensitivity, also known as the true positive rate, is the likelihood that a test will result in a true positive, whereas specificity, also known as the true negative rate, is the likelihood that a test will result in a true negative.}
+
+\begin{equation}
+	\label{eqn:pre}
+	\text{Precision} = \frac{TP}{TP + FP}
+\end{equation}
+
+\begin{equation}
+	\label{eqn:f1}
+	\text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\
+\end{equation}
+
+Precision (Equation \ref{eqn:pre}) or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative.
+F1-score (Equation \ref{eqn:f1}), on the other hand refers the harmonic mean of precision and recall which mean the higher the f1-score is, the higher both precision and recall is.
 Besides, the expected value of precision, f1-score and recall-score are also applied because of the multi-class problem.
-\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
+
+\begin{equation}
+	\label{eqn:acc}
+	\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN}
+\end{equation}
+
+\begin{equation}
+	\label{eqn:balacc}
+	\text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}
+\end{equation}
+
 The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicate the probability of TP versus the probability of FP.
@@
 		\hline
-		MobileNetV2 & - & 0.81\\
+		MobileNetV2 & 0.83 & 0.81\\
 		\hline
@@
 		\hline
-		No. Parameters & \textbf{5.5M} & 20.2M & 55.9M\\
+		No. Trainable Parameters & \textbf{5,490,039} & 17,382,935 & 47,599,671\\
 		\hline
@@
 		\hline
+		Computational Complexity & & &\\		
+		\hline
 	\end{tabular}
-	\caption{How Performance of MobileNetV3Large be optimized}
+	\caption{\change[H.K.D]{Performance Comparison between MobileNetV3Large and DenseNet201, InceptionResNetV2}{How Performance of MobileNetV3Large be optimized}}
 	\label{table:optimized-performance-mobile-model}
@@
 		\hline
-		InceptionResNetV2 & 0.971 & \textbf{0.974}\\
+		InceptionResNetV2 & 0.971 & \textbf{0.975}\\
 		\hline
@@
 		\hline
-		ResNet152 & - & 0.87\\
+		ResNet152 & 0.97 & 0.87\\
 		\hline
@@
 		\hline
-		MobileNetV2 & - & \textbf{0.97}\\
+		MobileNetV2 & 0.95 & \textbf{0.97}\\
 		\hline
@@
 		\hline
-		MobileNetV3Large & - & \textbf{0.97}\\
-		\hline
-		NasNetMobile & - & \textbf{0.97}\\
+		MobileNetV3Large & 0.96 & \textbf{0.97}\\
+		\hline
+		NasNetMobile & 0.96 & \textbf{0.97}\\
 		\hline
 	\end{tabular}
-	\caption{AUC(area under the curve) of all models.
+	\caption{AUC (area under the curve) of all models.
 AD stands for augmented data, this indicate that the model is trained with augmented data.
@@
 		\hline
-		Our Proposed & 0.9	& 0.86 &\textbf{0.86} & \textbf{0.81} & 0.974\\
+		Our Proposed & 0.9	& 0.86 &\textbf{0.86} & \textbf{0.81} & 0.975\\
 		\hline
@@
 This result opens the door to constructing a great performance model that can be applied to mobile, IoT devices.
+\add[H.K.D]{As the result, proposed method and others still face the problem of badly distinguish between melanoma and black nevus because in some cases, the melanoma and the nevus image has the same lesion size and color.}
 \vspace{6pt}
@@
 
+\bibitem[Author2(year)]{WV006-01}
+Gary King, Langche Zeng Logistic Regression in Rare Events Data
+{\em Oxford Journal} 
+{\bf 2001}.
+
+\bibitem[Author2(year)]{2012.4305}
+Shervan Fekri-Ershad, Mohammad Saberi and Farshad Tajeripour AN INNOVATIVE SKIN DETECTION APPROACH
+USING COLOR BASED IMAGE RETRIEVAL TECHNIQUE
+{\em IJMA} 
+{\bf 2012}.
+
 \end{thebibliography}

### 2022-09-12 MDPI/sensors-1915564/template.tex
Update Paper Review 1.1
Update Paper Review 1.3

@@
 	\centering
-		\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
-			\hline
-			Research & Deep Learning & Machine Learning & Data 
-			Augmentation & Feture Extraction & Data set\\
-			\hline
-			\cite{03358} & x & & x & & HAM10000\\
-			\hline
-			\cite{03798} & x & x & x & x & HAM10000\\
-			\hline
-			\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
-			\hline
-			\cite{09418} & x & & x & & HAM10000\\
-			\hline
-			\cite{01284} & x & & x & & HAM10000\\
-			\hline
-			\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
-			\hline
-			\cite{03225} & x & & x & & HAM10000\\
-			\hline
-			\cite{12602} & x & & x & & HAM10000\\
-			\hline
-			\cite{03426} & x & & x & & HAM10000\\
-			\hline
-			\cite{03910} & x & & x & & HAM10000\\
-			\hline
-			\cite{05045} & & x & x & x & HAM10000\\
+	\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} | p{1cm} |}
+		\hline
+		Work & Deep Learning & Machine Learning & Data 
+		Augmentation & Feature Extractor & Data set & Result\\
+		\hline
+		\cite{03358} & Classify & & x & & HAM10000 & 0.93 (ACC)\\
+		\hline
+		\cite{03798} & Classify & Classify & x & x & HAM10000 & 0.9 (ACC)\\
+		\hline
+		\cite{10348} & Classify & Classify & x & & HAM10000, $PH^2$ & \\
+		\hline
+		\cite{09418} & Classify & & x & & HAM10000 & 0.88 (ACC)\\
+		\hline
+		\cite{01284} & Classify & & x & & HAM10000 & 0.86 (ACC)\\
+		\hline
+		\cite{06612} & Classify & & x & x & HAM10000, BCN-20000, MSK & 0.85 (ACC)\\
+		\hline
+		\cite{03225} & Classify & & x & & HAM10000 & 0.85 (ACC)\\
+		\hline
+		\cite{12602} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
+		\hline
+		\cite{03426} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
+		\hline
+		\cite{03910} & Classify & & x & & HAM10000 & 0.74 (recall)\\
+		\hline
+		\cite{05045} & & Classify & x & x & HAM10000 & \\
+		\hline
+		\cite{2101.133} & Classify&  & x &  & HAM10000 & 0.92 (ACC)\\
+		\hline
+		\cite{22750} & Seg&  &  &  & HAM10000 & 0.99 (ACC)\\
+		\hline
+		\cite{9445180} & Seg &  &  &  & HAM10000 & 0.97 (ACC)\\
 		\hline
@@
 
-Using those above backbones has been tried by many previous papers.
+Using those above backbones has been tried by many previous researches.
 Rishu Garg et al \mbox{\cite{03798}} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set.
@@
 
+Instead of using the whole imbalanced data set, Abayomi-alli et al decide to separate the data set into two subset, one contains only melanoma and the other one contains the rest \mbox{\cite{2101.133}}.
+Before feeding the data to classify the melanoma, the training data is then augmented by SMOTE method.
+SMOTE creates artificial instances by oversampling the minority class.
+SMOTE recognizes k-minority class neighbors that are near to each minority class sample by using the covariance matrix.
+This approach got the accuracy, recall and f1-score of 0.92, 0.87 and 0.82, respectively.
+
 Amirreaza et al \mbox{\cite{10348}} do not only use those above backbone model but also used InceptionV3 \mbox{\cite{00567}} model.
@@
 Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3.
-The best ROC AUC values for melanoma and basal
-cell carcinoma are 0.94 (ResNet152) and 0.93 (DenseNet201).
+The best ROC AUC values for melanoma and basal cell carcinoma are 0.94 (ResNet152) and 0.93 (DenseNet201).
 
@@
 The low recall score may be due to the imbalanced data set.
+
+Abnormal, skin lesion segmentation, on the other hand, also play an important role in skin lesion classification.
+Nawaz et al create a framework for Melanoma segmentation \mbox{\cite{22750}}.
+Their proposed method is Unet model but using the backbone is densenet77 and all residual block is changed into dense block which contains a sequence of Convolution and an Average Pooling.
+This melanoma segmentation approach got the accuracy of 0.99.
+Kadry et al, otherwise, using Unet model with VGG deep convolution layer, pooling on the skip connection.
+This approach can completely extract the whole lesion, though overlap by hair.
+This approach got the accuracy of 0.97.
 
@@
 
+\begin{figure}[!htb]
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{Definitions/CM/dn201cm}
+		\caption{DenseNet201 Confusion Matrix}\label{fig:densenet201cm}
+	\end{minipage}\hfill
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{Definitions/CM/irv2cm}
+		\caption{InceptionResNetV2 Confusion Matrix}\label{fig:irv2cm}
+	\end{minipage}
+\end{figure}
+
 \begin{figure}[H]
@@
 		\hline
-		MobileNetV3Small & - & \textbf{0.96}\\
+		MobileNetV3Small & 0.67 & \textbf{0.96}\\
 		\hline
@@
 \end{table}
+
+\begin{figure}[!htb]
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{Definitions/ROC/densenet201}
+		\caption{DenseNet201 Class ROC}\label{fig:densenet201auc}
+	\end{minipage}\hfill
+	\begin{minipage}{0.48\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{Definitions/ROC/irv2}
+		\caption{InceptionResNetV2 Class ROC}\label{fig:irv2auc}
+	\end{minipage}
+\end{figure}
 
@@
 besides, a new weight loss function is applied to figure out the data imbalance problem.
-Finally, the combination of InceptionResNetV2, Soft-Attention, and Metadata is the best model.
-Although the accuracy and the precision of the model are not the highest, the f1-score, recall, and AUC-score is the highest and the most balanced indicator.
+Finally, the combination of InceptionResNetV2, Soft-Attention, and Metadata is the best model with the accuracy of 0.9.
+Although the accuracy and the precision of the model are not the highest, the f1-score, recall, and AUC-score of 0.86, 0.81 and 0.975, respectively is the highest and the most balanced indicator.
 Therefore, InceptionResnetV2 can classify well in all classes including low samples classes.
-Otherwise, during the experiment, the combination of MobileNetV3, Soft-Attention, and Metadata achieve an accuracy that is nearly the same as InceptionResNetV2, though with fewer number parameters and depth.
+Otherwise, during the experiment, the combination of MobileNetV3, Soft-Attention, and Metadata achieve an accuracy of 0.86 that is nearly the same as InceptionResNetV2, though with fewer number parameters and depth.
 Therefore the infer time is much less than the InceptionResNetV2.
@@
 
-\dataavailability{The code and the data analysis report can be found here: \\https://github.com/KhoiDOO/Skin-Disease-Detection-HAM100000.git}
+\dataavailability{The code and the data analysis report can be found here: \\https://github.com/ScaleMind-C9308A/Skin-Disease-Detection-HAM100000.git}
 
@@
 
+\bibitem[Author2(year)]{2101.133}
+OLUSOLA OLUWAKEMI ABAYOMI-ALLI, ROBERTAS DAMAŠEVIČIUS,,
+SANJAY MISRA, RYTIS MASKELIŪNAS, ADEBAYO ABAYOMI-ALLI Malignant skin melanoma detection using image augmentation by oversampling in nonlinear lower-dimensional embedding manifold
+{\em TUBITAK} 
+{\bf 2021}.
+
+\bibitem[Author2(year)]{22750}
+Marriam Nawaz, Tahira Nazir, Momina Masood, Farooq Ali, 
+Muhammad Attique Khan, Usman Tariq, Naveera Sahar,
+Robertas Damaševicius Melanoma segmentation: A framework of improved
+DenseNet77 and UNET convolutional neural network
+{\em Wiley} 
+{\bf 2022}.
+
+\bibitem[Author2(year)]{9445180}
+Seifedine Kadry, David Taniar, Robertas Damaševičius, Venkatesan Rajinikanth, Isah A. Lawal,
+Robertas Damaševicius Extraction of Abnormal Skin Lesion from
+Dermoscopy Image using VGG-SegNet
+{\em Wiley} 
+{\bf 2022}.
 \end{thebibliography}

### 2022-09-13 MDPI/sensors-1915564/template.tex
Update Review 1.5

@@
 It is worth to note that a new loss function	that takes into account the data imbalance is also proposed.
-Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively.
+Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.99, respectively.
 Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than InceptionResNetV2.}
@@
 		\hline
-		InceptionResNetV2 & 0.971 & \textbf{0.975}\\
-		\hline
-		DenseNet201 & 0.93 & \textbf{0.97}\\
+		InceptionResNetV2 & 0.971 & \textbf{0.99}\\
+		\hline
+		DenseNet201 & 0.93 & \textbf{0.99}\\
 		\hline
@@
 \begin{figure}[!htb]
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{Definitions/ROC/densenet201}
-		\caption{DenseNet201 Class ROC}\label{fig:densenet201auc}
-	\end{minipage}\hfill
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{Definitions/ROC/irv2}
-		\caption{InceptionResNetV2 Class ROC}\label{fig:irv2auc}
-	\end{minipage}
+	\centering
+	\includegraphics[width=1\linewidth]{Definitions/ROC/denvsirv2}
+	\caption{ROC of DenseNet201 and InceptionResNetV2}\label{fig:densenet201auc}
 \end{figure}
@@
 		\hline
-		Our Proposed & 0.9	& 0.86 &\textbf{0.86} & \textbf{0.81} & 0.975\\
-		\hline
-		InceptionResNetV2\cite{03358} & 0.93 & 0.89 & 0.75 & 0.71 & 0.97\\
+		Our Proposed & 0.9	& 0.86 &\textbf{0.86} & \textbf{0.81} & \textbf{0.99}\\
+		\hline
+		InceptionResNetV2\cite{03358} & 0.93 & 0.89 & 0.75 & 0.71 & \textbf{0.99}\\
 		\hline

### 2022-09-16 MDPI/sensors-1915564/template.tex
Paper Review 1.6

@@
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Viet Dung Nguyen, Ngoc Dung Bui and Hoang Khoi Do}
+\AuthorNames{Viet Dung Nguyen, Ngoc Dung Bui, and Hoang Khoi Do}
 
@@
 According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive.
-In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential.
+In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience, and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential.
 Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed.
-In this paper, a combination of \add[H.K.D]{one} SOTA model \change[H.K.D]{such as}{including} DenseNet, InceptionNet, ResNet, NasNet,  MobileNet and Soft-Attention is proposed.
-Furthermore, personal information including age and gender are also used.
-It is worth to note that a new loss function	that takes into account the data imbalance is also proposed.
+In this paper, a combination of one Deep Learning model (DenseNet, InceptionNet, ResNet, etc) with Soft-Attention, which unsupervisedly extract a heat map of main skin lesions.
+Furthermore, personal information including age and gender is also used.
+It is worth noting that a new loss function that takes into account the data imbalance is also proposed.
 Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.99, respectively.
-Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than InceptionResNetV2.}
+Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves an accuracy of 0.86 and 30 times faster diagnosis than InceptionResNetV2.}
 
@@
 Survival is, however, generally poor after the illness has spread beyond the skin \mbox{\cite{11872}}.
-Additionally, there is a need for an efficient solution because to the rising prevalence of skin malignancies, low awareness among a population that is expanding, and a lack of sufficient clinical competence and services.}{Skin cancer is one of the most common cancers leading to worldwide death.
+Additionally, there is a need for an efficient solution because of the rising prevalence of skin malignancies, low awareness among a population that is expanding, and a lack of sufficient clinical competence and services.}{Skin cancer is one of the most common cancers leading to worldwide death.
 Every day, more than 9500 \mbox{\cite{03358}} people in the United States are diagnosed with skin cancer.
@@
 However, once the disease progresses beyond the skin, survival is poor \mbox{\cite{11872}}.
-Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.}
+Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solutions.}
 
@@
 For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively.
-DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer.
+DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then the soft-max layer.
 
@@
 Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al.
-Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \mbox{\cite{10348}} by Amirreza Rezvantalab et al.
+Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out-of-distribution skin lesion images as stated in \mbox{\cite{10348}} by Amirreza Rezvantalab et al.
 Matrix Transformation, besides is also applied before the soft-max activation function in \mbox{\cite{05045}} by Michele Alberti et al.}
@@
 
-On the other hand, there are also many state of the art whose great performance on skin lesion classification.
-The Student and Teacher Model is also a high performance model in 2021 \mbox{\cite{03225}}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other.
+		On the other hand, there are also many state-of-the-art whose great performance on skin lesion classification.
+The Student and Teacher Model is also a high-performance model in 2021 \mbox{\cite{03225}}, which is created by Xiaohan Xing et al as the combination of two models which share the memory with the other one.
 Therefore, they can take full advantage of what others learn.
-The Student and Teacher model get the accuracy of 0.85, however the precision and f1-score are quite low 0.76.
+The Student and Teacher model gets an accuracy of 0.85, however, the precision and f1-score are quite low 0.76.
 
@@
 		In Machine Learning, there are also many approaches.
-Since the image data is quite complex for Machine Learning algorithm, therefore using feature extractor or feature preprocessing to another form of data is recommended.
+Since the image data is quite complex for Machine Learning algorithms, therefore using feature extractor or feature preprocessing to another form of data is recommended.
 
 		Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al.
-In this approach, the data is fed directly into the Machine Learning algorithm and show out no promising result, therefore Rishu Garg et al dose not show the result of the Machine Learning algorithm.
+In this approach, the data is fed directly into the Machine Learning algorithm and shows no promising result, therefore Rishu Garg et al does not show the result of the Machine Learning algorithm.
 
@@
 	- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
-- Using metadata including age, gender, localization as another input of the model\\
+	- Using metadata including age, gender, and localization as another input of the model\\
 	- Using Soft-Attention as a feature extractor of the model\\
@@
 There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
-The distribution of the data set is shown in the Table \ref{table:data-distribution} below:
+The distribution of the data set is shown in Table \ref{table:data-distribution} below:
 
@@
 	\subsubsection{Metadata}
-The HAM10000 data set \cite{10417} also contain the metadata of patient including gender, age, and the capturing position illustrated in Table \ref{table:metadata sample}
+	The HAM10000 data set \cite{10417} also contains the metadata of the patient including gender, age, and the capturing position illustrated in Table \ref{table:metadata sample}
 	\begin{table}[H]
@@
 	\subsubsection{Overall Architecture}
-The whole architecture of the model is represented in the Figure \ref{fig:main-model}.
-The model takes two input including Image data and Metadata.
-Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.
+	The whole architecture of the model is represented in Figure \ref{fig:main-model}.
+The model takes two inputs including Image Data and Metadata.
+The metadata branch otherwise is preprocessed before feeding into a dense layer and then concatenate with the output of the Soft-Attention layer.
 
@@
 
-The Figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research.
-In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module.
-Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module.
+	Figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research.
+In detail, the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module.
+Similarly, ResNet50 and ResNet152 also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module.
 InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module.
@@
 This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge.
-The detail structure and information can be found at the Apendix \ref{appendix-table:detailed structure model}}
+The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed structure model}}
 		\label{fig:model-structure}
@@
 
-The Figure \ref{fig:mobile-model-structure}, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
-All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module.
-The NasNetMobile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell.
+	Figure \ref{fig:mobile-model-structure}, on the other hand, shows the detailed structure of mobile-based mobile and its combination with Soft-Attention.
+All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 with the Soft-Attention module.
+The NasNetMobile, otherwise, combines with the Soft-Attention module by replacing the last Normal Cell.
 	\begin{figure}[H]
@@
 		\caption{Overall Mobile-based Model Architecture.
-This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
-The detail structure and information can be found at the Apendix \ref{appendix-table:detailed mobile model structure}}
+This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
+The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed mobile model structure}}
 		\label{fig:mobile-model-structure}
@@
 	\subsubsection{Input Schema}
-\add[H.K.D]{Image preprocessing is an essential part before the training process because of the ability to extract main pattern of an image.
-In this stage, the image can be changed the color channel so that the main feature is separated from the useless part.
-Image Retrieval, otherwise has significantly create a vector that represent the main feature of an image.
+	\add[H.K.D]{Image preprocessing is an essential part of the training process because of the ability to extract the main pattern of an image.
+In this stage, the image can be changed to the other color channel so that the main feature is separated from the useless part.
+Image Retrieval otherwise has significantly created a vector that represents the main feature of an image.
 Those image retrieval techniques can be energy compaction, primitive pattern units, etc.
-Shervan Fekri-Ershad et al create an feature vector by calculating the element wise product of histogram vector in each channel of an image \mbox{\cite{2012.4305}}.
+Shervan Fekri-Ershad et al create a feature vector by calculating the element-wise product of the histogram vector in each channel of an image \mbox{\cite{2012.4305}}.
 Then comparing the Euclidean distance between this feature vector and the average feature vector of the whole data set with a thresh hold, they can extract the skin part of the image.}
 
-In this research, the image data is both augmented for all class, the number of image increase to 18015 images and keep original form.
-Before feeding into the backbone model, the images is pre-processed by the input requirement of each model.
-DenseNet201 \cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set.
+	In this research, the image data is augmented for all class, the number of image increase to 18015 images and keep the original form.
+Before feeding into the backbone model, the images are pre-processed by the input requirement of each model.
+DenseNet201 \cite{06993} requires the input pixel values to be scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set.
 In Resnet50 and Resnet152 \cite{03385} \cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling.
@@
 In the research \cite{03910}, they decide to keep the missing value and set its value to $0$.
-The sex and anatomical site are categorical encoded.
-The age, on the other hand is numerical normalized.
+The sex and anatomical site are categorically encoded.
+The age, on the other hand, is numerically normalized.
 After processing, the metadata is fed into a two-layer neural network with 256 neurons each.
@@
 The network’s output is concatenated with the CNN’s feature vector after global average pooling.
-Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata.
+Especially, they use a simple data augmentation strategy to address the problem of missing values in metadata.
 During training, they randomly encode each property as missing with a probability of $p = 0.1$.
 
-In this research, the unknowns is kept as a type as discussed in Metadata section.
-Sex, anatomical site and age are also category encoded and numerical normalized, respectively.
+	In this research, the unknowns are kept as a type as discussed in the Metadata section.
+Sex, anatomical site, and age are also category encoded and numerically normalized, respectively.
 After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons.
-Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section.
-The Input schema is described in the Table \ref{fig:input-schema}
+Finally, this dense layer is then concatenated with the output of Soft-Attention which is then discussed in the Soft-Attention section.
+The Input schema is described in Table \ref{fig:input-schema}
 
@@
 	In this paper, the backbone models used in this paper are DenseNet201 \cite{06993}, Inception \cite{00567}, MobileNets \cite{04861} \cite{04381} \cite{02244}, ResNet \cite{03385} \cite{05027}, and NasNet \cite{07012}.
-The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance.
-Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated.
+The combination of DenseNet201, InceptionResNetV2, and Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance.
+Otherwise, Resnet50 also well classify but with a much less number of parameters and depth than based on its f1-score and precision stated.
 Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed.
-On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.
+On the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.
 
@@
 			\hline
-		Model & Size(MB) & Parameters & Depth \\ 
-		\hline
-		Resnet50 & 98 & 25.6M & 107 \\ 
-		\hline
-		Resnet152 & 232 & 60.4M & 311 \\ 
-		\hline
-		DenseNet201 & 80 & 20.2M & 402 \\
-		\hline
-		InceptionResNetV2 & 215 & 55.9M & 449 \\
-		\hline
-		MobileNet & 16 & 4.3M & 55 \\ 
-		\hline
-		MobileNetV2 & 14 & 3.5M & 105 \\ 
-		\hline
-		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
-		\hline
-		MobileNetV3Large & Unknown & 5.5M & 118 \\
-		\hline
-		NasnetMobile & 23 & 5.3M & 308 \\
-		\hline
-		NasnetLarge & 343 & 88.9M & 533 \\ 
+			Model & Size(MB) & No. Trainable Parameters & Depth \\ 
+			\hline
+			Resnet50 & 98 & 25,583,592 & 107 \\ 
+			\hline
+			Resnet152 & 232 & 60,268,520 & 311 \\ 
+			\hline
+			DenseNet201 & 80 & 20,013,928 & 402 \\
+			\hline
+			InceptionResNetV2 & 215 & 55,813,192 & 449 \\
+			\hline
+			MobileNetV2 & 14 & 3,504,872 & 105 \\ 
+			\hline
+			MobileNetV3Small & Unknown & 2,542,856 & 88 \\ 
+			\hline
+			MobileNetV3Large & Unknown & 5,483,032 & 118 \\
+			\hline
+			NasnetMobile & 23 & 5,289,978 & 308 \\
+			\hline
+			NasnetLarge & 343 & 88,753,150 & 533 \\ 
 			\hline
@@
 Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights.
-Soft-Attention is described in the Equation \ref{eqn:softatt}.
+Soft-Attention is described in Equation \ref{eqn:softatt}.
 	\begin{equation}
@@
 
-The Figure \ref{fig:soft-attention} shows the two main steps of applying Soft-Attention is applied in two main steps.
+	Figure \ref{fig:soft-attention} shows the two main steps of applying Soft-Attention.
 Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map \cite{08513}.
@@
 This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar.
-Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.
+Finally, the output of the Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.
 
@@
 
-After feeding into ReLU function layer, the heat feature map is processed in two paths.
+	After feeding into the ReLU function layer, the heat feature map is processed in two paths.
 The first path is the 2-dimensional Max Pooling.
-In the second path, the feature map, on the other hand is fed into the Soft-Attention Layer before the 2-dimensional Max Pooling.
+In the second path, the feature map, on the other hand, is fed into the Soft-Attention Layer before the 2-dimensional Max Pooling.
 After all, these two paths are then concatenated, fed into a ReLU layer, and a Dropout with the probability of $0.5$.
@@
 
-where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$.
+	where $\hat{y}^c_i$  is the output of the model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$.
 Since the data set face the imbalanced problem then class weight for the loss is applied.
-In this research, both of the original weight and a new weight formula is implementation.
-Originally, the weight is calculated by taking the inverse of percentage that each class accounts for.
+In this research, both the original weight and a new weight formula are implemented.
+Originally, the weight is calculated by taking the inverse of the percentage that each class accounts for.
 The new weight formula is described in the Equation \ref{eqn:weightformula} and \ref{eqn:vector-inverse-percent}.
-\add{This weight formula is the original weight multiplies with the inverse of number of class in the data set which make the training more balanced.
+\add{This weight formula is the original weight multiplied by the inverse of the number of classes in the data set which makes the training more balanced.
 It is inspired by the “balanced” heuristic proposed by Gary King et al\mbox{\cite{WV006-01}}}
@@
 
-where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.
+	where $N$ is the number of the training sample, $C$ is the number of classes, and $N_i$ is the number of samples in each class $i$. $D$ is the matrix containing the inverse of $C \times N_i$.
 
@@
 	\subsubsection{Training}
-Before training, the data set is split into two sub set for training (90 percent) and validation (10 percent).
-Test set, otherwise is provided by the HAM10000 data set, contains 857 images.
+	Before training, the data set is split into two subsets for training (90 percent) and validation (10 percent).
+The test set, otherwise provided by the HAM10000 data set, contains 857 images.
 To analyze the effect of augmented data on the model, before the training the image data is augmented to $53573$ images by the following technique:\\
@@
 	- Zoom Range:  Zoom in or zoom out the image \add[H.K.D]{in a range of 0.1} to create new image. \\
-- Horizontal and vertical flipping: Flipping the image horizontally and vertically to create new image.\\
-Otherwise, all of models is trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$.
-The initial epochs is set to 250 epochs and the Early Stopping is also applied to stop the training as the accuracy of validation set does not increase after $25$ epochs.
+	- Horizontal and vertical flipping: Flipping the image horizontally and vertically to create a new image.\\
+	Otherwise, all models are trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$.
+The initial epochs are set to 250 epochs and the Early Stopping is also applied to stop the training as the accuracy of the validation set does not increase after $25$ epochs.
 Besides, the batch size is set to $32$.
@@
 	\subsubsection{Tools}
-TensorFlow and Keras are two of the most popular framework to build deep learning model.
-In this research, Keras based on TensorFlow is used to build, clone the backbone model which is pre-trained with the image-net data set.
-Otherwise, the models are trained by NVIDIA RTX TitanV and the data set is pre-processed with the CPU Intel I5 32 processors, RAM 32GB.
-In detail, the GPU is setup with CUDA 11.6, cuDNN 8.3 and ChipSRT as the requirement of TensorFlow version 2.7.0.
+	TensorFlow and Keras are two of the most popular framework to build a deep learning model.
+In this research, Keras based on TensorFlow is used to build, and clone the backbone model which is pre-trained with the image-net data set.
+Otherwise, the models are trained by NVIDIA RTX TitanV, and the data set is pre-processed with the CPU Intel I5 32 processors, and RAM 32GB.
+In detail, the GPU is set up with CUDA 11.6, cuDNN 8.3, and ChipSRT as the requirement of TensorFlow version 2.7.0.
 	\subsubsection{Evaluation Metrics}
@@
 Consider a confusion matrix $A$ with $C$ number of class.
-Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively, therefore $A^i_k$ is the element at row i and column k
+Let $A^i$ and $A^j$ be the set of $A$ rows and columns respectively, therefore $A^i_k$ is the element at row i and column k
 	\[
@@
 	\]
-The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$.
-The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
+	The True Positive(TP) of all classes in this case is the main diagonal of the matrix $A$.
+The following method is used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all classes:
 
@@
 
-\change[H.K.D]{Sensitivity  and Specificity  mathematically describe the accuracy of a test which reports the presence or absence of a condition.
-Individuals for which the condition is satisfied are considered "positive" and those for which it is not are considered "negative".
+	\change[H.K.D]{Sensitivity and Specificity mathematically describe the accuracy of a test that reports the presence or absence of a condition.
+Individuals for which the condition is satisfied are considered "positive" and those for which it is not considered "negative".
 Sensitivity or true positive rate refers to the probability of a positive test, conditioned on truly being positive while Specificity or true negative rate refers to the probability of a negative test, conditioned on truly being negative.}{Sensitivity (Equation \mbox{\ref{eqn:sens}}) and Specificity (Equation \mbox{\ref{eqn:spec}}) mathematically describe the accuracy of a test that identifies a condition's presence or absence. Sensitivity, also known as the true positive rate, is the likelihood that a test will result in a true positive, whereas specificity, also known as the true negative rate, is the likelihood that a test will result in a true negative.}
@@
 	Precision (Equation \ref{eqn:pre}) or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative.
-F1-score (Equation \ref{eqn:f1}), on the other hand refers the harmonic mean of precision and recall which mean the higher the f1-score is, the higher both precision and recall is.
-Besides, the expected value of precision, f1-score and recall-score are also applied because of the multi-class problem.
+F1-score (Equation \ref{eqn:f1}), on the other hand, refers to the harmonic mean of precision and recall which means the higher the f1-score is, the higher both precision and recall is.
+Besides, the expected value of precision, f1-score, and recall-score are also applied because of the multi-class problem.
 
@@
 
-The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicate the probability of TP versus the probability of FP.
+	The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of TP versus the probability of FP.
 
@@
 
-According to the Table \ref{table:overall-acc}, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only.
-While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.79$ and $0.84$ respectively, their training with metadata are $0.90$ and $0.89$, respectively.
-Furthermore, Resnet50 trained with metadata data has the accuracy that outperform the Resnet50 trained with augmented data and is twice as high as Resnet152 trained with metadata.
-On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.86$, $0.86$, respectively.
+	According to Table \ref{table:overall-acc}, it is clear that the model trained with metadata has higher accuracy than the model trained with augmented data only.
+While InceptionResNetV2 and DenseNet201 trained with augmented data have an accuracy of $0.79$ and $0.84$ respectively, their training with metadata is $0.90$ and $0.89$, respectively.
+Furthermore, Resnet50 trained with metadata data has an accuracy that outperforms the Resnet50 trained with augmented data and is twice as high as Resnet152 trained with metadata.
+On the other hand, the mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have quite good accuracy of $0.81$, $0.86$, $0.86$, respectively.
 
@@
 ACC stands for accuracy.
-AD stands for augmented data, this indicate that the model is trained with augmented data.
-MD stands for Metadata which indicate that the model is trained with Metadata}
+AD stands for augmented data, this indicates that the model is trained with augmented data.
+MD stands for Metadata which indicates that the model is trained with Metadata}
 		\label{table:overall-acc}
@@
 	Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to Figure \ref{fig:den f1}, \ref{fig:incep f1}, \ref{fig:den recall}, and \ref{fig:incep recall}.
-As a results, augmented data model does not classify well on all class as InceptionResNetV2 trained on augmented data have f1-score on class df and akiec is just above $0.3$ and $0.4$, separately while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way arcoding to the Figure \ref{fig:incep f1}.
-However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class.
+As the result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data have f1-score on class df and akiec is just above $0.3$ and $0.4$, separately while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to the Figure \ref{fig:incep f1}.
+However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depths are equal to or larger than 400 have balanced the f1-score in class.
 The others still face the imbalanced term.
-Since this data set is not balanced, therefore using augmented data can make the model more  bias to the class which has larger sample.
-Using the metadata, though still make the model bias, it does contributes to the improvement of  the performance of the model.
+Since this data set is not balanced, therefore using augmented data can make the model more biased to the class which has a larger number of samples.
+Using the metadata, though still making the model biased, does contribute to the improvement of the performance of the model.
 
@@
 	This problem is also true with the recall score according to Figure \ref{fig:den recall} and \ref{fig:incep recall}.
-DenseNet201, InceptionResNetV2, trained with augmented data has expected value of recall of $0.56$, $0.69$, respectively, while the combination of DenseNet201, Metadata and the new weight loss function achieve the expected value of recall: $0.82$.
+DenseNet201, and InceptionResNetV2, trained with augmented data have an expected value of recall of $0.56$, and $0.69$, respectively, while the combination of DenseNet201, Metadata, and the new weight loss function achieve the expected value of recall: $0.82$.
 Therefore, metadata does improve the model performance by reducing the amount of data needed for achieving higher results.
-On the other hand, the reason why the model become much more balanced is the weighted loss function.
-Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class.
+On the other hand, the reason why the model becomes much more balanced is the weighted loss function.
+The weighted loss function has the ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class.
 DenseNet201, InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$.
@@
 		\includegraphics[width=1\linewidth]{Definitions/den re}
-	\caption{The comparison between recal scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss}
+		\caption{The comparison between recall scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss}
 		\label{fig:den recall}
@@
 
-Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance.
+	Another interesting point found during the experiment is that MobileNetV2, MobileNetV3, and NasNetMobile have a small number of parameters and depth, though have relatively good performance.
 MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately according to the Table \ref{appendix-table:mobile-performance}.
-It's transparent that MobileNetV3Large and NasNetMobile are the two best performance model.
+It's transparent that MobileNetV3Large and NasNetMobile are the two best performance models.
 Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile.
@@
 			\hline
-		Time Prediction(s/epochs) & \textbf{116} & 1000 & 3500 \\
-		\hline
-		Computational Complexity & & &\\		
+			Training Time(seconds/epoch) & 116 & 1000 & 3500\\
+			\hline
+			Infer Time(seconds) & \textbf{0.13} & 1.16 & 4.08 \\
 			\hline
@@
 
-The Table \ref{table:optimized-performance-mobile-model} shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others.
-In detail, MobileNetV3Large whose the number of parameters is 5.5 millions which is four and ten times less than DenseNet201 and InceptionResNetV2, respectively.
+	Table \ref{table:optimized-performance-mobile-model} shows that the MobileNetV3Large, though the number of parameters is much smaller than the DenseNet201, InceptionResNetV2, achieves the accuracy nearly to the others.
+In detail, MobileNetV3Large whose number of parameters is 5.5 million that is four and ten times less than DenseNet201 and InceptionResNetV2, respectively.
 The depth of MobileNetV3Large, on the other hand, is four times less than DenseNet201, InceptionResNetV2 which are 118 hidden layers as opposed to 402, 449 of DenseNet201 and InceptionResNetV2, separately.
-Although, the MobileNetV3Larege only achieve the accuracy of 0.86 the time need for prediction is 10 and 30 times less than the other opponents.
-If the MobileNetV3Large need a harder process of parameter hyper-tuning to achieve a better result, which is also the future target of this research.
-
-The Table \ref{table:overall-auc} shows the AUC score of the three models InceptionResNetV2, Densenet201, and ResNet50 which is trained with only augmented data or metadata.
+Although, the MobileNetV3Larege only achieves the accuracy of 0.86 the time needed for prediction is 10 and 30 times less than the other opponents.
+If the MobileNetV3Large needs a harder process of parameter hyper-tuning to achieve a better result, which is also the future target of this research.
+
+	Table \ref{table:overall-auc} shows the AUC score of the three models InceptionResNetV2, Densenet201, and ResNet50 which are trained with only augmented data or metadata.
 It's transparent that the InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: 0.974 and 0.971 as opposed to 0.972 and 0.93, respectively.
-ResNet50 trained with augmented data, on the other hand have higher auc-score: 0.95 as compared to 0.93 of ResNet50 trained with metadata.
-Overall, InceptionResNetV2 trained with metadata reach the peak with the auc-score of 0.974.
+ResNet50 trained with augmented data, on the other hand, has a higher AUC score: 0.95 as compared to 0.93 for ResNet50 trained with metadata.
+Overall, InceptionResNetV2 trained with metadata reached the peak with the AUC score of 0.974.
 The InceptionResNetV2 trained with metadata is also compared with the others to find out the best models trained.
-According to the figure 15, the InceptionResNetV2 still hit the peak of 0.974 auc-score.
-ResNet152, otherwise is the worst model with the auc-score of 0.87.
-Other models, on the other hand have the approximately same of auc-score.
+According to Figure \ref{fig:densevsirv2}, the InceptionResNetV2 hits the peak of 0.99 AUC score.
+ResNet152 otherwise is the worst model with the AUC score of 0.87.
+Other models, on the other hand, have the approximately same AUC score.
 
@@
 		\caption{AUC (area under the curve) of all models.
-AD stands for augmented data, this indicate that the model is trained with augmented data.
-MD stands for Metadata which indicate that the model is trained with Metadata}
+AD stands for augmented data, this indicates that the model is trained with augmented data.
+MD stands for Metadata which indicates that the model is trained with Metadata}
 		\label{table:overall-auc}
@@
 		\includegraphics[width=1\linewidth]{Definitions/ROC/denvsirv2}
-	\caption{ROC of DenseNet201 and InceptionResNetV2}\label{fig:densenet201auc}
+		\caption{ROC of DenseNet201 and InceptionResNetV2}\label{fig:densevsirv2}
 	\end{figure}
 
-Besides the comparison between original weight loss calculated by the sample percentage of each class model and the new weight loss based model is also conducted on the three best performance model including InceptionResNetV2, DenseNet201, MobileNetV3.
-After the experiment, it is found out that the new weight loss function dose not only contribute to the model to overcome the data imbalance problem but it also make the accuracy increase.
-The performance of models is described in the Table \ref{table:loss-comparision}
+	Besides the comparison between the original weight loss calculated by the sample percentage of each class model and the new weight loss-based model is also conducted on the three best performance models including InceptionResNetV2, DenseNet201, and MobileNetV3.
+After the experiment, it is found that the new weight loss function does not only contribute to the model to overcome the data imbalance problem but also makes the accuracy increase.
+The performance of models is described in Table \ref{table:loss-comparision}
 
@@
 			DenseNet201 & 0.81 & 0.84 & 0.89\\
-		MobileNetV3 & 0.79 & 0.80 & 0.86\\
+			MobileNetV3Large & 0.79 & 0.80 & 0.86\\
 			\hline
 		\end{tabular}
-	\caption{Loss based model accuracy comparison}
+		\caption{Loss-based model accuracy comparison}
 		\label{table:loss-comparision}
@@
 
-After reviewing, the InceptionResNetV2 is found to be the best model trained.
-Futhermore, the InceptionResNetV2 is compared with the other state of the art researched model.
-According to the Table \ref{table:comparative-analysis}, there are six research that use the same data set: HAM10000 but different approaches.
+	According to Table \ref{table:densenet201auc} and Table \ref{table:loss-comparision}, the InceptionResNetV2 is found to be the best model trained.
+Furthermore, the InceptionResNetV2 is compared with the other state-of-the-art researched model.
+According to Table \ref{table:comparative-analysis}, six pieces of research use the same data set: HAM10000 but different approaches.
 These models used in that research are also SOTA models sorted in ascending order.
-The Table shows that the accuracy of the combination of InceptionResNetV2 with Soft-Attention, metadata and weight loss in this research is less than the InceptionResNetV2 with Soft-Attention and augmented data: 0.90 compared to 0.93 respectively.
-However, since Soumyyak et al use data augmentation for all class of an imbalanced data set, the f1-score and recall score are much lower.
-This is because the model in that research can only classify well on NV and VASC class which have the highest number of samples.
-On the other hand, the InceptionResNetV2 in this research also outperform the other model according to 5 indicator: accuracy, precision, f1-score, recall score, and auc score.
+The Table shows that the accuracy of the combination of InceptionResNetV2 with Soft-Attention, metadata, and weight loss in this research is less than the InceptionResNetV2 with Soft-Attention and augmented data: 0.90 compared to 0.93 respectively.
+However, since Soumyyak et al uses data augmentation for all class of an imbalanced data set, the f1-score and recall score is much lower.
+This is because the model in that research can only classify well on NV and VASC classes which have the highest number of samples.
+On the other hand, the InceptionResNetV2 in this research also outperforms the other model according to 5 indicators: accuracy, precision, f1-score, recall score, and AUC score.
+
 	\FloatBarrier
@@
 			\hline
-		Model & Accuracy & Precision & f1-score & recall & auc-score\\
-		\hline
-		Our Proposed & 0.9	& 0.86 &\textbf{0.86} & \textbf{0.81} & \textbf{0.99}\\
-		\hline
-		InceptionResNetV2\cite{03358} & 0.93 & 0.89 & 0.75 & 0.71 & \textbf{0.99}\\
+			Approach & Accuracy & Precision & f1-score & recall & auc-score\\
+			\hline
+			InceptionResNetV2\cite{03358} & 0.93 & 0.89 & 0.75 & 0.71 & 0.97\\
 			\hline
@@
 			Student and Teacher\cite{03225} & 0.85 & 0.76 & 0.76 & - & - \\
+			\hline
+			Proposed Method & 0.9	& 0.86 &\textbf{0.86} & \textbf{0.81} & \textbf{0.99}\\
 			\hline
@@
 
-However, there is still some drawbacks of the model that the InceptionResNetV2 cannot well classify the melanoma and the nevus.
-According to Figure \ref{fig:nevusVSmela} the model sometime classify the black nevus as the melanoma because of the same color between them.
+	However, there are still some drawbacks of the model that the InceptionResNetV2 cannot well classify melanoma and nevus.
+According to Figure \ref{fig:nevusVSmela} the model sometime classifies the black nevus as melanoma because of the same color between them.
 However, this problem is not true for the hard black or big melanoma or the red black nevus.
-Some future approach that can be proposed are change the type of color to other to fix the same color problem.
+Some future approaches that can be proposed are changing the type of color to other to fix the same color problem.
 
@@
 	\section{Conclusions}
-In this research, our proposed is to construct a model as a combination of backbone models and Soft-Attention.
+	In this research, our proposal is to construct a model as a combination of backbone models and Soft-Attention.
 Moreover, the model takes two inputs including image data and metadata.
 besides, a new weight loss function is applied to figure out the data imbalance problem.
-Finally, the combination of InceptionResNetV2, Soft-Attention, and Metadata is the best model with the accuracy of 0.9.
-Although the accuracy and the precision of the model are not the highest, the f1-score, recall, and AUC-score of 0.86, 0.81 and 0.975, respectively is the highest and the most balanced indicator.
+Finally, the combination of InceptionResNetV2, Soft-Attention, and Metadata is the best model with an accuracy of 0.9.
+Although the accuracy and the precision of the model are not the highest, the f1-score, recall, and AUC-score of 0.86, 0.81, and 0.975, respectively is the highest and the most balanced indicator.
 Therefore, InceptionResnetV2 can classify well in all classes including low samples classes.
-Otherwise, during the experiment, the combination of MobileNetV3, Soft-Attention, and Metadata achieve an accuracy of 0.86 that is nearly the same as InceptionResNetV2, though with fewer number parameters and depth.
+Otherwise, during the experiment, the combination of MobileNetV3, Soft-Attention, and Metadata achieve an accuracy of 0.86 which is nearly the same as InceptionResNetV2, though with fewer number parameters and depth.
 Therefore the infer time is much less than the InceptionResNetV2.
 This result opens the door to constructing a great performance model that can be applied to mobile, IoT devices.
-\add[H.K.D]{As the result, proposed method and others still face the problem of badly distinguish between melanoma and black nevus because in some cases, the melanoma and the nevus image has the same lesion size and color.}
+\add[H.K.D]{As a result, the proposed method and others still face the problem of badly distinguishing between melanoma and black nevus because in some cases, the melanoma and the nevus image have the same lesion size and color.}
 	\vspace{6pt}
@@
 		\begin{tabular}{@{}ll}
-CAD & Computer aided diagnosis\\
+			CAD & Computer-aided diagnosis\\
 			AI & Artificial Intelligence\\
@@
 		\end{adjustwidth}
-	\caption{Details Structure of Models except Mobile models.
-SA stands for Soft-Attention, SA Module denotes whether that model use Soft-Attention Module.
+		\caption{Details Structure of Models except for Mobile models.
+SA stands for Soft-Attention, SA Module denotes whether that model uses Soft-Attention Module.
 GAP stands for Global Average Pooling.
@@
 		\end{adjustwidth}
-	\caption{Details Structure of Mobile based Models.
-SA stands for Soft-Attention, SA Module denotes whether that model use Soft-Attention Module.
+		\caption{Details Structure of Mobile-based Models.
+SA stands for Soft-Attention, SA Module denotes whether that model uses Soft-Attention Module.
 SE which stands for Squeeze-And-Excite shows whether that block has Squeeze-And-Excite.
@@
 			\caption{F1-Score of each class: akiec, bcc, bkl, df, mel, nv, vasc which are denoted in the abbreviation.
-The last column is the expected value of f1-score from each model.
+The last column is the expected value of the f1-score from each model.
 All model in the first column is the models trained in this research.
 The term "with Augmented Data" means that model is trained with data augmenting during the training, there is no metadata or weight loss contribution.
-The term "with Metadata and WeightLoss" means that the model is trained with metadata including age, gender, localization and the weight loss function, there is no augmented data contribution}
+The term "with Metadata and WeightLoss" means that the model is trained with metadata including age, gender, localization, and the weight loss function, there is no augmented data contribution}
 			\label{appendix-table:F1-score-summary}
@@
 			\end{tabular}
-	\caption{Deeper analyzing of mobile model.
-This table illustrate the other indicators of the four mobile-based models including MobileNetV2, MobileNetV3Small, MobileNetV3Large, NasNetMobile.
+			\caption{Deeper analysis of the mobile model.
+This table illustrates the other indicators of the four mobile-based models including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
 The indicators are Accuracy, Balanced Accuracy, Precision, F1-score, Sensitivity, Specificity, and ROC - AUC score.
-All of them are average indicator}
+All of them are average indicators}
 			\label{appendix-table:mobile-performance}
@@
 			\bibitem[Author2(year)]{2012.4305}
-Shervan Fekri-Ershad, Mohammad Saberi and Farshad Tajeripour AN INNOVATIVE SKIN DETECTION APPROACH
+			Shervan Fekri-Ershad, Mohammad Saberi, and Farshad Tajeripour AN INNOVATIVE SKIN DETECTION APPROACH
 			USING COLOR BASED IMAGE RETRIEVAL TECHNIQUE

### 2022-09-16 MDPI/sensors-1915564/template.tex
Update Paper Review 1.7

@@
 % Authors, for the paper (add full first names)
-\Author{Viet Dung Nguyen $^{1,\dagger, *}$\orcidA{}, Ngoc Dung Bui $^{2,\dagger}$\orcidB and Hoang Khoi Do  $^{1,\dagger}$\orcidC{}}
+\Author{Viet Dung Nguyen $^{1,\dagger, *}$\orcidA{}, Ngoc Dung Bui $^{2, *}$\orcidB{} and Hoang Khoi Do  $^{1,\dagger}$\orcidC{}}
 
@@
 % Contact information of the corresponding author
-\corres{Correspondence: dung.nguyenviet1@hust.edu.vn; Tel.:  +84-9834-443-22 (N.V.D.)}
+\corres{Correspondences: dung.nguyenviet1@hust.edu.vn; Tel.:  +84-9834-443-22 (N.V.D.), dnbui@utc.edu.vn; Tel: +84-9130-451-30 (N.D.B.)}
 

### 2022-09-29 MDPI/manuscript.v6/sensors-1915564.tex
Update Paper Proof Reading

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[sensors,article,accept,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
\externaleditor{Academic Editor: Ahmed Bouridane
}
\datereceived{30 August 2022} 
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{23 September 2022} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{makecell}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{comment}

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%============================================3=====================
% Full title of the paper (Capitalized)
\Title{Skin Lesion Classification on Imbalanced Data Using Deep Learning with Soft Attention}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Skin Lesion Classification on Imbalanced Data Using Deep Learning with Soft Attention}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7152-0191} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0001-9934-7474} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-2566-5637} % Add \orcidC{} behind the author's name

% Authors, for the paper (add full first names)
\Author{\hl{Viet Dung Nguyen} %MDPI: Please carefully check the accuracy of names and affiliations.
 $^{1, }$*$^{,\dagger}$\orcidA{}, Ngoc Dung Bui $^{2,\dagger}$\orcidB~and Hoang Khoi Do  $^{1,\dagger}$\orcidC{}}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Viet Dung Nguyen, Ngoc Dung Bui and Hoang Khoi Do}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Nguyen, V.D.; Bui, N.D.; Do, H.K.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)

\address{%
$^{1}$ \quad \hl{School of} %MDPI: We remmoved affiliation 3 since it is duplicated with affiliation 1, please confirm
 Electrical and Electronic Engineering, Hanoi University of Science and Technology, \hl{Hanoi 100000, } %MDPI: newly added the city and post code, the same below, please confirm.
 Vietnam; \hl{khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct.
\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, \hl{Hanoi 10000, } 
 Vietnam; dnbui@utc.edu.vn\\
%$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi University of Science \hl{and Technology,} %MDPI: Please add the city and post code
% Vietnam; khoi.dh200322@sis.hust.edu.vn

 }

% Contact information of the corresponding author
\corres{Correspondence: dung.nguyenviet1@hust.edu.vn; Tel.:  +84-9834-443-22}

% Current address and/or shared authorship
\firstnote{\hl{Current address:} %MDPI: Please check that the address information is complete. If the address is the same as affiliation, please mergy the address information into affiliation. 
 1st Dai Co Viet Street, \hl{Hanoi 10000,} 
 Vietnam.} 
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e., \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	 diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022, there will be about 100,000 people suffering from skin cancer, and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience, and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of SOTA models such as DenseNet, InceptionNet, ResNet, NasNet, MobileNet and Soft-Attention is proposed. Furthermore, personal information including age and gender are also used. It is worth noting that a new loss function	that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and the new loss function gives 90\% accuracy as well as mean of precision, f1-score, recall, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively. When using MobileNetV3Large combined with Soft-Attention and the new loss function, even though the number of parameters is 11 times less and the number of hidden layers is four times less, it achieves 0.86 accuracy and 30 times faster diagnosis than InceptionResNetV2.}

% Keywords
\keyword{\highlighting{skin lesions;} %MDPI: We removed the uppercase of keyword, please confirm  
 classification; deep learning; Soft-Attention; imbalance}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{0} %% Remove this when starting to work on the template.
\begin{comment}
	\section{How to Use This~Template}

	The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the~positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For~any questions, please contact the editorial office of the journal or support@mdpi.com. For~LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.

	% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
\end{comment}

\section{Introduction}
\unskip 
\subsection{Problem~Statement}
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500~\highlighting{\cite{03358}} %MDPI: References should be cited in numerical order. Refs. [1], [4], [11], [26], [31], [32], [37]'s citations are missing(08332, 09365, 11797, 02357, 8943952, 07261). Please reorder all references and cited them all in order.
 people in the United States are diagnosed with skin cancer. Otherwise, 3.6~\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the~global incidence of skin cancer continues to increase~\cite{11872}. In~2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States~\cite{11872}. On~the other hand, if~patients are diagnosed early, the~survival rate is correlated with 99\%. However, once the disease progresses beyond the skin, survival is poor~\cite{11872}. Moreover, with~the increasing incidence of skin cancers, low awareness among a growing population, and~a lack of adequate clinical expertise and services, there is a need for effective~solutions.

Recently, deep learning particularly, and~machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and~Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and~X-ray image is used extensively in clinical practice. In~Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In~Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In~Medical Treatment, AI models are applied to build solutions to a specific disease; medicine revolution is an example. In~various studies, AI algorithms have provided various end-to-end solutions to the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and~foot ulcers across multiple image modalities of medical imaging~\cite{11872}.

To adapt the rise in skin cancer cases, AI algorithms over the last decade have had great performance. Some typical models that can be mentioned are DenseNet~\cite{06993}, EfficientNet~\cite{04861}, Inception~\cite{00567}, MobileNets\cite{04861,04381,02244}, ResNet~\cite{03385,05027}, and~NasNet~\cite{07012}. Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work~section.

\subsection{Related~Works}
Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in~\cite{03358}. Soumyyak et al. construct several models formed by the combination of a backbone model including DenseNet201~\cite{06993}, InceptionResNetV2~\cite{00567}, ResNet50~\cite{03385,05027}, VGG16~\cite{1556} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For~ResNet50 and VGG16, the~Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2 otherwise concatenate with the Soft-Attention before a fully-connected layer and~then the soft-max~layer.

Using those above backbones has been tried by many previous papers. Rishu Garg et al.~\cite{03798} use the transfer learning approach with a CNN-based model: ResNet50 and VGG16 which are pretrained with ImageNet data set. They also use data augmentation to avoid the imbalance of the data set. Histogram equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, and Support Vector~Machine.

Amirreaza et al.~\cite{10348} not only use those above backbone models but also used the  InceptionV3~\cite{00567} model. In~that research, the~data sets HAM10000 and $PH^2$ are combined to create a eight-class data set. Before~feeding into the deep CNN models, the~image is resized to (224, 224) for DenseNet201, ResNet152, and InceptionResNetV2 and (229, 229) for~InceptionV3.

Another paper that uses the backbone models is~\cite{09418}. Hemanth et al. decide to use EfficientNet~\cite{11946} and SeNET~\cite{01507} instead and the CutOut~\cite{04552v2} method, which involves creating holes of different sizes on the images, i.e.,~technically making a random portion of an image inactive during the data augmentation~process.

Otherwise,~ref~\cite{01284} also used Deep Convolution Neural Network, Peng Yao et al. used RandArgument, which crops an image into several images from a fixed size, DropBlock, which is used for regularization, Multi-Weighted New Loss, which is used for dealing with the imbalanced data problem, and an end-to-end Cumulative Learning Strategy, which can more effectively balance representation learning and classifier learning without additional computational~cost.

Another state of the art is GradCam and Kernel SHAP~\cite{06612}. Kyle Young et al. create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In~that research, they use three data sets containing HAM10000, BCN-20000 and MSK. Before~feeding into the models, the~images are preprocessed and binarized with a very low threshold to find the center of~mass.

On the other hand, there are also many state of the art models with great performance on skin lesion classification. The~Student and Teacher Model is also a high-performance model in 2021~\cite{03225}, which was created by Xiaohan Xing et al. as the combination of two models that share memory with each other. Therefore, they can take full advantage of what others~learn.

SkinLinkNet~\cite{12602} and WonderM~\cite{03426} both tested the effect of segmentation on the skin lesion classification problem created by Amirreza et al. and Yeong Chan et al., respectively. In~WonderM, the~method used is padding the image so that the image has the shape increased from (450, 600) to (600, 600). In~SkinLinkNet, instead of resizing the image down to (448, 448), both SkinLinkNet and WonderM use UNet to perform the segmentation task, although~they use EfficientNetB0 and DenseNet to perform the classification task, respectively.

Another approach is using metadata including gender, age, and~capturing position, as stated in~\cite{03910} by Nil Gessert~et~al. The~metadata are fed into a fully connected neural network after being encoded into a one-hot vector. All missing data points of age is set to 0. To~overcome the missing data problem, the~research applies one-hot encoding to the group, but the initial validation is poor performance; then, numerical encoding is~applied.

On the other hand, skin lesion classification problems are not only applied by deep learning but also machine learning. Random Forest, XGBoost, and~Support Vector Machines are tested by~\cite{03798} of Rishu Garg~et~al. Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images, as stated in~\cite{10348} by Amirreza Rezvantalab~et~al. Matrix transformation, besides,~is also applied before the soft-max activation function in~\cite{05045} by Michele Alberti~et~al.

\begin{table}[H]\setlength{\tabcolsep}{0.9mm}\renewcommand{\arraystretch}{1.2}
	\caption{\hl{Related} %MDPI: 1. Please cite the table in the text and ensure the first citation of each table appears in numerical order. 2. Please confirm if the vertical line is necessary, if not, please remove it.
 Works~Summary.}
	\label{table:related-work-summary}
	%\centering

\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering

	\begin{tabular}{|c|c|c|c|c|c|}
	\noalign{\hrule height 1pt}

		\textbf{Research} & \textbf{Deep Learning} & \textbf{Machine Learning} & \textbf{Data 
		Augmentation} & \textbf{Feture Extraction} & \textbf{Data Set}\\
		\hline~\cite{03358} & x & & x & & HAM10000\\
		\hline~\cite{03798} & x & x & x & x & HAM10000\\
		\hline~\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
		\hline~\cite{09418} & x & & x & & HAM10000\\
		\hline~\cite{01284} & x & & x & & HAM10000\\
		\hline~\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
		\hline~\cite{03225} & x & & x & & HAM10000\\
		\hline~\cite{12602} & x & & x & & HAM10000\\
		\hline~\cite{03426} & x & & x & & HAM10000\\
		\hline~\cite{03910} & x & & x & & HAM10000\\
		\hline~\cite{05045} & & x & x & x & HAM10000\\
		\noalign{\hrule height 1pt}

	\end{tabular}
\end{adjustwidth}
\end{table}
\unskip
\subsection{Proposed~Method}
In this research, a~new model is constructed from the combination of:

\begin{itemize}
\item[-]	Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and~MobileNetV2/V3;
\item[-]		Using metadata including age, gender, localization as another input of the~model;
\item[-]		Using Soft-Attention as a feature extractor of the~model;
\item[-]		A new weight loss function.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and~Methods}
\unskip
\subsection{Materials}
\subsubsection{Image~Data}
The data set used in this paper is the HAM10000 data set published by the Havard University Dataverse~\cite{10417}. There are a total of 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), basal cell carcinoma (BCC),  benign keratosis-like lesions (solar lentigines/seborrheic keratoses andchen-planus-like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and~vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The~distribution of the data set is shown in the Table~\ref{table:data-distribution} below.

\begin{table}[H]\renewcommand{\arraystretch}{1.2}\setlength{\tabcolsep}{3mm}

	\caption{Data Distribution in~HAM10000.}
	\label{table:data-distribution}
	\begin{tabular}{|c c c c c c c c c|} 
		\noalign{\hrule height 1pt}

		\textbf{Class} & \textbf{AKIEC} & \textbf{BCC} & \textbf{BKL} & \textbf{DF} & \textbf{MEL} & \textbf{NV} & \textbf{VASC} & \textbf{Total} \\ 
		\hline
		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10,015 \\
		\noalign{\hrule height 1pt}
	\end{tabular}
\end{table}
\unskip

\begin{figure}[H]
	%\centering
	\includegraphics[width=1\linewidth]{Definitions/DataDistribution}
	\caption{\hl{Example} %MDPI: 1. Please cite the figure in the text and ensure the first citation of each figure appears in numerical order. 2. Please confirm if the vertical line is necessary, if not, please remove it.
 image of each~class.}
	\label{fig:data-sample}
\end{figure}

More than 50\% of lesions are confirmed through histopathology (HISTO); the~ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or~confirmation by in vivo confocal microscopy (CONFOCAL). On~the other hand, before~being used for training, the whole data are shuffled and then split into two parts. Here, $90$\% and $10$\% of the data is used for training and validating respectively. Images in this data set have the type of $RGB$ and shape of (450, 600). However, each backbone needs different input sizes of images as well as the range of pixel~value.

\subsubsection{Metadata}
The HAM10000 data set~\cite{10417} also contains the metadata of each patient including gender, age, and~the capturing position, as illustrated in Table~\ref{table:metadata sample}.
\begin{table}[H]\setlength{\tabcolsep}{11.7mm}

	\caption{\hl{Metadata} example in the data~set.}%MDPI: Please confirm if the vertical line is necessary, if not, please remove it.
	\label{table:metadata sample}
	\begin{tabular}{|c c c c |} 
	\noalign{\hrule height 1pt}

		\textbf{ID} & \textbf{Age} & \textbf{Gender} & \textbf{Local}\\ 
		\hline
		ISIC-00001 & 15 & Male & back\\
		\hline
		ISIC-00002 & 85 & Female & elbow\\
		\noalign{\hrule height 1pt}

	\end{tabular}
\end{table}
\unskip
\subsection{Methodology}
\unskip
\subsubsection{Overall~Architecture}
The whole architecture of the model is represented in the Figure~\ref{fig:main-model}. The~model takes two input including Image data and Metadata. The metadata branch, otherwise, is preprocessed before feeding into a dense layer; then, it concatenates with the output of the Soft-Attention~layer.

\begin{figure}[H]
	%\centering
	\includegraphics[width=0.8\linewidth]{Definitions/MainModel - Model Form}
	\caption{Overall Model~Architecture.}
	\label{fig:main-model}
\end{figure}

Figure~\ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research. In~detail, the combination of DenseNet201 and Soft-Attention is formed by replacing the three last (DenseBlock, Global Average Pooling, and~the fully connected layer) with the Soft-Attention Module. Similarity, ResNet50 and ResNet152 also replaced the last three (Residual Block, Global Average Pooling, and~the fully connected layer) with the Soft-Attention module. InceptionResNetV2, on~the other hand, replaces the average pool and the last dropout with the Soft-Attention Module. The~last two, Normal Cell in NasNetLarge, is replaced with the Soft-Attention~module.

\begin{figure}[H]
	%\centering
	\includegraphics[width=0.8\linewidth]{Definitions/Model Structure}
	\caption{\hl{Overall Original} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7)
 Model Architecture. This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and~NasNetLarge. The~detailed structure and information can be found in Appendix \ref{app1} Table \ref{appendix-table:detailed structure model}.}
	\label{fig:model-structure}
\end{figure}

Figure~\ref{fig:mobile-model-structure}, on~the other hand, shows the detailed structure of the mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution layers 1 \hl{$\times$} %MDPI: We revised the "x" into a multiplication sign ("\times" U+00D7). Please confirm.
 1 with the Soft-Attention module. The~NasNetMobile, otherwise, combines with the Soft-Attention module by replacing the last normal~cell. 
\begin{figure}[H]
	%\centering
	\includegraphics[width=0.8\linewidth]{Definitions/Mobile Model Structure}
	\caption{\hl{Overall mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7)
 model architecture. This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and~NasNetMobile. The~detailed structure and information can be found in Appendix \ref{app2} Table  \ref{appendix-table:detailed mobile model structure}.}
	\label{fig:mobile-model-structure}
\end{figure}
\unskip

\subsubsection{Input~Schema}
In this research, the~image data are both augmented for all classes, the~number of images increases to 18,015 images, and it keeps the original form. Before~feeding into the backbone model, the~images are preprocessed by the input requirement of each model. DenseNet201~\cite{06993} requires the input pixels values to be scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In~Resnet50 and Resnet152~\cite{03385,05027}, the~images are converted from $RGB$ to $BGR$; then, each color channel is zero-centered with respect to the ImageNet data set without~scaling. InceptionResNetV2~\cite{11946}, on~the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet~\cite{04861,04381,02244}, NasNetMobile and NasNetLarge~\cite{07012} require the input pixel is in range of $-1$ and $1$.

On the other hand, the~metadata are also used as another input. In~the research~\cite{03910}, they decide to keep the missing value and set its value to $0$. The~sex and anatomical site are categorical encoded. The~age, on~the other hand is numerical normalized. After~processing, the~metadata are fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a~ReLU~\cite{08375} activation, and~dropout with $p = 0.4$. The~network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simple data augmentation strategy to address the problem of missing values in metadata. During~training, they randomly encode each property as missing with a probability of $p = 0.1$.

In this research, the~unknowns are kept as a type as discussed in Metadata section. Sex, anatomical site and age are also category encoded and numerical normalized, respectively. After~processing, the~metadata are then concatenated and fed into a dense layer of 4096~neurons. Finally, this dense layer is then concatenated with the output of Soft-Attention, which is then discussed in the Soft-Attention section. The~Input schema is described in \hl{Figure} %MDPI: We changed Table to Figure. Please confirm this revision.
 \ref{fig:input-schema}.

\begin{figure}[H]
%	\centering
	\includegraphics[width=1\linewidth]{"Definitions/Input Schema"}
	\caption{Input~Schema.}
	\label{fig:input-schema}
\end{figure}
\unskip

\subsubsection{Backbone~Model}
In this paper, the~backbone models used in this paper are DenseNet201~\cite{06993}, Inception~\cite{00567}, MobileNets~\cite{04861,04381,02244}, ResNet~\cite{03385,05027}, and~NasNet~\cite{07012}. The~combination of DenseNet201, InceptionResNetV2 and the Soft-Attention layer are both tested by the previous paper~\cite{03358} with a great performance. Otherwise, Resnet50 also well classifies but with much fewer parameters and less depth than based on its f1-score and precision stated. Therefore, in~this paper, the~performance of the Resnet152 and NasnetLarge models, which have more parameters and depth, is analyzed. On~the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed, which has fewer parameters and~depth.

\begin{table}[H]\setlength{\tabcolsep}{7.9mm}
\renewcommand{\arraystretch}{1.2}

	\caption{\hl{Size,} %MDPI: 1. Please cite the table in the text and ensure the first citation of each table appears in numerical order. 2. Please confirm if the vertical line is necessary, if not, please remove it.
 parameters, and depth of the backbone model used in this~paper.}
	\label{table:model-summary}
	\begin{tabular}{|l | c c c|} 
		\noalign{\hrule height 1pt}

		\textbf{Model} &\textbf{ Size (MB)} & \textbf{Parameters} & \textbf{Depth} \\ 
		\hline
		Resnet50 & 98 & 25.6 M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4 M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2 M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9 M & 449 \\
		\hline
		MobileNet & 16 & 4.3 M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5 M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5 M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5 M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3 M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9 M & 533 \\ 
	\noalign{\hrule height 1pt}
	\end{tabular}
\end{table}
\unskip

\subsubsection{Soft-Attention~Module}
Soft-Attention has been used in various applications: image caption generation such as~\cite{03044} or handwriting verification~\cite{202017}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. Soft-Attention is described in the below equation:
\[
f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]
Figure~\ref{fig:soft-attention} shows the two main steps of applying Soft-Attention. Firstly, the~input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map~\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network (CNN) is then input to a 3D convolution layer whose weights are $W_k \in R^{h \times w \times d \times K}$. The~output of this convolution is normalized using the soft-max function to generate \hl{K} %MDPI: Please change the forward italics of the variables in the text and formulas to be consistent
 (a constant value) attention maps. These $K$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, which is a~learnable scalar. Finally, the~output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention~maps.

\begin{figure}[H]
	%\centering
	\includegraphics[width=1\linewidth]{Definitions/SoftAttention}
	\caption{\hl{Soft-Attention~Layer.} %MDPI: Please revise the "*" into a multiplication sign ("\times" U+00D7)
}
	\label{fig:soft-attention}
\end{figure}

In this research, the~Soft-Attention layer is applied in the same way in this research~\cite{03358}. The~Soft-Attention module is described in Figure~\ref{fig:soft-attention-block}.

\begin{figure}[H]
	%\centering
	\includegraphics[width=0.5\linewidth]{Definitions/SoftAttentionBlock}
	\caption{\hl{Soft-Attention~Module.} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7)
}
	\label{fig:soft-attention-block}
\end{figure}

After feeding into the ReLU function layer, the~heat feature map is processed in two paths. The~first path is the two-dimensional Max Pooling. In~the second path, the~feature map, on~the other hand is fed into the Soft-Attention layer before the two-dimensional Max Pooling. After~all, these two paths are then concatenated and fed into a ReLU layer with~a dropout with the probability of $0.5$.

\subsubsection{Loss~Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and~$C$ be the number of training examples and number of classes, respectively. The~categorical cross-entropy loss is presented as:
\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
where $\hat{y}^c_i$  is the output of the model, $y^c_i$ is the target that the model should return, and $W_c$ is the weight of class $c$. Since the data sets face the imbalanced problem, then class weight for the loss is applied. In~this research, both the original weight and a new weight formula are implemented. Originally, the~weight is calculated by taking the inverse of percentage that each class accounts for. The~new weight formula is described as follows:
\[W = N \odot D\]
\[D = \begin{bmatrix}
	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
\end{bmatrix}\]
where $N$ is the number of training samples, $C$ is the number of classes, $N_i$ is the number of samples in each class $i$. $D$ is the matrix that contains the inverse of $C \times N_i$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\unskip
\subsection{Experimental~Setup}
\unskip
\subsubsection{Training}
Before training, the~data set is split into two subsets for training (90\%) and validation (10\%). The test set otherwise is provided by the HAM10000 data set, and it contains 857 images. To~analyze the effect of augmented data on the model, before~the training, the image data are augmented to 53573 images by the following technique:

\begin{itemize}
\item[-]	Rotation range: rotate the image in a fixed~angle.
\item[-]		Width and height shift range: Shift the image horizontally and vertically, respectively.
\item[-]		Zoom range:  Zoom in or zoom out the image to create new~image. 
\item[-]		Horizontal and vertical flipping: Flipping the image horizontally and vertically to create new~image.
\end{itemize}

Otherwise, all of the models are trained with the Adam Optimizer~\cite{6980} with the learning rate of $0.001$, which is reduced by a factor of $0.2$ to a minimum learning rate of \hl{$0.1 \times 10^6$}%MDPI: We revised the "x" into a multiplication sign ("\times" U+00D7). Please confirm.
, and~the epsilon is set to $0.1$. The~initial epochs is set to 250~epochs, and the Early Stopping is also applied to stop the training, as the accuracy of the validation set does not increase after $25$ epochs. The~batch size is set to $32$.

\subsubsection{Tools}
TensorFlow and Keras are two of the most popular frameworks to build deep learning models. In~this research, Keras based on TensorFlow is used to build and clone the backbone model, which is pre-trained with the Image-Net data set. Otherwise, the~models are trained by NVIDIA RTX TitanV, and the data set is preprocessed with the CPU Intel I5 32 processors, RAM 32~GB. In~detail, the~GPU is set up with CUDA 11.6, cuDNN 8.3 and ChipSRT as the requirement of TensorFlow version~2.7.0.
\subsubsection{Evaluation~Metrics}

The model is evaluated by using the confusion matrix and related metrics. The \mbox{Figure~\ref{fig:confusion-matrix}} illustrates the presentation of a $2 \times 2$ confusion matrix used for class $2$. Consider a confusion matrix $A$ with $C$ number of classes. Let $A^i$ and $A^j$ be the set of $A$ rows and columns, respectively; therefore $A^i_k$ is the element at row i and column k.
\[
A = \begin{bmatrix}
	a_{11} & a_{12} & \dots & a_{1j} \\
	a_{21} & a_{22} & \dots & a_{2j} \\
	\vdots & \vdots	&  & \vdots\\
	a_{i1} & a_{i2} & \dots & a_{ij} 
\end{bmatrix}
\]

\vspace{-12pt}

\begin{figure}[H]
	\begin{minipage}{0.48\textwidth}
	%	\centering
		\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
		\caption{Confusion~Matrix.}\label{fig:confusion-matrix}
	\end{minipage}

\end{figure}

\vspace{-12pt}

\begin{figure}[H]

	\begin{minipage}{0.48\textwidth}
		%\centering
		\includegraphics[width=.7\linewidth]{Definitions/AUC}
		\caption{\hl{Area Under} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
 the~Curve.}\label{fig:AUC}
	\end{minipage}
\end{figure}

The True Positive (\hl{TP}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent
) of all classes in this case is the main diagonal of the matrix $A$. The~following methods are used to calculate the False Positives (\hl{FP}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent
), False Negatives (\hl{FN}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent
), and~True Negatives (\hl{TN}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent
) of all classes:
\[
FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
\]
\[
TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
	TN_1 & TN_2 & \dots & TN_c
\end{bmatrix}
\]
\hl{Then,} %MDPI: Please confirm should the no indentation be retained
 the~model is evaluated by the following metrics:
\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
where Sensitivity and Specificity mathematically describe the accuracy of a test which reports the presence or absence of a condition. Individuals for which the condition is satisfied are considered ``positive'' and those for which it is not are considered ``negative''. Sensitivity or the True Positive rate refers to the probability of a positive test, which is conditioned on truly being positive while Specificity  or the True Negative rate refers to the probability of a negative test, which is conditioned on truly being negative.
\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
\hl{Precision} %MDPI: Please confirm should the no indentation be retained
 or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative. F1-score, on~the other hand, refers the harmonic mean of precision and recall, which means the higher the f1-score is, the~higher both precision and recall are. The~expected value of precision, f1-score and recall score are also applied because of the multi-class problem.
\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
\hl{The last} %MDPI: Please confirm should the no indentation be retained
 metric is the $AUC$ score standing for Area Under the Curve, which is the Receiver Operating Curve (ROC) that indicates the probability of TP versus the probability of~FP.

\subsection{Discussion} 
\begin{comment}
	\begin{figure}[H]
		\centering
		\includegraphics[width=1\linewidth]{Definitions/ACCALL}
		\caption{Accuracy of all models trained in this~research}
		\label{fig:accall}
	\end{figure}
\end{comment}

According to Table~\ref{table:overall-acc}, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only. While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.79$ and $0.84$, respectively, their training with metadata are $0.90$ and $0.89$, respectively. Furthermore, Resnet50 trained with metadata data has the accuracy that outperforms the Resnet50 trained with augmented data and is twice as high as Resnet152 trained with metadata. On~the other hand, mobile models including MobileNetV2, MobileNetV3Large, and~NasNetMobile, even though they have a much smaller number of parameters and depth than the other models, have quite good accuracy scores of $0.81$, $0.86$, and $0.86$, respectively.

\begin{table}[H]\renewcommand{\arraystretch}{1.2}\setlength{\tabcolsep}{12.3mm}
	\caption{Accuracy of all models. ACC stands for accuracy. AD stands for augmented data; this indicates that the model is trained with augmented data. MD stands for metadata, which indicates that the model is trained with~metadata.}
	\label{table:overall-acc}
	\begin{tabular}{| l | c  c | }
	\noalign{\hrule height 1pt}

		\textbf{Model} & \textbf{ACC (AD)} & \textbf{ACC (MD)}\\ 
		\hline
		InceptionResNetV2 & 0.79 & \textbf{\hl{0.90} %MDPI: 1. Please confirm if the bold should be retained. 2. Please confirm if the vertical line is necessary, if not, please remove it.
}\\
		\hline
		DenseNet201 & 0.84 & \textbf{0.89}\\
		\hline
		ResNet50 & 0.76 & 0.70\\
		\hline
		ResNet152 & 0.81 & 0.57\\
		\hline
		NasNetLarge & - & 0.84\\
		\hline
		MobileNetV2 & - & 0.81\\
		\hline
		MobileNetV3Small & - & 0.78\\
		\hline
		MobileNetV3Large & 0.85 & \textbf{0.86}\\
		\hline
		NasNetMobile & 0.84 & \textbf{0.86}\\
		\noalign{\hrule height 1pt}

	\end{tabular}
\end{table}

Moreover, the~model trained with augmented data does not only have low accuracy but the f1-score and the recall score also are imbalanced according to Figures~\ref{fig:den f1}--\ref{fig:incep recall}. As~a result, the augmented data model does not classify well on all classes, as InceptionResNetV2 trained on augmented data has an f1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to Figure~\ref{fig:incep f1}. However, only DenseNet201, InceptionResNetV2, and~NasNetLarge whose depth are equal to or larger than 400 have balanced f1-scores on class. The~others still face the imbalanced term. Since this data set is not balanced, therefore, using augmented data can make the model more  biased to the class which has a larger sample. Although using the metadata still leads to model bias, it does contribute to the improvement of  the performance of the~model.

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/den f1}
	\caption{The comparison between f1-scores of DenseNet201 trained with augmented data and the one trained with metadata and weight~loss.}
	\label{fig:den f1}
\end{figure}
\unskip
\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/in f1}
	\caption{The comparison between f1-scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight~loss.}
	\label{fig:incep f1}
\end{figure}

\textls[+25]{This problem is also true with the recall score according to Figures~\ref{fig:den recall} and \ref{fig:incep recall}.} DenseNet201 and InceptionResNetV2 trained with augmented data have expected recall values of $0.56$ and $0.69$, respectively, while the combination of DenseNet201, Metadata and the new weight loss function achieve the expected value of recall: $0.82$. Therefore, metadata do improve the model performance by reducing the amount of data needed for achieving higher results. On~the other hand, the~reason why the model becomes much more balanced is the weighted loss function. Weight loss function has the ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. DenseNet201 and InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$ and $0.82$, respectively, as~opposed to their training in akiec without weighted loss function: $0.65$ and $0.37$.

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/den re}
	\caption{The comparison between recal scores of DenseNet201 trained with augmented data and the one trained with metadata and weight~loss.}
	\label{fig:den recall}
\end{figure}
\unskip

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/in re}
	\caption{The comparison between recall scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight~loss.}
	\label{fig:incep recall}
\end{figure}

Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have a small number of parameters and depth, but they~have relatively good performance. MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall scores of $0.92$, $1$, $0.92$, and $0.92$, separately, according to Table~\ref{appendix-table:mobile-performance}. It is transparent that MobileNetV3Large and NasNetMobile are the two best performance models. Nevertheless, MobileNetV3Large has fewer parameters and depth than~NasNetMobile.

Table~\ref{table:optimized-performance-mobile-model} shows that MobileNetV3Large, although~the number of parameters is much smaller than that of DenseNet201. InceptionResNetV2 achieves an accuracy near to the others. In~detail, MobileNetV3Large has 5.5 million parameters, which is four and ten times less than DenseNet201 and InceptionResNetV2, respectively. The~depth of MobileNetV3Large, on~the other hand, is four times less than DenseNet201, InceptionResNetV2, which is 118 hidden layers as opposed to the 402 and 449 values of DenseNet201 and InceptionResNetV2, separately. Although MobileNetV3Larege only achieves an accuracy of 0.86, the time needed for prediction is 10 and 30 times less than the other opponents. Since MobileNetV3Large needs a harder process of parameter hyper-tuning to achieve a better result, this is also the future target of this~research.

\begin{table}[H]\setlength{\tabcolsep}{1.6mm}\renewcommand{\arraystretch}{1.2}
	\caption{How the performance of MobileNetV3Large can be~optimized.}%MDPI: Please confirm if the vertical line is necessary, if not, please remove it.
	\label{table:optimized-performance-mobile-model}
	\begin{tabular}{| l | c | c | c |}
		\noalign{\hrule height 1pt}

		\textbf{Model} &\textbf{ MobileNetV3Large} & \textbf{DenseNet201 }& \textbf{InceptionResnetV2}\\
		\hline
		No. Parameters & \textbf{\hl{5.5 M} %MDPI: Please confirm if the bold should be retained.
} & 20.2 M & 55.9 M\\
		\hline
		Depth & \textbf{118} & 402 & 449\\
		\hline
		Accuracy & 0.86 & 0.89 & 0.90\\
		\hline
		Time Prediction(s/epochs) & \textbf{116} & 1000 & 3500 \\
	\noalign{\hrule height 1pt}

	\end{tabular}
\end{table}

Table~\ref{table:overall-auc} shows the AUC score of the three models---InceptionResNetV2, Densenet201, and~ResNet50---which are trained with only augmented data or metadata. It is transparent that InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: 0.974 and 0.971 as opposed to 0.972 and 0.93, respectively. ResNet50 trained with augmented data, on~the other hand, has a higher AUC-score: 0.95 as compared to 0.93 of ResNet50 trained with metadata. Overall, InceptionResNetV2 trained with metadata reaches the peak with an AUC score of 0.974. InceptionResNetV2 trained with metadata is also compared with the others to find out the best models trained. According to  \hl{\mbox{Figure~15},} %MDPI: There is no Figure 15 in the text, please revise.
InceptionResNetV2 still hit the peak AUC score of 0.974. In contrast, ResNet152 is the worst model with the AUC score of 0.87. Other models, on~the other hand, have the approximately the same AUC score.

\begin{table}[H]\renewcommand{\arraystretch}{1.2}\setlength{\tabcolsep}{12.2mm}

	\caption{AUC (area under the curve) of all models. AD stands for augmented data; this indicates that the model is trained with augmented data. MD stands for metadata, which indicates that the model is trained with~metadata.}
	\label{table:overall-auc}
	\begin{tabular}{| l | c  c | }
	\noalign{\hrule height 1pt}

		\textbf{Model} & \textbf{AUC (AD)} & \textbf{AUC (MD)}\\ 
		\hline
		InceptionResNetV2 & 0.971 & \textbf{\hl{0.974} %MDPI: Please confirm if the bold should be retained.
}\\
		\hline
		DenseNet201 & 0.93 & \textbf{0.97}\\
		\hline
		ResNet50 & \textbf{0.95} & 0.93 \\
		\hline
		ResNet152 & - & 0.87\\
		\hline
		NasNetLarge & - & \textbf{0.96}\\
		\hline
		MobileNetV2 & - & \textbf{0.97}\\
		\hline
		MobileNetV3Small & - & \textbf{0.96}\\
		\hline
		MobileNetV3Large & - & \textbf{0.97}\\
		\hline
		NasNetMobile & - & \textbf{0.97}\\
		\noalign{\hrule height 1pt}
	\end{tabular}
\end{table}

%\clearpage

In addition to the comparison between original weight loss calculated by the sample percentage of each class model and the new weight loss-based model, it is also conducted on the three best-performing models, including InceptionResNetV2, DenseNet201, and MobileNetV3. After~the experiment, it is found out that the new weight loss function does not only contribute to the model to overcome the data imbalance problem but it also makes the accuracy increase. The~performance of models is described in Table~\ref{table:loss-comparision}.

\begin{table}[H]\setlength{\tabcolsep}{2.75mm}\renewcommand{\arraystretch}{1.2}

	\caption{\hl{Loss}-based model accuracy~comparison.}%MDPI:  Please confirm if the vertical line is necessary, if not, please remove it.
	\label{table:loss-comparision}
	\begin{tabular}{| l | c | c | c |}
		\noalign{\hrule height 1pt}

		\textbf{Model} & \textbf{No Weight }& \textbf{Original Loss Accuracy} & \textbf{New Loss Accuracy}\\
		\hline
		InceptionResNetV2 & 0.74 & 0.79 & 0.90\\
		DenseNet201 & 0.81 & 0.84 & 0.89\\
		MobileNetV3 & 0.79 & 0.80 & 0.86\\
			\noalign{\hrule height 1pt}
	\end{tabular}
\end{table}

After reviewing, InceptionResNetV2 is found to be the best model trained. Futhermore, InceptionResNetV2 is compared with the other state of the art researched models. According to Table~\ref{table:comparative-analysis}, there are six researchers that use the same data set: HAM10000, but they have different approaches. These models used in that research are also SOTA models sorted in ascending order. The~table shows that the accuracy of the combination of InceptionResNetV2 with Soft-Attention, metadata and weight loss in this research is less than that of InceptionResNetV2 with Soft-Attention and augmented data: 0.90 compared to 0.93, respectively. However, since Soumyyak et al. use data augmentation for all classes of an imbalanced data set, the~f1-score and recall score are much lower. This is because the model in that research can only classify well on NV and VASC classes, which have the highest number of samples. On~the other hand, InceptionResNetV2 in this research also outperforms the other models according to five indicators: accuracy, precision, f1-score, recall score, and~AUC score. 
\FloatBarrier
\begin{table}[H]\renewcommand{\arraystretch}{1.2}\setlength{\tabcolsep}{1.6mm}
	\caption{Comparative~Analysis.}%MDPI:  Please confirm if the vertical line is necessary, if not, please remove it.
	\label{table:comparative-analysis}
	\begin{tabular}{| l| c | c | c | c | c |}
		\noalign{\hrule height 1pt}

		\textbf{Model} & \textbf{Accuracy} & \textbf{Precision} & \textbf{F1-Score} & \textbf{Recall} & \textbf{Auc-Score}\\
		\hline
		Our Proposed & 0.9	& 0.86 &\textbf{\hl{0.86} %MDPI: Please confirm if the bold should be retained.
} & \textbf{0.81} & 0.974\\
		\hline
		InceptionResNetV2~\cite{03358} & 0.93 & 0.89 & 0.75 & 0.71 & 0.97\\
		\hline~\cite{03798} & - & 0.88 & 0.77 & 0.74 & - \\
		\hline~\cite{09418} & 0.88 & - & - & - & - \\
		\hline~\cite{01284} & 0.86 & - & - & - & - \\
		\hline
		GradCam and Kernel SHAP~\cite{06612} & 0.88 & - & - & - & - \\
		\hline
		Student and Teacher~\cite{03225} & 0.85 & 0.76 & 0.76 & - & - \\
			\noalign{\hrule height 1pt}
	\end{tabular}
\end{table}

However, there is still some drawbacks of the model: InceptionResNetV2 cannot well classify the melanoma and the nevus. According to Figure~\ref{fig:nevusVSmela}, the model sometimes classifies the black nevus as the melanoma because of the same color between them. However, this problem is not true for the hard black or big melanoma or the red black nevus. Some future approaches that can be proposed would be to change the type of color to the other to fix the same color~problem.

\begin{figure}[H]
	%\centering
	\includegraphics[width=0.9\linewidth]{Definitions/img_class_nevus_mela}
	\caption{Model ability to classify melanoma and~nevus.}
	\label{fig:nevusVSmela}
\end{figure}
\unskip

\section{Conclusions}
In this research, our proposal is to construct a model as a combination of backbone models and Soft-Attention. Moreover, the~model takes two inputs, including image data and metadata. A~new weight loss function is applied to figure out the data imbalance problem. Finally, the~combination of InceptionResNetV2, Soft-Attention, and~metadata is the best model. Although~the accuracy and the precision of the model are not the highest, the~f1-score, recall, and~AUC score are the highest and the most balanced indicators. Therefore, InceptionResnetV2 can classify well in all classes including low-samples classes. Otherwise, during~the experiment, the~combination of MobileNetV3, Soft-Attention, and~metadata achieves an accuracy that is nearly the same as InceptionResNetV2, although~with fewer  parameters and depth. Therefore, the infer time is much less than that of InceptionResNetV2. This result opens the door to constructing a great performance model that can be applied to mobile and IoT devices.  
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, V.D.N. and H.K.D.; methodology, V.D.N. and H.K.D.; software, K.D.; validation, V.D.N., N.D.B. and H.K.D.; formal analysis, V.D.N. and H.K.D.; investigation, V.D.N., N.D.B. and H.K.D.; resources, V.D.N.; data curation, H.K.D.; writing---original draft preparation, H.K.D.; writing---review and editing, V.D.N. and N.D.B.; visualization, H.K.D.; supervision, V.D.N. and N.D.B.; project administration, V.D.N. All authors have read and agreed to the published version of the~manuscript.}

\funding{This research received no external~funding.}

\institutionalreview{Not applicable.}

\informedconsent{Not applicable.}

\dataavailability{\textls[-15]{The code and the data analysis report can be found here:} \url{https://github.com/KhoiDOO/Skin-Disease-Detection-HAM100000.git}  (\hl{accessed on}%MDPI: Please add the access date (Format: Date Month Year) that earlier than Received date. e.g., (accessed on 29 August 2022).
).}

\conflictsofinterest{The authors declare no conflict of~interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
%\sampleavailability{}

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
CAD & Computer-aided diagnosis\\
AI & Artificial intelligence\\
AKIEC~~~~~~~~~~~~~ & Actinic keratoses and intraepithelial carcinoma or Bowen's disease\\
BCC & Basal Cell Carcinoma\\
BKL & Benign Keratosis-like Lesions\\
\end{tabular}

\noindent 
\begin{tabular}{@{}ll}

DF & Dermatofibroma\\
MEL & Melanoma\\
NV & Melanocytic Nevi\\
VASC & Vascular Lesions\\
HISTO & Histopathology\\
FOLLOWUP & Follow-up examination\\
CONSENSUS & Expert Consensus\\
CONFOCAL & Confocal Microscopy\\
RGB & Red Green Blue\\
BGR & Blue Green Red\\
TP & True Positives\\
FN & False Negatives\\
TN & True Negatives\\
FP & False Positives\\
Sens & Sensitivity\\
Spec & Specificity\\
AUC & Area Under the Curve\\
ROC & Receiver Operating Curve\\
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional

%\startlandscape

\appendixtitles{yes} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{Detailed Model Structure}\label{app1}

\vspace{-6pt}

\begin{table}[H]\renewcommand{\arraystretch}{1.2}
	\caption{\hl{Detailed structure} %MDPI: 1. We revised the "x" into a multiplication sign ("\times" U+00D7). Please confirm. 2. Please confirm if the vertical line is necessary, if not, please remove it.
 of models except for mobile models. SA stands for Soft-Attention, SA Module denotes whether that model uses the Soft-Attention module. GAP stands for Global Average Pooling. FC stands for Fully Connected~Layer.\label{appendix-table:detailed structure model}}
    \tablesize{\scriptsize}	
	\begin{adjustwidth}{-\extralength}{0cm}

		%\newcolumntype{C}{>{\centering\arraybackslash}X}
%{\fontsize{7}{7}\selectfont
%\tablesize{\fontsize{7}{7}\selectfont}
%
%

\setlength{\cellWidtha}{\fulllength/10-2\tabcolsep-0in}
\setlength{\cellWidthb}{\fulllength/10-2\tabcolsep-0in}
\setlength{\cellWidthc}{\fulllength/10-2\tabcolsep-0in}
\setlength{\cellWidthd}{\fulllength/10-2\tabcolsep-0in}
\setlength{\cellWidthe}{\fulllength/10-2\tabcolsep-0in}
\setlength{\cellWidthf}{\fulllength/10-2\tabcolsep-0.01in}
\setlength{\cellWidthg}{\fulllength/10-2\tabcolsep-0.01in}
\setlength{\cellWidthh}{\fulllength/10-2\tabcolsep-0.01in}
\setlength{\cellWidthi}{\fulllength/10-2\tabcolsep-0.01in}
\setlength{\cellWidthj}{\fulllength/10-2\tabcolsep-0.01in}
\scalebox{1}[1]{\begin{tabularx}{\fulllength}{|>{\PreserveBackslash\raggedright}m{\cellWidtha}|>{\PreserveBackslash\raggedright}m{\cellWidthb}|>{\PreserveBackslash\raggedright}m{\cellWidthc}|>{\PreserveBackslash\raggedright}m{\cellWidthd}|>{\PreserveBackslash\raggedright}m{\cellWidthe}|>{\PreserveBackslash\raggedright}m{\cellWidthf}|>{\PreserveBackslash\raggedright}m{\cellWidthg}|>{\PreserveBackslash\raggedright}m{\cellWidthh}|>{\PreserveBackslash\raggedright}m{\cellWidthi}|>{\PreserveBackslash\raggedright}m{\cellWidthj}|}

	%\begin{tabularx}{\fulllength}{l|l|l|l|l|l|l|l|l|l}
			\noalign{\hrule height 1pt}

			\textbf{DenseNet-201} & \textbf{DenseNet-201 + SA} & \textbf{Inception-ResNetV2} & \textbf{Inception-ResNetV2 + SA} & \textbf{ResNet-50} & \textbf{ResNet-50 + SA} & \textbf{ResNet-152} & \textbf{ResNet-152 + SA} & \textbf{NasNet-Large} & \textbf{NasNet-Large + SA}\\
			\hline
			Conv2D \mbox{\mbox{7 $\times$ 7}} & Conv2D \mbox{7 $\times$ 7} & STEM& STEM& Conv2D \mbox{7 $\times$ 7}& Conv2D \mbox{7 $\times$ 7}& Conv2D \mbox{7 $\times$ 7}& Conv2D \mbox{7 $\times$ 7}& Conv2D \mbox{3 $\times$ 3}& Conv2D \mbox{3 $\times$ 3}\\ \hline
			Pooling \mbox{3 $\times$ 3} & Pooling \mbox{3 $\times$ 3} & & & Pooling \mbox{3 $\times$ 3}& Pooling  \mbox{3 $\times$ 3}& Pooling  \mbox{3 $\times$ 3}& Pooling  \mbox{3 $\times$ 3}& Pooling& Pooling\\ \hline		
			DenseBlock $\times$ 6 & DenseBlock $\times$ 6 & Inception ResNet A $\times$ 10& Inception ResNet A $\times$ 10& Residual Block $\times$ 3& Residual Block $\times$ 3& Residual Block $\times$ 3& Residual Block $\times$ 3& Reduction Cell $\times$ 2& Reduction Cell $\times$ 2\\  \hline
			Conv2D \mbox{1 $\times$ 1} & Conv2D \mbox{1 $\times$ 1} & Reduction A & Reduction A & & & & & Normal Cell $\times$ N& Normal Cell $\times$ N\\	\hline			
			Average pool \mbox{2 $\times$ 2} & Average pool \mbox{2 $\times$ 2} & & & & & & & & \\ \hline			
			DenseBlock $\times$ 12 & DenseBlock $\times$ 12 & Inception ResNet B $\times$ 20& Inception ResNet B $\times$ 20& Residual Block $\times$ 4& Residual Block $\times$ 4& Residual Block $\times$ 8& Residual Block $\times$ 8& Reduction Cell& Reduction Cell\\ \hline
			Conv2D \mbox{1 $\times$ 1} & Conv2D \mbox{1 $\times$ 1} & Reduction B & Reduction B & & & & & Normal Cell $\times$ N& Normal Cell $\times$ N\\			\hline
			Average pool \mbox{2 $\times$ 2} & Average pool \mbox{2 $\times$ 2} & & & & & & & & \\ \hline
			DenseBlock $\times$ 48 & DenseBlock $\times$ 12 & Inception ResNet C $\times$ 5& Inception ResNet C $\times$ 5& Residual Block $\times$ 6& Residual Block $\times$ 6& Residual Block $\times$ 36& Residual Block $\times$ 36& Reduction Cell& Reduction Cell\\ \hline
			Conv2D \mbox{1 $\times$ 1} & Conv2D \mbox{1 $\times$ 1} & & & & & & & Normal Cell $\times$ N& Normal Cell $\times$ N$-$2\\			\hline
			Average pool \mbox{2 $\times$ 2} & Average pool \mbox{2 $\times$ 2} & & & & & & & & \\ \hline
			DenseBlock $\times$ 29 & DenseBlock $\times$ 29 & & & Residual Block $\times$ 3& & Residual Block $\times$ 3& & & \\ \hline
			DenseBlock $\times$ 3 & \textbf{\hl{SA Module} %MDPI: Please confirm if the bold should be retained.
} & & \textbf{SA Module}& & \textbf{SA Module}& & \textbf{SA Module}& & \textbf{SA Module}\\	\hline
			GAP \mbox{7 $\times$ 7} & & Average pool& & GAP \mbox{7 $\times$ 7}& & GAP \mbox{7 $\times$ 7}& & & \\			\hline
			FC 1000D & & Dropout (0.8)& & FC 1000D& & FC 1000D& & & \\ \hline
			SoftMax & SoftMax & SoftMax& SoftMax& SoftMax& SoftMax& SoftMax& SoftMax& SoftMax& SoftMax\\ 			
			\noalign{\hrule height 1pt}
		\end{tabularx}
		}

	\end{adjustwidth}
\end{table}

%\finishlandscape

\section[\appendixname~\thesection]{Detailed Mobile-Based Model Structure}\label{app2}

\vspace{-6pt}

\begin{table}[H]\renewcommand{\arraystretch}{1.2}

	\caption{\hl{Detailed} structure of mobile-based models. SA stands for Soft-Attention, SA Module denotes whether that model uses the Soft-Attention module. SE stands for Squeeze-And-Excite, and it shows whether that block has~Squeeze-And-Excite. \label{appendix-table:detailed mobile model structure}}%MDPI: Please confirm if the vertical line is necessary, if not, please remove it.

    \tablesize{\footnotesize}	
	\begin{adjustwidth}{-\extralength}{0cm}
		%\newcolumntype{C}{>{\centering\arraybackslash}X}

		\setlength{\cellWidtha}{\fulllength/8-2\tabcolsep-0in}
\setlength{\cellWidthb}{\fulllength/8-2\tabcolsep-0in}
\setlength{\cellWidthc}{\fulllength/8-2\tabcolsep-0in}
\setlength{\cellWidthd}{\fulllength/8-2\tabcolsep-0in}
\setlength{\cellWidthe}{\fulllength/8-2\tabcolsep-0.01in}
\setlength{\cellWidthf}{\fulllength/8-2\tabcolsep-0.01in}
\setlength{\cellWidthg}{\fulllength/8-2\tabcolsep-0.01in}
\setlength{\cellWidthh}{\fulllength/8-2\tabcolsep-0.01in}
\scalebox{1}[1]{\begin{tabularx}{\fulllength}{|>{\PreserveBackslash\raggedright}m{\cellWidtha}|>{\PreserveBackslash\raggedright}m{\cellWidthb}|>{\PreserveBackslash\raggedright}m{\cellWidthc}|>{\PreserveBackslash\raggedright}m{\cellWidthd}|>{\PreserveBackslash\raggedright}m{\cellWidthe}|>{\PreserveBackslash\raggedright}m{\cellWidthf}|>{\PreserveBackslash\raggedright}m{\cellWidthg}|>{\PreserveBackslash\raggedright}m{\cellWidthh}|}

	%	\begin{tabularx}{\fulllength}{l|l|l|l|l|l|l|l|l}
			\noalign{\hrule height 1pt}
			\textbf{MobileNetV2} & \textbf{MobileNetV2 + SA} & \textbf{MobileNetV3 Small} & \textbf{MobileNetV3 Small + SA} & \textbf{MobileNetV3 Large} & \textbf{MobileNetV3 Large + SA} & \textbf{NasNet Mobile} & \textbf{NasNetMobile + SA}\\
			\hline
			Conv2D & Conv2D& Conv2D \mbox{3 $\times$ 3}& Conv2D \mbox{3 $\times$ 3}& Conv2D \mbox{3 $\times$ 3}& Conv2D \mbox{3 $\times$ 3} & Normal Cell & Normal Cell\\	\hline		
			bottleneck & bottleneck & bottleneck \mbox{3 $\times$ 3} SE& bottleneck \mbox{3 $\times$ 3} SE& bottleneck \mbox{3 $\times$ 3} 3 repeated& bottleneck \mbox{3 $\times$ 3} 3 repeated& Reduction Cell& Reduction Cell\\ \hline					
			bottleneck 2 repeated& bottleneck 2 repeated& bottleneck \mbox{3 $\times$ 3}& bottleneck \mbox{3 $\times$ 3}& bottleneck \mbox{5 $\times$ 5} SE 3 repeated& bottleneck \mbox{5 $\times$ 5} SE 3 repeated & Normal Cell & Normal Cell\\ \hline	
			bottleneck 3 repeated& bottleneck 3 repeated& bottleneck \mbox{5 $\times$ 5} SE 8 repeated& bottleneck \mbox{5 $\times$ 5} SE 8 repeated& bottleneck \mbox{3 $\times$ 3} 4 repeated& bottleneck \mbox{3 $\times$ 3} 4 repeated& Reduction Cell & Reduction Cell\\ \hline	
			bottleneck 4 repeated& bottleneck 4 repeated& & & bottleneck \mbox{3 $\times$ 3} SE 2 repeated& bottleneck \mbox{3 $\times$ 3} SE 2 repeated & Normal Cell&\\ \hline	
			bottleneck 3 repeated& bottleneck 3 repeated& & & bottleneck \mbox{5 $\times$ 5} SE 3 repeated& bottleneck \mbox{5 $\times$ 5} SE 3 repeated&& \\ \hline	
			bottleneck 3 repeated& bottleneck & & & & && \\ \hline	
			bottleneck & & & & & &&~ \\ \hline
			Conv2D \mbox{1 $\times$ 1} & & Conv2D \mbox{1 $\times$ 1} SE & Conv2D \mbox{1 $\times$ 1} SE& Conv2D \mbox{1 $\times$ 1}& Conv2D \mbox{1 $\times$ 1} & & \\ \hline
			AP \mbox{7 $\times$ 7} & & Pool \mbox{7 $\times$ 7}& Pool \mbox{7 $\times$ 7}& Pool \mbox{7 $\times$ 7}& Pool \mbox{7 $\times$ 7}& &~\\ \hline
			Conv2D \mbox{1 $\times$ 1} & \textbf{SA Module}& Conv2D \mbox{1 $\times$ 1} 2 repeated& \textbf{SA Module}& Conv2D \mbox{1 $\times$ 1} 2 repeated& \textbf{SA Module}& &\textbf{SA Module}\\ \hline
			Softmax & Softmax& Softmax& Softmax& Softmax& Softmax& Softmax & Softmax\\ 
			\noalign{\hrule height 1pt}
		\end{tabularx}}
	\end{adjustwidth}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[\appendixname~\thesection]{Detailed Model Performance}
\subsection[\appendixname~\thesection]{F1-Score Model Performance}

\vspace{-6pt}

\begin{table}[H]\renewcommand{\arraystretch}{1.2}\setlength{\tabcolsep}{4.2mm}

	\caption{\hl{F1-score%MDPI: Please confirm if the vertical line is necessary, if not, please remove it.
	} of each class: akiec, bcc, bkl, df, mel, nv, and vasc, which are denoted in the abbreviations. The~last column shows the expected value of f1-score from each model. All models in the first column are the models trained in this research. The~term ``with Augmented Data'' means that model is trained with data augmenting during the training; there is no metadata or weight loss contribution. The~term ``with Metadata and WeightLoss'' means that the model is trained with metadata including age, gender, localization and the weight loss function; there is no augmented data~contribution.}
	\label{appendix-table:F1-score-summary}

\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering
	\footnotesize{
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|} 
		\noalign{\hrule height 1pt}
		\textbf{Model} & \textbf{akiec} & \textbf{bcc} & \textbf{bkl} & \textbf{df} & \textbf{mel} & \textbf{nv} & \textbf{vasc} & \textbf{Mean} \\
		\hline
		DenseNet201 with Augmented Data & 0.56 & 0.75 & 0.64 & 0.62 & 0.60 & 0.93 & 0.85 & 0.70 \\ 
		\hline
		InceptionResNetV2 with Augmented Data & 0.42 &	0.63 & 0.51 & 0.35 & 0.57 & 0.9 & 0.7 & 0.58\\
		\hline
		Resnet50 with Augmented Data & 0.39 & 0.59 & 0.42 & 0.6 & 0.42 & 0.88 & 0.79 & 0.58\\
		\hline 	
		VGG16 with Augmented Data & 0.35 & 0.62 & 0.42 & 0.32 & 0.47 & 0.89 & 0.77 & 0.54\\ 
		\hline		
		DenseNet201 with Metadata and WeightLoss & \textbf{\hl{0.84} %MDPI: Please confirm if the bold should be retained.
} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
		\hline
		InceptionResNetV2 with Metadata and WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
		\hline
		Resnet50 with Metadata and WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
		\hline
		Resnet152 with Metadata and WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
		\hline
		NasNetLarge with Metadata and WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
		\hline
		MobileNetV2 with Metadata and WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
		\hline
		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
		\hline
		MobileNetV3Small with Metadata and WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
		\hline
		NasNetMobile with Metadata and WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
		\noalign{\hrule height 1pt}
	\end{tabular}}
\end{adjustwidth}
\end{table}

\subsection[\appendixname~\thesection]{Recall Model Performance}

\vspace{-6pt}

\begin{table}[H]\renewcommand{\arraystretch}{1.2}\setlength{\tabcolsep}{2.7mm}
	\caption{\hl{Recall%MDPI: Please confirm if the vertical line is necessary, if not, please remove it.
	} score of each class and the expected value of recall score from each~model.}
	\label{appendix-table:recall-score-summary}

    %\tablesize{\footnotesize}

	%\centering
\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering

	\begin{tabular}{|l|l|l|l|l|l|l|l|l|}  
		\noalign{\hrule height 1pt}
		\textbf{Model} & \textbf{akiec} & \textbf{bcc} & \textbf{bkl} & \textbf{df} & \textbf{mel} & \textbf{nv} & \textbf{vasc} & \textbf{Mean} \\
		\hline
		DenseNet201 with Augmented Data & 0.65 & 0.75 & 0.59 & 0.53 & 0.54 & 0.93 & 0.85 & 0.69\\ 
		\hline
		InceptionResNetV2 with Augmented Data & 0.37 & 0.60 & 0.55 & 0.24 & 0.59 & 0.9 & 0.67 & 0.56\\
		\hline
		Resnet50 with Augmented Data & 0.33 & 0.56 & 0.38 & 0.53 & 0.40 & 0.92 & 0.81 & 0.56\\
		\hline 	
		VGG16 with Augmented Data & 0.31 & 0.66 & 0.37 & 0.24 & 0.40 & 0.94 & 0.71 & 0.51\\ 
		\hline		
		DenseNet201 with Metadata and WeightLoss & \textbf{\hl{0.85} %MDPI: Please confirm if the bold should be retained.
} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
		\hline
		InceptionResNetV2 with Metadata and WeightLoss & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
		\hline
		Resnet50 with Metadata and WeightLoss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
		\hline
		Resnet152 with Metadata and WeightLoss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
		\hline
		NasNetLarge with Metadata and WeightLoss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
		\hline
		MobileNetV2 with Metadata and WeightLoss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
		\hline
		MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
		\hline
		MobileNetV3Small with Metadata and WeightLoss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
		\hline
		NasNetMobile with Metadata and WeightLoss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
		\noalign{\hrule height 1pt}
	\end{tabular}
\end{adjustwidth}
\end{table}

\subsection[\appendixname~\thesection]{Detailed Mobile Model Perform}

\vspace{-6pt}

\begin{table}[H]\renewcommand{\arraystretch}{1.2}\setlength{\tabcolsep}{4.2mm}
	\caption{\hl{Deeper%MDPI: Please confirm if the vertical line is necessary, if not, please remove it.
	} analyzing of mobile model. This table illustrates the other indicators of the four mobile-based models including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The~indicators are Accuracy, Balanced Accuracy, Precision, F1-score, Sensitivity, Specificity, and~ROC--AUC score. All of them are average~indicators.}
	\label{appendix-table:mobile-performance}
	\begin{tabular}{|l | c | c | c | c|} 
		\noalign{\hrule height 1pt}
		\textbf{Model} & \textbf{\cite{04381}} & \textbf{\cite{02244} Small }&\textbf{ \cite{02244} Large} & \textbf{\cite{07012} Mobile}\\
		\hline
		Accuracy (avg) & 0.81 & 0.78 & 0.86 & \textbf{\hl{0.86} %MDPI: Please confirm if the bold should be retained.
}\\
		\hline
		Balanced Accuracy (avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
		\hline
		Precision (avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
		\hline
		F1-score (avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
		\hline
		Sensitivity (avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
		\hline
		Specificity (avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
		\hline
		ROC-AUC-score (avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
		\noalign{\hrule height 1pt}
	\end{tabular}
\end{table}

%\printendnotes[custom] % Un-comment to print a list of endnotes

\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g., according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}

\bibitem[Author1(year)]{08332}
\hl{Li, K.M.; Li, E.C.} %MDPI: We have completed all the missing information according to scholar, please check all references
 Skin Lesion Analysis Towards Melanoma Detection via End-to-end Deep Learning of Convolutional Neural Networks. 
{\em arXiv } 
{\bf{2018}}, arXiv:1807.08332.

\bibitem[Author2(year)]{03225}
Xing, X.; Hou, Y.; Li, H.; Yuan, Y.; Li, H.; Meng, M.Q.H.
  Categorical Relation-Preserving Contrastive Knowledge Distillation for Medical Image Classification. 
In  \emph{International Conference on Medical Image Computing and Computer-Assisted Intervention}; Springer: Cham, Switzerland, 
{2021}.

\bibitem[Author2(year)]{03798}
Garg, R.; Maheshwari, S.; Shukla, A. Decision Support System for Detection and Classification of Skin Cancer using CNN. In \emph{Innovations in Computational Intelligence and Computer Vision}; Springer: Singapore.{2019}.

\bibitem[Author2(year)]{09365}
Li, X.; Lu, Y.; Desrosiers, C.; Liu, X. Out-of-Distribution Detection for Skin Lesion Images with Deep Isolation Forest. In \emph{International Workshop on Machine Learning in Medical Imaging}; Springer: Cham, Switzerland, 
{2020}.

\bibitem[Author2(year)]{10348}
Rezvantalab, A.; Safigholi, H.; Karimijeshni, S. Dermatologist Level Dermoscopy Skin Cancer Classification Using Different Deep Learning Convolutional Neural Networks Algorithms. 
{\em arXiv } 
{\bf 2021}, arXiv:1810.10348.

\bibitem[Author2(year)]{06612}
Young, K.; Booth, G.; Simpson, B.; Dutton, R.; Shrapnel, S.  Dermatologist Level Dermoscopy Deep neural network or dermatologist? {\em Nature} 
{\bf \hl{2021}%MDPI: Please add the volume and pagination, or doi number.
}.

\bibitem[Author2(year)]{10417}
Tsch, l P.; Rosendahl, C.; Kittler, H. The HAM10000 data set, a large collection of multi-source dermatoscopic images of common pigmented skin lesions. 
{\em Sci. Data} 
{\bf 2018}, \emph{5}, 1--9.

\bibitem[Author2(year)]{05045}
Alberti, M.; Botros, A.; Schutz, N.; Ingold, R.; Liwicki, M.; Seuret, M. Trainable Spectrally Initializable Matrix Transformations in Convolutional Neural Networks. In Proceedings of the 2020 25th International Conference on Pattern Recognition (ICPR), Milan, Italy, 10--15 January 2021 .

\bibitem[Author2(year)]{09418}
Nadipineni, H. Method to Classify Skin Lesions using Dermoscopic images. {\em arXiv} 
{\bf 2020}, arXiv:2008.09418.

\bibitem[Author2(year)]{03910}
Gessert, N.; Nielsen, M.; Shaikh, M.; Werner, R.; Schlaefer, A. Skin Lesion Classification Using Ensembles of Multi-Resolution EfficientNets with Meta Data. 
{\em MethodsX} 
{\bf 2020}, \emph{7}, 100864.

\bibitem[Author2(year)]{11797}
Poduval, P.; Loya, H.; Sethi, A. Functional Space Variational Inference for Uncertainty Estimation in Computer Aided Diagnosis. 
{\em arXiv} 
{\bf 2020}, arXiv:2005.11797.

\bibitem[Author2(year)]{01284}

Yao, P.; Shen, S.; Xu, M.; Liu, P.; Zhang, F.;  Xing, J., Shao, P.; Kaffenberger, B.; Xu, R.X. 
Single Model Deep Learning on Imbalanced Small Datasets for Skin Lesion Classification. 
{\em IEEE Trans. Med. Imaging} 
{\bf 2022}, \emph{41}, 1242--1254.

\bibitem[Author2(year)]{11872}
Goyal, M.; Knackstedt, T.; Yan, S.; Hassanpour, S.  Artificial Intelligence-Based Image Classification for Diagnosis of Skin Cancer: Challenges and Opportunities. 
{\em Comput. Biol. Med.} 
{\bf 2020}, \emph{127}, 104065.

\bibitem[Author2(year)]{03358}
Datta, S.K.; Shaikh, M.A.; Srihari, S.N.; Gao, M. Soft-Attention Improves Skin Cancer Classification Performance. In \emph{Interpretability of Machine Intelligence in Medical Image Computing, and Topological Data Analysis and Its Applications for Medical Data}; Springer: Cham, Switzerland, 
{2021}.

\bibitem[Author2(year)]{12602}
Mahbod, A.; Tsch, l P.; Langs, G.; Ecker, R.; Ellinger, I.  The Effects of Skin Lesion Segmentation on the Performance of Dermatoscopic Image Classification.
{\em Comput. Methods Programs Biomed.} 
{\bf 2020}, \emph{197}, 105725.

\bibitem[Author2(year)]{03426}
Lee, Y.C.; Jung, S.H.; Won, H.H. WonDerM: Skin Lesion Classification with Fine-tuned Neural Networks.
{\em arXiv} 
{\bf 2019}, arXiv:1808.03426.

\bibitem[Author2(year)]{06993}
{Gao, H.; Zhuang, L.; Kilian, Q.  \emph{Weinberger: Densely Connected Convolutional Network};} 
{\hl{IEEE Computer Society: Washington, DC, USA,}} 
{2018}.

\bibitem[Author2(year)]{11946}
Tan, M.; Le Q. EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks.
In Proceedings of the 36th {International Conference on Machine Learning}\hl{, Long Beach, CA, USA, 9--15 June 2019.}

\bibitem[Author2(year)]{00567}
Szegedy, C.; Vanhoucke, V.; Ioffe, S.; Shlens, J.; Wojna, Z.  Rethinking the Inception Architecture for Computer Vision.
In Proceedings of the IEEE Conference on Computer Vision and Pattern {Recognition (CVPR),} Boston, MA, USA, 7--12 June 
{2015}.

\bibitem[Author2(year)]{04861}
Howard, A.G.; Zhu, M.; Chen, B.; Kalenichenko, D.; Wang, W.;  Weyand, T.;  Andreetto, M.; Adam, H. MobileNets: Efficient Convolutional Neural Networks for Mobile Vision Applications.
{\em arXiv} 
{\bf 2017}, arXiv:1704.04861.

\bibitem[Author2(year)]{04381}
Sandler, M.; Howard, A.; Zhu, M.; Zhmoginov, A.;Chen, L.C. MobileNetV2: Inverted Residuals and Linear Bottlenecks.
In Proceedings of the IEEE Conference on Computer Vision and {Pattern Recognition,} Salt Lake City, UT, USA, 18--22 June 
{2018}.

\bibitem[Author2(year)]{02244}
Howard, A.; Sandler, M.; Chu, G.; Chen, Li.; Chen, B.; Tan, M.; Wang, W.; Zhu, Y.; Pang, R.; Vasudevan, V.; Le, Q.V.; Adam, H. Searching for MobileNetV3.
In Proceedings of the IEEE/CVF International Conference on \hl{Computer Vision, Seoul, Korea, 27--28 October } %MDPI: Please add the location and date of the conference
{2019}.

\bibitem[Author2(year)]{03385}
He, K.; Zhang, X.; Ren, S.; Sun, J. Deep Residual Learning for Image Recognition.
In Proceedings of the IEEE Conference on Computer Vision and {Pattern Recognition, } Boston, MA, USA, 7--12 June 
{2015}.

\bibitem[Author2(year)]{05027}
He, K.; Zhang, X.; Ren, S.; Sun, J. Identity Mappings in Deep Residual Networks.
In \emph{European Conference on Computer Vision}; Springer: Cham, Switzerland,
{2016}.

\bibitem[Author2(year)]{1556}
Simonyan, K.; Zisserman, A. Very Deep Convolutional Networks for Large-Scale Image Recognition.
{\em arXiv} 
{\bf 2016}, arXiv:1409.1556.

\bibitem[Author2(year)]{02357}
\highlighting{Chollet, F. Xception:} %MDPI: This label 02357 of the reference is duplicated with ref31, and these two refs have not been cited in main text, please revise.
 \hl{Deep Learning with Depthwise Separable Convolutions.}
\hl{In Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition,  Honolulu, HI, USA, 21--26 July 2017.}

\bibitem[Author2(year)]{6980}
Kingma, D.P.; Ba, J. Adam: A Method for Stochastic Optimization.
{\em arXiv} 
{\bf 2017}, arXiv:1412.6980.

\bibitem[Author2(year)]{03044}
Xu, K., Ba, J., Kiros, R., Cho, K., Courville, A., Salakhudinov, R.; Zemel, R.; Bengio, Y. Show, Attend and Tell: Neural Image Caption Generation with Visual Attention. In Proceedings of the 32nd  {International Conference on Frontiers in Handwriting Recognition, \hl{Lille, France, 7--9 July 2015}}.

\bibitem[Author2(year)]{202017}
\hl{Shaikh, M.A.;} %MDPI: Please confirm is Refs. 29 and 31 are duplicated.If so, please remove ref. 31 and rearrange all the references to appear in numerical order. Please ensure that there are no duplicated references.
 \hl{Duan, T.; Chauhan, M.; Srihari, S.N. Attention based writer independent verification In Proceedings of the 2020 17th International Conference on Frontiers in Handwriting Recognition,  Dortmund, Germany, 8--10 September
2020.}

\bibitem[Author2(year)]{08513}
Tomita, N.; Abdollahi, B.; Wei, J.; Ren, B.; Suriawinata, A.; Hassanpour, S. Attention-Based Deep Neural Networks for Detection of Cancerous and Precancerous Esophagus Tissue on Histopathological Slides.
{\em JAMA Netw.} 
{\bf 2020}, \emph{2}, e1914645.

\bibitem[Author2(year)]{02357}
\hl{Shaikh, M.A.;} %MDPI: %MDPI: Please confirm is Refs. 31 and 29 are duplicated. If so, please remove ref. 31 and rearrange all the references to appear in numerical order. Please ensure that there are no duplicated references.
 \hl{Duan, T.; Chauhan, M.; Srihari, S.N. In Proceedings of the 2020 17th International Conference on Frontiers in Handwriting Recognition,
2019.}

\bibitem[Author2(year)]{8943952}
Ho, Y.; Wookey, S. The Real-World-Weight Cross-Entropy Loss Function: Modeling the Costs of Mislabeling.
\emph{IEEE Access }
{\bf 2020}, \emph{8}, 4806--4813.

\bibitem[Author2(year)]{07012}
Zoph, B.; Vasudevan, V.; Shlens, J.; Le, Q.V. Learning Transferable Architectures for Scalable Image Recognition. 
In Proceedings of the IEEE Conference on Computer Vision and{Pattern Recognition, }  Honolulu, HI, USA, 21--26 July 
{2017}.

\bibitem[Author2(year)]{08375}
Fred, A. Agarap Deep Learning using Rectified Linear Units (ReLU).
{\em arXiv} 
{\bf 2019}, arXiv:1803.08375.

\bibitem[Author2(year)]{01507}
Hu, J.; Shen, L.; Albanie, S.; Sun, G.; Wu, E. Squeeze-and-Excitation Networks.
In Proceedings of the IEEE Conference on Computer Vision and {Pattern Recognition,} Salt Lake City, UT, USA, 18--22 June 2018.

\bibitem[Author2(year)]{04552v2}
DeVries, T.; Taylor, G.W. Improved Regularization of Convolutional Neural Networks with Cutout. 
{\em arXiv} 
{\bf 2017}, arXiv:1708.04552.

\bibitem[Author2(year)]{07261}
Szegedy, C.; Ioffe, S.; Vanhoucke, V.; Alemi, A. Inception-v4, Inception-ResNet and the Impact of Residual Connections on Learning.
{In Proceedings of the AAAI Conference}, New Orleans, LO, USA,
2--7 February {2018}.

\end{thebibliography}

\end{adjustwidth}
% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\end{adjustwidth}

\end{document}

### 2022-09-29 MDPI/sensors-1915564-redo - For Proof/Definitions/journalnames.tex
Update Paper Proof Reading

%%Updated on 20 April 2022
%,% Website Name,%,%,% Website Name,%%,% Full Name,%%,% Short Name,%%,% DOI abbr,%%,% ISSN,% \continuouspages
%\DeclareOption{}{\gdef\@journal{}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{acoustics}{\gdef\@journal{acoustics}\gdef\@journalfull{Acoustics}\gdef\@journalshort{Acoustics}\gdef\@doiabbr{acoustics}\gdef\@ISSN{2624-599X}\gdef\@continuouspages{yes}}
\DeclareOption{actuators}{\gdef\@journal{actuators}\gdef\@journalfull{Actuators}\gdef\@journalshort{Actuators}\gdef\@doiabbr{act}\gdef\@ISSN{2076-0825}}
\DeclareOption{addictions}{\gdef\@journal{addictions}\gdef\@journalfull{Addictions}\gdef\@journalshort{Addictions}\gdef\@doiabbr{}\gdef\@ISSN{0006-0006}}
\DeclareOption{admsci}{\gdef\@journal{admsci}\gdef\@journalfull{Administrative Sciences}\gdef\@journalshort{Adm. Sci.}\gdef\@doiabbr{admsci}\gdef\@ISSN{2076-3387}}
\DeclareOption{adolescents}{\gdef\@journal{adolescents}\gdef\@journalfull{Adolescents}\gdef\@journalshort{Adolescents}\gdef\@doiabbr{adolescents}\gdef\@ISSN{2673-7051}\gdef\@continuouspages{yes}}
\DeclareOption{aerospace}{\gdef\@journal{aerospace}\gdef\@journalfull{Aerospace}\gdef\@journalshort{Aerospace}\gdef\@doiabbr{aerospace}\gdef\@ISSN{2226-4310}}
\DeclareOption{agriculture}{\gdef\@journal{agriculture}\gdef\@journalfull{Agriculture}\gdef\@journalshort{Agriculture}\gdef\@doiabbr{agriculture}\gdef\@ISSN{2077-0472}}
\DeclareOption{agriengineering}{\gdef\@journal{agriengineering}\gdef\@journalfull{AgriEngineering}\gdef\@journalshort{AgriEngineering}\gdef\@doiabbr{agriengineering}\gdef\@ISSN{2624-7402}\gdef\@continuouspages{yes}}
\DeclareOption{agrochemicals}{\gdef\@journal{agrochemicals}\gdef\@journalfull{Agrochemicals}\gdef\@journalshort{Agrochemicals}\gdef\@doiabbr{agrochemicals}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{agronomy}{\gdef\@journal{agronomy}\gdef\@journalfull{Agronomy}\gdef\@journalshort{Agronomy}\gdef\@doiabbr{agronomy}\gdef\@ISSN{2073-4395}}
\DeclareOption{ai}{\gdef\@journal{ai}\gdef\@journalfull{AI}\gdef\@journalshort{AI}\gdef\@doiabbr{ai}\gdef\@ISSN{2673-2688}\gdef\@continuouspages{yes}}
\DeclareOption{air}{\gdef\@journal{air}\gdef\@journalfull{Air}\gdef\@journalshort{Air}\gdef\@doiabbr{air}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{algorithms}{\gdef\@journal{algorithms}\gdef\@journalfull{Algorithms}\gdef\@journalshort{Algorithms}\gdef\@doiabbr{a}\gdef\@ISSN{1999-4893}}
\DeclareOption{allergies}{\gdef\@journal{allergies}\gdef\@journalfull{Allergies}\gdef\@journalshort{Allergies}\gdef\@doiabbr{allergies}\gdef\@ISSN{2313-5786}}
\DeclareOption{alloys}{\gdef\@journal{alloys}\gdef\@journalfull{Alloys}\gdef\@journalshort{Alloys}\gdef\@doiabbr{alloys}\gdef\@ISSN{2674-063X}\gdef\@continuouspages{yes}}
\DeclareOption{analytica}{\gdef\@journal{analytica}\gdef\@journalfull{Analytica}\gdef\@journalshort{Analytica}\gdef\@doiabbr{analytica}\gdef\@ISSN{2673-4532}\gdef\@continuouspages{yes}}
\DeclareOption{analytics}{\gdef\@journal{analytics}\gdef\@journalfull{Analytics}\gdef\@journalshort{Analytics}\gdef\@doiabbr{analytics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{anatomia}{\gdef\@journal{anatomia}\gdef\@journalfull{Anatomia}\gdef\@journalshort{Anatomia}\gdef\@doiabbr{anatomia}\gdef\@ISSN{2813-0545}\gdef\@continuouspages{yes}}
\DeclareOption{animals}{\gdef\@journal{animals}\gdef\@journalfull{Animals}\gdef\@journalshort{Animals}\gdef\@doiabbr{ani}\gdef\@ISSN{2076-2615}}
\DeclareOption{antibiotics}{\gdef\@journal{antibiotics}\gdef\@journalfull{Antibiotics}\gdef\@journalshort{Antibiotics}\gdef\@doiabbr{antibiotics}\gdef\@ISSN{2079-6382}}
\DeclareOption{antibodies}{\gdef\@journal{antibodies}\gdef\@journalfull{Antibodies}\gdef\@journalshort{Antibodies}\gdef\@doiabbr{antib}\gdef\@ISSN{2073-4468}}
\DeclareOption{antioxidants}{\gdef\@journal{antioxidants}\gdef\@journalfull{Antioxidants}\gdef\@journalshort{Antioxidants}\gdef\@doiabbr{antiox}\gdef\@ISSN{2076-3921}}
\DeclareOption{applbiosci}{\gdef\@journal{applbiosci}\gdef\@journalfull{Applied Biosciences}\gdef\@journalshort{Appl. Biosci.}\gdef\@doiabbr{applbiosci}\gdef\@ISSN{2813-0464}\gdef\@continuouspages{yes}}
\DeclareOption{appliedchem}{\gdef\@journal{appliedchem}\gdef\@journalfull{AppliedChem}\gdef\@journalshort{AppliedChem}\gdef\@doiabbr{appliedchem}\gdef\@ISSN{2673-9623}\gdef\@continuouspages{yes}}
\DeclareOption{appliedmath}{\gdef\@journal{appliedmath}\gdef\@journalfull{AppliedMath}\gdef\@journalshort{AppliedMath}\gdef\@doiabbr{appliedmath}\gdef\@ISSN{2673-9909}\gdef\@continuouspages{yes}}
\DeclareOption{applmech}{\gdef\@journal{applmech}\gdef\@journalfull{Applied Mechanics}\gdef\@journalshort{Appl. Mech.}\gdef\@doiabbr{applmech}\gdef\@ISSN{2673-3161}\gdef\@continuouspages{yes}}
\DeclareOption{applmicrobiol}{\gdef\@journal{applmicrobiol}\gdef\@journalfull{Applied Microbiology}\gdef\@journalshort{Appl. Microbiol.}\gdef\@doiabbr{applmicrobiol}\gdef\@ISSN{2673-8007}\gdef\@continuouspages{yes}}
\DeclareOption{applnano}{\gdef\@journal{applnano}\gdef\@journalfull{Applied Nano}\gdef\@journalshort{Appl. Nano}\gdef\@doiabbr{applnano}\gdef\@ISSN{2673-3501}\gdef\@continuouspages{yes}}
\DeclareOption{applsci}{\gdef\@journal{applsci}\gdef\@journalfull{Applied Sciences}\gdef\@journalshort{Appl. Sci.}\gdef\@doiabbr{app}\gdef\@ISSN{2076-3417}}
\DeclareOption{aquacj}{\gdef\@journal{aquacj}\gdef\@journalfull{Aquaculture Journal}\gdef\@journalshort{Aquac. J.}\gdef\@doiabbr{aj}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{architecture}{\gdef\@journal{architecture}\gdef\@journalfull{Architecture}\gdef\@journalshort{Architecture}\gdef\@doiabbr{architecture}\gdef\@ISSN{2673-8945}\gdef\@continuouspages{yes}}
\DeclareOption{arts}{\gdef\@journal{arts}\gdef\@journalfull{Arts}\gdef\@journalshort{Arts}\gdef\@doiabbr{arts}\gdef\@ISSN{2076-0752}}
\DeclareOption{asc}{\gdef\@journal{asc}\gdef\@journalfull{Automatic Systems and Control}\gdef\@journalshort{Autom. Syst. Control}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{asi}{\gdef\@journal{asi}\gdef\@journalfull{Applied System Innovation}\gdef\@journalshort{Appl. Syst. Innov.}\gdef\@doiabbr{asi}\gdef\@ISSN{2571-5577}}
\DeclareOption{astronomy}{\gdef\@journal{astronomy}\gdef\@journalfull{Astronomy}\gdef\@journalshort{Astronomy}\gdef\@doiabbr{astronomy}\gdef\@ISSN{2674-0346}\gdef\@continuouspages{yes}}
\DeclareOption{atmosphere}{\gdef\@journal{atmosphere}\gdef\@journalfull{Atmosphere}\gdef\@journalshort{Atmosphere}\gdef\@doiabbr{atmos}\gdef\@ISSN{2073-4433}}
\DeclareOption{atoms}{\gdef\@journal{atoms}\gdef\@journalfull{Atoms}\gdef\@journalshort{Atoms}\gdef\@doiabbr{atoms}\gdef\@ISSN{2218-2004}}
\DeclareOption{audiolres}{\gdef\@journal{audiolres}\gdef\@journalfull{Audiology Research}\gdef\@journalshort{Audiol. Res.}\gdef\@doiabbr{audiolres}\gdef\@ISSN{2039-4349}\gdef\@continuouspages{yes}}
\DeclareOption{automation}{\gdef\@journal{automation}\gdef\@journalfull{Automation}\gdef\@journalshort{Automation}\gdef\@doiabbr{automation}\gdef\@ISSN{2673-4052}\gdef\@continuouspages{yes}}
\DeclareOption{axioms}{\gdef\@journal{axioms}\gdef\@journalfull{Axioms}\gdef\@journalshort{Axioms}\gdef\@doiabbr{axioms}\gdef\@ISSN{2075-1680}}
\DeclareOption{bacteria}{\gdef\@journal{bacteria}\gdef\@journalfull{Bacteria}\gdef\@journalshort{Bacteria}\gdef\@doiabbr{bacteria}\gdef\@ISSN{2674-1334}\gdef\@continuouspages{yes}}
\DeclareOption{batteries}{\gdef\@journal{batteries}\gdef\@journalfull{Batteries}\gdef\@journalshort{Batteries}\gdef\@doiabbr{batteries}\gdef\@ISSN{2313-0105}}
\DeclareOption{bdcc}{\gdef\@journal{bdcc}\gdef\@journalfull{Big Data and Cognitive Computing}\gdef\@journalshort{Big Data Cogn. Comput.}\gdef\@doiabbr{bdcc}\gdef\@ISSN{2504-2289}}
\DeclareOption{behavsci}{\gdef\@journal{behavsci}\gdef\@journalfull{Behavioral Sciences}\gdef\@journalshort{Behav. Sci.}\gdef\@doiabbr{bs}\gdef\@ISSN{2076-328X}}
\DeclareOption{beverages}{\gdef\@journal{beverages}\gdef\@journalfull{Beverages}\gdef\@journalshort{Beverages}\gdef\@doiabbr{beverages}\gdef\@ISSN{2306-5710}}
\DeclareOption{biochem}{\gdef\@journal{biochem}\gdef\@journalfull{BioChem}\gdef\@journalshort{BioChem}\gdef\@doiabbr{biochem}\gdef\@ISSN{2673-6411}\gdef\@continuouspages{yes}}
\DeclareOption{bioengineering}{\gdef\@journal{bioengineering}\gdef\@journalfull{Bioengineering}\gdef\@journalshort{Bioengineering}\gdef\@doiabbr{bioengineering}\gdef\@ISSN{2306-5354}}
\DeclareOption{biologics}{\gdef\@journal{biologics}\gdef\@journalfull{Biologics}\gdef\@journalshort{Biologics}\gdef\@doiabbr{biologics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biology}{\gdef\@journal{biology}\gdef\@journalfull{Biology}\gdef\@journalshort{Biology}\gdef\@doiabbr{biology}\gdef\@ISSN{2079-7737}}
\DeclareOption{biomass}{\gdef\@journal{biomass}\gdef\@journalfull{Biomass}\gdef\@journalshort{Biomass}\gdef\@doiabbr{biomass}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomechanics}{\gdef\@journal{biomechanics}\gdef\@journalfull{Biomechanics}\gdef\@journalshort{Biomechanics}\gdef\@doiabbr{biomechanics}\gdef\@ISSN{2673-7078}\gdef\@continuouspages{yes}}
\DeclareOption{biomed}{\gdef\@journal{biomed}\gdef\@journalfull{BioMed}\gdef\@journalshort{BioMed}\gdef\@doiabbr{biomed}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomedicines}{\gdef\@journal{biomedicines}\gdef\@journalfull{Biomedicines}\gdef\@journalshort{Biomedicines}\gdef\@doiabbr{biomedicines}\gdef\@ISSN{2227-9059}}
\DeclareOption{biomedinformatics}{\gdef\@journal{biomedinformatics}\gdef\@journalfull{Biomedinformatics}\gdef\@journalshort{Biomedinformatics}\gdef\@doiabbr{biomedinformatics}\gdef\@ISSN{2673-7426}\gdef\@continuouspages{yes}}
\DeclareOption{biomimetics}{\gdef\@journal{biomimetics}\gdef\@journalfull{Biomimetics}\gdef\@journalshort{Biomimetics}\gdef\@doiabbr{biomimetics}\gdef\@ISSN{2313-7673}}
\DeclareOption{biomolecules}{\gdef\@journal{biomolecules}\gdef\@journalfull{Biomolecules}\gdef\@journalshort{Biomolecules}\gdef\@doiabbr{biom}\gdef\@ISSN{2218-273X}}
\DeclareOption{biophysica}{\gdef\@journal{biophysica}\gdef\@journalfull{Biophysica}\gdef\@journalshort{Biophysica}\gdef\@doiabbr{biophysica}\gdef\@ISSN{2673-4125}\gdef\@continuouspages{yes}}
\DeclareOption{biosensors}{\gdef\@journal{biosensors}\gdef\@journalfull{Biosensors}\gdef\@journalshort{Biosensors}\gdef\@doiabbr{bios}\gdef\@ISSN{2079-6374}}
\DeclareOption{biotech}{\gdef\@journal{biotech}\gdef\@journalfull{BioTech}\gdef\@journalshort{BioTech}\gdef\@doiabbr{biotech}\gdef\@ISSN{2673-6284}}
\DeclareOption{birds}{\gdef\@journal{birds}\gdef\@journalfull{Birds}\gdef\@journalshort{Birds}\gdef\@doiabbr{birds}\gdef\@ISSN{2673-6004}\gdef\@continuouspages{yes}}
\DeclareOption{bloods}{\gdef\@journal{bloods}\gdef\@journalfull{Bloods}\gdef\@journalshort{Bloods}\gdef\@doiabbr{bloods}\gdef\@ISSN{2673-415X}}
\DeclareOption{blsf}{\gdef\@journal{blsf}\gdef\@journalfull{Biology and Life Sciences Forum}\gdef\@journalshort{Biol. Life Sci. Forum}\gdef\@doiabbr{blsf	}\gdef\@ISSN{2673-9976}}
\DeclareOption{brainsci}{\gdef\@journal{brainsci}\gdef\@journalfull{Brain Sciences}\gdef\@journalshort{Brain Sci.}\gdef\@doiabbr{brainsci}\gdef\@ISSN{2076-3425}}
\DeclareOption{breath}{\gdef\@journal{breath}\gdef\@journalfull{Breath}\gdef\@journalshort{Breath}\gdef\@doiabbr{breath}\gdef\@ISSN{}}
\DeclareOption{buildings}{\gdef\@journal{buildings}\gdef\@journalfull{Buildings}\gdef\@journalshort{Buildings}\gdef\@doiabbr{buildings}\gdef\@ISSN{2075-5309}}
\DeclareOption{businesses}{\gdef\@journal{businesses}\gdef\@journalfull{Businesses}\gdef\@journalshort{Businesses}\gdef\@doiabbr{businesses}\gdef\@ISSN{2673-7116}\gdef\@continuouspages{yes}}
\DeclareOption{cancers}{\gdef\@journal{cancers}\gdef\@journalfull{Cancers}\gdef\@journalshort{Cancers}\gdef\@doiabbr{cancers}\gdef\@ISSN{2072-6694}}
\DeclareOption{carbon}{\gdef\@journal{carbon}\gdef\@journalfull{C}\gdef\@journalshort{C}\gdef\@doiabbr{c}\gdef\@ISSN{2311-5629}}
\DeclareOption{cardiogenetics}{\gdef\@journal{cardiogenetics}\gdef\@journalfull{Cardiogenetics}\gdef\@journalshort{Cardiogenetics}\gdef\@doiabbr{cardiogenetics}\gdef\@ISSN{2035-8148}\gdef\@continuouspages{yes}}
\DeclareOption{catalysts}{\gdef\@journal{catalysts}\gdef\@journalfull{Catalysts}\gdef\@journalshort{Catalysts}\gdef\@doiabbr{catal}\gdef\@ISSN{2073-4344}}
\DeclareOption{cells}{\gdef\@journal{cells}\gdef\@journalfull{Cells}\gdef\@journalshort{Cells}\gdef\@doiabbr{cells}\gdef\@ISSN{2073-4409}}
\DeclareOption{ceramics}{\gdef\@journal{ceramics}\gdef\@journalfull{Ceramics}\gdef\@journalshort{Ceramics}\gdef\@doiabbr{ceramics}\gdef\@ISSN{2571-6131}\gdef\@continuouspages{yes}}
\DeclareOption{challenges}{\gdef\@journal{challenges}\gdef\@journalfull{Challenges}\gdef\@journalshort{Challenges}\gdef\@doiabbr{challe}\gdef\@ISSN{2078-1547}}
\DeclareOption{chemengineering}{\gdef\@journal{chemengineering}\gdef\@journalfull{ChemEngineering}\gdef\@journalshort{ChemEngineering}\gdef\@doiabbr{chemengineering}\gdef\@ISSN{2305-7084}}
\DeclareOption{chemistry}{\gdef\@journal{chemistry}\gdef\@journalfull{Chemistry}\gdef\@journalshort{Chemistry}\gdef\@doiabbr{chemistry}\gdef\@ISSN{2624-8549}\gdef\@continuouspages{yes}}
\DeclareOption{chemosensors}{\gdef\@journal{chemosensors}\gdef\@journalfull{Chemosensors}\gdef\@journalshort{Chemosensors}\gdef\@doiabbr{chemosensors}\gdef\@ISSN{2227-9040}}
\DeclareOption{chemproc}{\gdef\@journal{chemproc}\gdef\@journalfull{Chemistry Proceedings}\gdef\@journalshort{Chem. Proc.}\gdef\@doiabbr{chemproc}\gdef\@ISSN{2673-4583}}
\DeclareOption{children}{\gdef\@journal{children}\gdef\@journalfull{Children}\gdef\@journalshort{Children}\gdef\@doiabbr{children}\gdef\@ISSN{2227-9067}}
\DeclareOption{chips}{\gdef\@journal{chips}\gdef\@journalfull{Chips}\gdef\@journalshort{Chips}\gdef\@doiabbr{chips}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{cimb}{\gdef\@journal{cimb}\gdef\@journalfull{Current Issues in Molecular Biology}\gdef\@journalshort{Curr. Issues Mol. Biol.}\gdef\@doiabbr{cimb}\gdef\@ISSN{1467-3045}\gdef\@continuouspages{yes}}
\DeclareOption{civileng}{\gdef\@journal{civileng}\gdef\@journalfull{CivilEng}\gdef\@journalshort{CivilEng}\gdef\@doiabbr{civileng}\gdef\@ISSN{2673-4109}\gdef\@continuouspages{yes}}
\DeclareOption{cleantechnol}{\gdef\@journal{cleantechnol}\gdef\@journalfull{Clean Technologies}\gdef\@journalshort{Clean Technol.}\gdef\@doiabbr{cleantechnol}\gdef\@ISSN{2571-8797}\gdef\@continuouspages{yes}}
\DeclareOption{climate}{\gdef\@journal{climate}\gdef\@journalfull{Climate}\gdef\@journalshort{Climate}\gdef\@doiabbr{cli}\gdef\@ISSN{2225-1154}}
\DeclareOption{clinpract}{\gdef\@journal{clinpract}\gdef\@journalfull{Clinics and Practice}\gdef\@journalshort{Clin. Pract.}\gdef\@doiabbr{clinpract}\gdef\@ISSN{2039-7283}\gdef\@continuouspages{yes}}
\DeclareOption{clockssleep}{\gdef\@journal{clockssleep}\gdef\@journalfull{Clocks \& Sleep}\gdef\@journalshort{Clocks\&Sleep}\gdef\@doiabbr{clockssleep}\gdef\@ISSN{2624-5175}\gdef\@continuouspages{yes}}
\DeclareOption{cmd}{\gdef\@journal{cmd}\gdef\@journalfull{Corrosion and Materials Degradation}\gdef\@journalshort{Corros. Mater. Degrad.}\gdef\@doiabbr{cmd}\gdef\@ISSN{2624-5558}\gdef\@continuouspages{yes}}
\DeclareOption{coasts}{\gdef\@journal{coasts}\gdef\@journalfull{Coasts}\gdef\@journalshort{Coasts}\gdef\@doiabbr{coasts}\gdef\@ISSN{2673-964X}\gdef\@continuouspages{yes}}
\DeclareOption{coatings}{\gdef\@journal{coatings}\gdef\@journalfull{Coatings}\gdef\@journalshort{Coatings}\gdef\@doiabbr{coatings}\gdef\@ISSN{2079-6412}}
\DeclareOption{colloids}{\gdef\@journal{colloids}\gdef\@journalfull{Colloids Interfaces}\gdef\@journalshort{Colloids Interfaces}\gdef\@doiabbr{colloids}\gdef\@ISSN{2504-5377}}
\DeclareOption{colorants}{\gdef\@journal{colorants}\gdef\@journalfull{Colorants}\gdef\@journalshort{Colorants}\gdef\@doiabbr{colorants}\gdef\@ISSN{2079-6447}\gdef\@continuouspages{yes}}
\DeclareOption{commodities}{\gdef\@journal{commodities}\gdef\@journalfull{Commodities}\gdef\@journalshort{Commodities}\gdef\@doiabbr{commodities}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{compounds}{\gdef\@journal{compounds}\gdef\@journalfull{Compounds}\gdef\@journalshort{Compounds}\gdef\@doiabbr{compounds}\gdef\@ISSN{2673-6918}\gdef\@continuouspages{yes}}
\DeclareOption{computation}{\gdef\@journal{computation}\gdef\@journalfull{Computation}\gdef\@journalshort{Computation}\gdef\@doiabbr{computation}\gdef\@ISSN{2079-3197}}
\DeclareOption{computers}{\gdef\@journal{computers}\gdef\@journalfull{Computers}\gdef\@journalshort{Computers}\gdef\@doiabbr{computers}\gdef\@ISSN{2073-431X}}
\DeclareOption{condensedmatter}{\gdef\@journal{condensedmatter}\gdef\@journalfull{Condensed Matter}\gdef\@journalshort{Condens. Matter}\gdef\@doiabbr{condmat}\gdef\@ISSN{2410-3896}}
\DeclareOption{conservation}{\gdef\@journal{conservation}\gdef\@journalfull{Conservation}\gdef\@journalshort{Conservation}\gdef\@doiabbr{conservation}\gdef\@ISSN{2673-7159}\gdef\@continuouspages{yes}}
\DeclareOption{constrmater}{\gdef\@journal{constrmater}\gdef\@journalfull{Construction Materials}\gdef\@journalshort{Constr. Mater.}\gdef\@doiabbr{constrmater}\gdef\@ISSN{2673-7108}\gdef\@continuouspages{yes}}
\DeclareOption{cosmetics}{\gdef\@journal{cosmetics}\gdef\@journalfull{Cosmetics}\gdef\@journalshort{Cosmetics}\gdef\@doiabbr{cosmetics}\gdef\@ISSN{2079-9284}}
\DeclareOption{covid}{\gdef\@journal{covid}\gdef\@journalfull{COVID}\gdef\@journalshort{COVID}\gdef\@doiabbr{covid}\gdef\@ISSN{2673-8112}\gdef\@continuouspages{yes}}
\DeclareOption{crops}{\gdef\@journal{crops}\gdef\@journalfull{Crops}\gdef\@journalshort{Crops}\gdef\@doiabbr{crops}\gdef\@ISSN{2673-7655}\gdef\@continuouspages{yes}}
\DeclareOption{cryptography}{\gdef\@journal{cryptography}\gdef\@journalfull{Cryptography}\gdef\@journalshort{Cryptography}\gdef\@doiabbr{cryptography}\gdef\@ISSN{2410-387X}}
\DeclareOption{crystals}{\gdef\@journal{crystals}\gdef\@journalfull{Crystals}\gdef\@journalshort{Crystals}\gdef\@doiabbr{cryst}\gdef\@ISSN{2073-4352}}
\DeclareOption{csmf}{\gdef\@journal{csmf}\gdef\@journalfull{Computer Sciences \& Mathematics Forum}\gdef\@journalshort{Comput. Sci. Math. Forum}\gdef\@doiabbr{csmf}\gdef\@ISSN{2813-0324}}
\DeclareOption{ctn}{\gdef\@journal{ctn}\gdef\@journalfull{Clinical and Translational Neuroscience}\gdef\@journalshort{CTN}\gdef\@doiabbr{Clin. Transl. Neurosci.}\gdef\@ISSN{2514-183X}}
\DeclareOption{curroncol}{\gdef\@journal{curroncol}\gdef\@journalfull{Current Oncology}\gdef\@journalshort{Curr. Oncol.}\gdef\@doiabbr{curroncol}\gdef\@ISSN{1718-7729}\gdef\@continuouspages{yes}}
\DeclareOption{cyber}{\gdef\@journal{cyber}\gdef\@journalfull{Cyber}\gdef\@journalshort{Cyber}\gdef\@doiabbr{cyber}\gdef\@ISSN{2624-800X}}
\DeclareOption{dairy}{\gdef\@journal{dairy}\gdef\@journalfull{Dairy}\gdef\@journalshort{Dairy}\gdef\@doiabbr{dairy}\gdef\@ISSN{2624-862X}\gdef\@continuouspages{yes}}
\DeclareOption{data}{\gdef\@journal{data}\gdef\@journalfull{Data}\gdef\@journalshort{Data}\gdef\@doiabbr{data}\gdef\@ISSN{2306-5729}}
\DeclareOption{dentistry}{\gdef\@journal{dentistry}\gdef\@journalfull{Dentistry Journal}\gdef\@journalshort{Dent. J.}\gdef\@doiabbr{dj}\gdef\@ISSN{2304-6767}}
\DeclareOption{dermato}{\gdef\@journal{dermato}\gdef\@journalfull{Dermato}\gdef\@journalshort{Dermato}\gdef\@doiabbr{dermato}\gdef\@ISSN{2673-6179}\gdef\@continuouspages{yes}}
\DeclareOption{dermatopathology}{\gdef\@journal{dermatopathology}\gdef\@journalfull{Dermatopathology}\gdef\@journalshort{Dermatopathology}\gdef\@doiabbr{dermatopathology}\gdef\@ISSN{2296-3529}\gdef\@continuouspages{yes}}
\DeclareOption{designs}{\gdef\@journal{designs}\gdef\@journalfull{Designs}\gdef\@journalshort{Designs}\gdef\@doiabbr{designs}\gdef\@ISSN{2411-9660}}
\DeclareOption{diabetology}{\gdef\@journal{diabetology}\gdef\@journalfull{Diabetology}\gdef\@journalshort{Diabetology}\gdef\@doiabbr{diabetology}\gdef\@ISSN{2673-4540}\gdef\@continuouspages{yes}}
\DeclareOption{diagnostics}{\gdef\@journal{diagnostics}\gdef\@journalfull{Diagnostics}\gdef\@journalshort{Diagnostics}\gdef\@doiabbr{diagnostics}\gdef\@ISSN{2075-4418}}
\DeclareOption{dietetics}{\gdef\@journal{dietetics}\gdef\@journalfull{Dietetics}\gdef\@journalshort{Dietetics}\gdef\@doiabbr{dietetics}\gdef\@ISSN{2674-0311}\gdef\@continuouspages{yes}}
\DeclareOption{digital}{\gdef\@journal{digital}\gdef\@journalfull{Digital}\gdef\@journalshort{Digital}\gdef\@doiabbr{digital}\gdef\@ISSN{2673-6470}\gdef\@continuouspages{yes}}
\DeclareOption{disabilities}{\gdef\@journal{disabilities}\gdef\@journalfull{Disabilities}\gdef\@journalshort{Disabilities}\gdef\@doiabbr{disabilities}\gdef\@ISSN{2673-7272}\gdef\@continuouspages{yes}}
\DeclareOption{diseases}{\gdef\@journal{diseases}\gdef\@journalfull{Diseases}\gdef\@journalshort{Diseases}\gdef\@doiabbr{diseases}\gdef\@ISSN{2079-9721}}
\DeclareOption{diversity}{\gdef\@journal{diversity}\gdef\@journalfull{Diversity}\gdef\@journalshort{Diversity}\gdef\@doiabbr{d}\gdef\@ISSN{1424-2818}}
\DeclareOption{dna}{\gdef\@journal{dna}\gdef\@journalfull{DNA}\gdef\@journalshort{DNA}\gdef\@doiabbr{dna}\gdef\@ISSN{2673-8856}\gdef\@continuouspages{yes}}
\DeclareOption{drones}{\gdef\@journal{drones}\gdef\@journalfull{Drones}\gdef\@journalshort{Drones}\gdef\@doiabbr{drones}\gdef\@ISSN{2504-446X}}
\DeclareOption{dynamics}{\gdef\@journal{dynamics}\gdef\@journalfull{Dynamics}\gdef\@journalshort{Dynamics}\gdef\@doiabbr{dynamics}\gdef\@ISSN{2673-8716}\gdef\@continuouspages{yes}}
\DeclareOption{earth}{\gdef\@journal{earth}\gdef\@journalfull{Earth}\gdef\@journalshort{Earth}\gdef\@doiabbr{earth}\gdef\@ISSN{2673-4834}\gdef\@continuouspages{yes}}
\DeclareOption{ebj}{\gdef\@journal{ebj}\gdef\@journalfull{European Burn Journal}\gdef\@journalshort{Eur. Burn J.}\gdef\@doiabbr{ebj}\gdef\@ISSN{2673-1991}\gdef\@continuouspages{yes}}
\DeclareOption{ecologies}{\gdef\@journal{ecologies}\gdef\@journalfull{Ecologies}\gdef\@journalshort{Ecologies}\gdef\@doiabbr{ecologies}\gdef\@ISSN{2673-4133}\gdef\@continuouspages{yes}}
\DeclareOption{econometrics}{\gdef\@journal{econometrics}\gdef\@journalfull{Econometrics}\gdef\@journalshort{Econometrics}\gdef\@doiabbr{econometrics}\gdef\@ISSN{2225-1146}}
\DeclareOption{economies}{\gdef\@journal{economies}\gdef\@journalfull{Economies}\gdef\@journalshort{Economies}\gdef\@doiabbr{economies}\gdef\@ISSN{2227-7099}}
\DeclareOption{education}{\gdef\@journal{education}\gdef\@journalfull{Education Sciences}\gdef\@journalshort{Educ. Sci.}\gdef\@doiabbr{educsci}\gdef\@ISSN{2227-7102}}
\DeclareOption{ejihpe}{\gdef\@journal{ejihpe}\gdef\@journalfull{European Journal of Investigation in Health Psychology and Education}\gdef\@journalshort{Eur. J. Investig. Health Psychol. Educ.}\gdef\@doiabbr{ejihpe}\gdef\@ISSN{2254-9625}\gdef\@continuouspages{yes}}
\DeclareOption{electricity}{\gdef\@journal{electricity}\gdef\@journalfull{Electricity}\gdef\@journalshort{Electricity}\gdef\@doiabbr{electricity}\gdef\@ISSN{2673-4826}\gdef\@continuouspages{yes}}
\DeclareOption{electrochem}{\gdef\@journal{electrochem}\gdef\@journalfull{Electrochem}\gdef\@journalshort{Electrochem}\gdef\@doiabbr{electrochem}\gdef\@ISSN{2673-3293}\gdef\@continuouspages{yes}}
\DeclareOption{electronicmat}{\gdef\@journal{electronicmat}\gdef\@journalfull{Electronic Materials}\gdef\@journalshort{Electron. Mater.}\gdef\@doiabbr{electronicmat}\gdef\@ISSN{2673-3978}\gdef\@continuouspages{yes}}
\DeclareOption{electronics}{\gdef\@journal{electronics}\gdef\@journalfull{Electronics}\gdef\@journalshort{Electronics}\gdef\@doiabbr{electronics}\gdef\@ISSN{2079-9292}}
\DeclareOption{encyclopedia}{\gdef\@journal{encyclopedia}\gdef\@journalfull{Encyclopedia}\gdef\@journalshort{Encyclopedia}\gdef\@doiabbr{encyclopedia}\gdef\@ISSN{2673-8392}\gdef\@continuouspages{yes}}
\DeclareOption{endocrines}{\gdef\@journal{endocrines}\gdef\@journalfull{Endocrines}\gdef\@journalshort{Endocrines}\gdef\@doiabbr{endocrines}\gdef\@ISSN{2673-396X}\gdef\@continuouspages{yes}}
\DeclareOption{energies}{\gdef\@journal{energies}\gdef\@journalfull{Energies}\gdef\@journalshort{Energies}\gdef\@doiabbr{en}\gdef\@ISSN{1996-1073}}
\DeclareOption{eng}{\gdef\@journal{eng}\gdef\@journalfull{Eng-Advances in Engineering}\gdef\@journalshort{Eng}\gdef\@doiabbr{eng}\gdef\@ISSN{2673-4117}\gdef\@continuouspages{yes}}
\DeclareOption{engproc}{\gdef\@journal{engproc}\gdef\@journalfull{Engineering Proceedings}\gdef\@journalshort{Eng. Proc.}\gdef\@doiabbr{engproc}\gdef\@ISSN{2673-4591}}
%\DeclareOption{ent}{\gdef\@journal{ent}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{entomology}{\gdef\@journal{entomology}\gdef\@journalfull{Entomology}\gdef\@journalshort{Entomology}\gdef\@doiabbr{entomology}\gdef\@ISSN{2813-0502}\gdef\@continuouspages{yes}}	
\DeclareOption{entropy}{\gdef\@journal{entropy}\gdef\@journalfull{Entropy}\gdef\@journalshort{Entropy}\gdef\@doiabbr{e}\gdef\@ISSN{1099-4300}}
\DeclareOption{environments}{\gdef\@journal{environments}\gdef\@journalfull{Environments}\gdef\@journalshort{Environments}\gdef\@doiabbr{environments}\gdef\@ISSN{2076-3298}}
\DeclareOption{environsciproc}{\gdef\@journal{environsciproc}\gdef\@journalfull{Environmental Sciences Proceedings}\gdef\@journalshort{Environ. Sci. Proc.}\gdef\@doiabbr{environsciproc}\gdef\@ISSN{2673-4931}}
\DeclareOption{epidemiologia}{\gdef\@journal{epidemiologia}\gdef\@journalfull{Epidemiologia}\gdef\@journalshort{Epidemiologia}\gdef\@doiabbr{epidemiologia}\gdef\@ISSN{2673-3986}\gdef\@continuouspages{yes}}
\DeclareOption{epigenomes}{\gdef\@journal{epigenomes}\gdef\@journalfull{Epigenomes}\gdef\@journalshort{Epigenomes}\gdef\@doiabbr{epigenomes}\gdef\@ISSN{2075-4655}}
\DeclareOption{est}{\gdef\@journal{est}\gdef\@journalfull{Electrochemical Science and Technology}\gdef\@journalshort{Electrochem. Sci. Technol.}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{fermentation}{\gdef\@journal{fermentation}\gdef\@journalfull{Fermentation}\gdef\@journalshort{Fermentation}\gdef\@doiabbr{fermentation}\gdef\@ISSN{2311-5637}}
\DeclareOption{fibers}{\gdef\@journal{fibers}\gdef\@journalfull{Fibers}\gdef\@journalshort{Fibers}\gdef\@doiabbr{fib}\gdef\@ISSN{2079-6439}}
\DeclareOption{fintech}{\gdef\@journal{fintech}\gdef\@journalfull{FinTech}\gdef\@journalshort{FinTech}\gdef\@doiabbr{fintech}\gdef\@ISSN{2674-1032}\gdef\@continuouspages{yes}}
\DeclareOption{fire}{\gdef\@journal{fire}\gdef\@journalfull{Fire}\gdef\@journalshort{Fire}\gdef\@doiabbr{fire}\gdef\@ISSN{2571-6255}}
\DeclareOption{fishes}{\gdef\@journal{fishes}\gdef\@journalfull{Fishes}\gdef\@journalshort{Fishes}\gdef\@doiabbr{fishes}\gdef\@ISSN{2410-3888}}
\DeclareOption{fluids}{\gdef\@journal{fluids}\gdef\@journalfull{Fluids}\gdef\@journalshort{Fluids}\gdef\@doiabbr{fluids}\gdef\@ISSN{2311-5521}}
\DeclareOption{foods}{\gdef\@journal{foods}\gdef\@journalfull{Foods}\gdef\@journalshort{Foods}\gdef\@doiabbr{foods}\gdef\@ISSN{2304-8158}}
\DeclareOption{forecasting}{\gdef\@journal{forecasting}\gdef\@journalfull{Forecasting}\gdef\@journalshort{Forecasting}\gdef\@doiabbr{forecast}\gdef\@ISSN{2571-9394}\gdef\@continuouspages{yes}}
\DeclareOption{forensicsci}{\gdef\@journal{forensicsci}\gdef\@journalfull{Forensic Sciences}\gdef\@journalshort{Forensic Sci.}\gdef\@doiabbr{forensicsci}\gdef\@ISSN{2673-6756}\gdef\@continuouspages{yes}}
\DeclareOption{forests}{\gdef\@journal{forests}\gdef\@journalfull{Forests}\gdef\@journalshort{Forests}\gdef\@doiabbr{f}\gdef\@ISSN{1999-4907}}
\DeclareOption{foundations}{\gdef\@journal{foundations}\gdef\@journalfull{Foundations}\gdef\@journalshort{Foundations}\gdef\@doiabbr{foundations}\gdef\@ISSN{2673-9321}\gdef\@continuouspages{yes}}
\DeclareOption{fractalfract}{\gdef\@journal{fractalfract}\gdef\@journalfull{Fractal and Fractional}\gdef\@journalshort{Fractal Fract.}\gdef\@doiabbr{fractalfract}\gdef\@ISSN{2504-3110}}
\DeclareOption{fuels}{\gdef\@journal{fuels}\gdef\@journalfull{Fuels}\gdef\@journalshort{Fuels}\gdef\@doiabbr{fuels}\gdef\@ISSN{2673-3994}\gdef\@continuouspages{yes}}
\DeclareOption{futureinternet}{\gdef\@journal{futureinternet}\gdef\@journalfull{Future Internet}\gdef\@journalshort{Future Internet}\gdef\@doiabbr{fi}\gdef\@ISSN{1999-5903}}
%\DeclareOption{futureparasites}{\gdef\@journal{futureparasites}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{futurepharmacol}{\gdef\@journal{futurepharmacol}\gdef\@journalfull{Future Pharmacology}\gdef\@journalshort{Future Pharm.}\gdef\@doiabbr{futurepharmacol}\gdef\@ISSN{2673-9879}\gdef\@continuouspages{yes}}
\DeclareOption{futurephys}{\gdef\@journal{futurephys}\gdef\@journalfull{Future Physics}\gdef\@journalshort{Future Phys.}\gdef\@doiabbr{futurephys}\gdef\@ISSN{2624-6503}}
\DeclareOption{futuretransp}{\gdef\@journal{futuretransp}\gdef\@journalfull{Future Transportation}\gdef\@journalshort{Future Transp.}\gdef\@doiabbr{futuretransp}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{galaxies}{\gdef\@journal{galaxies}\gdef\@journalfull{Galaxies}\gdef\@journalshort{Galaxies}\gdef\@doiabbr{galaxies}\gdef\@ISSN{2075-4434}}
\DeclareOption{games}{\gdef\@journal{games}\gdef\@journalfull{Games}\gdef\@journalshort{Games}\gdef\@doiabbr{g}\gdef\@ISSN{2073-4336}}
\DeclareOption{gases}{\gdef\@journal{gases}\gdef\@journalfull{Gases}\gdef\@journalshort{Gases}\gdef\@doiabbr{gases}\gdef\@ISSN{2673-5628}\gdef\@continuouspages{yes}}
\DeclareOption{gastroent}{\gdef\@journal{gastroent}\gdef\@journalfull{Gastroenterology Insights}\gdef\@journalshort{Gastroenterol. Insights}\gdef\@doiabbr{gastroent}\gdef\@ISSN{2036-7422}\gdef\@continuouspages{yes}}
\DeclareOption{gastrointestdisord}{\gdef\@journal{gastrointestdisord}\gdef\@journalfull{Gastrointestinal Disorders}\gdef\@journalshort{Gastrointest. Disord.}\gdef\@doiabbr{gidisord}\gdef\@ISSN{2624-5647}\gdef\@continuouspages{yes}}
\DeclareOption{gels}{\gdef\@journal{gels}\gdef\@journalfull{Gels}\gdef\@journalshort{Gels}\gdef\@doiabbr{gels}\gdef\@ISSN{2310-2861}}
\DeclareOption{genealogy}{\gdef\@journal{genealogy}\gdef\@journalfull{Genealogy}\gdef\@journalshort{Genealogy}\gdef\@doiabbr{genealogy}\gdef\@ISSN{2313-5778}}
\DeclareOption{genes}{\gdef\@journal{genes}\gdef\@journalfull{Genes}\gdef\@journalshort{Genes}\gdef\@doiabbr{genes}\gdef\@ISSN{2073-4425}}
\DeclareOption{geographies}{\gdef\@journal{geographies}\gdef\@journalfull{Geographies}\gdef\@journalshort{Geographies}\gdef\@doiabbr{geographies}\gdef\@ISSN{2673-7086}\gdef\@continuouspages{yes}}
\DeclareOption{geohazards}{\gdef\@journal{geohazards}\gdef\@journalfull{GeoHazards}\gdef\@journalshort{GeoHazards}\gdef\@doiabbr{geohazards}\gdef\@ISSN{2624-795X}\gdef\@continuouspages{yes}}
\DeclareOption{geomatics}{\gdef\@journal{geomatics}\gdef\@journalfull{Geomatics}\gdef\@journalshort{Geomatics}\gdef\@doiabbr{geomatics}\gdef\@ISSN{2673-7418}\gdef\@continuouspages{yes}}
\DeclareOption{geosciences}{\gdef\@journal{geosciences}\gdef\@journalfull{Geosciences}\gdef\@journalshort{Geosciences}\gdef\@doiabbr{geosciences}\gdef\@ISSN{2076-3263}}
\DeclareOption{geotechnics}{\gdef\@journal{geotechnics}\gdef\@journalfull{Geotechnics}\gdef\@journalshort{Geotechnics}\gdef\@doiabbr{geotechnics}\gdef\@ISSN{2673-7094}\gdef\@continuouspages{yes}}
\DeclareOption{geriatrics}{\gdef\@journal{geriatrics}\gdef\@journalfull{Geriatrics}\gdef\@journalshort{Geriatrics}\gdef\@doiabbr{geriatrics}\gdef\@ISSN{2308-3417}}
\DeclareOption{grasses}{\gdef\@journal{grasses}\gdef\@journalfull{Grasses}\gdef\@journalshort{Grasses}\gdef\@doiabbr{grasses}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hazardousmatters}{\gdef\@journal{hazardousmatters}\gdef\@journalfull{Hazardous Matters}\gdef\@journalshort{Hazard. Matters}\gdef\@doiabbr{}\gdef\@ISSN{0014-0014}}
\DeclareOption{healthcare}{\gdef\@journal{healthcare}\gdef\@journalfull{Healthcare}\gdef\@journalshort{Healthcare}\gdef\@doiabbr{healthcare}\gdef\@ISSN{2227-9032}}
\DeclareOption{hearts}{\gdef\@journal{hearts}\gdef\@journalfull{Hearts}\gdef\@journalshort{Hearts}\gdef\@doiabbr{hearts}\gdef\@ISSN{2673-3846}\gdef\@continuouspages{yes}}
\DeclareOption{hemato}{\gdef\@journal{hemato}\gdef\@journalfull{Hemato}\gdef\@journalshort{Hemato}\gdef\@doiabbr{hemato}\gdef\@ISSN{2673-6357}\gdef\@continuouspages{yes}}
\DeclareOption{hematolrep}{\gdef\@journal{hematolrep}\gdef\@journalfull{Hematology Reports}\gdef\@journalshort{Hematol. Rep.}\gdef\@doiabbr{hematolrep}\gdef\@ISSN{2038-8330}\gdef\@continuouspages{yes}}
\DeclareOption{heritage}{\gdef\@journal{heritage}\gdef\@journalfull{Heritage}\gdef\@journalshort{Heritage}\gdef\@doiabbr{heritage}\gdef\@ISSN{2571-9408}\gdef\@continuouspages{yes}}
\DeclareOption{highthroughput}{\gdef\@journal{highthroughput}\gdef\@journalfull{High-Throughput}\gdef\@journalshort{High-Throughput}\gdef\@doiabbr{ht}\gdef\@ISSN{2571-5135}}
\DeclareOption{histories}{\gdef\@journal{histories}\gdef\@journalfull{Histories}\gdef\@journalshort{Histories}\gdef\@doiabbr{histories}\gdef\@ISSN{2409-9252}\gdef\@continuouspages{yes}}
\DeclareOption{horticulturae}{\gdef\@journal{horticulturae}\gdef\@journalfull{Horticulturae}\gdef\@journalshort{Horticulturae}\gdef\@doiabbr{horticulturae}\gdef\@ISSN{2311-7524}}
\DeclareOption{humanities}{\gdef\@journal{humanities}\gdef\@journalfull{Humanities}\gdef\@journalshort{Humanities}\gdef\@doiabbr{h}\gdef\@ISSN{2076-0787}}
\DeclareOption{humans}{\gdef\@journal{humans}\gdef\@journalfull{Humans}\gdef\@journalshort{Humans}\gdef\@doiabbr{humans}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hydrobiology}{\gdef\@journal{hydrobiology}\gdef\@journalfull{Hydrobiology}\gdef\@journalshort{Hydrobiology	}\gdef\@doiabbr{hydrobiology}\gdef\@ISSN{2673-9917}\gdef\@continuouspages{yes}}
\DeclareOption{hydrogen}{\gdef\@journal{hydrogen}\gdef\@journalfull{Hydrogen}\gdef\@journalshort{Hydrogen}\gdef\@doiabbr{hydrogen}\gdef\@ISSN{2673-4141}\gdef\@continuouspages{yes}}
\DeclareOption{hydrology}{\gdef\@journal{hydrology}\gdef\@journalfull{Hydrology}\gdef\@journalshort{Hydrology}\gdef\@doiabbr{hydrology}\gdef\@ISSN{2306-5338}}
\DeclareOption{hygiene}{\gdef\@journal{hygiene}\gdef\@journalfull{Hygiene}\gdef\@journalshort{Hygiene}\gdef\@doiabbr{hygiene}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{idr}{\gdef\@journal{idr}\gdef\@journalfull{Infectious Disease Reports}\gdef\@journalshort{Infect. Dis. Rep.}\gdef\@doiabbr{idr}\gdef\@ISSN{2036-7449}\gdef\@continuouspages{yes}}
\DeclareOption{ijerph}{\gdef\@journal{ijerph}\gdef\@journalfull{International Journal of Environmental Research and Public Health}\gdef\@journalshort{Int. J. Environ. Res. Public Health}\gdef\@doiabbr{ijerph}\gdef\@ISSN{1660-4601}}
\DeclareOption{ijfs}{\gdef\@journal{ijfs}\gdef\@journalfull{International Journal of Financial Studies}\gdef\@journalshort{Int. J. Financial Stud.}\gdef\@doiabbr{ijfs}\gdef\@ISSN{2227-7072}}
\DeclareOption{ijgi}{\gdef\@journal{ijgi}\gdef\@journalfull{ISPRS International Journal of Geo-Information}\gdef\@journalshort{ISPRS Int. J. Geo-Inf.}\gdef\@doiabbr{ijgi}\gdef\@ISSN{2220-9964}}
\DeclareOption{ijms}{\gdef\@journal{ijms}\gdef\@journalfull{International Journal of Molecular Sciences}\gdef\@journalshort{Int. J. Mol. Sci.}\gdef\@doiabbr{ijms}\gdef\@ISSN{1422-0067}}
\DeclareOption{ijns}{\gdef\@journal{ijns}\gdef\@journalfull{International Journal of Neonatal Screening}\gdef\@journalshort{Int. J. Neonatal Screen.}\gdef\@doiabbr{ijns}\gdef\@ISSN{2409-515X}}
\DeclareOption{ijpb}{\gdef\@journal{ijpb}\gdef\@journalfull{International Journal of Plant Biology}\gdef\@journalshort{Int. J. Plant Biol.}\gdef\@doiabbr{ijpb}\gdef\@ISSN{2037-0164}\gdef\@continuouspages{yes}}
\DeclareOption{ijtm}{\gdef\@journal{ijtm}\gdef\@journalfull{International Journal of Translational Medicine}\gdef\@journalshort{Int. J. Transl. Med.}\gdef\@doiabbr{ijtm}\gdef\@ISSN{2673-8937}\gdef\@continuouspages{yes}}
\DeclareOption{ijtpp}{\gdef\@journal{ijtpp}\gdef\@journalfull{International Journal of Turbomachinery Propulsion and Power}\gdef\@journalshort{Int. J. Turbomach. Propuls. Power}\gdef\@doiabbr{ijtpp}\gdef\@ISSN{2504-186X}}
\DeclareOption{ime}{\gdef\@journal{ime}\gdef\@journalfull{International Medical Education}\gdef\@journalshort{Int. Med. Educ.}\gdef\@doiabbr{ime}\gdef\@ISSN{2813-141X}\gdef\@continuouspages{yes}}
\DeclareOption{immuno}{\gdef\@journal{immuno}\gdef\@journalfull{Immuno}\gdef\@journalshort{Immuno}\gdef\@doiabbr{immuno}\gdef\@ISSN{2673-5601}\gdef\@continuouspages{yes}}
\DeclareOption{informatics}{\gdef\@journal{informatics}\gdef\@journalfull{Informatics}\gdef\@journalshort{Informatics}\gdef\@doiabbr{informatics}\gdef\@ISSN{2227-9709}}
\DeclareOption{information}{\gdef\@journal{information}\gdef\@journalfull{Information}\gdef\@journalshort{Information}\gdef\@doiabbr{info}\gdef\@ISSN{2078-2489}}
\DeclareOption{infrastructures}{\gdef\@journal{infrastructures}\gdef\@journalfull{Infrastructures}\gdef\@journalshort{Infrastructures}\gdef\@doiabbr{infrastructures}\gdef\@ISSN{2412-3811}}
\DeclareOption{inorganics}{\gdef\@journal{inorganics}\gdef\@journalfull{Inorganics}\gdef\@journalshort{Inorganics}\gdef\@doiabbr{inorganics}\gdef\@ISSN{2304-6740}}
\DeclareOption{insects}{\gdef\@journal{insects}\gdef\@journalfull{Insects}\gdef\@journalshort{Insects}\gdef\@doiabbr{insects}\gdef\@ISSN{2075-4450}}
\DeclareOption{instruments}{\gdef\@journal{instruments}\gdef\@journalfull{Instruments}\gdef\@journalshort{Instruments}\gdef\@doiabbr{instruments}\gdef\@ISSN{2410-390X}}
\DeclareOption{inventions}{\gdef\@journal{inventions}\gdef\@journalfull{Inventions}\gdef\@journalshort{Inventions}\gdef\@doiabbr{inventions}\gdef\@ISSN{2411-5134}}
\DeclareOption{iot}{\gdef\@journal{iot}\gdef\@journalfull{IoT}\gdef\@journalshort{IoT}\gdef\@doiabbr{iot}\gdef\@ISSN{2624-831X}\gdef\@continuouspages{yes}}
\DeclareOption{j}{\gdef\@journal{j}\gdef\@journalfull{J}\gdef\@journalshort{J}\gdef\@doiabbr{j}\gdef\@ISSN{2571-8800}\gdef\@continuouspages{yes}}
\DeclareOption{jal}{\gdef\@journal{jal}\gdef\@journalfull{Journal of Ageing and Longevity}\gdef\@journalshort{J. Ageing Longev.}\gdef\@doiabbr{jal}\gdef\@ISSN{2673-9259}\gdef\@continuouspages{yes}}
\DeclareOption{jcdd}{\gdef\@journal{jcdd}\gdef\@journalfull{Journal of Cardiovascular Development and Disease}\gdef\@journalshort{J. Cardiovasc. Dev. Dis.}\gdef\@doiabbr{jcdd}\gdef\@ISSN{2308-3425}}
\DeclareOption{jcm}{\gdef\@journal{jcm}\gdef\@journalfull{Journal of Clinical Medicine}\gdef\@journalshort{J. Clin. Med.}\gdef\@doiabbr{jcm}\gdef\@ISSN{2077-0383}}
\DeclareOption{jcp}{\gdef\@journal{jcp}\gdef\@journalfull{Journal of Cybersecurity and Privacy}\gdef\@journalshort{J. Cybersecur. Priv.}\gdef\@doiabbr{jcp}\gdef\@ISSN{2624-800X}\gdef\@continuouspages{yes}}
\DeclareOption{jcs}{\gdef\@journal{jcs}\gdef\@journalfull{Journal of Composites Science}\gdef\@journalshort{J. Compos. Sci.}\gdef\@doiabbr{jcs}\gdef\@ISSN{2504-477X}}
\DeclareOption{jcto}{\gdef\@journal{jcto}\gdef\@journalfull{Journal of Clinical \& Translational Ophthalmology}\gdef\@journalshort{J. Clin. Transl. Ophthalmol.}\gdef\@doiabbr{jcto}\gdef\@ISSN{2813-1053}\gdef\@continuouspages{yes}}
\DeclareOption{jdb}{\gdef\@journal{jdb}\gdef\@journalfull{Journal of Developmental Biology}\gdef\@journalshort{J. Dev. Biol.}\gdef\@doiabbr{jdb}\gdef\@ISSN{2221-3759}}
\DeclareOption{jeta}{\gdef\@journal{jeta}\gdef\@journalfull{Journal of Experimental and Theoretical Analyses}\gdef\@journalshort{J. Exp. Theor. Anal.}\gdef\@doiabbr{jeta}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{jfb}{\gdef\@journal{jfb}\gdef\@journalfull{Journal of Functional Biomaterials}\gdef\@journalshort{J. Funct. Biomater.}\gdef\@doiabbr{jfb}\gdef\@ISSN{2079-4983}}
\DeclareOption{jfmk}{\gdef\@journal{jfmk}\gdef\@journalfull{Journal of Functional Morphology and Kinesiology}\gdef\@journalshort{J. Funct. Morphol. Kinesiol.}\gdef\@doiabbr{jfmk}\gdef\@ISSN{2411-5142}}
\DeclareOption{jimaging}{\gdef\@journal{jimaging}\gdef\@journalfull{Journal of Imaging}\gdef\@journalshort{J. Imaging}\gdef\@doiabbr{jimaging}\gdef\@ISSN{2313-433X}}
\DeclareOption{jintelligence}{\gdef\@journal{jintelligence}\gdef\@journalfull{Journal of Intelligence}\gdef\@journalshort{J. Intell.}\gdef\@doiabbr{jintelligence}\gdef\@ISSN{2079-3200}}
\DeclareOption{jlpea}{\gdef\@journal{jlpea}\gdef\@journalfull{Journal of Low Power Electronics and Applications}\gdef\@journalshort{J. Low Power Electron. Appl.}\gdef\@doiabbr{jlpea}\gdef\@ISSN{2079-9268}}
\DeclareOption{jmmp}{\gdef\@journal{jmmp}\gdef\@journalfull{Journal of Manufacturing and Materials Processing}\gdef\@journalshort{J. Manuf. Mater. Process.}\gdef\@doiabbr{jmmp}\gdef\@ISSN{2504-4494}}
\DeclareOption{jmp}{\gdef\@journal{jmp}\gdef\@journalfull{Journal of Molecular Pathology}\gdef\@journalshort{J. Mol. Pathol.}\gdef\@doiabbr{jmp}\gdef\@ISSN{2673-5261}\gdef\@continuouspages{yes}}
\DeclareOption{jmse}{\gdef\@journal{jmse}\gdef\@journalfull{Journal of Marine Science and Engineering}\gdef\@journalshort{J. Mar. Sci. Eng.}\gdef\@doiabbr{jmse}\gdef\@ISSN{2077-1312}}
\DeclareOption{jne}{\gdef\@journal{jne}\gdef\@journalfull{Journal of Nuclear Engineering}\gdef\@journalshort{J. Nucl. Eng.}\gdef\@doiabbr{jne}\gdef\@ISSN{2673-4362}\gdef\@continuouspages{yes}}
\DeclareOption{jnt}{\gdef\@journal{jnt}\gdef\@journalfull{Journal of Nanotheranostics}\gdef\@journalshort{J. Nanotheranostics}\gdef\@doiabbr{jnt}\gdef\@ISSN{2624-845X}\gdef\@continuouspages{yes}}
\DeclareOption{jof}{\gdef\@journal{jof}\gdef\@journalfull{Journal of Fungi}\gdef\@journalshort{J. Fungi}\gdef\@doiabbr{jof}\gdef\@ISSN{2309-608X}}
\DeclareOption{joitmc}{\gdef\@journal{joitmc}\gdef\@journalfull{Journal of Open Innovation: Technology Market and Complexity}\gdef\@journalshort{J. Open Innov. Technol. Mark. Complex.}\gdef\@doiabbr{joitmc}\gdef\@ISSN{2199-8531}}
\DeclareOption{jor}{\gdef\@journal{jor}\gdef\@journalfull{Journal of Respiration}\gdef\@journalshort{J. Respir.}\gdef\@doiabbr{jor}\gdef\@ISSN{2673-527X}\gdef\@continuouspages{yes}}
\DeclareOption{journalmedia}{\gdef\@journal{journalmedia}\gdef\@journalfull{Journalism and Media}\gdef\@journalshort{Journal. Media}\gdef\@doiabbr{journalmedia}\gdef\@ISSN{2673-5172}\gdef\@continuouspages{yes}}
\DeclareOption{jox}{\gdef\@journal{jox}\gdef\@journalfull{Journal of Xenobiotics}\gdef\@journalshort{J. Xenobiot.}\gdef\@doiabbr{jox}\gdef\@ISSN{2039-4713}\gdef\@continuouspages{yes}}
\DeclareOption{jpm}{\gdef\@journal{jpm}\gdef\@journalfull{Journal of Personalized Medicine}\gdef\@journalshort{J. Pers. Med.}\gdef\@doiabbr{jpm}\gdef\@ISSN{2075-4426}}
\DeclareOption{jrfm}{\gdef\@journal{jrfm}\gdef\@journalfull{Journal of Risk and Financial Management}\gdef\@journalshort{J. Risk Financial Manag.}\gdef\@doiabbr{jrfm}\gdef\@ISSN{1911-8074}}
\DeclareOption{jsan}{\gdef\@journal{jsan}\gdef\@journalfull{Journal of Sensor and Actuator Networks}\gdef\@journalshort{J. Sens. Actuator Netw.}\gdef\@doiabbr{jsan}\gdef\@ISSN{2224-2708}}
\DeclareOption{jtaer}{\gdef\@journal{jtaer}\gdef\@journalfull{Journal of Theoretical and Applied Electronic Commerce Research}\gdef\@journalshort{J. Theor. Appl. Electron. Commer. Res.}\gdef\@doiabbr{jtaer}\gdef\@ISSN{0718-1876}\gdef\@continuouspages{yes}}
\DeclareOption{jvd}{\gdef\@journal{jvd}\gdef\@journalfull{Journal of Vascular Diseases}\gdef\@journalshort{JVD}\gdef\@doiabbr{jvd}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{jzbg}{\gdef\@journal{jzbg}\gdef\@journalfull{Journal of Zoological and Botanical Gardens}\gdef\@journalshort{J. Zool. Bot. Gard.}\gdef\@doiabbr{jzbg}\gdef\@ISSN{2673-5636}\gdef\@continuouspages{yes}}
%\DeclareOption{kidney}{\gdef\@journal{kidney}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{kidneydial}{\gdef\@journal{kidneydial}\gdef\@journalfull{Kidney and Dialysis}\gdef\@journalshort{Kidney Dial.}\gdef\@doiabbr{kinasesphosphatases}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{kinasesphosphatases}{\gdef\@journal{kinasesphosphatases}\gdef\@journalfull{Kinases and Phosphatases}\gdef\@journalshort{Kinases Phosphatases}\gdef\@doiabbr{kinasesphosphatases}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{knowledge}{\gdef\@journal{knowledge}\gdef\@journalfull{Knowledge}\gdef\@journalshort{Knowledge}\gdef\@doiabbr{knowledge}\gdef\@ISSN{2673-9585}\gdef\@continuouspages{yes}}
\DeclareOption{land}{\gdef\@journal{land}\gdef\@journalfull{Land}\gdef\@journalshort{Land}\gdef\@doiabbr{land}\gdef\@ISSN{2073-445X}}
\DeclareOption{languages}{\gdef\@journal{languages}\gdef\@journalfull{Languages}\gdef\@journalshort{Languages}\gdef\@doiabbr{languages}\gdef\@ISSN{2226-471X}}
\DeclareOption{laws}{\gdef\@journal{laws}\gdef\@journalfull{Laws}\gdef\@journalshort{Laws}\gdef\@doiabbr{laws}\gdef\@ISSN{2075-471X}}
\DeclareOption{life}{\gdef\@journal{life}\gdef\@journalfull{Life}\gdef\@journalshort{Life}\gdef\@doiabbr{life}\gdef\@ISSN{2075-1729}}
\DeclareOption{liquids}{\gdef\@journal{liquids}\gdef\@journalfull{Liquids}\gdef\@journalshort{Liquids}\gdef\@doiabbr{liquids}\gdef\@ISSN{2673-8015}\gdef\@continuouspages{yes}}
\DeclareOption{literature}{\gdef\@journal{literature}\gdef\@journalfull{Literature}\gdef\@journalshort{Literature}\gdef\@doiabbr{literature}\gdef\@ISSN{2410-9789}\gdef\@continuouspages{yes}}
\DeclareOption{livers}{\gdef\@journal{livers}\gdef\@journalfull{Livers}\gdef\@journalshort{Livers}\gdef\@doiabbr{livers}\gdef\@ISSN{2673-4389}\gdef\@continuouspages{yes}}
\DeclareOption{logics}{\gdef\@journal{logics}\gdef\@journalfull{Logics}\gdef\@journalshort{Logics}\gdef\@doiabbr{logics}\gdef\@ISSN{2813-0405}\gdef\@continuouspages{yes}}
\DeclareOption{logistics}{\gdef\@journal{logistics}\gdef\@journalfull{Logistics}\gdef\@journalshort{Logistics}\gdef\@doiabbr{logistics}\gdef\@ISSN{2305-6290}}
\DeclareOption{lubricants}{\gdef\@journal{lubricants}\gdef\@journalfull{Lubricants}\gdef\@journalshort{Lubricants}\gdef\@doiabbr{lubricants}\gdef\@ISSN{2075-4442}}
\DeclareOption{lymphatics}{\gdef\@journal{lymphatics}\gdef\@journalfull{Lymphatics}\gdef\@journalshort{Lymphatics}\gdef\@doiabbr{lymphatics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}	
\DeclareOption{machines}{\gdef\@journal{machines}\gdef\@journalfull{Machines}\gdef\@journalshort{Machines}\gdef\@doiabbr{machines}\gdef\@ISSN{2075-1702}}
\DeclareOption{macromol}{\gdef\@journal{macromol}\gdef\@journalfull{Macromol}\gdef\@journalshort{Macromol}\gdef\@doiabbr{macromol}\gdef\@ISSN{2673-6209}\gdef\@continuouspages{yes}}
\DeclareOption{magnetism}{\gdef\@journal{magnetism}\gdef\@journalfull{Magnetism}\gdef\@journalshort{Magnetism}\gdef\@doiabbr{magnetism}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{magnetochemistry}{\gdef\@journal{magnetochemistry}\gdef\@journalfull{Magnetochemistry}\gdef\@journalshort{Magnetochemistry}\gdef\@doiabbr{magnetochemistry}\gdef\@ISSN{2312-7481}}
\DeclareOption{make}{\gdef\@journal{make}\gdef\@journalfull{Machine Learning and Knowledge Extraction}\gdef\@journalshort{Mach. Learn. Knowl. Extr.}\gdef\@doiabbr{make}\gdef\@ISSN{2504-4990}\gdef\@continuouspages{yes}}
\DeclareOption{marinedrugs}{\gdef\@journal{marinedrugs}\gdef\@journalfull{Marine Drugs}\gdef\@journalshort{Mar. Drugs}\gdef\@doiabbr{md}\gdef\@ISSN{1660-3397}}
\DeclareOption{materials}{\gdef\@journal{materials}\gdef\@journalfull{Materials}\gdef\@journalshort{Materials}\gdef\@doiabbr{ma}\gdef\@ISSN{1996-1944}}
\DeclareOption{materproc}{\gdef\@journal{materproc}\gdef\@journalfull{Materials Proceedings}\gdef\@journalshort{Mater. Proc.}\gdef\@doiabbr{materproc}\gdef\@ISSN{2673-4605}}
\DeclareOption{mathematics}{\gdef\@journal{mathematics}\gdef\@journalfull{Mathematics}\gdef\@journalshort{Mathematics}\gdef\@doiabbr{math}\gdef\@ISSN{2227-7390}}
\DeclareOption{mca}{\gdef\@journal{mca}\gdef\@journalfull{Mathematical and Computational Applications}\gdef\@journalshort{Math. Comput. Appl.}\gdef\@doiabbr{mca}\gdef\@ISSN{2297-8747}}
\DeclareOption{measurements}{\gdef\@journal{measurements}\gdef\@journalfull{Measurements}\gdef\@journalshort{Measurements}\gdef\@doiabbr{measurements}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{medicina}{\gdef\@journal{medicina}\gdef\@journalfull{Medicina}\gdef\@journalshort{Medicina}\gdef\@doiabbr{medicina}\gdef\@ISSN{1648-9144}}
\DeclareOption{medicines}{\gdef\@journal{medicines}\gdef\@journalfull{Medicines}\gdef\@journalshort{Medicines}\gdef\@doiabbr{medicines}\gdef\@ISSN{2305-6320}}
\DeclareOption{medsci}{\gdef\@journal{medsci}\gdef\@journalfull{Medical Sciences}\gdef\@journalshort{Med. Sci.}\gdef\@doiabbr{medsci}\gdef\@ISSN{2076-3271}}
\DeclareOption{membranes}{\gdef\@journal{membranes}\gdef\@journalfull{Membranes}\gdef\@journalshort{Membranes}\gdef\@doiabbr{membranes}\gdef\@ISSN{2077-0375}}
\DeclareOption{merits}{\gdef\@journal{merits}\gdef\@journalfull{Merits}\gdef\@journalshort{Merits}\gdef\@doiabbr{merits}\gdef\@ISSN{2673-8104}\gdef\@continuouspages{yes}}
\DeclareOption{metabolites}{\gdef\@journal{metabolites}\gdef\@journalfull{Metabolites}\gdef\@journalshort{Metabolites}\gdef\@doiabbr{metabo}\gdef\@ISSN{2218-1989}}
\DeclareOption{metals}{\gdef\@journal{metals}\gdef\@journalfull{Metals}\gdef\@journalshort{Metals}\gdef\@doiabbr{met}\gdef\@ISSN{2075-4701}}
\DeclareOption{meteorology}{\gdef\@journal{meteorology}\gdef\@journalfull{Meteorology}\gdef\@journalshort{Meteorology}\gdef\@doiabbr{meteorology}\gdef\@ISSN{2674-0494}\gdef\@continuouspages{yes}}
\DeclareOption{methane}{\gdef\@journal{methane}\gdef\@journalfull{Methane}\gdef\@journalshort{Methane}\gdef\@doiabbr{methane}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{metrology}{\gdef\@journal{metrology}\gdef\@journalfull{Metrology}\gdef\@journalshort{Metrology}\gdef\@doiabbr{metrology}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{micro}{\gdef\@journal{micro}\gdef\@journalfull{Micro}\gdef\@journalshort{Micro}\gdef\@doiabbr{micro}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{microarrays}{\gdef\@journal{microarrays}\gdef\@journalfull{Microarrays}\gdef\@journalshort{Microarrays}\gdef\@doiabbr{microarrays}\gdef\@ISSN{2076-3905}}
\DeclareOption{microbiolres}{\gdef\@journal{microbiolres}\gdef\@journalfull{Microbiology Research}\gdef\@journalshort{Microbiol. Res.}\gdef\@doiabbr{microbiolres}\gdef\@ISSN{2036-7481}\gdef\@continuouspages{yes}}
\DeclareOption{micromachines}{\gdef\@journal{micromachines}\gdef\@journalfull{Micromachines}\gdef\@journalshort{Micromachines}\gdef\@doiabbr{mi}\gdef\@ISSN{2072-666X}}
\DeclareOption{microorganisms}{\gdef\@journal{microorganisms}\gdef\@journalfull{Microorganisms}\gdef\@journalshort{Microorganisms}\gdef\@doiabbr{microorganisms}\gdef\@ISSN{2076-2607}}
\DeclareOption{microplastics}{\gdef\@journal{microplastics}\gdef\@journalfull{Microplastics}\gdef\@journalshort{Microplastics}\gdef\@doiabbr{microplastics}\gdef\@ISSN{2673-8929}\gdef\@continuouspages{yes}}
\DeclareOption{minerals}{\gdef\@journal{minerals}\gdef\@journalfull{Minerals}\gdef\@journalshort{Minerals}\gdef\@doiabbr{min}\gdef\@ISSN{2075-163X}}
\DeclareOption{mining}{\gdef\@journal{mining}\gdef\@journalfull{Mining}\gdef\@journalshort{Mining}\gdef\@doiabbr{mining}\gdef\@ISSN{2673-6489}\gdef\@continuouspages{yes}}
\DeclareOption{modelling}{\gdef\@journal{modelling}\gdef\@journalfull{Modelling}\gdef\@journalshort{Modelling}\gdef\@doiabbr{modelling}\gdef\@ISSN{2673-3951}\gdef\@continuouspages{yes}}
\DeclareOption{molbank}{\gdef\@journal{molbank}\gdef\@journalfull{Molbank}\gdef\@journalshort{Molbank}\gdef\@doiabbr{M}\gdef\@ISSN{1422-8599}}
\DeclareOption{molecules}{\gdef\@journal{molecules}\gdef\@journalfull{Molecules}\gdef\@journalshort{Molecules}\gdef\@doiabbr{molecules}\gdef\@ISSN{1420-3049}}
\DeclareOption{mps}{\gdef\@journal{mps}\gdef\@journalfull{Methods and Protocols}\gdef\@journalshort{Methods Protoc.}\gdef\@doiabbr{mps}\gdef\@ISSN{2409-9279}}
\DeclareOption{msf}{\gdef\@journal{msf}\gdef\@journalfull{Medical Sciences Forum}\gdef\@journalshort{Med. Sci. Forum}\gdef\@doiabbr{msf}\gdef\@ISSN{2673-9992}}
\DeclareOption{mti}{\gdef\@journal{mti}\gdef\@journalfull{Multimodal Technologies and Interaction}\gdef\@journalshort{Multimodal Technol. Interact.}\gdef\@doiabbr{mti}\gdef\@ISSN{2414-4088}}
\DeclareOption{muscles}{\gdef\@journal{muscles}\gdef\@journalfull{Muscles}\gdef\@journalshort{Muscles}\gdef\@doiabbr{muscles}\gdef\@ISSN{2813-0413}\gdef\@continuouspages{yes}}
\DeclareOption{nanoenergyadv}{\gdef\@journal{nanoenergyadv}\gdef\@journalfull{Nanoenergy Advances}\gdef\@journalshort{Nanoenergy Adv.}\gdef\@doiabbr{nanoenergyadv}\gdef\@ISSN{2673-706X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomanufacturing}{\gdef\@journal{nanomanufacturing}\gdef\@journalfull{Nanomanufacturing}\gdef\@journalshort{Nanomanufacturing}\gdef\@doiabbr{nanomanufacturing}\gdef\@ISSN{2673-687X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomaterials}{\gdef\@journal{nanomaterials}\gdef\@journalfull{Nanomaterials}\gdef\@journalshort{Nanomaterials}\gdef\@doiabbr{nano}\gdef\@ISSN{2079-4991}}
\DeclareOption{ncrna}{\gdef\@journal{ncrna}\gdef\@journalfull{Non-Coding RNA}\gdef\@journalshort{Non-Coding RNA}\gdef\@doiabbr{ncrna}\gdef\@ISSN{2311-553X}}
\DeclareOption{network}{\gdef\@journal{network}\gdef\@journalfull{Network}\gdef\@journalshort{Network}\gdef\@doiabbr{network}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{neuroglia}{\gdef\@journal{neuroglia}\gdef\@journalfull{Neuroglia}\gdef\@journalshort{Neuroglia}\gdef\@doiabbr{neuroglia}\gdef\@ISSN{2571-6980}\gdef\@continuouspages{yes}}
\DeclareOption{neurolint}{\gdef\@journal{neurolint}\gdef\@journalfull{Neurology International}\gdef\@journalshort{Neurol. Int.}\gdef\@doiabbr{neurolint}\gdef\@ISSN{2035-8377}\gdef\@continuouspages{yes}}
\DeclareOption{neurosci}{\gdef\@journal{neurosci}\gdef\@journalfull{NeuroSci}\gdef\@journalshort{NeuroSci}\gdef\@doiabbr{neurosci}\gdef\@ISSN{2673-4087}\gdef\@continuouspages{yes}}
\DeclareOption{nitrogen}{\gdef\@journal{nitrogen}\gdef\@journalfull{Nitrogen}\gdef\@journalshort{Nitrogen}\gdef\@doiabbr{nitrogen}\gdef\@ISSN{2504-3129}\gdef\@continuouspages{yes}}
\DeclareOption{notspecified}{\gdef\@journal{notspecified}\gdef\@journalfull{Journal Not Specified}\gdef\@journalshort{Journal Not Specified}\gdef\@doiabbr{}\gdef\@ISSN{}}
%%\DeclareOption{nri}{\gdef\@journal{nri}\gdef\@journalfull{Natural Resources Informatics}\gdef\@journalshort{Nat. Resour. Inform.}\gdef\@doiabbr{nri}\gdef\@ISSN{2673-981X}\gdef\@continuouspages{yes}}
\DeclareOption{nursrep}{\gdef\@journal{nursrep}\gdef\@journalfull{Nursing Reports}\gdef\@journalshort{Nurs. Rep.}\gdef\@doiabbr{nursrep}\gdef\@ISSN{2039-4403}\gdef\@continuouspages{yes}}
\DeclareOption{nutraceuticals}{\gdef\@journal{nutraceuticals}\gdef\@journalfull{Nutraceuticals}\gdef\@journalshort{Nutraceuticals}\gdef\@doiabbr{nutraceuticals}\gdef\@ISSN{1661-3821}\gdef\@continuouspages{yes}}
\DeclareOption{nutrients}{\gdef\@journal{nutrients}\gdef\@journalfull{Nutrients}\gdef\@journalshort{Nutrients}\gdef\@doiabbr{nu}\gdef\@ISSN{2072-6643}}
\DeclareOption{obesities}{\gdef\@journal{obesities}\gdef\@journalfull{Obesities}\gdef\@journalshort{Obesities}\gdef\@doiabbr{obesities}\gdef\@ISSN{2673-4168}\gdef\@continuouspages{yes}}
\DeclareOption{oceans}{\gdef\@journal{oceans}\gdef\@journalfull{Oceans}\gdef\@journalshort{Oceans}\gdef\@doiabbr{oceans}\gdef\@ISSN{2673-1924}\gdef\@continuouspages{yes}}
\DeclareOption{ohbm}{\gdef\@journal{ohbm}\gdef\@journalfull{Journal of Otorhinolaryngology Hearing and Balance Medicine}\gdef\@journalshort{J. Otorhinolaryngol. Hear. Balance Med.}\gdef\@doiabbr{ohbm}\gdef\@ISSN{2504-463X}}
\DeclareOption{onco}{\gdef\@journal{onco}\gdef\@journalfull{Onco}\gdef\@journalshort{Onco}\gdef\@doiabbr{onco}\gdef\@ISSN{2673-7523}\gdef\@continuouspages{yes}}
%\DeclareOption{oncopathology}{\gdef\@journal{oncopathology}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{optics}{\gdef\@journal{optics}\gdef\@journalfull{Optics}\gdef\@journalshort{Optics}\gdef\@doiabbr{opt}\gdef\@ISSN{2673-3269}\gdef\@continuouspages{yes}}
\DeclareOption{oral}{\gdef\@journal{oral}\gdef\@journalfull{Oral}\gdef\@journalshort{Oral}\gdef\@doiabbr{oral}\gdef\@ISSN{2673-6373}\gdef\@continuouspages{yes}}
\DeclareOption{organics}{\gdef\@journal{organics}\gdef\@journalfull{Organics}\gdef\@journalshort{Organics}\gdef\@doiabbr{org}\gdef\@ISSN{2673-401X}\gdef\@continuouspages{yes}}
\DeclareOption{organoids}{\gdef\@journal{organoids}\gdef\@journalfull{Organoids}\gdef\@journalshort{Organoids}\gdef\@doiabbr{organoids}\gdef\@ISSN{2674-1172}\gdef\@continuouspages{yes}}
\DeclareOption{osteology}{\gdef\@journal{osteology}\gdef\@journalfull{Osteology}\gdef\@journalshort{Osteology}\gdef\@doiabbr{osteology}\gdef\@ISSN{2673-4036}\gdef\@continuouspages{yes}}
\DeclareOption{oxygen}{\gdef\@journal{oxygen}\gdef\@journalfull{Oxygen}\gdef\@journalshort{Oxygen}\gdef\@doiabbr{oxygen}\gdef\@ISSN{2673-9801}\gdef\@continuouspages{yes}}
\DeclareOption{parasites}{\gdef\@journal{parasites}\gdef\@journalfull{Parasites}\gdef\@journalshort{Parasites}\gdef\@doiabbr{parasites}\gdef\@ISSN{2673-5946}}
\DeclareOption{parasitologia}{\gdef\@journal{parasitologia}\gdef\@journalfull{Parasitologia}\gdef\@journalshort{Parasitologia}\gdef\@doiabbr{parasitologia}\gdef\@ISSN{2673-6772}\gdef\@continuouspages{yes}}
\DeclareOption{particles}{\gdef\@journal{particles}\gdef\@journalfull{Particles}\gdef\@journalshort{Particles}\gdef\@doiabbr{particles}\gdef\@ISSN{2571-712X}\gdef\@continuouspages{yes}}
\DeclareOption{pathogens}{\gdef\@journal{pathogens}\gdef\@journalfull{Pathogens}\gdef\@journalshort{Pathogens}\gdef\@doiabbr{pathogens}\gdef\@ISSN{2076-0817}}
\DeclareOption{pathophysiology}{\gdef\@journal{pathophysiology}\gdef\@journalfull{Pathophysiology}\gdef\@journalshort{Pathophysiology}\gdef\@doiabbr{pathophysiology}\gdef\@ISSN{0928-4680}\gdef\@continuouspages{yes}}
\DeclareOption{pediatrrep}{\gdef\@journal{pediatrrep}\gdef\@journalfull{Pediatric Reports}\gdef\@journalshort{Pediatr. Rep.}\gdef\@doiabbr{pediatric}\gdef\@ISSN{2036-7503}\gdef\@continuouspages{yes}}
\DeclareOption{pharmaceuticals}{\gdef\@journal{pharmaceuticals}\gdef\@journalfull{Pharmaceuticals}\gdef\@journalshort{Pharmaceuticals}\gdef\@doiabbr{ph}\gdef\@ISSN{1424-8247}}
\DeclareOption{pharmaceutics}{\gdef\@journal{pharmaceutics}\gdef\@journalfull{Pharmaceutics}\gdef\@journalshort{Pharmaceutics}\gdef\@doiabbr{pharmaceutics}\gdef\@ISSN{1999-4923}}
\DeclareOption{pharmacoepidemiology}{\gdef\@journal{pharmacoepidemiology}\gdef\@journalfull{Pharmacoepidemiology}\gdef\@journalshort{Pharmacoepidemiology}\gdef\@doiabbr{pharma}\gdef\@ISSN{2813-0618}\gdef\@continuouspages{yes}}
\DeclareOption{pharmacy}{\gdef\@journal{pharmacy}\gdef\@journalfull{Pharmacy}\gdef\@journalshort{Pharmacy}\gdef\@doiabbr{pharmacy}\gdef\@ISSN{2226-4787}}
\DeclareOption{philosophies}{\gdef\@journal{philosophies}\gdef\@journalfull{Philosophies}\gdef\@journalshort{Philosophies}\gdef\@doiabbr{philosophies}\gdef\@ISSN{2409-9287}}
\DeclareOption{photochem}{\gdef\@journal{photochem}\gdef\@journalfull{Photochem}\gdef\@journalshort{Photochem}\gdef\@doiabbr{photochem}\gdef\@ISSN{2673-7256}\gdef\@continuouspages{yes}}
\DeclareOption{photonics}{\gdef\@journal{photonics}\gdef\@journalfull{Photonics}\gdef\@journalshort{Photonics}\gdef\@doiabbr{photonics}\gdef\@ISSN{2304-6732}}
\DeclareOption{phycology}{\gdef\@journal{phycology}\gdef\@journalfull{Phycology}\gdef\@journalshort{Phycology}\gdef\@doiabbr{phycology}\gdef\@ISSN{2673-9410}\gdef\@continuouspages{yes}}
\DeclareOption{physchem}{\gdef\@journal{physchem}\gdef\@journalfull{Physchem}\gdef\@journalshort{Physchem}\gdef\@doiabbr{physchem}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{physics}{\gdef\@journal{physics}\gdef\@journalfull{Physics}\gdef\@journalshort{Physics}\gdef\@doiabbr{physics}\gdef\@ISSN{2624-8174}\gdef\@continuouspages{yes}}
\DeclareOption{physiologia}{\gdef\@journal{physiologia}\gdef\@journalfull{Physiologia}\gdef\@journalshort{Physiologia}\gdef\@doiabbr{physiologia}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{plants}{\gdef\@journal{plants}\gdef\@journalfull{Plants}\gdef\@journalshort{Plants}\gdef\@doiabbr{plants}\gdef\@ISSN{2223-7747}}
\DeclareOption{plasma}{\gdef\@journal{plasma}\gdef\@journalfull{Plasma}\gdef\@journalshort{Plasma}\gdef\@doiabbr{plasma}\gdef\@ISSN{2571-6182}\gdef\@continuouspages{yes}}
\DeclareOption{pollutants}{\gdef\@journal{pollutants}\gdef\@journalfull{Pollutants}\gdef\@journalshort{Pollutants}\gdef\@doiabbr{pollutants}\gdef\@ISSN{2673-4672}\gdef\@continuouspages{yes}}
\DeclareOption{polymers}{\gdef\@journal{polymers}\gdef\@journalfull{Polymers}\gdef\@journalshort{Polymers}\gdef\@doiabbr{polym}\gdef\@ISSN{2073-4360}}
\DeclareOption{polysaccharides}{\gdef\@journal{polysaccharides}\gdef\@journalfull{Polysaccharides}\gdef\@journalshort{Polysaccharides}\gdef\@doiabbr{polysaccharides}\gdef\@ISSN{2673-4176}\gdef\@continuouspages{yes}}
\DeclareOption{poultry}{\gdef\@journal{poultry}\gdef\@journalfull{Poultry}\gdef\@journalshort{Poultry}\gdef\@doiabbr{poultry}\gdef\@ISSN{2674-1164}\gdef\@continuouspages{yes}}
\DeclareOption{powders}{\gdef\@journal{powders}\gdef\@journalfull{Powders}\gdef\@journalshort{Powders}\gdef\@doiabbr{powders}\gdef\@ISSN{2674-0516}\gdef\@continuouspages{yes}}
\DeclareOption{preprints}{\gdef\@journal{preprints}\gdef\@journalfull{Preprints}\gdef\@journalshort{Preprints}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{proceedings}{\gdef\@journal{proceedings}\gdef\@journalfull{Proceedings}\gdef\@journalshort{Proceedings}\gdef\@doiabbr{proceedings}\gdef\@ISSN{2504-3900}}
\DeclareOption{processes}{\gdef\@journal{processes}\gdef\@journalfull{Processes}\gdef\@journalshort{Processes}\gdef\@doiabbr{pr}\gdef\@ISSN{2227-9717}}
\DeclareOption{prosthesis}{\gdef\@journal{prosthesis}\gdef\@journalfull{Prosthesis}\gdef\@journalshort{Prosthesis}\gdef\@doiabbr{prosthesis}\gdef\@ISSN{2673-1592}\gdef\@continuouspages{yes}}
\DeclareOption{proteomes}{\gdef\@journal{proteomes}\gdef\@journalfull{Proteomes}\gdef\@journalshort{Proteomes}\gdef\@doiabbr{proteomes}\gdef\@ISSN{2227-7382}}
\DeclareOption{psf}{\gdef\@journal{psf}\gdef\@journalfull{Physical Sciences Forum}\gdef\@journalshort{Phys. Sci. Forum}\gdef\@doiabbr{psf}\gdef\@ISSN{2673-9984}}
\DeclareOption{psych}{\gdef\@journal{psych}\gdef\@journalfull{Psych}\gdef\@journalshort{Psych}\gdef\@doiabbr{psych}\gdef\@ISSN{2624-8611}\gdef\@continuouspages{yes}}
\DeclareOption{psychiatryint}{\gdef\@journal{psychiatryint}\gdef\@journalfull{Psychiatry International}\gdef\@journalshort{Psychiatry Int.}\gdef\@doiabbr{psychiatryint}\gdef\@ISSN{2673-5318}\gdef\@continuouspages{yes}}
\DeclareOption{psychoactives}{\gdef\@journal{psychoactives}\gdef\@journalfull{Psychoactives}\gdef\@journalshort{Psychoactives}\gdef\@doiabbr{psychoactives}\gdef\@ISSN{2813-1851}\gdef\@continuouspages{yes}}
\DeclareOption{publications}{\gdef\@journal{publications}\gdef\@journalfull{Publications}\gdef\@journalshort{Publications}\gdef\@doiabbr{publications}\gdef\@ISSN{2304-6775}}
\DeclareOption{quantumrep}{\gdef\@journal{quantumrep}\gdef\@journalfull{Quantum Reports}\gdef\@journalshort{Quantum Rep.}\gdef\@doiabbr{quantum}\gdef\@ISSN{2624-960X}\gdef\@continuouspages{yes}}
\DeclareOption{quaternary}{\gdef\@journal{quaternary}\gdef\@journalfull{Quaternary}\gdef\@journalshort{Quaternary}\gdef\@doiabbr{quat}\gdef\@ISSN{2571-550X}}
\DeclareOption{qubs}{\gdef\@journal{qubs}\gdef\@journalfull{Quantum Beam Science}\gdef\@journalshort{Quantum Beam Sci.}\gdef\@doiabbr{qubs}\gdef\@ISSN{2412-382X}}
\DeclareOption{radiation}{\gdef\@journal{radiation}\gdef\@journalfull{Radiation}\gdef\@journalshort{Radiation}\gdef\@doiabbr{radiation}\gdef\@ISSN{2673-592X}\gdef\@continuouspages{yes}}
\DeclareOption{reactions}{\gdef\@journal{reactions}\gdef\@journalfull{Reactions}\gdef\@journalshort{Reactions}\gdef\@doiabbr{reactions}\gdef\@ISSN{2624-781X}\gdef\@continuouspages{yes}}
\DeclareOption{receptors}{\gdef\@journal{receptors}\gdef\@journalfull{Receptors}\gdef\@journalshort{Receptors}\gdef\@doiabbr{receptors}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{recycling}{\gdef\@journal{recycling}\gdef\@journalfull{Recycling}\gdef\@journalshort{Recycling}\gdef\@doiabbr{recycling}\gdef\@ISSN{2313-4321}}
\DeclareOption{regeneration}{\gdef\@journal{regeneration}\gdef\@journalfull{Regeneration}\gdef\@journalshort{Regeneration}\gdef\@doiabbr{regeneration}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{religions}{\gdef\@journal{religions}\gdef\@journalfull{Religions}\gdef\@journalshort{Religions}\gdef\@doiabbr{rel}\gdef\@ISSN{2077-1444}}
\DeclareOption{remotesensing}{\gdef\@journal{remotesensing}\gdef\@journalfull{Remote Sensing}\gdef\@journalshort{Remote Sens.}\gdef\@doiabbr{rs}\gdef\@ISSN{2072-4292}}
\DeclareOption{reports}{\gdef\@journal{reports}\gdef\@journalfull{Reports}\gdef\@journalshort{Reports}\gdef\@doiabbr{reports}\gdef\@ISSN{2571-841X}}
\DeclareOption{reprodmed}{\gdef\@journal{reprodmed}\gdef\@journalfull{Reproductive Medicine}\gdef\@journalshort{Reprod. Med.}\gdef\@doiabbr{reprodmed}\gdef\@ISSN{2673-3897}\gdef\@continuouspages{yes}}
\DeclareOption{resources}{\gdef\@journal{resources}\gdef\@journalfull{Resources}\gdef\@journalshort{Resources}\gdef\@doiabbr{resources}\gdef\@ISSN{2079-9276}}
\DeclareOption{rheumato}{\gdef\@journal{rheumato}\gdef\@journalfull{Rheumato}\gdef\@journalshort{Rheumato}\gdef\@doiabbr{rheumato}\gdef\@ISSN{2674-0621}\gdef\@continuouspages{yes}}
\DeclareOption{risks}{\gdef\@journal{risks}\gdef\@journalfull{Risks}\gdef\@journalshort{Risks}\gdef\@doiabbr{risks}\gdef\@ISSN{2227-9091}}
\DeclareOption{robotics}{\gdef\@journal{robotics}\gdef\@journalfull{Robotics}\gdef\@journalshort{Robotics}\gdef\@doiabbr{robotics}\gdef\@ISSN{2218-6581}}
\DeclareOption{ruminants}{\gdef\@journal{ruminants}\gdef\@journalfull{Ruminants}\gdef\@journalshort{Ruminants}\gdef\@doiabbr{ruminants}\gdef\@ISSN{2673-933X}\gdef\@continuouspages{yes}}
\DeclareOption{safety}{\gdef\@journal{safety}\gdef\@journalfull{Safety}\gdef\@journalshort{Safety}\gdef\@doiabbr{safety}\gdef\@ISSN{2313-576X}}
\DeclareOption{sci}{\gdef\@journal{sci}\gdef\@journalfull{Sci}\gdef\@journalshort{Sci}\gdef\@doiabbr{sci}\gdef\@ISSN{2413-4155}}
\DeclareOption{scipharm}{\gdef\@journal{scipharm}\gdef\@journalfull{Scientia Pharmaceutica}\gdef\@journalshort{Sci. Pharm.}\gdef\@doiabbr{scipharm}\gdef\@ISSN{2218-0532}}
\DeclareOption{seeds}{\gdef\@journal{seeds}\gdef\@journalfull{Seeds}\gdef\@journalshort{Seeds}\gdef\@doiabbr{seeds}\gdef\@ISSN{2674-1024}\gdef\@continuouspages{yes}}
\DeclareOption{sensors}{\gdef\@journal{sensors}\gdef\@journalfull{Sensors}\gdef\@journalshort{Sensors}\gdef\@doiabbr{s}\gdef\@ISSN{1424-8220}}
\DeclareOption{separations}{\gdef\@journal{separations}\gdef\@journalfull{Separations}\gdef\@journalshort{Separations}\gdef\@doiabbr{separations}\gdef\@ISSN{2297-8739}}
\DeclareOption{sexes}{\gdef\@journal{sexes}\gdef\@journalfull{Sexes}\gdef\@journalshort{Sexes}\gdef\@doiabbr{sexes}\gdef\@ISSN{2411-5118}\gdef\@continuouspages{yes}}
\DeclareOption{signals}{\gdef\@journal{signals}\gdef\@journalfull{Signals}\gdef\@journalshort{Signals}\gdef\@doiabbr{signals}\gdef\@ISSN{2624-6120}\gdef\@continuouspages{yes}}
\DeclareOption{sinusitis}{\gdef\@journal{sinusitis}\gdef\@journalfull{Sinusitis}\gdef\@journalshort{Sinusitis}\gdef\@doiabbr{sinusitis}\gdef\@ISSN{2309-107X}\gdef\@continuouspages{yes}}
\DeclareOption{skins}{\gdef\@journal{skins}\gdef\@journalfull{Skins}\gdef\@journalshort{Skins}\gdef\@doiabbr{skins}\gdef\@ISSN{}}
\DeclareOption{smartcities}{\gdef\@journal{smartcities}\gdef\@journalfull{Smart Cities}\gdef\@journalshort{Smart Cities}\gdef\@doiabbr{smartcities}\gdef\@ISSN{2624-6511}\gdef\@continuouspages{yes}}
\DeclareOption{sna}{\gdef\@journal{sna}\gdef\@journalfull{Sinusitis and Asthma}\gdef\@journalshort{Sinusitis Asthma}\gdef\@doiabbr{sna}\gdef\@ISSN{2624-7003}}
\DeclareOption{societies}{\gdef\@journal{societies}\gdef\@journalfull{Societies}\gdef\@journalshort{Societies}\gdef\@doiabbr{soc}\gdef\@ISSN{2075-4698}}
\DeclareOption{socsci}{\gdef\@journal{socsci}\gdef\@journalfull{Social Sciences}\gdef\@journalshort{Soc. Sci.}\gdef\@doiabbr{socsci}\gdef\@ISSN{2076-0760}}
\DeclareOption{software}{\gdef\@journal{software}\gdef\@journalfull{Software}\gdef\@journalshort{Software}\gdef\@doiabbr{software}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{soilsystems}{\gdef\@journal{soilsystems}\gdef\@journalfull{Soil Systems}\gdef\@journalshort{Soil Syst.}\gdef\@doiabbr{soilsystems}\gdef\@ISSN{2571-8789}}
\DeclareOption{solar}{\gdef\@journal{solar}\gdef\@journalfull{Solar}\gdef\@journalshort{Solar}\gdef\@doiabbr{solar}\gdef\@ISSN{2673-9941}\gdef\@continuouspages{yes}}
\DeclareOption{solids}{\gdef\@journal{solids}\gdef\@journalfull{Solids}\gdef\@journalshort{Solids}\gdef\@doiabbr{solids}\gdef\@ISSN{2673-6497}\gdef\@continuouspages{yes}}
\DeclareOption{spectroscj}{\gdef\@journal{spectroscj}\gdef\@journalfull{Spectroscopy Journal}\gdef\@journalshort{Spectrosc. J.}\gdef\@doiabbr{spectroscj}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{sports}{\gdef\@journal{sports}\gdef\@journalfull{Sports}\gdef\@journalshort{Sports}\gdef\@doiabbr{sports}\gdef\@ISSN{2075-4663}}
\DeclareOption{standards}{\gdef\@journal{standards}\gdef\@journalfull{Standards}\gdef\@journalshort{Standards}\gdef\@doiabbr{standards}\gdef\@ISSN{2305-6703}\gdef\@continuouspages{yes}}
\DeclareOption{stats}{\gdef\@journal{stats}\gdef\@journalfull{Stats}\gdef\@journalshort{Stats}\gdef\@doiabbr{stats}\gdef\@ISSN{2571-905X}\gdef\@continuouspages{yes}}
\DeclareOption{std}{\gdef\@journal{std}\gdef\@journalfull{Surgical Techniques Development}\gdef\@journalshort{Surg. Tech. Dev.}\gdef\@doiabbr{std}\gdef\@ISSN{2038-9582}\gdef\@continuouspages{yes}}
\DeclareOption{stresses}{\gdef\@journal{stresses}\gdef\@journalfull{Stresses}\gdef\@journalshort{Stresses}\gdef\@doiabbr{stresses}\gdef\@ISSN{2673-7140}\gdef\@continuouspages{yes}}
\DeclareOption{surfaces}{\gdef\@journal{surfaces}\gdef\@journalfull{Surfaces}\gdef\@journalshort{Surfaces}\gdef\@doiabbr{surfaces}\gdef\@ISSN{2571-9637}\gdef\@continuouspages{yes}}
\DeclareOption{surgeries}{\gdef\@journal{surgeries}\gdef\@journalfull{Surgeries}\gdef\@journalshort{Surgeries}\gdef\@doiabbr{surgeries}\gdef\@ISSN{2017-2017}\gdef\@continuouspages{yes}}
\DeclareOption{suschem}{\gdef\@journal{suschem}\gdef\@journalfull{Sustainable Chemistry}\gdef\@journalshort{Sustain. Chem.}\gdef\@doiabbr{suschem}\gdef\@ISSN{2673-4079}\gdef\@continuouspages{yes}}
\DeclareOption{sustainability}{\gdef\@journal{sustainability}\gdef\@journalfull{Sustainability}\gdef\@journalshort{Sustainability}\gdef\@doiabbr{su}\gdef\@ISSN{2071-1050}}
\DeclareOption{symmetry}{\gdef\@journal{symmetry}\gdef\@journalfull{Symmetry}\gdef\@journalshort{Symmetry}\gdef\@doiabbr{sym}\gdef\@ISSN{2073-8994}}
\DeclareOption{synbio}{\gdef\@journal{synbio}\gdef\@journalfull{Synbio}\gdef\@journalshort{Synbio}\gdef\@doiabbr{synbio}\gdef\@ISSN{2674-0583}\gdef\@continuouspages{yes}}
\DeclareOption{systems}{\gdef\@journal{systems}\gdef\@journalfull{Systems}\gdef\@journalshort{Systems}\gdef\@doiabbr{systems}\gdef\@ISSN{2079-8954}}
\DeclareOption{taxonomy}{\gdef\@journal{taxonomy}\gdef\@journalfull{Taxonomy}\gdef\@journalshort{Taxonomy}\gdef\@doiabbr{taxonomy}\gdef\@ISSN{2673-6500}\gdef\@continuouspages{yes}}
\DeclareOption{technologies}{\gdef\@journal{technologies}\gdef\@journalfull{Technologies}\gdef\@journalshort{Technologies}\gdef\@doiabbr{technologies}\gdef\@ISSN{2227-7080}}
\DeclareOption{telecom}{\gdef\@journal{telecom}\gdef\@journalfull{Telecom}\gdef\@journalshort{Telecom}\gdef\@doiabbr{telecom}\gdef\@ISSN{2673-4001}\gdef\@continuouspages{yes}}
\DeclareOption{test}{\gdef\@journal{test}\gdef\@journalfull{Test}\gdef\@journalshort{Test}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{textiles}{\gdef\@journal{textiles}\gdef\@journalfull{Textiles}\gdef\@journalshort{Textiles}\gdef\@doiabbr{textiles}\gdef\@ISSN{2673-7248}\gdef\@continuouspages{yes}}
\DeclareOption{thalassrep}{\gdef\@journal{thalassrep}\gdef\@journalfull{Thalassemia Reports}\gdef\@journalshort{Thalass. Rep.}\gdef\@doiabbr{thalassrep}\gdef\@ISSN{2039-4365}\gdef\@continuouspages{yes}}
\DeclareOption{thermo}{\gdef\@journal{thermo}\gdef\@journalfull{Thermo}\gdef\@journalshort{Thermo}\gdef\@doiabbr{thermo}\gdef\@ISSN{2673-7264}\gdef\@continuouspages{yes}}
\DeclareOption{tomography}{\gdef\@journal{tomography}\gdef\@journalfull{Tomography}\gdef\@journalshort{Tomography}\gdef\@doiabbr{tomography}\gdef\@ISSN{2379-139X}\gdef\@continuouspages{yes}}
\DeclareOption{tourismhosp}{\gdef\@journal{tourismhosp}\gdef\@journalfull{Tourism and Hospitality}\gdef\@journalshort{Tour. Hosp.}\gdef\@doiabbr{tourhosp}\gdef\@ISSN{2673-5768}\gdef\@continuouspages{yes}}
\DeclareOption{toxics}{\gdef\@journal{toxics}\gdef\@journalfull{Toxics}\gdef\@journalshort{Toxics}\gdef\@doiabbr{toxics}\gdef\@ISSN{2305-6304}}
\DeclareOption{toxins}{\gdef\@journal{toxins}\gdef\@journalfull{Toxins}\gdef\@journalshort{Toxins}\gdef\@doiabbr{toxins}\gdef\@ISSN{2072-6651}}
\DeclareOption{transplantology}{\gdef\@journal{transplantology}\gdef\@journalfull{Transplantology}\gdef\@journalshort{Transplantology}\gdef\@doiabbr{transplantology}\gdef\@ISSN{2673-3943}\gdef\@continuouspages{yes}}
\DeclareOption{transportation}{\gdef\@journal{transportation}\gdef\@journalfull{Transportation}\gdef\@journalshort{Transportation}\gdef\@doiabbr{transportation}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{traumacare}{\gdef\@journal{traumacare}\gdef\@journalfull{Trauma Care}\gdef\@journalshort{Trauma Care}\gdef\@doiabbr{traumacare}\gdef\@ISSN{2673-866X}\gdef\@continuouspages{yes}}
\DeclareOption{traumas}{\gdef\@journal{traumas}\gdef\@journalfull{Traumas}\gdef\@journalshort{Traumas}\gdef\@doiabbr{traumas}\gdef\@ISSN{2673-7477}\gdef\@continuouspages{yes}}
\DeclareOption{tropicalmed}{\gdef\@journal{tropicalmed}\gdef\@journalfull{Tropical Medicine and Infectious Disease}\gdef\@journalshort{Trop. Med. Infect. Dis.}\gdef\@doiabbr{tropicalmed}\gdef\@ISSN{2414-6366}}
\DeclareOption{universe}{\gdef\@journal{universe}\gdef\@journalfull{Universe}\gdef\@journalshort{Universe}\gdef\@doiabbr{universe}\gdef\@ISSN{2218-1997}}
\DeclareOption{urbansci}{\gdef\@journal{urbansci}\gdef\@journalfull{Urban Science}\gdef\@journalshort{Urban Sci.}\gdef\@doiabbr{urbansci}\gdef\@ISSN{2413-8851}}
\DeclareOption{uro}{\gdef\@journal{uro}\gdef\@journalfull{Uro}\gdef\@journalshort{Uro}\gdef\@doiabbr{uro}\gdef\@ISSN{2673-4397}\gdef\@continuouspages{yes}}
\DeclareOption{vaccines}{\gdef\@journal{vaccines}\gdef\@journalfull{Vaccines}\gdef\@journalshort{Vaccines}\gdef\@doiabbr{vaccines}\gdef\@ISSN{2076-393X}}
\DeclareOption{vehicles}{\gdef\@journal{vehicles}\gdef\@journalfull{Vehicles}\gdef\@journalshort{Vehicles}\gdef\@doiabbr{vehicles}\gdef\@ISSN{2624-8921}\gdef\@continuouspages{yes}}
\DeclareOption{venereology}{\gdef\@journal{venereology}\gdef\@journalfull{Venereology}\gdef\@journalshort{Venereology}\gdef\@doiabbr{venereology}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{vetsci}{\gdef\@journal{vetsci}\gdef\@journalfull{Veterinary Sciences}\gdef\@journalshort{Vet. Sci.}\gdef\@doiabbr{vetsci}\gdef\@ISSN{2306-7381}}
\DeclareOption{vibration}{\gdef\@journal{vibration}\gdef\@journalfull{Vibration}\gdef\@journalshort{Vibration}\gdef\@doiabbr{vibration}\gdef\@ISSN{2571-631X}\gdef\@continuouspages{yes}}
\DeclareOption{virtualworlds}{\gdef\@journal{virtualworlds}\gdef\@journalfull{Virtual Worlds}\gdef\@journalshort{Virtual Worlds}\gdef\@doiabbr{virtualworlds}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{viruses}{\gdef\@journal{viruses}\gdef\@journalfull{Viruses}\gdef\@journalshort{Viruses}\gdef\@doiabbr{v}\gdef\@ISSN{1999-4915}}
\DeclareOption{vision}{\gdef\@journal{vision}\gdef\@journalfull{Vision}\gdef\@journalshort{Vision}\gdef\@doiabbr{vision}\gdef\@ISSN{2411-5150}}
\DeclareOption{waste}{\gdef\@journal{waste}\gdef\@journalfull{Waste}\gdef\@journalshort{Waste}\gdef\@doiabbr{waste}\gdef\@ISSN{2813-0391}\gdef\@continuouspages{yes}}
\DeclareOption{water}{\gdef\@journal{water}\gdef\@journalfull{Water}\gdef\@journalshort{Water}\gdef\@doiabbr{w}\gdef\@ISSN{2073-4441}}
\DeclareOption{wem}{\gdef\@journal{wem}\gdef\@journalfull{Wildlife Ecology and Management}\gdef\@journalshort{Wildl. Ecol. Manag.}\gdef\@doiabbr{}\gdef\@ISSN{1234-4321}}
\DeclareOption{wevj}{\gdef\@journal{wevj}\gdef\@journalfull{World Electric Vehicle Journal}\gdef\@journalshort{World Electr. Veh. J.}\gdef\@doiabbr{wevj}\gdef\@ISSN{2032-6653}}
\DeclareOption{wind}{\gdef\@journal{wind}\gdef\@journalfull{Wind}\gdef\@journalshort{Wind}\gdef\@doiabbr{wind}\gdef\@ISSN{2674-032X}\gdef\@continuouspages{yes}}
\DeclareOption{women}{\gdef\@journal{women}\gdef\@journalfull{Women}\gdef\@journalshort{Women}\gdef\@doiabbr{women}\gdef\@ISSN{2673-4184}\gdef\@continuouspages{yes}}
\DeclareOption{world}{\gdef\@journal{world}\gdef\@journalfull{World}\gdef\@journalshort{World}\gdef\@doiabbr{world}\gdef\@ISSN{2673-4060}\gdef\@continuouspages{yes}}
\DeclareOption{youth}{\gdef\@journal{youth}\gdef\@journalfull{Youth}\gdef\@journalshort{Youth}\gdef\@doiabbr{youth}\gdef\@ISSN{2673-995X}\gdef\@continuouspages{yes}}
\DeclareOption{zoonoticdis}{\gdef\@journal{zoonoticdis}\gdef\@journalfull{Zoonotic Diseases}\gdef\@journalshort{Zoonotic Dis.}\gdef\@doiabbr{zoonoticdis}\gdef\@ISSN{2813-0227}\gdef\@continuouspages{yes}}

### 2022-09-29 MDPI/sensors-1915564-redo - For Proof/sensors-1915564.tex
Update Paper Proof Reading

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[sensors,article,accept,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
\externaleditor{Academic Editor: {Ahmed Bouridane} %MDPI: Please add academic editor if available.
}
\datereceived{30 August 2022} 
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{23 September 2022} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{makecell}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{soulutf8}
\usepackage[adjustmargins]{LatexPackage/trackchanges}
\addeditor{H.K.D}

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Skin Lesion Classification on Imbalanced Data Using Deep Learning with Soft Attention}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Skin Lesion Classification on Imbalanced Data Using Deep Learning with Soft Attention}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7152-0191} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0001-9934-7474} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-2566-5637} % Add \orcidC{} behind the author's name

% Authors, for the paper (add full first names)
\Author{\hl{Viet} %MDPI: Please carefully check the accuracy of names and affiliations.
 Dung Nguyen $^{1,\dagger,}$*\orcidA{}, Ngoc Dung Bui $^{2,}$\hl{*} %MDPI: The correspondence author is different from the submitting system. Please confirm which one is correct.
\orcidB{} and Hoang Khoi Do  $^{1,\dagger}$\orcidC{}}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Viet Dung Nguyen, Ngoc Dung Bui, and Hoang Khoi Do}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Nguyen, V.D.; Bui, N.D.; Do, H.K.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)

\address{$^{1}$ \quad \hl{School} %MDPI: we combined the same affiliation 1 and 3, please confirm.
 of Electrical and Electronic Engineering, Hanoi University of Science and Technology, \hl{Vietnam;} %MDPI: Please add the city and post code.
\hl{ khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct.
\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, \hl{Vietnam} %MDPI: Please add the city and post code.
}

% Contact information of the corresponding author
\corres{Correspondences: dung.nguyenviet1@hust.edu.vn (V.D.N.); dnbui@utc.edu.vn (N.D.B.); \mbox{Tel.: +84-9834-443-22 (N.V.D.);} +84-9130-451-30 (N.D.B.)}

% Current address and/or shared authorship
\firstnote{Current address: 1st Dai Co Viet Street, \hl{Ha Noi, 100000, } %MDPI: 1. Please add the postal code. If the postal code is not available, please provide the P.O. Box. 2. If this address is the supplementary of address 1, then please combine them together. 
%H.K.D We have already provied the postal code
 Vietnam.} 
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience, and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of one Deep Learning model (DenseNet, InceptionNet, ResNet, etc) with Soft-Attention, which unsupervisedly extract a heat map of main skin lesions. Furthermore, personal information including age and gender are also used. It is worth noting that a new loss function that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and the new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.99, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and the new loss function, even though the number of parameters is 11~times less and the number of hidden layers is 4 times less, it achieves an accuracy of 0.86 and 30 times faster diagnosis than InceptionResNetV2.}

% Keywords
\keyword{\highlighting{skin lesions;} %MDPI: We removed the uppercase of some keywords, please confirm  
classification; deep learning; soft-attention; imbalance} 
% Confirmed, we also removed the duplicated "skin lesions"

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\setcounter{section}{0} %% Remove this when starting to work on the template.
	\begin{comment}
		\section{How to Use this Template}

		The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.

		% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
	\end{comment}

	\section{Introduction} 
	\subsection{Problem Statement}
%	\change[H.K.D]{One of the most common malignancies that cause death globally is skin cancer. In the United States, more than 9500 persons receive a skin cancer diagnosis each day~\mbox{\cite{03358}}. The Skin Cancer Foundation reports that there is an ongoing rise in the incidence of skin cancer worldwide~\mbox{\cite{11872}}. In the United States, 192,310 new cases of melanoma are anticipated to be detected in 2019. On the other hand, if patients receive an early diagnosis, their chances of survival are 99 percent. Survival is, however, generally poor after the illness has spread beyond the skin~\mbox{\cite{11872}}. Additionally, there is a need for an efficient solution because of the rising prevalence of skin malignancies, low awareness among a population that is expanding, and a lack of sufficient clinical competence and services.}
	{Skin cancer is one of the most common cancers leading to worldwide death. \hl{Every day, more than 9500~\mbox{\cite{03358}} }%MDPI: We adjust the number of cited reference, please check the cited reference again.
	people in the United States are diagnosed with skin cancer. Otherwise, 3.6~\mbox{\cite{03358}} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase~\mbox{\cite{11872}}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States~\mbox{\cite{11872}}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent. However, once the disease progresses beyond the skin, survival is poor~\mbox{\cite{11872}}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solutions.}

	Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD)\cite{11797} has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to build solutions to a specific disease; medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions to the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging \cite{11872}.

	To adapt the rise in skin cancer cases, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet~\cite{04861}, Inception \cite{00567}\hl{\mbox{\cite{07261}}}, MobileNets\cite{04861,04381,02244}, \hl{Xception\mbox{\cite{02357}}}, ResNet \cite{03385,05027}, and NasNet \cite{07012}. Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.

	\subsection{Related Works}
%	\change[H.K.D]{Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in~\mbox{\cite{03358}}. Soumyyak~et~al. construct several models formed by the combination of a backbone model including DenseNet201~\mbox{\cite{06993}}, InceptionResNetV2~\mbox{\cite{00567}}, ResNet50~\mbox{\cite{03385,05027}}, VGG16~\mbox{\cite{1556}} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then the soft-max layer.

%		Using those above backbones has been tried by many previous papers. Rishu\linebreak Garg~et~al.~\mbox{\cite{03798}} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set. Besides, they also use data augmentation to avoid the imbalance of the data set. Histogram Equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, Support Vector Machine.

%		Amirreaza~et~al.~\mbox{\cite{10348}} do not only use those above backbone model but also used InceptionV3~\mbox{\cite{00567}} model. In that research, the dataset HAM10000 and $PH^2$ are combined to create a 8 classes data set. Before feeding into the Deep CNN models, the image is resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2 and (229, 229) for InceptionV3.

%		Another paper that uses the backbone models is~\mbox{\cite{09418}}, Hemanth~et~al. decide to use EfficientNet~\mbox{\cite{11946}} and SeNET~\mbox{\cite{01507}} instead and CutOut~\mbox{\cite{04552v2}} method which involves creating holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process.

%		Otherwise, Ref.~\mbox{\cite{01284}} also used Deep Convolution Neural Network, Peng Yao~et~al. used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost.

%		Another state of the art is GradCam and Kernel SHAP~\mbox{\cite{06612}}, Kyle Young~et~al. create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research they use three data sets containing HAM10000, BCN-20000 and MSK. Before feeding into the models, the images are preprocessed by binarized with a very low threshold to find the center of mass.

%		On the other hand, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021~\mbox{\cite{03225}}, which is created by Xiaohan Xing~et~al. as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others~learn.

%		SkinLinkNet~\mbox{\cite{12602}} and WonderM~\mbox{\cite{03426}} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza~et~al. and Yeong Chan~et~al., respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450, 600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively.

%		Another approach is using metadata including gender, age, and capturing position as stated in~\mbox{\cite{03910}} by Nil Gessert~et~al. The metadata is fed into fully connected neural network after being encoded into one-hot vector. All missing data point of age is set to 0. To overcome the missing data problem, the research apply one-hot encoding to the group but the initial validation is poor performance then numerical encoding is applied.

%		On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by~\mbox{\cite{03798}} of Rishu Garg~et~al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out-of-distribution skin lesion images as stated in~\mbox{\cite{10348}} by Amirreza Rezvantalab~et~al. Matrix Transformation, besides is also applied before the soft-max activation function in~\mbox{\cite{05045}} by Michele Alberti~et~al. }

	{Skin lesion classification is not a new area, since there are many great performance models constructed, recent years. The skin classification approaches can be divided into two main approaches: Deep Learning and Machine Learning. Both approaches gain great performance. Data Augmentation and Feature Extractor, otherwise are two main supporters that make the model better.
		\begin{table}[H]
\caption{\hl{Related} %MDPI: we updated the format of all tables, please confirm the change. Please cite the table in the text and ensure the first citation of each table appears in numerical order.
 Works Summary.}
\label{table:related-work-summary}

\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering
\centering
\begin{tabular}{ c  p{1.8cm}  p{1.8cm}  p{2.55cm}  p{1.5cm}  p{5cm}  p{2cm} }
	\toprule
	\textbf{Work} & \textbf{Deep Learning} & \textbf{Machine Learning} & \textbf{Data\linebreak Augmentation} & \textbf{Feature Extractor} & \textbf{Data Set} & \textbf{Result}\\
	\midrule
	\cite{03358} & Classify & & x & & HAM10000 & 0.93 (ACC)\\
	\midrule
	\cite{03798} & Classify & Classify & x & x & HAM10000 & 0.9 (ACC)\\
	\midrule
	\cite{10348} & Classify & Classify & x & & HAM10000, $PH^2$ & \\
	\midrule
	\cite{09418} & Classify & & x & & HAM10000 & 0.88 (ACC)\\
	\midrule
	\cite{01284} & Classify & & x & & HAM10000 & 0.86 (ACC)\\
	\midrule
	\cite{06612} & Classify & & x & x & HAM10000, BCN-20000, MSK & 0.85 (ACC)\\
	\midrule
	\cite{03225} & Classify & & x & & HAM10000 & 0.85 (ACC)\\
	\midrule
	\cite{12602} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
	\midrule
	\cite{03426} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
	\midrule
	\cite{03910} & Classify & & x & & HAM10000 & 0.74 (recall)\\
	\midrule
	\cite{05045} & & Classify & x & x & HAM10000 & \\
	\midrule
	\cite{2101.133} & Classify&  & x &  & HAM10000 & 0.92 (ACC)\\
	\midrule
	\cite{22750} & Seg&  &  &  & HAM10000 & 0.99 (ACC)\\
	\midrule
	\cite{9445180} & Seg &  &  &  & HAM10000 & 0.97 (ACC)\\
	\bottomrule
\end{tabular}
\end{adjustwidth}
		\end{table}
		\subsubsection{Deep Learning Approach}
		In Deep Learning, one of the most cutting-edge technologies  used is Soft-Attention, as stated in~\mbox{\cite{03358}}. Soumyyak~et~al. constructed several models formed by a combination of a backbone model including DenseNet201~\mbox{\cite{06993}}, InceptionResNetV2~\mbox{\cite{00567}}, ResNet50~\mbox{\cite{03385,05027}}, VGG16~\mbox{\cite{1556}} and Soft-Attention layer. Their approach adds the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2 then concatenate with  Soft-Attention before a fully-connected layer and then soft-max layer. Soumyyak~et~al.'s proposed method gained great performances and also outperformed many other studies with an accuracy of 0.93 and a precision of 0.92. However, using  data augmentation on an imbalanced dataset resulted in subpar classification  classify with respect to the  classes; therefore, their model obtained a  recall and f1-score of 0.71 and 0.75, respectively. In this research, our proposed method also considers this problem and solves it.

		Using the above-mentioned backbones has been attempted previously. Rishu Garg~et~al.~\mbox{\cite{03798}} used a transfer learning approach with a CNN-based model: ResNet50 and VGG1,6 which are pretrained with an ImageNet data set. In addition, they also use data augmentation to avoid an imbalance occuring in  the dataset. Histogram equalization is also used to increase the contrast of  skin lesions before being fed into machine learning algorithms including Random Forest, XGBoost, and Support Vector Machine.	Histogram equalization can be considered as a heat map that takes the main feature as the number of occurrences of the same value pixel. This approach also gain great performances with an accuracy of 0.90 and  precision of 0.88. However, this approach can be biased since only one skin image of the dataset contains the skin lesion at the center and the background skin, and the histogram may treat the background with increased numbers of occurrence with respect to the same pixel value. In this research study, our proposed method used  Soft-Attention, which can create a heat map feature of the lesion. Otherwise, Rishu Garg~et~al.'s proposed method also faced the problem of imbalanced classification due to an imbalanced dataset with the f1-score and recall at 0.77 and 0.74, respectively.

		Instead of using the entire imbalanced data set, Abayomi-alli~et~al. decided to separate the dataset into two subsets: one contains only melanoma and the other one contains the rest~\mbox{\cite{2101.133}}. Before feeding the data to classify  melanoma, training data are then augmented by the SMOTE method. SMOTE creates artificial instances by oversampling the minority class. SMOTE recognizes k-minority class neighbors that are near  each minority class sample by using the covariance matrix. This approach obtained an accuracy, recall, and f1-score of 0.92, 0.87, and 0.82, respectively.

		Amirreaza~et~al.~\mbox{\cite{10348}} did not only use the backbone model mentioned above but also used the InceptionV3~\mbox{\cite{00567}} model. In this research study,  datasets HAM10000 and $PH^2$ are combined to create an eight-class dataset. Before being fed into  Deep CNN models, the image was resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2, and (229, 229) for InceptionV3. The best ROC AUC values for melanoma and basal cell carcinoma are 0.94 (ResNet152) and 0.93 (DenseNet201).

		Another paper that uses  backbone models is~\mbox{\cite{09418}},  in which Hemanth~et~al. decided to use EfficientNet~\mbox{\cite{11946}} and SeNET~\mbox{\cite{01507}} instead and the CutOut~\mbox{\cite{04552v2}} method, which involves creating holes of different sizes on  images, i.e., technically making a random portion of image inactive during the data augmentation process. Although this approach obtained an accuracy of 0.88, it may be biased due to the CutOut method since this method can create a hole overlap in the skin lesion field. The method's accuracy is also low due to the data-augmentation process.

		Otherwise, Ref.~\mbox{\cite{01284}} also used a Deep Convolution Neural Network, and Peng Yao~et~al. used RandArgument, which crops an image into several images from a fixed size; DropBlock, which is used for regularization, Multi-Weighted New Loss, which is used for dealing with the imbalanced data problem; end-to-end Cumulative Learning Strategy, which can more effectively balance representation learning; and classifier learning, without additional computational costs. This approach obtained an accuracy of 0.86. Although this approach figureed out the data imbalance problem, the result of obtaining a low accuracy may due to  RandArgument. If the skin lesion part of the image is quite big or  small, the cropped image may only contain  skin or the lesion is spread out in the entire image.

		\hl{Another state-of-the-art method is GradCam and Kernel SHAP~\mbox{\cite{06612}}. Kyle Young~et~al. created an agnostic model, which includes local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification. In that research study, they used three datasets containing HAM10000, BCN-20000, and MSK. Before feeding into the models,  images are preprocessed by binarization with a very low threshold to find the center of mass. This approach obtained an  AUC score of 0.85.} %Please check if meaning is retained. %H.K.D Fine

		On the other hand, there are also many state-of-the-art methods with great performance on skin lesion classification. The Student-and-Teacher Model is also a high-performance model introduced in 2021~\mbox{\cite{03225}}, and it is created by Xiaohan Xing~et~al. as a combination of two models that share  memories with the other model. Therefore, the models can take full advantage of what others learn. The Student-and-Teacher model obtained an accuracy of 0.85; however, the precision and f1-score are quite low, resulting in a value of 0.76.

		SkinLinkNet~\mbox{\cite{12602}} and WonderM~\mbox{\cite{03426}} are both tested the effect of segmentation on skin lesion classification problems created by Amirreza~et~al. and Yeong Chan~et~al., respectively. In WonderM, the method used is to pad the image so that the image has an increase in shape  from (450, 600) to (600, 600). In SkinLinkNet,  the image is instead resized down to (448, 448). Both  SkinLinkNet and WonderM used UNet to perform the segmentation task, although they used EfficientNetB0 and DenseNet to perform the classification task. This approach obtained an AUC score of 0.92.

		Another approach is to use metadata, including gender, age, and capturing positions, as stated in~\mbox{\cite{03910}} by Nil Gessert~et~al.  Metadata are fed into a fully connected neural network after  encoded into a one-hot vector. All missing data points with respect to age are set to 0. To overcome the missing data problem, the research study applied one-hot encoding to the group, but the initial validation resulted in poor performance then when numerical encoding was applied. The metadata are then fed into two block networks, each one containing a Dense Layer, Batch Normalization, am ReLU activation function, and a Dropout. After all the feature vectors were extracted, the image was then concatenated with the feature vector extracted from metadata. Otherwise,  data augmentation was also applied. This approach obtained a  recall score of 0.74. The low recall score may be due to the imbalanced data set.

		Abnormal, skin lesion segmentation, on the other hand, also plays an important role in skin lesion classification. Nawaz~et~al. created a framework for Melanoma segmentation~\mbox{\cite{22750}}. Their proposed method is a Unet model but used  densenet77 as the  backbone, and all residual blocks were changed into dense block, which contains a sequence of Convolution and  Average Pooling. This melanoma segmentation approach obtain an accuracy of 0.99. Kadry~et~al. used a Unet model with a VGG deep convolution layer by pooling on the skip connection. This approach can completely extract the entire lesion, although there was an overlap observed with hair. This approach obtained an  accuracy of 0.97.

		\subsubsection{Machine Learning Approach}
		In Machine Learning, there are also many approaches. Since the image's data are quite complex for machine learning algorithms,  using feature extractors or feature preprocessing for transformation to another form of data is recommended.

		Random Forest, XGBoost, and Support Vector Machines are tested by~\mbox{\cite{03798}} of Rishu Garg~et~al. In this approach, the data are fed directly into the Machine Learning algorithm and shows no promising results; therefore, Rishu Garg~et~al. did not show the results of the used machine learning algorithm.

		In addition, Deep Isolation Forest is applied before the soft-max activation of the deep learning model to detect the  distribution of skin lesion images, as stated in~\mbox{\cite{09365}} by Amirreza Rezvantalab~et~al. In the Deep Isolation Forest, an feature extractor is applied by using CNN to learn the main pattern of the image. After that, the feature map is then fed into K isolation forest estimators by using bagging algorithms. The Deep Isolation Forest obtained  an accuracy of 0.9 and a confidence of 0.86. However, the AUC score is only 0.74, and this may due to the limitation of the machine learning algorithm.

		Matrix transformation is also applied before the soft-max activation function in~\mbox{\cite{05045}} by Michele Alberti~et~al. In this approach, the image is fed into a general model by using a sequence of residual block. The feature maps created from those above the residual block is then fed into  Global Average Pooling to create a feature vector. This feature vector is then extracted by CNN-1D and transformed by Discrete Fourier Transformation (DFT) as a filter before proceeding to the soft-max layer. 
	}

	\subsection{Proposed Method}
	In this research, a new model is constructed from the combination of:

	\begin{itemize}
	\item[-] Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3;
	\item[-] Using metadata including age, gender, localization as another input of the model;
	\item[-] Using Soft-Attention as a feature extractor of the model;
	\item[-] A new weight loss function.
	\end{itemize}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Materials and Methods}
	\subsection{Materials}
	\subsubsection{Image Data}
	The data set used in this paper is the HAM10000 data set published by the Havard University Dataverse \cite{10417}. There are a total of 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), basal cell carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the Table \ref{table:data-distribution} below:

	\begin{table}[H]
		\caption{Data Distribution in HAM10000.}
		\label{table:data-distribution}
		\setlength{\tabcolsep}{3.05mm}\begin{tabular}{c c c c c c c c c} 
\toprule
\textbf{Class} & \textbf{AKIEC} & \textbf{BCC} & \textbf{BKL} & \textbf{DF} & \textbf{MEL} & \textbf{NV} & \textbf{VASC} & \textbf{Total} \\ 
\midrule
No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10,015 \\
\bottomrule
		\end{tabular}
	\end{table}

	More than 50\% of lesions are confirmed through histopathology (HISTO); the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in vivo confocal microscopy (CONFOCAL). On the other hand, before being used for training, the whole data are shuffled and then split into two parts. Here, $90$\% and $10$\% of the data is used for training and validating respectively. Images \hl{(See Figure \mbox{\ref{fig:data-sample}})} in this data set have the type of $RGB$ and shape of (450, 600). However, each backbone needs the different input sizes of images as well as the range of pixel value.
	\begin{figure}[H]
		\includegraphics[width=1\linewidth]{Definitions/DataDistribution}
		\caption{\hl{Example} %MDPI: 1. Please cite the figure in the text and ensure the first citation of each figure appears in numerical order. 2. Please confirm if the vertical line is necessary, if not, please remove it.
		% H.K.D We have provied the citation to the Figure 1 and feel the current version of vertical line quite great
 image of each class.}
		\label{fig:data-sample}
	\end{figure}

	\subsubsection{Metadata}
	The HAM10000 data set \cite{10417} also contains the metadata of each patient including gender, age, and the capturing position, as illustrated in Table \ref{table:metadata sample}.
	\begin{table}[H]
		\caption{\hl{Metadata}  example in the data set.}%MDPI: We remove the vertical line, please confirm. % H.K.D Confirm
		\label{table:metadata sample}
		\setlength{\tabcolsep}{11.8mm}\begin{tabular}{c c c c } 
\toprule
\textbf{ID} & \textbf{Age} & \textbf{Gender} & \textbf{Local}\\ 
\midrule
ISIC-00001 & 15 & Male & back\\
\midrule
ISIC-00002 & 85 & Female & elbow\\
\bottomrule
		\end{tabular}
	\end{table}
	\subsection{Methodology}
	\subsubsection{Overall Architecture}
	The whole architecture of the model is represented in the Figure \ref{fig:main-model}. The model takes two inputs including Image data and Metadata. The metadata branch otherwise is preprocessed before feeding into a dense layer; then, it concatenates with the output of the Soft-Attention~layer.

	\begin{figure}[H]
		\includegraphics[width=0.8\linewidth]{Definitions/MainModel - Model Form}
		\caption{Overall Model Architecture.}
		\label{fig:main-model}
	\end{figure}

	Figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research. In detail, the combination of DenseNet201 and Soft-Attention is formed by replacing the three last (DenseBlock, Global Average Pooling, and the fully connected layer) with the Soft-Attention Module. Similarly, ResNet50 and ResNet152 also replaced the last three (Residual Block, Global Average Pooling, and the fully connected layer) with the Soft-Attention module. InceptionResNetV2, on the other hand, replaces the average pool and the last dropout with the Soft-Attention Module. The last two, Normal Cell in NasNetLarge is replaced with the Soft-Attention module.

	\begin{figure}[H]
		\includegraphics[width=0.7\linewidth]{Definitions/Model Structure}
		\caption{\hl{Overall Original} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) % H.K.D confirm
 Model Architecture. This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed structure model}.}
		\label{fig:model-structure}
	\end{figure}

	Figure \ref{fig:mobile-model-structure}, on the other hand, shows the detailed structure of the mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution layers 1 \hl{$\times$} %MDPI: We revised the "x" into a multiplication sign ("\times" U+00D7). Please confirm.
 1 with the Soft-Attention module. The NasNetMobile, otherwise, combines with the Soft-Attention module by replacing the last normal cell. 
	\begin{figure}[H]
		\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
		\caption{\hl{Overall mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) H.K.D confirm
 model architecture. This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed mobile model structure}.}
		\label{fig:mobile-model-structure}
	\end{figure}

	\subsubsection{Input Schema}
	{Image preprocessing is an essential part of the training process because of its ability to extract the main pattern of an image. In this stage, the image can be changed to the other color channel so that the main feature is separated from the useless part. Image Retrieval  has significantly created a vector that represents the main feature of an image. These image retrieval techniques can include energy compaction, primitive pattern units, etc. Shervan Fekri-Ershad~et~al. created a feature vector by calculating the element-wise product of the histogram vector in each channel of an image~\mbox{\cite{2012.4305}}}. Then, by comparing the Euclidean distance between this feature vector and the average feature vector of the entire dataset with a thresh hold, they can extract the skin portion of the image.

	In this research, the image data are both augmented for all classes, the number of images increases to 18,015 images , and it keeps the original form. Before feeding into the backbone model, the images are pre-processed by the input requirement of each model. DenseNet201 \cite{06993} requires the input pixels values to be scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152 \cite{03385,05027}, the images are converted from $RGB$ to $BGR$; then, each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2~\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet \cite{04861,04381,02244}, NasNetMobile and NasNetLarge \cite{07012} require the input pixel is in range of $-1$ and $1$.

	On the other hand, the metadata are also used as another input. In the research \cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorically encoded. The age, on the other hand, is numerically normalized. After processing, the metadata are fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU \cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simple data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

	In this research, the unknowns are kept as a type as discussed in the Metadata section. Sex, anatomical site, and age are also category encoded and numerically normalized, respectively. After processing, the metadata are then concatenated and fed into a dense layer of 4096 neurons. Finally, this dense layer is then concatenated with the output of Soft-Attention which is then discussed in the Soft-Attention section. The Input schema is described in \hl{Figure} %MDPI: We changed Table to Figure. Please confirm this revision. 
	%H.K.D Great
 \ref{fig:input-schema}.

	\begin{figure}[H]
		\includegraphics[width=1\linewidth]{"Definitions/Input Schema"}
		\caption{Input Schema.}
		\label{fig:input-schema}
	\end{figure}

	\subsubsection{Backbone Model}
	In this paper, the backbone models used in this paper are DenseNet201 \cite{06993}, Inception~\cite{00567}, MobileNets \cite{04861,04381,02244}, ResNet \cite{03385,05027}, and NasNet \cite{07012}. The combination of DenseNet201, InceptionResNetV2, and the Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance. Otherwise, Resnet50 also well classifies but with much fewer number of parameters and less depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge models, which have more parameters and depth, is analyzed. On the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed, which has fewer parameters \hl{(see Figure \mbox{\ref{table:model-summary}})} and depth.

	\begin{table}[H]
		\caption{\hl{Size} %MDPI: 1. Please cite the table in the text and ensure the first citation of each table appears in numerical order. 2. We remove the vertical line, please confirm.
 , parameters, and depth of the backbone model used in this paper.}
		\label{table:model-summary}
		\setlength{\tabcolsep}{5.2mm}\begin{tabular}{l  c c c} 
\toprule
\textbf{Model} & \textbf{Size (MB)} & \textbf{No. Trainable Parameters} & \textbf{Depth} \\ 
\midrule
Resnet50 & 98 & 25,583,592 & 107 \\ 
\midrule
Resnet152 & 232 & 60,268,520 & 311 \\ 
\midrule
DenseNet201 & 80 & 20,013,928 & 402 \\
\midrule
InceptionResNetV2 & 215 & 55,813,192 & 449 \\
\midrule
MobileNetV2 & 14 & 3,504,872 & 105 \\ 
\midrule
MobileNetV3Small & Unknown & 2,542,856 & 88 \\ 
\midrule
MobileNetV3Large & Unknown & 5,483,032 & 118 \\
\midrule
NasnetMobile & 23 & 5,289,978 & 308 \\
\midrule
NasnetLarge & 343 & 88,753,150 & 533 \\ 
\bottomrule
		\end{tabular}
	\end{table}

	\subsubsection{Soft-Attention Module}
	Soft-Attention has been used in various applications: image caption generation such as \cite{03044} or handwriting verification \cite{202017}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. Soft-Attention is described in the below equation \eqref{eqn:softatt}.

	\begin{equation}
		\label{eqn:softatt}
		f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
	\end{equation}

	Figure \ref{fig:soft-attention} shows the two main steps of applying Soft-Attention. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map \cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network (CNN), is then input to a 3D convolution layer whose weights are $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the soft-max function to generate \hl{\textit{K}} %MDPI: Please change the forward italics of the variables in the text and formulas to be consistent
	% H.K.D We have the changed the "K" into italics form
 (a constant value) attention maps. These $K$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, which is a learnable scalar. Finally, the output of the Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.

	\begin{figure}[H]
		\includegraphics[width=1\linewidth]{Definitions/SoftAttention}
		\caption{\hl{Soft-Attention~Layer.} %MDPI: Please revise the "*" into a multiplication sign ("\times" U+00D7)
}
		\label{fig:soft-attention}
	\end{figure}

	In this research, the Soft-Attention layer is applied in the same way in this research \cite{03358}. The Soft-Attention module is described in the Figure \ref{fig:soft-attention-block}.

	\begin{figure}[H]
		\includegraphics[width=0.5\linewidth]{Definitions/SoftAttentionBlock}
		\caption{\hl{Soft-Attention~Module.} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7)
		%H.K.D We have already changed the the multiplication sign into "x" in the Figure 6
}
		\label{fig:soft-attention-block}
	\end{figure}

	After feeding into the ReLU function layer, the heat feature map is processed in two paths. The first path is the two-dimensional Max Pooling. In the second path, the feature map, on the other hand, is fed into the Soft-Attention layer before the two-dimensional Max Pooling. After all, these two paths are then concatenated and fed into a ReLU layer with a dropout with the probability of $0.5$.

	\subsubsection{Loss Function}
	The loss function used in this paper is categorical cross-entropy \hl{\mbox{\cite{8943952}}}. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ be the number of training examples and number of classes respectively. The categorical cross-entropy loss is presented in the Equation \eqref{eqn:weightlossfunction}:
	\begin{equation}
		\label{eqn:weightlossfunction}
		L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)
	\end{equation}
	where $\hat{y}^c_i$  is the output of the model and $y^c_i$ is the target that the model should return, and $W_c$ is the weight of class $c$. Since the data sets face the imbalanced problem, then class weight for the loss is applied. In this research, both the original weight and a new weight formula are implemented. Originally, the weight is calculated by taking the inverse of the percentage that each class accounts for. The new weight formula is described in the Equations \eqref{eqn:weightformula} and \eqref{eqn:vector-inverse-percent}. {This weight formula is the original weight multiplied by the inverse of the number of classes in the data set which makes the training more balanced. It is inspired by the “balanced” heuristic proposed by Gary King~et~al.~\mbox{\cite{WV006-01}}}.

	\begin{equation}
		\label{eqn:weightformula}
		W = N \odot D
	\end{equation}

	\begin{equation}
		\label{eqn:vector-inverse-percent}
		D = \begin{bmatrix}
\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
		\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
		\end{bmatrix}
	\end{equation}
where $N$ is the number of the training samples, $C$ is the number of classes, and $N_i$ is the number of samples in each class $i$. $D$ is the matrix that contains the inverse of $C \times N_i$.

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Results}
	\subsection{Experimental Setup}
	\subsubsection{Training}
	Before training, the data set is split into two subsets for training (90\%) and validation (10\%). The test set, otherwise is  provided by the HAM10000 data set, and it contains 857 images. To analyze the effect of augmented data on the model, before the training; the image data are augmented to 53,573 images by the following technique:

	\begin{itemize}
	\item[-] Rotation range: rotate the image in an {angle range of 180}. 
	\item[-] Width and height shift range: Shift the image horizontally and vertically {in a range of 0.1}, respectively. 
	\item[-] Zoom range:  Zoom in or zoom out the image {in a range of 0.1} to create new image. 
	\item[-] Horizontal and vertical flipping: Flipping the image horizontally and vertically to create a new image.
	\end{itemize}

	Otherwise, all of the models are trained with the Adam \hl{Optimizer} %MDPI: The citation of references [37-42] are missing. Please add and renumber the references to appear in numerical order.
 \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 \times 10^6$, and the epsilon is set to $0.1$. The initial epochs are set to 250 epochs, and the Early Stopping is also applied to stop the training as the accuracy of the validation set does not increase after $25$~epochs. The batch size is set to $32$.

	\subsubsection{Tools}
	TensorFlow and Keras are two of the most popular frameworks to build a deep learning models. In this research, Keras based on TensorFlow is used to build, and clone the backbone model which is pre-trained with the Image-Net data set. Otherwise, the models are trained by NVIDIA RTX TitanV, and the data set is pre-processed with the CPU Intel I5 32 processors, and RAM 32 GB. In detail, the GPU is set up with CUDA 11.6, cuDNN 8.3, and ChipSRT as the requirement of TensorFlow version 2.7.0.
	\subsubsection{Evaluation Metrics}

	The model is evaluated by using the confusion matrix and related metrics. The Figure~\ref{fig:confusion-matrix} illustrates the presentation of a $2 \times 2$ confusion matrix used for class $2$ . Consider a confusion matrix $A$ with $C$ number of classes. Let $A^i$ and $A^j$ be the set of $A$ rows and columns respectively, therefore $A^i_k$ is the element at row $i$ and column $k$

	\[
	A = \begin{bmatrix}
		a_{11} & a_{12} & \dots & a_{1j} \\
		a_{21} & a_{22} & \dots & a_{2j} \\
		\vdots & \vdots	&  & \vdots\\
		a_{i1} & a_{i2} & \dots & a_{ij} 
	\end{bmatrix}
	\]

\vspace{-12pt}
		\begin{figure}[H]
\includegraphics[width=0.6\linewidth]{Definitions/Confusion-matrix}
\caption{Confusion Matrix.}\label{fig:confusion-matrix}
		\end{figure}\unskip
\begin{figure}[H]
\includegraphics[width=.5\linewidth]{Definitions/AUC}
\caption{\hl{Area} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order. % H.K.D Citation provided
 Under the Curve.}\label{fig:AUC}
	\end{figure}

	The True Positive (\hl{\textit{TP}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
) of all classes in this case is the main diagonal of the matrix $A$. The~following methods are used to calculate the False Positives (\hl{\textit{FP}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
), False Negatives (\hl{\textit{FN}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
), and~True Negatives (\hl{\textit{TN}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
) of all classes:

	\begin{equation}
		\label{eqn:FP}
		FP = -TP + \sum_{k=1}^{i}A^i_k
	\end{equation}

	\begin{equation}
		\label{eqn:FN}
		FN = -TP + \sum_{k=1}^{j}A^j_k
	\end{equation}

\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering
	\begin{equation}
		\label{eqn:TN}
		TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
TN_1 & TN_2 & \dots & TN_c
		\end{bmatrix}
	\end{equation}
\end{adjustwidth}

	\hl{Then,} %MDPI: Please confirm should the no indentation be retained
	% H.K.D I think it would be better if there is no indentation but do not know to do it, could you help me remove it.
 the model is evaluated by the following metrics:

	\begin{equation}
		\label{eqn:sens}
		\text{Sensitivity (Sens)} = \frac{TP}{TP + FN}
	\end{equation}

	\begin{equation}
		\label{eqn:spec}
		\text{Specificity (Spec)} = \frac{TN}{TN + FP}
	\end{equation}

%	\change[H.K.D]{Sensitivity and Specificity mathematically describe the accuracy of a test that reports the presence or absence of a condition. Individuals for which the condition is satisfied are considered "positive" and those for which it is not considered "negative". Sensitivity or true positive rate refers to the probability of a positive test, conditioned on truly being positive while Specificity or true negative rate refers to the probability of a negative test, conditioned on truly being negative.}
	{{Sensitivity (Equation \mbox{\eqref{eqn:sens}}) and specificity (Equation \mbox{\eqref{eqn:spec}}) mathematically describe the accuracy of a test that identifies a condition's presence or absence. Sensitivity, also known as the true positive rate, is the likelihood that a test will result in a true positive, whereas specificity, also known as the true negative rate, is the likelihood that a test will result in a true negative.}}

	\begin{equation}
		\label{eqn:pre}
		\text{Precision} = \frac{TP}{TP + FP}
	\end{equation}

	\begin{equation}
		\label{eqn:f1}
		\text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\
	\end{equation}

	\hl{Precision} %MDPI: Please confirm should the no indentation be retained
	% H.K.D I think it would be better if there is no indentation but do not know to do it, could you help me remove it.
 (Equation \eqref{eqn:pre}) or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative. F1-score (Equation \eqref{eqn:f1}), on the other hand, refers to the harmonic mean of precision and recall, which means the higher the f1-score is, the higher both precision and recall are. Besides, the expected value of precision, f1-score, and recall-score are also applied because of the multi-class problem.

	\begin{equation}
		\label{eqn:acc}
		\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN}
	\end{equation}

	\begin{equation}
		\label{eqn:balacc}
		\text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}
	\end{equation}

	\hl{The last} %MDPI: Please confirm should the no indentation be retained
	% H.K.D I think it would be better if there is no indentation but do not know to do it, could you help me remove it.
 metric is the $AUC$ \hl{(see Figure \mbox{\ref{fig:AUC}})} score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of TP versus the probability of FP.

	\subsection{Discussion} 
	\begin{comment}
		\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{Definitions/ACCALL}
\caption{Accuracy of all models trained in this research.}
\label{fig:accall}
		\end{figure}
	\end{comment}

	According to Table \ref{table:overall-acc}, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only. While InceptionResNetV2 and DenseNet201 trained with augmented data have an accuracy of $0.79$ and $0.84$, respectively, their training with metadata are $0.90$ and $0.89$, respectively. Furthermore, Resnet50 trained with metadata data has the accuracy that outperforms the Resnet50 trained with augmented data and is twice as high as Resnet152 trained with metadata. On the other hand, mobile models including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though they have a much smaller number of parameters and depth than the other model, they have quite good accuracy scores of $0.81$, $0.86$ and $0.86$, respectively.

	\begin{table}[H]
		\caption{Accuracy of all models. ACC stands for accuracy. AD stands for augmented data; this indicates that the model is trained with augmented data. MD stands for metadata, which indicates that the model is trained with metadata.}
		\label{table:overall-acc}
		\setlength{\tabcolsep}{12.38mm}\begin{tabular}{ l  c  c  }
\toprule
\textbf{Model} & \textbf{ACC (AD)} & \textbf{ACC (MD)}\\ 
\midrule
InceptionResNetV2 & 0.79 & \textbf{\hl{0.90} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. 
%H.K.D We have already explain it in the paragraph before the Table 5
}\\
\midrule
DenseNet201 & 0.84 & \textbf{0.89}\\
\midrule
ResNet50 & 0.76 & 0.70\\
\midrule
ResNet152 & 0.81 & 0.57\\
\midrule
NasNetLarge & 0.56 & 0.84\\
\midrule
MobileNetV2 & 0.83 & 0.81\\
\midrule
MobileNetV3Small & 0.83 & 0.78\\
\midrule
MobileNetV3Large & 0.85 & \textbf{0.86}\\
\midrule
NasNetMobile & 0.84 & \textbf{0.86}\\
\bottomrule
		\end{tabular}
	\end{table}

	Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to Figures \ref{fig:den f1}--\ref{fig:incep recall}. As a result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data has an f1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to the Figure \ref{fig:incep f1}. However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depths are equal to or larger than 400 have balanced the f1-scores on class. The others still face the imbalanced term. Since this data set is not balanced, therefore using augmented data can make the model more biased to the class which has a larger sample. Although using the metadata still leads to model biased, it does contribute to the improvement of the performance of the~model.

	\begin{figure}[H]
		\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=1.2\linewidth]{Definitions/CM/dn201cm}
		\end{minipage}
\caption{\hl{DenseNet201} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
	% H.K.D Citation Provided
 Confusion Matrix.}\label{fig:densenet201cm}
		\end{figure}\unskip

		\begin{figure}[H]
		\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=1.2\linewidth]{Definitions/CM/irv2cm}
		\end{minipage}
\caption{\hl{InceptionResNetV2} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
% H.K.D Citation Provided
 Confusion Matrix.}\label{fig:irv2cm}
	\end{figure}

	\begin{figure}[H]
		\centering
		\includegraphics[width=1\linewidth]{Definitions/den f1}
		\caption{The comparison between f1 scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
		\label{fig:den f1}
	\end{figure}\unskip
	\begin{figure}[H]
		\centering
		\includegraphics[width=1\linewidth]{Definitions/in f1}
		\caption{The comparison between f1 scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
		\label{fig:incep f1}
	\end{figure}

\textls[-15]{	This problem is also true with the recall score according to Figures \ref{fig:den recall} and \ref{fig:incep recall}. DenseNet201 and InceptionResNetV2, trained with augmented data have expected recall values of $0.56$ and $0.69$, respectively, while the combination of DenseNet201, Metadata, and the new weight loss function achieve the expected value of recall: $0.82$. Therefore, metadata do improve the model performance by reducing the amount of data needed for achieving higher results. On the other hand, the reason why the model becomes much more balanced is the weighted loss function. Weight loss function has the ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. DenseNet201 and InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$ and $0.82$, respectively, as opposed to their training in akiec without weighted loss function: $0.65$ and $0.37$. }

	\begin{figure}[H]
		\centering
		\includegraphics[width=1\linewidth]{Definitions/den re}
		\caption{The comparison between recall scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
		\label{fig:den recall}
	\end{figure}\unskip

	\begin{figure}[H]
		\centering
		\includegraphics[width=1\linewidth]{Definitions/in re}
		\caption{The comparison between recall scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
		\label{fig:incep recall}
	\end{figure}

	Another interesting point found during the experiment is that MobileNetV2, MobileNetV3, and NasNetMobile have a small number of parameters and depth, but they have relatively good performance. MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall scores of $0.92$, $1$, $0.92$ and  $0.92$, separately, according to the Table \ref{appendix-table:mobile-performance}. It is transparent that MobileNetV3Large and NasNetMobile are the two best performance models. Nevertheless, MobileNetV3Large has fewer number of parameters and depth than NasNetMobile.

	Table \ref{table:optimized-performance-mobile-model} shows that the MobileNetV3Large, although the number of parameters is much smaller than that of DenseNet201. InceptionResNetV2, achieves an accuracy nearly to the others. In detail, MobileNetV3Large whose number of parameters has 5.5 million parameters, which is four and ten times less than DenseNet201 and InceptionResNetV2, respectively. The depth of MobileNetV3Large, on the other hand, is four times less than DenseNet201, InceptionResNetV2 which are 118 hidden layers as opposed to the 402 and 449 values of DenseNet201 and InceptionResNetV2, separately. Although, MobileNetV3Larege only achieves an accuracy of 0.86, the time needed for prediction is 10 and 30 times less than the other opponents. Since MobileNetV3Large needs a harder process of parameter hyper-tuning to achieve a better result, this is also the future target of this research.
	\begin{table}[H]
		\caption{%\change[H.K.D]{Performance Comparison between MobileNetV3Large and DenseNet201, InceptionResNetV2}
		{How the performance of MobileNetV3Large can be optimized.}}
		\label{table:optimized-performance-mobile-model}

\begin{adjustwidth}{-\extralength}{0cm}
\centering %% If there is a figure in wide page, please release command \centering
		\setlength{\tabcolsep}{6.6mm}\begin{tabular}{ l  c  c  c }
\toprule
\textbf{Model} & \textbf{MobileNetV3Large} & \textbf{DenseNet201} & \textbf{InceptionResnetV2}\\
\midrule
No. Trainable Parameters & \textbf{\hl{5,490,039} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. The following highlights are the same.
} & 17,382,935 & 47,599,671\\
\midrule
Depth & \textbf{118} & 402 & 449\\
\midrule
Accuracy & 0.86 & 0.89 & 0.90\\
\midrule
Training Time (seconds/epoch) & 116 & 1000 & 3500\\
\midrule
Infer Time (seconds) & \textbf{0.13} & 1.16 & 4.08 \\
\bottomrule
		\end{tabular}
\end{adjustwidth}
	\end{table}

	Table \ref{table:overall-auc} shows the AUC score of the three models—InceptionResNetV2, Densenet201, and ResNet50—which are trained with only augmented data or metadata. It is transparent that the InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: both 0.99 as opposed to 0.972 and 0.93, respectively. ResNet50 trained with augmented data, on the other hand, has a higher AUC-score: 0.95 as compared to 0.93 of ResNet50 trained with metadata. Overall, InceptionResNetV2 trained with metadata reaches the peak with an AUC score of 0.974. The InceptionResNetV2 trained with metadata is also compared with the others to find out the best models trained. According to Figure \ref{fig:densevsirv2}, \hl{\mbox{\ref{fig:densenet201cm}, and \ref{fig:irv2cm}}} the InceptionResNetV2 still hit the peak AUC score of 0.99. In contrast, ResNet152 otherwise is the worst model with the AUC score of 0.87. Other models, on the other hand, have the approximately the same AUC score.

	\begin{table}[H]
			\caption{AUC (area under the curve) of all models. AD stands for augmented data, this indicates that the model is trained with augmented data. MD stands for metadata, which indicates that the model is trained with metadata.}
		\label{table:overall-auc}
	\setlength{\tabcolsep}{12.3mm}\begin{tabular}{ l  c  c  }
\toprule
\textbf{Model} & \textbf{AUC (AD)} & \textbf{AUC (MD)}\\ 
\midrule
InceptionResNetV2 & 0.971 & \textbf{\hl{0.99} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. The following highlights are the same.
%H.K.D We have already added the explaination in the paragraph before the Table 7
}\\
\midrule
DenseNet201 & 0.93 & \textbf{0.99}\\
\midrule
ResNet50 & \textbf{0.95} & 0.93 \\
\midrule
ResNet152 & 0.97 & 0.87\\
\midrule
NasNetLarge & 0.74 & \textbf{0.96}\\
\midrule
MobileNetV2 & 0.95 & \textbf{0.97}\\
\midrule
MobileNetV3Small & 0.67 & \textbf{0.96}\\
\midrule
MobileNetV3Large & 0.96 & \textbf{0.97}\\
\midrule
NasNetMobile & 0.96 & \textbf{0.97}\\
\bottomrule
		\end{tabular}
	\end{table}\unskip
		\begin{figure}[H]
		\centering
		\includegraphics[width=.9\linewidth]{Definitions/ROC/denvsirv2}
		\caption{ROC of DenseNet201 and InceptionResNetV2.}\label{fig:densevsirv2}
	\end{figure}

	In addition to the comparison between the original weight loss calculated by the sample percentage of each class model and the new weight loss-based model, it is also conducted on the three best-performing models including InceptionResNetV2, DenseNet201, and MobileNetV3. After the experiment, it is found out that the new weight loss function does not only contribute to the model to overcome the data imbalance problem but it also makes the accuracy increase. The performance of models is described in Table \ref{table:loss-comparision}.

	According to \hl{Tables} %MDPI: there is no table:densenet201auc in the tex, please check and revise.
	% H.K.D We have removed the unnecessary part
	\ref{table:loss-comparision}, the InceptionResNetV2 is found to be the best model trained. Furthermore, the InceptionResNetV2 is compared with the other state of the art researched models. According to Table \ref{table:comparative-analysis}, there are six researchers that use the same data set: HAM10000 but they have  different approaches. These models used in that research are also SOTA models sorted in ascending order. The table shows that the accuracy of the combination of InceptionResNetV2 with Soft-Attention, metadata, and weight loss in this research is less than that of InceptionResNetV2 with Soft-Attention and augmented data: 0.90 compared to 0.93 respectively. However, since Soumyyak~et~al. uses data augmentation for all class of an imbalanced data set, the f1-score and recall score are much lower. This is because the model in that research can only classify well on NV and VASC classes, which have the highest number of samples. On the other hand, the InceptionResNetV2 in this research also outperforms the other models according to five indicators: accuracy, precision, f1-score, recall score, and AUC score. 
	\begin{table}[H]
			\caption{Loss-based model accuracy comparison.}
		\label{table:loss-comparision}
	\setlength{\tabcolsep}{2.8mm}\begin{tabular}{ l  c  c  c }
\toprule
\textbf{Model} & \textbf{No Weight} & \textbf{Original Loss Accuracy} & \textbf{New Loss Accuracy}\\
\midrule
InceptionResNetV2 & 0.74 & 0.79 & 0.90\\
DenseNet201 & 0.81 & 0.84 & 0.89\\
MobileNetV3Large & 0.79 & 0.80 & 0.86\\
\bottomrule
		\end{tabular}
	\end{table} 
\unskip

	\begin{table}[H]
		\caption{Comparative Analysis.}
		\label{table:comparative-analysis}
				\setlength{\tabcolsep}{1.6mm}\begin{tabular}{ p{5cm}  c  c  c  c  c }
\toprule
\textbf{Approach} & \textbf{Accuracy} & \textbf{Precision} & \textbf{F1-Score} & \textbf{Recall} & \textbf{Auc-Score}\\
\midrule
InceptionResNetV2~\cite{03358} & 0.93 & 0.89 & 0.75 & 0.71 & 0.97\\
\midrule
\cite{03798} & - & 0.88 & 0.77 & 0.74 & - \\
\midrule
\cite{09418} & 0.88 & - & - & - & - \\
\midrule
\cite{01284} & 0.86 & - & - & - & - \\
\midrule
GradCam and Kernel SHAP~\cite{06612} & 0.88 & - & - & - & - \\
\midrule
Student and Teacher~\cite{03225} & 0.85 & 0.76 & 0.76 & - & - \\
\midrule
Proposed Method & 0.9	& 0.86 & \hl{0.86} & \hl{0.81} & \hl{0.99}%MDPI: Please confirm if the bold should be retained. If not necessary, please remove.
\\
\bottomrule
		\end{tabular}
	\end{table}

	However, there are still some drawbacks of the model: the InceptionResNetV2 cannot well classify the melanoma and the nevus. According to Figure \ref{fig:nevusVSmela} the model sometime classifies the black nevus as the melanoma because of the same color between them. However, this problem is not true for the hard black or big melanoma or the red black nevus. Some future approaches that can be proposed would be to change the type of color to the other to fix the same color problem.

	\begin{figure}[H]
		\centering
		\includegraphics[width=1\linewidth]{Definitions/img_class_nevus_mela}
		\caption{Model ability to classify melanoma and nevus.}
		\label{fig:nevusVSmela}
	\end{figure}

	\section{Conclusions}
	In this research, our proposal is to construct a model as a combination of backbone models and Soft-Attention. Moreover, the model takes two inputs, including image data and metadata. A new weight loss function is applied to figure out the data imbalance problem. Finally, the combination of InceptionResNetV2, Soft-Attention, and metadata is the best model with an accuracy of 0.9. Although the accuracy and the precision of the model are not the highest, the f1-score, recall, and AUC score of 0.86, 0.81, and 0.975, respectively are the highest and the most balanced indicators. Therefore, InceptionResnetV2 can classify well in all classes including low-samples classes. Otherwise, during the experiment, the combination of MobileNetV3, Soft-Attention, and metadata achieves an accuracy of 0.86 that is nearly the same as InceptionResNetV2, although with fewer number parameters and depth. Therefore the infer time is much less than that of  InceptionResNetV2. This result opens the door to constructing a great performance model that can be applied to mobile and IoT devices. {As a result, the proposed method and others still face the problem of badly distinguishing between melanoma and black nevus because in some cases, the melanoma and the nevus image have the same lesion size and color.}
	\vspace{6pt}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%% optional
	%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

	% Only for the journal Methods and Protocols:
	% If you wish to submit a video article, please do so with any other supplementary material.
	% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\authorcontributions{Conceptualization, V.D.N. and H.K.D.; methodology, V.D.N. and H.K.D.; software, H.K.D.; validation, V.D.N., N.D.B. and H.K.D.; formal analysis, V.D.N. and H.K.D.; investigation, V.D.N., N.D.B. and H.K.D.; resources, V.D.N.; data curation, H.K.D.; writing---original draft preparation, H.K.D.; writing---review and editing, V.D.N. and N.D.B.; visualization, H.K.D.; supervision, V.D.N. and N.D.B.; project administration, V.D.N. All authors have read and agreed to the published version of the manuscript.}

	\funding{This research received no external funding.}

	\institutionalreview{Not applicable.}

	\informedconsent{Not applicable.}

	\dataavailability{\textls[-15]{The code and the data analysis report can be found here:} \url{https://github.com/KhoiDOO/Skin-Disease-Detection-HAM100000.git}  (\hl{accessed on 29 August 2022}%MDPI: Please add the access date (Format: Date Month Year) that earlier than Received date. e.g., (accessed on 29 August 2022).
	% H.K.D Access on Date has been provided
).}

	\acknowledgments{We thank Vingroup innovation Foundation (VINIF) projtect code VININF.2021.DA00192 for providing computational resources for the work}

	\conflictsofinterest{The authors declare no conflict of interest.}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%% Optional
%	\sampleavailability{}

	%% Only for journal Encyclopedia
	%\entrylink{The Link to this entry published on the encyclopedia platform.}

	\abbreviations{Abbreviations}{
		The following abbreviations are used in this manuscript:\\

		\noindent 
		\begin{tabular}{@{}ll}
CAD & Computer-aided diagnosis\\
AI & Artificial Intelligence\\
AKIEC & Actinic keratoses and intraepithelial carcinoma or Bowen's disease\\
BCC & Basal Cell Carcinoma\\
BKL & Benign Keratosis-like Lesions\\
DF & Dermatofibroma\\
MEL & Melanoma\\
NV & Melanocytic Nevi\\
VASC & Vascular Lesions\\
HISTO & Histopathology\\
FOLLOWUP & Follow-up examination\\
CONSENSUS & Expert Consensus\\
CONFOCAL & Confocal Microscopy\\
RGB & Red Green Blue\\
BGR & Blue Green Red\\
TP & True Positives\\
FN & False Negatives\\
TN & True Negatives\\
FP & False Positives\\
Sens & Sensitivity\\
Spec & Specificity\\
AUC & Area Under the Curve\\
ROC & Receiver Operating Curve\\
		\end{tabular}
	}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%% Optional

	\appendixtitles{yes} 
	\appendixstart
	\appendix
\startlandscape

\begin{adjustwidth}{+\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering
	\section[\appendixname~\thesection]{Detailed Model Structure}

	\begin{table}[H]
			\caption{\hl{Detailed structure} %MDPI: 1. We revised the "x" into a multiplication sign ("\times" U+00D7). Please confirm. 2. Please confirm if the vertical line is necessary, if not, please remove it.
			% H.K.D Incredibly beautiful table
 of models except for mobile models. SA stands for Soft-Attention, SA Module denotes whether that model uses the Soft-Attention module. GAP stands for Global Average Pooling. FC stands for Fully Connected Layer.\label{appendix-table:detailed structure model}}
%\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{p{2.2cm}  p{2.2cm}  p{2.2cm}  p{2.6cm}  p{2.2cm}  p{2.2cm}  p{2.2cm}  p{2.2cm}  p{2.4cm}  p{2.6cm}}
	\toprule
	\textbf{DenseNet-201} & \textbf{DenseNet-201 + SA} & \textbf{Inception-ResNetV2} & \textbf{Inception-ResNetV2 +~SA} & \textbf{ResNet-50} & \textbf{ResNet-50 +~SA} & \textbf{ResNet-152} & \textbf{ResNet-152 +~SA} & \textbf{NasNet-Large} & \textbf{NasNet-Large +~SA}\\
	\midrule
	Conv2D $7 \times 7$ & Conv2D $7 \times 7$ & STEM& STEM& Conv2D $7 \times 7$& Conv2D $7 \times 7$& Conv2D $7 \times 7$& Conv2D $7 \times 7$& Conv2D $3 \times 3$& Conv2D $3 \times 3$\\ \midrule
	Pooling $3 \times 3$ & Pooling $3 \times 3$ & & & Pooling $3 \times 3$& Pooling  $3 \times 3$& Pooling  $3 \times 3$& Pooling  $3 \times 3$& Pooling& Pooling\\ \midrule		
	DenseBlock $\times$~6 & DenseBlock $\times$~6 & Inception ResNet A $\times$~10& Inception ResNet A $\times$~10& Residual Block $\times$~3& Residual Block $\times$~3& Residual Block $\times$~3& Residual Block $\times$~3& Reduction Cell $\times$~2& Reduction Cell $\times$~2\\  \midrule
	Conv2D $1 \times 1$ & Conv2D $1 \times 1$ & Reduction A & Reduction A & & & & & Normal Cell $\times$~N& Normal Cell $\times$~N\\	\midrule
	Average pool $2 \times 2$ & Average pool $2 \times 2$ & & & & & & & & \\ \midrule
	DenseBlock $\times$~12 & DenseBlock $\times$~12 & Inception ResNet B $\times$~20& Inception ResNet B $\times$~20& Residual Block $\times$~4& Residual Block $\times$~4& Residual Block $\times$~8& Residual Block $\times$~8& Reduction Cell& Reduction Cell\\ \midrule
	Conv2D $1 \times 1$ & Conv2D $1 \times 1$ & Reduction B & Reduction B & & & & & Normal Cell $\times$~N& Normal Cell $\times$ N\\\midrule
	Average pool $2 \times 2$ & Average pool $2 \times 2$ & & & & & & & & \\ \midrule
	DenseBlock $\times$ 48 & DenseBlock $\times$~12 & Inception ResNet C $\times$~5& Inception ResNet C $\times$~5& Residual Block $\times$~6& Residual Block $\times$ 6& Residual Block $\times$~36& Residual Block $\times$~36& Reduction Cell& Reduction Cell\\ \midrule
	Conv2D $1 \times 1$ & Conv2D $1 \times 1$ & & & & & & & Normal Cell $\times$~N& Normal Cell $\times$~N-2\\\midrule
	Average pool $2 \times 2$ & Average pool $2 \times 2$ & & & & & & & & \\ \midrule
	DenseBlock $\times$~29 & DenseBlock $\times$~29 & & & Residual Block $\times$~3& & Residual Block $\times$~3& & & \\ \midrule
	DenseBlock $\times$ 3 & \textbf{\hl{SA Module} %MDPI: Please confirm if the bold should be retained. % H.K.D It should be retained
} & & \textbf{SA Module}& & \textbf{SA Module}& & \textbf{SA Module}& & \textbf{SA Module}\\	\midrule
	GAP $7 \times 7$ & & Average pool& & GAP $7 \times 7$& & GAP $7 \times 7$& & & \\\midrule
	FC 1000D & & Dropout (0.8)& & FC 1000D& & FC 1000D& & & \\ \midrule
	SoftMax & SoftMax & SoftMax& SoftMax& SoftMax& SoftMax& SoftMax& SoftMax& SoftMax& SoftMax\\ 
	\bottomrule
\end{tabularx}
	\end{table}

	\section[\appendixname~\thesection]{Detailed Mobile-based Model Structure}

	\begin{table}[H]
		\caption{\hl{Detailed} structure of mobile-based models. SA stands for Soft-Attention, SA Module denotes whether that model uses the Soft-Attention module. SE which stands for Squeeze-And-Excite, and it shows whether that block has Squeeze-And-Excite. \label{appendix-table:detailed mobile model structure}}%MDPI: We remove the vertical line, please confirm.
		% The most fantastic and spectacular table in the world
%\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{p{3cm}  p{3cm}  p{4.2cm}  p{3cm}  p{3cm}  p{3cm}  p{2.3cm}  p{2.3cm}}
	\toprule
	\textbf{MobileNetV2} & \textbf{MobileNetV2 + SA} & \textbf{MobileNetV3 Small} & \textbf{MobileNetV3 Small + SA} & \textbf{MobileNetV3 Large} & \textbf{MobileNetV3 Large + SA} & \textbf{NasNet Mobile} & \textbf{NasNetMobile + SA}\\
	\midrule
	Conv2D & Conv2D& Conv2D $3 \times 3$& Conv2D $3 \times 3$& Conv2D $3 \times 3$& Conv2D $3 \times 3$ & Normal Cell & Normal Cell\\	\midrule		
	bottleneck & bottleneck & bottleneck $3 \times 3$ SE& bottleneck $3 \times 3$ SE& bottleneck $3 \times 3$ 3 repeated& bottleneck $3 \times 3$ 3 repeated& Reduction Cell& Reduction Cell\\ \midrule		
	bottleneck 2 repeated& bottleneck 2 repeated& bottleneck $3 \times 3$& bottleneck $3 \times 3$& bottleneck $5 \times 5$ SE 3 repeated& bottleneck $5 \times 5$ SE 3 repeated & Normal Cell & Normal Cell\\ \midrule	
	bottleneck 3 repeated& bottleneck 3 repeated& bottleneck $5 \times 5$ SE 8 repeated& bottleneck $5 \times 5$ SE 8 repeated& bottleneck $3 \times 3$ 4 repeated& bottleneck $3 \times 3$ 4 repeated& Reduction Cell & Reduction Cell\\ \midrule	
	bottleneck 4 repeated& bottleneck 4 repeated& & & bottleneck $3 \times 3$ SE 2 repeated& bottleneck $3 \times 3$ SE 2 repeated & Normal Cell\\ \midrule	
	bottleneck 3 repeated& bottleneck 3 repeated& & & bottleneck $5 \times 5$ SE 3 repeated& bottleneck $5 \times 5$ SE 3 repeated& \\ \midrule	
	bottleneck 3 repeated& bottleneck & & & & & \\ \midrule	
	bottleneck & & & & & & \\ \midrule
	Conv2D $1 \times 1$ & & Conv2D $1 \times 1$ SE & Conv2D $1 \times 1$ SE& Conv2D $1 \times 1$& Conv2D $1 \times 1$ & & \\ \midrule
	AP $7 \times 7$ & & Pool $7 \times 7$& Pool $7 \times 7$& Pool $7 \times 7$& Pool $7 \times 7$& &\\ \midrule
	Conv2D $1 \times 1$ & \textbf{SA Module}& Conv2D $1 \times 1$ 2 repeated& \textbf{SA Module}& Conv2D $1 \times 1$ 2 repeated& \textbf{SA Module}& &\textbf{SA Module}\\ \midrule
	Softmax & Softmax& Softmax& Softmax& Softmax& Softmax& Softmax & Softmax\\ 
	\bottomrule
\end{tabularx}
	\end{table}

\end{adjustwidth}	\finishlandscape
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		\section[\appendixname~\thesection]{Detailed Model Performance}
		\subsection[\appendixname~\thesection]{F1-Score Model Performance}
		\begin{table}[H]
\caption{\hl{F1-score%MDPI: Please confirm if the vertical line is necessary, if not, please remove it. 
% H.K.D beautiful no vertical line
} of each class: akiec, bcc, bkl, df, mel, nv and vasc, which are denoted in the abbreviations. The last column shows the expected value of the f1-score from each model. All models in the first column are the models trained in this research. The term “with Augmented Data” means that model is trained with data augmenting during the training, there is no metadata or weight loss contribution. The term “with Metadata and WeightLoss” means that the model is trained with metadata including age, gender, localization, and the weight loss function, there is no augmented data contribution. \hl{Besides the bold number highlights achievement of the research}}
\label{appendix-table:F1-score-summary}

\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering
\centering
\begin{tabular}{p{9cm}  p{0.8cm}  p{0.8cm}  p{0.6cm}  p{0.6cm}  p{0.6cm}  p{0.6cm}  p{0.8cm}  p{0.9cm}} 
	\toprule
	\textbf{Model} & \textbf{akiec} & \textbf{bcc} & \textbf{bkl} & \textbf{df} & \textbf{mel} & \textbf{nv} & \textbf{vasc} & \textbf{Mean} \\
	\midrule
	DenseNet201 with Augmented Data & 0.56 & 0.75 & 0.64 & 0.62 & 0.60 & 0.93 & 0.85 & 0.70 \\ 
	\midrule
	InceptionResNetV2 with Augmented Data & 0.42 &	0.63 & 0.51 & 0.35 & 0.57 & 0.9 & 0.7 & 0.58\\
	\midrule
	Resnet50 with Augmented Data & 0.39 & 0.59 & 0.42 & 0.6 & 0.42 & 0.88 & 0.79 & 0.58\\
	\midrule 	
	VGG16 with Augmented Data & 0.35 & 0.62 & 0.42 & 0.32 & 0.47 & 0.89 & 0.77 & 0.54\\ 
	\midrule		
	DenseNet201 with Metadata and WeightLoss & \textbf{\hl{0.84} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. The following highlights are the same.
	% H.K.D Explaination provided
} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\
	\midrule
	InceptionResNetV2 with Metadata and WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\
	\midrule
	Resnet50 with Metadata and WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\
	\midrule
	Resnet152 with Metadata and WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\
	\midrule
	NasNetLarge with Metadata and WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\
	\midrule
	MobileNetV2 with Metadata and WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\
	\midrule
	MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\
	\midrule
	MobileNetV3Small with Metadata and WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\
	\midrule
	NasNetMobile with Metadata and WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\
	\bottomrule
\end{tabular}
\end{adjustwidth}
		\end{table}

		\subsection[\appendixname~\thesection]{Recall Model Performance}
		\begin{table}[H]
\caption{\hl{Recall%MDPI: We remove the vertical line, please confirm. %H.K.D too beautiful
} score of each class and the expected value of recall score from each model.}
\label{appendix-table:recall-score-summary}

\begin{adjustwidth}{-\extralength}{0cm}
%\centering %% If there is a figure in wide page, please release command \centering
\centering
\begin{tabular}{p{9cm}  p{0.8cm}  p{0.8cm}  p{0.6cm}  p{0.6cm}  p{0.6cm}  p{0.6cm}  p{0.8cm}  p{0.9cm}} 
	\toprule
	\textbf{Model} & \textbf{akiec} & \textbf{bcc} & \textbf{bkl} & \textbf{df} & \textbf{mel} & \textbf{nv} & \textbf{vasc} & \textbf{Mean} \\
	\midrule
	DenseNet201 with Augmented Data & 0.65 & 0.75 & 0.59 & 0.53 & 0.54 & 0.93 & 0.85 & 0.69\\ 
	\midrule
	InceptionResNetV2 with Augmented Data & 0.37 & 0.60 & 0.55 & 0.24 & 0.59 & 0.9 & 0.67 & 0.56\\
	\midrule
	Resnet50 with Augmented Data & 0.33 & 0.56 & 0.38 & 0.53 & 0.40 & 0.92 & 0.81 & 0.56\\
	\midrule 	
	VGG16 with Augmented Data & 0.31 & 0.66 & 0.37 & 0.24 & 0.40 & 0.94 & 0.71 & 0.51\\ 
	\midrule		
	DenseNet201 with Metadata and WeightLoss & \textbf{\hl{0.85}} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
	\midrule
	InceptionResNetV2 with Metadata and WeightLoss & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 0.93 & \textbf{0.81}\\
	\midrule
	Resnet50 with Metadata and WeightLoss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\
	\midrule
	Resnet152 with Metadata and WeightLoss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\
	\midrule
	NasNetLarge with Metadata and WeightLoss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\
	\midrule
	MobileNetV2 with Metadata and WeightLoss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\
	\midrule
	MobileNetV3Large with Metadata and WeightLoss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\
	\midrule
	MobileNetV3Small with Metadata and WeightLoss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\
	\midrule
	NasNetMobile with Metadata and WeightLoss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\
	\bottomrule
\end{tabular}
\end{adjustwidth}
		\end{table}

		\subsection[\appendixname~\thesection]{Detailed Mobile Model Perform}
		\begin{table}[H]
\caption{\hl{Deeper%MDPI: We remove the vertical line, please confirm. 
%H.K.D No more words to describe how beatiful the table is 
} analyzing of the mobile model. This table illustrates the other indicators of the four mobile-based models including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The indicators are Accuracy, Balanced Accuracy, Precision, F1-score, Sensitivity, Specificity, and ROC--AUC score. All of them are average indicators.}
\label{appendix-table:mobile-performance}
\setlength{\tabcolsep}{4.7mm}\begin{tabular}{l  c  c  c  c} 
	\toprule
	\textbf{Model} & \textbf{\cite{04381}} & \textbf{\cite{02244} Small} & \textbf{\cite{02244} Large} & \textbf{\cite{07012} Mobile}\\
	\midrule
	Accuracy (avg) & 0.81 & 0.78 & 0.86 & \textbf{\hl{0.86}}\\
	\midrule
	Balanced Accuracy (avg) & 0.86 & 0.87 & 0.87 & \textbf{0.88}\\ 
	\midrule
	Precision (avg) & 0.71 & 0.63 & \textbf{0.75} & 0.73\\
	\midrule
	F1-score (avg) & 0.75 & 0.70 & \textbf{0.79} & 0.78\\
	\midrule
	Sensitivity (avg) & 0.78 & 0.79 & 0.80 & \textbf{0.81}\\ 
	\midrule
	Specificity (avg) & 0.95 & 0.95 & 0.95 & \textbf{0.96}\\
	\midrule
	ROC-AUC-score (avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
	\bottomrule
\end{tabular}
		\end{table}

		%\printendnotes[custom] % Un-comment to print a list of endnotes
	\begin{adjustwidth}{-\extralength}{0cm}

		\reftitle{References}

		% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
		% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

		%=====================================
		% References, variant A: external bibliography
		%=====================================
		%\bibliography{your_external_BibTeX_file}

		%=====================================
		% References, variant B: internal bibliography
		%=====================================
		\begin{thebibliography}{999}

\bibitem[Author2(year)]{03358}
\hl{Datta, S.K.; Shaikh, M.A.; Srihari, S.N.; Gao, M.}%MDPI: We have completed all the missing information according to scholar, please check all references
 Soft-Attention Improves Skin Cancer Classification Performance. In \emph{Interpretability of Machine Intelligence in Medical Image Computing, and Topological Data Analysis and Its Applications for Medical Data}; Springer: Cham, Switzerland, 
{2021}.

\bibitem[Author2(year)]{11872}
Goyal, M.; Knackstedt, T.; Yan, S.; Hassanpour, S.  Artificial Intelligence-Based Image Classification for Diagnosis of Skin Cancer: Challenges and Opportunities. 
{\em Comput. Biol. Med.} 
{\bf 2020}, \emph{127}, 104065.

\bibitem[Author2(year)]{11797}
Poduval, P.; Loya, H.; Sethi, A. Functional Space Variational Inference for Uncertainty Estimation in Computer Aided Diagnosis. 
{\em arXiv} 
{\bf 2020}, arXiv:2005.11797.

\bibitem[Author2(year)]{06993}
{Gao, H.; Zhuang, L.; Kilian, Q.  Weinberger: Densely Connected Convolutional Network.} In Proceedings of the 2017 \hl{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, Honolulu, HI, USA, 21--26 July 2017.

\bibitem[Author2(year)]{04861}
Howard, A.G.; Zhu, M.; Chen, B.; Kalenichenko, D.; Wang, W.;  Weyand, T.;  Andreetto, M.; Adam, H. MobileNets: Efficient Convolutional Neural Networks for Mobile Vision Applications.
{\em arXiv} 
{\bf 2017}, arXiv:1704.04861.

\bibitem[Author2(year)]{00567}
Szegedy, C.; Vanhoucke, V.; Ioffe, S.; Shlens, J.; Wojna, Z.  Rethinking the Inception Architecture for Computer Vision.
In Proceedings of the IEEE Conference on Computer Vision and Pattern {Recognition (CVPR),} Boston, MA, USA, 7--12 June 
{2015}.

\bibitem[Author2(year)]{07261}
Szegedy, C.; Ioffe, S.; Vanhoucke, V.; Alemi, A. Inception-v4, Inception-ResNet and the Impact of Residual Connections on Learning.
{In Proceedings of the AAAI Conference}, New Orleans, LO, USA,
2--7 February {2018}.

\bibitem[Author2(year)]{04381}
Sandler, M.; Howard, A.; Zhu, M.; Zhmoginov, A.;Chen, L.C. MobileNetV2: Inverted Residuals and Linear Bottlenecks.
In Proceedings of the IEEE Conference on Computer Vision and {Pattern Recognition,} Salt Lake City, UT, USA, 18--22 June 
{2018}.

\bibitem[Author2(year)]{02244}
Howard, A.; Sandler, M.; Chu, G.; Chen, Li.; Chen, B.; Tan, M.; Wang, W.; Zhu, Y.; Pang, R.; Vasudevan, V.; Le, Q.V.; Adam, H. Searching for MobileNetV3.
In Proceedings of the 2019 IEEE/CVF International Conference on \hl{Computer Vision (ICCV), Seoul, Korea, 27 October--2 November 2019.}

\bibitem[Author2(year)]{02357}
Chollet, F. Xception: Deep Learning with Depthwise Separable Convolutions.
In Proceedings of the IEEE Conference on Computer Vision and {Pattern Recognition,}  Honolulu, HI, USA, 21--26 July {2017}.

\bibitem[Author2(year)]{03385}
He, K.; Zhang, X.; Ren, S.; Sun, J. Deep Residual Learning for Image Recognition.
In Proceedings of the IEEE Conference on Computer Vision and {Pattern Recognition, } Boston, MA, USA, 7--12 June 
{2015}.

\bibitem[Author2(year)]{05027}
He, K.; Zhang, X.; Ren, S.; Sun, J. Identity Mappings in Deep Residual Networks.
In \emph{European Conference on Computer Vision}; Springer: Cham, Switzerland,
{2016}.

\bibitem[Author2(year)]{07012}
Zoph, B.; Vasudevan, V.; Shlens, J.; Le, Q.V. Learning Transferable Architectures for Scalable Image Recognition. 
In Proceedings of the IEEE Conference on Computer Vision and{Pattern Recognition, }  Honolulu, HI, USA, 21--26 July 
{2017}.

\bibitem[Author2(year)]{03798}
Garg, R.; Maheshwari, S.; Shukla, A. Decision Support System for Detection and Classification of Skin Cancer using CNN. In \emph{Innovations in Computational Intelligence and Computer Vision}; Springer: Singapore, {2019}.

\bibitem[Author2(year)]{10348}
Rezvantalab, A.; Safigholi, H.; Karimijeshni, S. Dermatologist Level Dermoscopy Skin Cancer Classification Using Different Deep Learning Convolutional Neural Networks Algorithms. 
{\em arXiv} 
{\bf 2021}, arXiv:1810.10348.

\bibitem[Author2(year)]{09418}
Nadipineni, H. Method to Classify Skin Lesions using Dermoscopic images. {\em arXiv} 
{\bf 2020}, arXiv:2008.09418.		
\bibitem[Author2(year)]{01284}
Yao, P.; Shen, S.; Xu, M.; Liu, P.; Zhang, F.;  Xing, J., Shao, P.; Kaffenberger, B.; Xu, R.X. 
Single Model Deep Learning on Imbalanced Small Datasets for Skin Lesion Classification. 
{\em IEEE Trans. Med. Imaging} 
{\bf 2022}, \emph{41}, 1242--1254.

\bibitem[Author2(year)]{06612}
Young, K.; Booth, G.; Simpson, B.; Dutton, R.; Shrapnel, S.  Dermatologist Level Dermoscopy Deep neural network or dermatologist? {\em Nature} 
{\bf \hl{2021} %MDPI: Please add the volume and pagination, or doi number.
}.

\bibitem[Author2(year)]{03225}
Xing, X.; Hou, Y.; Li, H.; Yuan, Y.; Li, H.; Meng, M.Q.H.
  Categorical Relation-Preserving Contrastive Knowledge Distillation for Medical Image Classification. 
In  \emph{International Conference on Medical Image Computing and Computer-Assisted Intervention}; Springer: Cham, Switzerland, 
{2021}.

\bibitem[Author2(year)]{12602}
Mahbod, A.; Tsch, l P.; Langs, G.; Ecker, R.; Ellinger, I.  The Effects of Skin Lesion Segmentation on the Performance of Dermatoscopic Image Classification.
{\em Comput. Methods Programs Biomed.} 
{\bf 2020}, \emph{197}, 105725.

\bibitem[Author2(year)]{03426}
Lee, Y.C.; Jung, S.H.; Won, H.H. WonDerM: Skin Lesion Classification with Fine-tuned Neural Networks.
{\em arXiv} 
{\bf 2019}, arXiv:1808.03426.

\bibitem[Author2(year)]{03910}
Gessert, N.; Nielsen, M.; Shaikh, M.; Werner, R.; Schlaefer, A. Skin Lesion Classification Using Ensembles of Multi-Resolution EfficientNets with Meta Data. 
{\em MethodsX} 
{\bf 2020}, \emph{7}, 100864.

\bibitem[Author2(year)]{05045}
Alberti, M.; Botros, A.; Schutz, N.; Ingold, R.; Liwicki, M.; Seuret, M. Trainable Spectrally Initializable Matrix Transformations in Convolutional Neural Networks. In Proceedings of the 2020 25th International Conference on Pattern Recognition (ICPR), Milan, Italy, 10--15 January 2021.

\bibitem[Author2(year)]{2101.133}
Abayomi-Alli, O.O.; Damasevicius, R.; Misra, S.; Maskeliunas, R.; Abayomi-Alli, A. Malignant skin melanoma detection using image augmentation by oversamplingin nonlinear lower-dimensional embedding manifold. \emph{Turk. J. Electr. Eng. Comput. Sci.} {\bf 2021}, \emph{29}, 2600--2614.

\bibitem[Author2(year)]{22750}
Nawaz, M.; Nazir, T.; Masood, M.; Ali, F.;
Khan, M.A.; Tariq, U.; Sahar,N. 
Robertas Damaševicius Melanoma segmentation: A framework of improved DenseNet77 and UNET convolutional neural network.
{\em Int. J. Imaging Syst. Technol.} 
{\bf 2022}. https://doi.org/10.1002/ima.22750.

\bibitem[Author2(year)]{9445180}
Kadry, S.; Taniar, D.; Damaševičius, R.; Rajinikanth, V.; Lawal, I. A. Extraction of abnormal skin lesion from dermoscopy image using VGG-SegNet. In Proceedings of the 2021 Seventh International conference on Bio Signals, Images, and Instrumentation (ICBSII), Chennai, India, 25--27 March 2021.

\bibitem[Author2(year)]{1556}
Simonyan, K.; Zisserman, A. Very Deep Convolutional Networks for Large-Scale Image Recognition.
{\em arXiv} 
{\bf 2016}, arXiv:1409.1556.

\bibitem[Author2(year)]{11946}
Tan, M.; Le Q. EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks.
{\em arXiv} 
{\bf 2019}, 	arXiv:1905.11946.

\bibitem[Author2(year)]{01507}
Hu, J.; Shen, L.; Albanie, S.; Sun, G.; Wu, E. Squeeze-and-Excitation Networks.
In Proceedings of the IEEE Conference on Computer Vision and {Pattern Recognition,} Salt Lake City, UT, USA, 18--22 June 2018.

\bibitem[Author2(year)]{04552v2}
DeVries, T.; Taylor, G.W. Improved Regularization of Convolutional Neural Networks with Cutout. 
{\em arXiv} 
{\bf 2017}, arXiv:1708.04552.

\bibitem[Author2(year)]{09365}
Li, X.; Lu, Y.; Desrosiers, C.; Liu, X. Out-of-Distribution Detection for Skin Lesion Images with Deep Isolation Forest. In \emph{International Workshop on Machine Learning in Medical Imaging}; Springer: Cham, Switzerland, 
{2020}.

\bibitem[Author2(year)]{10417}
Tsch, l P.; Rosendahl, C.; Kittler, H. The HAM10000 data set, a large collection of multi-source dermatoscopic images of common pigmented skin lesions. 
{\em Sci. Data} 
{\bf 2018}, \emph{5}, 1--9.

\bibitem[Author2(year)]{2012.4305}
Fekri-Ershad, S.; Saberi, M.; Tajeripour, F. An innovative skin detection approach using color based image retrieval technique.
{\em arXiv} 
{\bf 2012}, arXiv:1207.1551.

\bibitem[Author2(year)]{08375}
Fred, A. Agarap Deep Learning using Rectified Linear Units (ReLU).
{\em arXiv} 
{\bf 2019}, arXiv:1803.08375.

\bibitem[Author2(year)]{03044}
Xu, K., Ba, J., Kiros, R., Cho, K., Courville, A., Salakhudinov, R.; Zemel, R.; Bengio, Y. Show, Attend and Tell: Neural Image Caption Generation with Visual Attention. In Proceedings of the 32nd International Conference on Machine Learning, Lille, Franc, 7--9 July 2015.

\bibitem[Author2(year)]{202017}
Shaikh, M.A.; Duan, T.; Chauhan, M.; Srihari, S.N. \hl{Attention} %MDPI: please check if this reference is dplicated with ref 40. If it is, please remove the duplicated reference and rearrange all the references to appear in numerical order. Please ensure that there are no duplicated references.
 based writer independent verification. In Proceedings of the 2020 17th International Conference on Frontiers in Handwriting Recognition,  Dortmund, Germany , 8--10 September
{2020}.

\bibitem[Author2(year)]{08513}
Tomita, N.; Abdollahi, B.; Wei, J.; Ren, B.; Suriawinata, A.; Hassanpour, S. Attention-Based Deep Neural Networks for Detection of Cancerous and Precancerous Esophagus Tissue on Histopathological Slides.
{\em JAMA Netw.} 
{\bf 2020}, \emph{2}, e1914645.

\bibitem[Author2(year)]{8943952}
Ho, Y.; Wookey, S. The Real-World-Weight Cross-Entropy Loss Function: Modeling the Costs of Mislabeling.
\emph{IEEE Access }
{\bf 2020}, \emph{8}, 4806--4813.

\bibitem[Author2(year)]{WV006-01}
King, G.; Zeng, L. Logistic Regression in Rare Events Data.
{\em Political Anal.} 
{\bf 2001}, \emph{9}, 137--163.

\bibitem[Author2(year)]{6980}
Kingma, D.P.; Ba, J. Adam: A Method for Stochastic Optimization.
{\em arXiv} 
{\bf 2017}, arXiv:1412.6980.

\bibitem[Author2(year)]{02357-1}
\hl{Shaikh, M.A.;} %MDPI: The label 02357 is repeated. We updated this one, please confirm. % H.K.D it's duplicated with the research paper cited 33, please remove it
 Duan, T.; Chauhan, M.; Srihari, S.N. \hl{In} %MDPI: please add the article title.
 Proceedings of the 2020 17th International Conference on Frontiers in Handwriting Recognition, Dortmund, Germany, 8--10 September 2020.

		\end{thebibliography}

		% If authors have biography, please use the format below
		%\section*{Short Biography of Authors}
		%\bio
		%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
		%{\textbf{Firstname Lastname} Biography of first author}
		%
		%\bio
		%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
		%{\textbf{Firstname Lastname} Biography of second author}

		% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
		% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
		% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%% for journal Sci
		%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\end{adjustwidth}

\end{document}

### 2022-10-03 MDPI/sensors-1915564 - Copy/sensors-1915564.tex
Update Paper Final Version

--- 2022-09-29 MDPI/sensors-1915564-redo - For Proof/sensors-1915564.tex
@@
 \usepackage{soulutf8}
-\usepackage[adjustmargins]{LatexPackage/trackchanges}
-\addeditor{H.K.D}
+%\usepackage[adjustmargins]{LatexPackage/trackchanges}
+%\addeditor{H.K.D}
 
@@
 % Authors, for the paper (add full first names)
-\Author{\hl{Viet} %MDPI: Please carefully check the accuracy of names and affiliations.
- Dung Nguyen $^{1,\dagger,}$*\orcidA{}, Ngoc Dung Bui $^{2,}$\hl{*} %MDPI: The correspondence author is different from the submitting system. Please confirm which one is correct.
+\Author{{Viet} %MDPI: Please carefully check the accuracy of names and affiliations.
+ Dung Nguyen $^{1,\dagger,}$*\orcidA{}, Ngoc Dung Bui $^{2,}${*} %MDPI: The correspondence author is different from the submitting system. Please confirm which one is correct.
 \orcidB{} and Hoang Khoi Do  $^{1,\dagger}$\orcidC{}}
@@
 
-\address{$^{1}$ \quad \hl{School} %MDPI: we combined the same affiliation 1 and 3, please confirm.
- of Electrical and Electronic Engineering, Hanoi University of Science and Technology, \hl{Vietnam;} %MDPI: Please add the city and post code.
-\hl{ khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct.
+\address{$^{1}$ \quad {School} %MDPI: we combined the same affiliation 1 and 3, please confirm.
+ of Electrical and Electronic Engineering, Hanoi University of Science and Technology, {Dai Co Viet, Ha Noi 100000, Vietnam;} %MDPI: Please add the city and post code.
+{khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct. %H.K.D confirmed
 \\
-$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, \hl{Vietnam} %MDPI: Please add the city and post code.
+$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, {Ha Noi 115000, Vietnam} %MDPI: Please add the city and post code.
 }
@@
 % Current address and/or shared authorship
-\firstnote{Current address: 1st Dai Co Viet Street, \hl{Ha Noi, 100000, } %MDPI: 1.
+\firstnote{Current address: 1st Dai Co Viet Street, {Ha Noi 100000, } %MDPI: 1.
 Please add the postal code.
@@
 It is worth noting that a new loss function that takes into account the data imbalance is also proposed.
-Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and the new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.99, respectively.
+Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and the new loss function gives 90 percent accuracy, mean of precision, F1-score, recall, and AUC of 0.81, 0.81, 0.82, and 0.99, respectively.
 Besides, using MobileNetV3Large combined with Soft-Attention and the new loss function, even though the number of parameters is 11~times less and the number of hidden layers is 4 times less, it achieves an accuracy of 0.86 and 30 times faster diagnosis than InceptionResNetV2.}
@@
 % Keywords
-\keyword{\highlighting{skin lesions;} %MDPI: We removed the uppercase of some keywords, please confirm  
+\keyword{{skin lesions;} %MDPI: We removed the uppercase of some keywords, please confirm  
 classification; deep learning; soft-attention; imbalance} 
@@
 	{Skin cancer is one of the most common cancers leading to worldwide death.
-\hl{Every day, more than 9500~\mbox{\cite{03358}} }%MDPI: We adjust the number of cited reference, please check the cited reference again.
+{Every day, more than 9500~\mbox{\cite{03358}} }%MDPI: We adjust the number of cited reference, please check the cited reference again.
 	people in the United States are diagnosed with skin cancer.
@@
 	To adapt the rise in skin cancer cases, AI algorithms over the last decade has a great performance.
-Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet~\cite{04861}, Inception \cite{00567}\hl{\mbox{\cite{07261}}}, MobileNets\cite{04861,04381,02244}, \hl{Xception\mbox{\cite{02357}}}, ResNet \cite{03385,05027}, and NasNet \cite{07012}.
+Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet  ~\cite{04861}, Inception  \cite{00567,07261}, MobileNets \cite{04861,04381,02244}, {Xception \mbox{\cite{02357}}}, ResNet \cite{03385,05027}, and NasNet   \cite{07012}.
 Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.
@@
 		\begin{table}[H]
-\caption{\hl{Related} %MDPI: we updated the format of all tables, please confirm the change. Please cite the table in the text and ensure the first citation of each table appears in numerical order.
- Works Summary.}
+\caption{{Summary of related} %MDPI: we updated the format of all tables, please confirm the change.
+Please cite the table in the text and ensure the first citation of each table appears in numerical order.
+%H.K.D We also changed the table caption
+works.}
 \label{table:related-work-summary}
@@
 Soumyyak~et~al.'s proposed method gained great performances and also outperformed many other studies with an accuracy of 0.93 and a precision of 0.92.
-However, using  data augmentation on an imbalanced dataset resulted in subpar classification  classify with respect to the  classes; therefore, their model obtained a  recall and f1-score of 0.71 and 0.75, respectively.
+However, using  data augmentation on an imbalanced dataset resulted in subpar classification  classify with respect to the  classes; therefore, their model obtained a  recall and F1-score of 0.71 and 0.75, respectively.
 In this research, our proposed method also considers this problem and solves it.
@@
 		Using the above-mentioned backbones has been attempted previously.
-Rishu Garg~et~al.~\mbox{\cite{03798}} used a transfer learning approach with a CNN-based model: ResNet50 and VGG1,6 which are pretrained with an ImageNet data set.
-In addition, they also use data augmentation to avoid an imbalance occuring in  the dataset.
-Histogram equalization is also used to increase the contrast of  skin lesions before being fed into machine learning algorithms including Random Forest, XGBoost, and Support Vector Machine.	Histogram equalization can be considered as a heat map that takes the main feature as the number of occurrences of the same value pixel.
+Rishu Garg~et~al.
+\mbox{\cite{03798}} used a transfer learning approach with a CNN-based model: ResNet50 and VGG16 which are pretrained with an ImageNet data set.
+In addition, they also use data augmentation to avoid an imbalance occurring in  the data set.
+Histogram equalization is also used to increase the contrast of  skin lesions before being fed into machine learning algorithms including Random Forest, XGBoost, and Support Vector Machine.
+Histogram equalization can be considered as a heat map that takes the main feature as the number of occurrences of the same value pixel.
 This approach also gain great performances with an accuracy of 0.90 and  precision of 0.88.
@@
 In this research study, our proposed method used  Soft-Attention, which can create a heat map feature of the lesion.
-Otherwise, Rishu Garg~et~al.'s proposed method also faced the problem of imbalanced classification due to an imbalanced dataset with the f1-score and recall at 0.77 and 0.74, respectively.
+Otherwise, Rishu Garg~et~al.'s proposed method also faced the problem of imbalanced classification due to an imbalanced dataset with the F1-score and recall at 0.77 and 0.74, respectively.
 
@@
 SMOTE recognizes k-minority class neighbors that are near  each minority class sample by using the covariance matrix.
-This approach obtained an accuracy, recall, and f1-score of 0.92, 0.87, and 0.82, respectively.
+This approach obtained an accuracy, recall, and F1-score of 0.92, 0.87, and 0.82, respectively.
 
@@
 Before being fed into  Deep CNN models, the image was resized to (224, 224) for DenseNet201, ResNet152, InceptionResNetV2, and (229, 229) for InceptionV3.
-The best ROC AUC values for melanoma and basal cell carcinoma are 0.94 (ResNet152) and 0.93 (DenseNet201).
+The best AUC values for melanoma and basal cell carcinoma are 0.94 (ResNet152) and 0.93 (DenseNet201).
 
@@
 
-		\hl{Another state-of-the-art method is GradCam and Kernel SHAP~\mbox{\cite{06612}}.
+		{Another state-of-the-art method is GradCam and Kernel SHAP~\mbox{\cite{06612}}.
 Kyle Young~et~al.
@@
 Before feeding into the models,  images are preprocessed by binarization with a very low threshold to find the center of mass.
-This approach obtained an  AUC score of 0.85.} %Please check if meaning is retained.
-%H.K.D Fine
+This approach obtained an  AUC of 0.85.} %Please check if meaning is retained.
+%V.D.N confirmed
 
@@
 Therefore, the models can take full advantage of what others learn.
-The Student-and-Teacher model obtained an accuracy of 0.85; however, the precision and f1-score are quite low, resulting in a value of 0.76.
+The Student-and-Teacher model obtained an accuracy of 0.85; however, the precision and F1-score are quite low, resulting in a value of 0.76.
 
@@
 Both  SkinLinkNet and WonderM used UNet to perform the segmentation task, although they used EfficientNetB0 and DenseNet to perform the classification task.
-This approach obtained an AUC score of 0.92.
+This approach obtained an AUC of 0.92.
 
@@
 Otherwise,  data augmentation was also applied.
-This approach obtained a  recall score of 0.74.
-The low recall score may be due to the imbalanced data set.
+This approach obtained a  recall of 0.74.
+The low recall may be due to the imbalanced data set.
 
@@
 created a framework for Melanoma segmentation~\mbox{\cite{22750}}.
-Their proposed method is a Unet model but used  densenet77 as the  backbone, and all residual blocks were changed into dense block, which contains a sequence of Convolution and  Average Pooling.
+Their proposed method is a Unet model but used  DenseNet77 as the  backbone, and all residual blocks were changed into dense block, which contains a sequence of Convolution and  Average Pooling.
 This melanoma segmentation approach obtain an accuracy of 0.99.
@@
 The Deep Isolation Forest obtained  an accuracy of 0.9 and a confidence of 0.86.
-However, the AUC score is only 0.74, and this may due to the limitation of the machine learning algorithm.
+However, the AUC is only 0.74, and this may due to the limitation of the machine learning algorithm.
 
@@
 	\begin{table}[H]
-		\caption{Data Distribution in HAM10000.}
+		\caption{Data distribution in HAM10000.}
 		\label{table:data-distribution}
@@
 Here, $90$\% and $10$\% of the data is used for training and validating respectively.
-Images \hl{(See Figure \mbox{\ref{fig:data-sample}})} in this data set have the type of $RGB$ and shape of (450, 600).
-However, each backbone needs the different input sizes of images as well as the range of pixel value.
-	\begin{figure}[H]
-		\includegraphics[width=1\linewidth]{Definitions/DataDistribution}
-		\caption{\hl{Example} %MDPI: 1.
+Images in this data set have the type of $RGB$ and shape of (450, 600).
+However, each backbone needs the different input sizes of images as well as the range of pixel value {(as shown in Figure \mbox{\ref{fig:data-sample}})}.
+	\begin{figure}[H]
+		\includegraphics[width=0.8\linewidth]{Definitions/DataDistribution}
+		\caption{{Example} %MDPI: 1.
 Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
@@
 	\begin{table}[H]
-		\caption{\hl{Metadata}  example in the data set.}%MDPI: We remove the vertical line, please confirm. % H.K.D Confirm
+		\caption{{Metadata}  example in the data set.}%MDPI: We remove the vertical line, please confirm. % H.K.D Confirm
 		\label{table:metadata sample}
@@
 	\begin{figure}[H]
-		\includegraphics[width=0.8\linewidth]{Definitions/MainModel - Model Form}
-		\caption{Overall Model Architecture.}
+		\includegraphics[width=0.9\linewidth]{Definitions/MainModel - Model Form.PNG}
+		\caption{Overall model architecture.}
 		\label{fig:main-model}
@@
 	\begin{figure}[H]
-		\includegraphics[width=0.7\linewidth]{Definitions/Model Structure}
-		\caption{\hl{Overall Original} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) % H.K.D confirm
- Model Architecture.
-This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge.
+		\includegraphics[width=0.9\linewidth]{Definitions/Model  Structure.PNG}
+		\caption{{Proposed} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) % H.K.D confirm. %H.K.D confirmed  
+ backbone model architecture.
+This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge {with Soft-Attention}.
 The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed structure model}.}
@@
 	\begin{figure}[H]
-		\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
-		\caption{\hl{Overall mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) H.K.D confirm
- model architecture.
+		\includegraphics[width=0.9\linewidth]{Definitions/Mobile Model Structure.PNG}
+		\caption{{Mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) H.K.D confirm
+ backbone model architecture.
 This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
@@
 Finally, this dense layer is then concatenated with the output of Soft-Attention which is then discussed in the Soft-Attention section.
-The Input schema is described in \hl{Figure} %MDPI: We changed Table to Figure.
+The Input schema is described in {Figure} %MDPI: We changed Table to Figure.
 Please confirm this revision.
@@
 		\includegraphics[width=1\linewidth]{"Definitions/Input Schema"}
-		\caption{Input Schema.}
+		\caption{Input schema.}
 		\label{fig:input-schema}
@@
 The combination of DenseNet201, InceptionResNetV2, and the Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance.
-Otherwise, Resnet50 also well classifies but with much fewer number of parameters and less depth than based on its f1-score and precision stated.
+Otherwise, Resnet50 also well classifies but with much fewer number of parameters and less depth than based on its F1-score and precision stated.
 Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge models, which have more parameters and depth, is analyzed.
-On the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed, which has fewer parameters \hl{(see Figure \mbox{\ref{table:model-summary}})} and depth.
+On the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed, which has fewer parameters {(as shown in Table \mbox{\ref{table:model-summary}})} and depth.
 
 	\begin{table}[H]
-		\caption{\hl{Size} %MDPI: 1. Please cite the table in the text and ensure the first citation of each table appears in numerical order. 2. We remove the vertical line, please confirm.
- , parameters, and depth of the backbone model used in this paper.}
+		\caption{{Size}, parameters, and depth of the backbone model used in this paper.}%MDPI: 1.
+Please cite the table in the text and ensure the first citation of each table appears in numerical order.
+2.
+We remove the vertical line, please confirm.
+		%V.D.N confirmed
 		\label{table:model-summary}
@@
 Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights.
-Soft-Attention is described in the below equation \eqref{eqn:softatt}.
+Soft-Attention is described in {Equation}
+	\eqref{eqn:softatt}. % V.D.N We update the uppercase of "Equation"
 
@@
 This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network (CNN), is then input to a 3D convolution layer whose weights are $W_k \in R^{h \times w \times d \times K}$.
-The output of this convolution is normalized using the soft-max function to generate \hl{\textit{K}} %MDPI: Please change the forward italics of the variables in the text and formulas to be consistent
+The output of this convolution is normalized using the soft-max function to generate {\textit{K}} %MDPI: Please change the forward italics of the variables in the text and formulas to be consistent
 	% H.K.D We have the changed the "K" into italics form
  (a constant value) attention maps.
-These $K$ attention maps are aggregated to produce a weight function called $\alpha$.
+These $\textit{K}$ attention maps are aggregated to produce a weight function called $\alpha$.
 This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, which is a learnable scalar.
@@
 		\includegraphics[width=1\linewidth]{Definitions/SoftAttention}
-		\caption{\hl{Soft-Attention~Layer.} %MDPI: Please revise the "*" into a multiplication sign ("\times" U+00D7)
+		\caption{{Soft-Attention layer.} %MDPI: Please revise the "*" into a multiplication sign ("\times" U+00D7) 
 }
@@
 
-	In this research, the Soft-Attention layer is applied in the same way in this research \cite{03358}. The Soft-Attention module is described in the Figure \ref{fig:soft-attention-block}.
+	In this research, the Soft-Attention layer is applied in the same way in \cite{03358}. The Soft-Attention module is described in Figure \ref{fig:soft-attention-block}.
 
@@
 		\includegraphics[width=0.5\linewidth]{Definitions/SoftAttentionBlock}
-		\caption{\hl{Soft-Attention~Module.} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7)
+		\caption{{Soft-Attention module.} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7)
 		%H.K.D We have already changed the the multiplication sign into "x" in the Figure 6
@@
 	\subsubsection{Loss Function}
-	The loss function used in this paper is categorical cross-entropy \hl{\mbox{\cite{8943952}}}.
+	The loss function used in this paper is categorical cross-entropy {\mbox{\cite{8943952}}}. %V.D.N We have provided the citation to paper 8943952.
 	Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$.
 Let $N$, and $C$ be the number of training examples and number of classes respectively.
-The categorical cross-entropy loss is presented in the Equation \eqref{eqn:weightlossfunction}:
+The categorical cross-entropy loss is presented in Equation \eqref{eqn:weightlossfunction}:
 	\begin{equation}
@@
 
-	Otherwise, all of the models are trained with the Adam \hl{Optimizer} %MDPI: The citation of references [37-42] are missing. Please add and renumber the references to appear in numerical order.
+	Otherwise, all of the models are trained with the Adam {optimizer} %MDPI: The citation of references [37-42] are missing.
+Please add and renumber the references to appear in numerical order.
+%H.K.D We have already provide the citations for all paper
  \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 \times 10^6$, and the epsilon is set to $0.1$.
@@
 		\begin{figure}[H]
-\includegraphics[width=0.6\linewidth]{Definitions/Confusion-matrix}
-\caption{Confusion Matrix.}\label{fig:confusion-matrix}
+\includegraphics[width=0.7\linewidth]{Definitions/Confusion-matrix}
+\caption{Confusion matrix.}\label{fig:confusion-matrix}
 		\end{figure}\unskip
 \begin{figure}[H]
-\includegraphics[width=.5\linewidth]{Definitions/AUC}
-\caption{\hl{Area} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order. % H.K.D Citation provided
- Under the Curve.}\label{fig:AUC}
+\includegraphics[width=.7\linewidth]{Definitions/AUC}
+\caption{{Area} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order. % H.K.D Citation provided
+ under the curve.}\label{fig:AUC}
 	\end{figure}
 
-	The True Positive (\hl{\textit{TP}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
+	The True Positive ({\textit{TP}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
 ) of all classes in this case is the main diagonal of the matrix $A$.
-The~following methods are used to calculate the False Positives (\hl{\textit{FP}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
-), False Negatives (\hl{\textit{FN}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
-), and~True Negatives (\hl{\textit{TN}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
+The~following methods are used to calculate the False Positives ({\textit{FP}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
+), False Negatives ({\textit{FN}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
+), and~True Negatives ({\textit{TN}}%MDPI: Please change the forward italics of the variables in the text and formulas to be consistent %H.K.D Italics word changed
 ) of all classes:
@@
 
-	\hl{Then,} %MDPI: Please confirm should the no indentation be retained
+	{Then,} %MDPI: Please confirm should the no indentation be retained
 	% H.K.D I think it would be better if there is no indentation but do not know to do it, could you help me remove it.
@@
 		\label{eqn:sens}
-		\text{Sensitivity (Sens)} = \frac{TP}{TP + FN}
+		\text{\textit{Sensitivity (Sens)}} = \frac{TP}{TP + FN}
 	\end{equation}
@@
 		\label{eqn:spec}
-		\text{Specificity (Spec)} = \frac{TN}{TN + FP}
+		\text{\textit{Specificity (Spec)}} = \frac{TN}{TN + FP}
 	\end{equation}
@@
 		\label{eqn:pre}
-		\text{Precision} = \frac{TP}{TP + FP}
+		\text{\textit{Precision}} = \frac{TP}{TP + FP}
 	\end{equation}
@@
 		\label{eqn:f1}
-		\text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\
+		\text{\textit{F1-score}} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\
 	\end{equation}
 
-	\hl{Precision} %MDPI: Please confirm should the no indentation be retained
-	% H.K.D I think it would be better if there is no indentation but do not know to do it, could you help me remove it.
+	{Precision} %MDPI: Please confirm should the no indentation be retained
+	% V.D.N confirmed
  (Equation \eqref{eqn:pre}) or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative.
-F1-score (Equation \eqref{eqn:f1}), on the other hand, refers to the harmonic mean of precision and recall, which means the higher the f1-score is, the higher both precision and recall are.
-Besides, the expected value of precision, f1-score, and recall-score are also applied because of the multi-class problem.
+F1-score (Equation \eqref{eqn:f1}), on the other hand, refers to the harmonic mean of precision and recall, which means the higher the F1-score is, the higher both precision and recall are.
+Besides, the expected value of precision, F1-score, and recall are also applied because of the multi-class problem.
 
@@
 		\label{eqn:acc}
-		\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN}
+		\text{\textit{Accuracy}} = \frac{TP + TN}{TP + FP + FN + TN}
 	\end{equation}
@@
 		\label{eqn:balacc}
-		\text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}
+		\text{\textit{Balanced Accuracy}} = \frac{\text{Sens} + \text{Spec}}{2}
 	\end{equation}
 
-	\hl{The last} %MDPI: Please confirm should the no indentation be retained
-	% H.K.D I think it would be better if there is no indentation but do not know to do it, could you help me remove it.
- metric is the $AUC$ \hl{(see Figure \mbox{\ref{fig:AUC}})} score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of TP versus the probability of FP.
+	{The last} %MDPI: Please confirm should the no indentation be retained
+	% V.D.N confirmed.
+ metric is the $AUC$ {(as shown in Figure \mbox{\ref{fig:AUC}})} score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of TP versus the probability of FP.
 
@@
 While InceptionResNetV2 and DenseNet201 trained with augmented data have an accuracy of $0.79$ and $0.84$, respectively, their training with metadata are $0.90$ and $0.89$, respectively.
-Furthermore, Resnet50 trained with metadata data has the accuracy that outperforms the Resnet50 trained with augmented data and is twice as high as Resnet152 trained with metadata.
+Furthermore, Resnet50 trained with metadata data has the accuracy that outperforms the Resnet50 trained with augmented data and is twice as high as ResNet152 trained with metadata.
 On the other hand, mobile models including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though they have a much smaller number of parameters and depth than the other model, they have quite good accuracy scores of $0.81$, $0.86$ and $0.86$, respectively.
@@
 AD stands for augmented data; this indicates that the model is trained with augmented data.
-MD stands for metadata, which indicates that the model is trained with metadata.}
+MD stands for metadata, which indicates that the model is trained with metadata.
+The bold numbers highlight the highest performance.}
 		\label{table:overall-acc}
@@
 \midrule
-InceptionResNetV2 & 0.79 & \textbf{\hl{0.90} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. 
+InceptionResNetV2 & 0.79 & \textbf{{0.90} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. 
 %H.K.D We have already explain it in the paragraph before the Table 5
@@
 \midrule
-DenseNet201 & 0.84 & \textbf{0.89}\\
+DenseNet201 & 0.84 & 0.89\\
 \midrule
@@
 
-	Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to Figures \ref{fig:den f1}--\ref{fig:incep recall}.
-As a result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data has an f1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to the Figure \ref{fig:incep f1}.
-However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depths are equal to or larger than 400 have balanced the f1-scores on class.
+	Moreover, the model trained with augmented data does not only have low accuracy but their F1-score and the recall also are imbalanced according to Figures \ref{fig:den f1}--\ref{fig:incep recall}.
+As a result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data has an F1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to the Figure \ref{fig:incep f1}.
+However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depths are equal to or larger than 400 have balanced the F1-scores on class.
 The others still face the imbalanced term.
@@
 \centering
-\includegraphics[width=1.2\linewidth]{Definitions/CM/dn201cm}
+\includegraphics[width=1.3\linewidth]{Definitions/CM/dn201cm}
 		\end{minipage}
-\caption{\hl{DenseNet201} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
+\caption{{DenseNet201} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
 	% H.K.D Citation Provided
- Confusion Matrix.}\label{fig:densenet201cm}
+ confusion matrix.}\label{fig:densenet201cm}
 		\end{figure}\unskip
@@
 \centering
-\includegraphics[width=1.2\linewidth]{Definitions/CM/irv2cm}
+\includegraphics[width=1.3\linewidth]{Definitions/CM/irv2cm}
 		\end{minipage}
-\caption{\hl{InceptionResNetV2} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
+\caption{{InceptionResNetV2} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
 % H.K.D Citation Provided
- Confusion Matrix.}\label{fig:irv2cm}
+ confusion matrix.}\label{fig:irv2cm}
 	\end{figure}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{Definitions/den f1}
-		\caption{The comparison between f1 scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
+		\includegraphics[width=1\linewidth]{Definitions/den f1.PNG}
+		\caption{The comparison between F1-scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
 		\label{fig:den f1}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{Definitions/in f1}
-		\caption{The comparison between f1 scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
+		\includegraphics[width=1\linewidth]{Definitions/in f1.PNG}
+		\caption{The comparison between F1-scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
 		\label{fig:incep f1}
@@
 
-\textls[-15]{	This problem is also true with the recall score according to Figures \ref{fig:den recall} and \ref{fig:incep recall}.
+\textls[-15]{	This problem is also true with the recall according to Figures \ref{fig:den recall} and \ref{fig:incep recall}.
 DenseNet201 and InceptionResNetV2, trained with augmented data have expected recall values of $0.56$ and $0.69$, respectively, while the combination of DenseNet201, Metadata, and the new weight loss function achieve the expected value of recall: $0.82$.
@@
 		\centering
-		\includegraphics[width=1\linewidth]{Definitions/den re}
-		\caption{The comparison between recall scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
+		\includegraphics[width=1\linewidth]{Definitions/den re.PNG}
+		\caption{The comparison between recall of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
 		\label{fig:den recall}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{Definitions/in re}
-		\caption{The comparison between recall scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
+		\includegraphics[width=1\linewidth]{Definitions/in re.PNG}
+		\caption{Comparison between recall of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
 		\label{fig:incep recall}
@@
 	Another interesting point found during the experiment is that MobileNetV2, MobileNetV3, and NasNetMobile have a small number of parameters and depth, but they have relatively good performance.
-MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall scores of $0.92$, $1$, $0.92$ and  $0.92$, separately, according to the Table \ref{appendix-table:mobile-performance}.
-It is transparent that MobileNetV3Large and NasNetMobile are the two best performance models.
+MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall of $0.92$, $1$, $0.92$ and  $0.92$, respectively, according to the Table \ref{appendix-table:mobile-performance}.
+It is obvious that MobileNetV3Large and NasNetMobile are the two best performance models.
 Nevertheless, MobileNetV3Large has fewer number of parameters and depth than NasNetMobile.
@@
 Since MobileNetV3Large needs a harder process of parameter hyper-tuning to achieve a better result, this is also the future target of this research.
+
 	\begin{table}[H]
-		\caption{%\change[H.K.D]{Performance Comparison between MobileNetV3Large and DenseNet201, InceptionResNetV2}
-		{How the performance of MobileNetV3Large can be optimized.}}
+		\caption{%\change[H.K.D]{Performance Comparison between MobileNetV3Large and DenseNet201, InceptionResNetV2} %V.D.N We have already changed the caption of Figure 6
+		{Comparison between MobileNetV3Large with DenseNet201 and InceptionResNetV2.}}
 		\label{table:optimized-performance-mobile-model}
@@
 \midrule
-No. Trainable Parameters & \textbf{\hl{5,490,039} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. The following highlights are the same.
+No. Trainable Parameters & \textbf{{5,490,039} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. The following highlights are the same.
 } & 17,382,935 & 47,599,671\\
@@
 	\end{table}
-
-	Table \ref{table:overall-auc} shows the AUC score of the three models—InceptionResNetV2, Densenet201, and ResNet50—which are trained with only augmented data or metadata.
-It is transparent that the InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: both 0.99 as opposed to 0.972 and 0.93, respectively.
-ResNet50 trained with augmented data, on the other hand, has a higher AUC-score: 0.95 as compared to 0.93 of ResNet50 trained with metadata.
-Overall, InceptionResNetV2 trained with metadata reaches the peak with an AUC score of 0.974.
+	Table \ref{table:overall-auc} shows the AUC of the three models—InceptionResNetV2, Densenet201, and ResNet50—which are trained with only augmented data or metadata.
+It is transparent that the InceptionResNetV2 and DenseNet201 have higher AUC trained with metadata: both 0.99 as opposed to 0.972 and 0.93, respectively.
+ResNet50 trained with augmented data, on the other hand, has a higher AUC of 0.95 as compared to 0.93 of ResNet50 trained with metadata.
+Overall, InceptionResNetV2 trained with metadata reaches the peak with an AUC of 0.974.
 The InceptionResNetV2 trained with metadata is also compared with the others to find out the best models trained.
-According to Figure \ref{fig:densevsirv2}, \hl{\mbox{\ref{fig:densenet201cm}, and \ref{fig:irv2cm}}} the InceptionResNetV2 still hit the peak AUC score of 0.99.
-In contrast, ResNet152 otherwise is the worst model with the AUC score of 0.87.
-Other models, on the other hand, have the approximately the same AUC score.
+According to Figure {\mbox{\ref{fig:densenet201cm}, \ref{fig:irv2cm}, and \ref{fig:densevsirv2}}} the InceptionResNetV2 still hit the peak AUC of 0.99.
+In contrast, ResNet152 otherwise is the worst model with the AUC of 0.87.
+Other models, on the other hand, have the approximately the same AUC.
 
 	\begin{table}[H]
-			\caption{AUC (area under the curve) of all models.
+			\caption{AUCs of all models.
 AD stands for augmented data, this indicates that the model is trained with augmented data.
-MD stands for metadata, which indicates that the model is trained with metadata.}
+MD stands for metadata, which indicates that the model is trained with metadata.
+Bold numbers highlight the highest performance}
 		\label{table:overall-auc}
@@
 \midrule
-InceptionResNetV2 & 0.971 & \textbf{\hl{0.99} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. The following highlights are the same.
+InceptionResNetV2 & 0.971 & \textbf{{0.99} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. The following highlights are the same.
 %H.K.D We have already added the explaination in the paragraph before the Table 7
@@
 \midrule
-ResNet50 & \textbf{0.95} & 0.93 \\
+ResNet50 & 0.95 & 0.93 \\
 \midrule
@@
 \midrule
-NasNetLarge & 0.74 & \textbf{0.96}\\
+NasNetLarge & 0.74 & 0.96\\
 \midrule
@@
 \midrule
-MobileNetV3Small & 0.67 & \textbf{0.96}\\
+MobileNetV3Small & 0.67 & 0.96\\
 \midrule
@@
 	\end{table}\unskip
+
 	\begin{figure}[H]
 		\centering
-		\includegraphics[width=.9\linewidth]{Definitions/ROC/denvsirv2}
+		\includegraphics[width=1\linewidth]{Definitions/ROC/denvsirv2}
 		\caption{ROC of DenseNet201 and InceptionResNetV2.}\label{fig:densevsirv2}
@@
 
-	According to \hl{Tables} %MDPI: there is no table:densenet201auc in the tex, please check and revise.
+	According to {Tables} %MDPI: there is no table:densenet201auc in the tex, please check and revise.
 	% H.K.D We have removed the unnecessary part
@@
 However, since Soumyyak~et~al.
-uses data augmentation for all class of an imbalanced data set, the f1-score and recall score are much lower.
+uses data augmentation for all class of an imbalanced data set, the F1-score and recall are much lower.
 This is because the model in that research can only classify well on NV and VASC classes, which have the highest number of samples.
-On the other hand, the InceptionResNetV2 in this research also outperforms the other models according to five indicators: accuracy, precision, f1-score, recall score, and AUC score.
+On the other hand, the InceptionResNetV2 in this research also outperforms the other models according to five indicators: accuracy, precision, F1-score, recall, and AUC.
 	\begin{table}[H]
@@
 	\begin{table}[H]
-		\caption{Comparative Analysis.}
+		\caption{Comparative Analysis. Bold numbers highlight the highest performance.}
 		\label{table:comparative-analysis}
@@
 \toprule
-\textbf{Approach} & \textbf{Accuracy} & \textbf{Precision} & \textbf{F1-Score} & \textbf{Recall} & \textbf{Auc-Score}\\
+\textbf{Approach} & \textbf{Accuracy} & \textbf{Precision} & \textbf{F1-score} & \textbf{Recall} & \textbf{AUC}\\
 \midrule
@@
 \midrule
-Proposed Method & 0.9	& 0.86 & \hl{0.86} & \hl{0.81} & \hl{0.99}%MDPI: Please confirm if the bold should be retained. If not necessary, please remove.
+Proposed Method & 0.9	& 0.86 & {\textbf{0.86}} & {\textbf{0.81}} & {\textbf{0.99}}%MDPI: Please confirm if the bold should be retained.
+If not necessary, please remove.
+%V.D.N We confirmed to continue to use bold numbers.
 \\
@@
 		\centering
-		\includegraphics[width=1\linewidth]{Definitions/img_class_nevus_mela}
+		\includegraphics[width=0.9\linewidth]{Definitions/img_class_nevus_mela}
 		\caption{Model ability to classify melanoma and nevus.}
@@
 	\section{Conclusions}
-	In this research, our proposal is to construct a model as a combination of backbone models and Soft-Attention.
+	In this work, we proposed a model formed by a combination of one backbone model and Soft-Attention.
 Moreover, the model takes two inputs, including image data and metadata.
@@
 Finally, the combination of InceptionResNetV2, Soft-Attention, and metadata is the best model with an accuracy of 0.9.
-Although the accuracy and the precision of the model are not the highest, the f1-score, recall, and AUC score of 0.86, 0.81, and 0.975, respectively are the highest and the most balanced indicators.
+Although the accuracy and the precision of the model are not the highest, the F1-score, recall, and AUC of 0.86, 0.81, and 0.975, respectively are the highest and the most balanced indicators.
 Therefore, InceptionResnetV2 can classify well in all classes including low-samples classes.
@@
 
-	\dataavailability{\textls[-15]{The code and the data analysis report can be found here:} \url{https://github.com/KhoiDOO/Skin-Disease-Detection-HAM100000.git}  (\hl{accessed on 29 August 2022}%MDPI: Please add the access date (Format: Date Month Year) that earlier than Received date.
+	\dataavailability{\textls[-15]{The code and the data analysis report can be found here:} \url{https://github.com/KhoiDOO/Skin-Disease-Detection-HAM100000.git}  ({accessed on 29 August 2022}%MDPI: Please add the access date (Format: Date Month Year) that earlier than Received date.
 e.g., (accessed on 29 August 2022).
@@
 ).} 
-
-	\acknowledgments{We thank Vingroup innovation Foundation (VINIF) projtect code VININF.2021.DA00192 for providing computational resources for the work}
+	\acknowledgments{We thank Vingroup innovation Foundation (VINIF) project code \\VINIF.2021.DA00192 for providing computational resources for the work} %V.D.N We have provided the acknowledgement.
 
@@
 	\begin{table}[H]
-			\caption{\hl{Detailed structure} %MDPI: 1.
+			\caption{{Detailed structure} %MDPI: 1.
 We revised the "x" into a multiplication sign ("\times" U+00D7).
@@
 	\begin{table}[H]
-		\caption{\hl{Detailed} structure of mobile-based models.
+		\caption{{Detailed} structure of mobile-based models.
 SA stands for Soft-Attention, SA Module denotes whether that model uses the Soft-Attention module.
@@
 		\begin{table}[H]
-\caption{\hl{F1-score%MDPI: Please confirm if the vertical line is necessary, if not, please remove it. 
+\caption{{F1-score%MDPI: Please confirm if the vertical line is necessary, if not, please remove it. 
 % H.K.D beautiful no vertical line
 } of each class: akiec, bcc, bkl, df, mel, nv and vasc, which are denoted in the abbreviations.
-The last column shows the expected value of the f1-score from each model.
+The last column shows the expected value of the F1-score from each model.
 All models in the first column are the models trained in this research.
@@
 The term “with Metadata and WeightLoss” means that the model is trained with metadata including age, gender, localization, and the weight loss function, there is no augmented data contribution.
-\hl{Besides the bold number highlights achievement of the research}}
+{Besides the bold number highlights achievement of the research}}
 \label{appendix-table:F1-score-summary}
@@
 	\midrule		
-	DenseNet201 with Metadata and WeightLoss & \textbf{\hl{0.84} %MDPI: Please add an explanation for bold in the table footer.
+	DenseNet201 with Metadata and WeightLoss & \textbf{{0.84} %MDPI: Please add an explanation for bold in the table footer.
 If the bold is unnecessary, please remove it.
@@
 		\begin{table}[H]
-\caption{\hl{Recall%MDPI: We remove the vertical line, please confirm. %H.K.D too beautiful
-} score of each class and the expected value of recall score from each model.}
+\caption{{Recall%MDPI: We remove the vertical line, please confirm. %H.K.D too beautiful
+} of each class and the expected value of recall from each model.}
 \label{appendix-table:recall-score-summary}
@@
 	\midrule		
-	DenseNet201 with Metadata and WeightLoss & \textbf{\hl{0.85}} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
+	DenseNet201 with Metadata and WeightLoss & \textbf{{0.85}} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\
 	\midrule
@@
 
-		\subsection[\appendixname~\thesection]{Detailed Mobile Model Perform}
+		\subsection[\appendixname~\thesection]{Detailed Mobile Model Performance}
 		\begin{table}[H]
-\caption{\hl{Deeper%MDPI: We remove the vertical line, please confirm. 
+\caption{{Deeper%MDPI: We remove the vertical line, please confirm. 
 %H.K.D No more words to describe how beatiful the table is 
@@
 This table illustrates the other indicators of the four mobile-based models including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
-The indicators are Accuracy, Balanced Accuracy, Precision, F1-score, Sensitivity, Specificity, and ROC--AUC score.
+The indicators are Accuracy, Balanced Accuracy, Precision, F1-score, Sensitivity, Specificity, and AUC.
 All of them are average indicators.}
@@
 	\midrule
-	Accuracy (avg) & 0.81 & 0.78 & 0.86 & \textbf{\hl{0.86}}\\
+	Accuracy (avg) & 0.81 & 0.78 & 0.86 & \textbf{{0.86}}\\
 	\midrule
@@
 	\midrule
-	ROC-AUC-score (avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
+	AUC (avg) & 0.96 & 0.95 & 0.96 & \textbf{0.97}\\
 	\bottomrule
@@
 \bibitem[Author2(year)]{03358}
-\hl{Datta, S.K.; Shaikh, M.A.; Srihari, S.N.; Gao, M.}%MDPI: We have completed all the missing information according to scholar, please check all references
+{Datta, S.K.; Shaikh, M.A.; Srihari, S.N.; Gao, M.}%MDPI: We have completed all the missing information according to scholar, please check all references
  Soft-Attention Improves Skin Cancer Classification Performance.
@@
 {Gao, H.; Zhuang, L.; Kilian, Q.
-Weinberger: Densely Connected Convolutional Network.} In Proceedings of the 2017 \hl{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, Honolulu, HI, USA, 21--26 July 2017.
+Weinberger: Densely Connected Convolutional Network.} In Proceedings of the 2017 {IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, Honolulu, HI, USA, 21--26 July 2017.
 
@@
 Howard, A.; Sandler, M.; Chu, G.; Chen, Li.; Chen, B.; Tan, M.; Wang, W.; Zhu, Y.; Pang, R.; Vasudevan, V.; Le, Q.V.; Adam, H. Searching for MobileNetV3.
-In Proceedings of the 2019 IEEE/CVF International Conference on \hl{Computer Vision (ICCV), Seoul, Korea, 27 October--2 November 2019.}
+In Proceedings of the 2019 IEEE/CVF International Conference on {Computer Vision (ICCV), Seoul, Korea, 27 October--2 November 2019.}
 
@@
 Young, K.; Booth, G.; Simpson, B.; Dutton, R.; Shrapnel, S.  Dermatologist Level Dermoscopy Deep neural network or dermatologist? {\em Nature} 
-{\bf \hl{2021} %MDPI: Please add the volume and pagination, or doi number.
-}.
+{\bf {2021}}, \emph{542}, 115--118.%MDPI: Please add the volume and pagination, or doi number.
 
@@
 Shaikh, M.A.; Duan, T.; Chauhan, M.; Srihari, S.N.
-\hl{Attention} %MDPI: please check if this reference is dplicated with ref 40.
+{Attention} %MDPI: please check if this reference is dplicated with ref 40.
 If it is, please remove the duplicated reference and rearrange all the references to appear in numerical order.
@@
 \bibitem[Author2(year)]{02357-1}
-\hl{Shaikh, M.A.;} %MDPI: The label 02357 is repeated. We updated this one, please confirm. % H.K.D it's duplicated with the research paper cited 33, please remove it
- Duan, T.; Chauhan, M.; Srihari, S.N. \hl{In} %MDPI: please add the article title.
+{Shaikh, M.A.;} %MDPI: The label 02357 is repeated. We updated this one, please confirm. % H.K.D it's duplicated with the research paper cited 33, please remove it
+ Duan, T.; Chauhan, M.; Srihari, S.N. {In} %MDPI: please add the article title.
  Proceedings of the 2020 17th International Conference on Frontiers in Handwriting Recognition, Dortmund, Germany, 8--10 September 2020.

### 2022-10-03 MDPI/sensors-1915564-redo - For Proof - Copy/sensors-1915564.tex
Update Paper Final Version

--- 2022-10-03 MDPI/sensors-1915564 - Copy/sensors-1915564.tex
@@
 \usepackage{soulutf8}
-%\usepackage[adjustmargins]{LatexPackage/trackchanges}
-%\addeditor{H.K.D}
+\usepackage[adjustmargins]{LatexPackage/trackchanges}
+\addeditor{H.K.D}
 
@@
  of Electrical and Electronic Engineering, Hanoi University of Science and Technology, {Dai Co Viet, Ha Noi 100000, Vietnam;} %MDPI: Please add the city and post code.
-{khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct. %H.K.D confirmed
+{dung.nguyenviet1@hust.edu.vn, khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct. %H.K.D confirmed
 \\
@@
 In this research study, our proposed method used  Soft-Attention, which can create a heat map feature of the lesion.
-Otherwise, Rishu Garg~et~al.'s proposed method also faced the problem of imbalanced classification due to an imbalanced dataset with the F1-score and recall at 0.77 and 0.74, respectively.
+Otherwise, Rishu Garg~et~al.'s proposed method also faced the problem of imbalanced classification due to an imbalanced dataset with the F1-score and recall of 0.77 and 0.74, respectively.
 
@@
 Kadry~et~al.
-used a Unet model with a VGG deep convolution layer by pooling on the skip connection.
+used a Unet model with a VGG16 deep convolution layer by pooling on the skip connection.
 This approach can completely extract the entire lesion, although there was an overlap observed with hair.
@@
 There are a total of 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), basal cell carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
-The distribution of the data set is shown in the Table \ref{table:data-distribution} below:
+The distribution of the data set is shown in Table \ref{table:data-distribution} below:
 
@@
 	Figure \ref{fig:mobile-model-structure}, on the other hand, shows the detailed structure of the mobile-based mobile and its combination with Soft-Attention.
-All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution layers 1 \hl{$\times$} %MDPI: We revised the "x" into a multiplication sign ("\times" U+00D7).
+All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution layers 1 {$\times$} %MDPI: We revised the "x" into a multiplication sign ("\times" U+00D7).
 Please confirm.
@@
 	The model is evaluated by using the confusion matrix and related metrics.
-The Figure~\ref{fig:confusion-matrix} illustrates the presentation of a $2 \times 2$ confusion matrix used for class $2$ .
+Figure~\ref{fig:confusion-matrix} illustrates the presentation of a $2 \times 2$ confusion matrix used for class $2$ .
 Consider a confusion matrix $A$ with $C$ number of classes.
@@
 	% V.D.N confirmed.
- metric is the $AUC$ {(as shown in Figure \mbox{\ref{fig:AUC}})} score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of TP versus the probability of FP.
+ metric is the $AUC$ {(as shown in Figure \mbox{\ref{fig:AUC}})} score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of \textit{TP} versus the probability of \textit{FP}.
 
@@
 MD stands for metadata, which indicates that the model is trained with metadata.
-The bold numbers highlight the highest performance.}
+The bold numbers highlight the highest performance.
+These results are calculated from the confusion matrix, the two highest model confusion matrices are DenseNet201 and InceptionResNetV2 (as shown in Figure {\mbox{\ref{fig:densenet201cm} and \ref{fig:irv2cm}}})}
 		\label{table:overall-acc}
@@
 
-	Moreover, the model trained with augmented data does not only have low accuracy but their F1-score and the recall also are imbalanced according to Figures \ref{fig:den f1}--\ref{fig:incep recall}.
-As a result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data has an F1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to the Figure \ref{fig:incep f1}.
+	Moreover, the model trained with augmented data does not only have low accuracy but their F1-score and recall also are imbalanced according to Figures \ref{fig:den f1}--\ref{fig:incep recall}.
+As a result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data has an F1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to Figure \ref{fig:den f1} and \ref{fig:incep f1}.
 However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depths are equal to or larger than 400 have balanced the F1-scores on class.
@@
 \centering
-\includegraphics[width=1.3\linewidth]{Definitions/CM/dn201cm}
+\includegraphics[width=1\linewidth]{Definitions/CM/dn201cm}
 		\end{minipage}
@@
 \centering
-\includegraphics[width=1.3\linewidth]{Definitions/CM/irv2cm}
+\includegraphics[width=1\linewidth]{Definitions/CM/irv2cm}
 		\end{minipage}
@@
 \textls[-15]{	This problem is also true with the recall according to Figures \ref{fig:den recall} and \ref{fig:incep recall}.
-DenseNet201 and InceptionResNetV2, trained with augmented data have expected recall values of $0.56$ and $0.69$, respectively, while the combination of DenseNet201, Metadata, and the new weight loss function achieve the expected value of recall: $0.82$.
+DenseNet201 and InceptionResNetV2, trained with augmented data have expected recall values of $0.56$ and $0.69$, respectively, while the combination of DenseNet201, Metadata, and the new weight loss function achieve the expected value of recall of $0.82$.
 Therefore, metadata do improve the model performance by reducing the amount of data needed for achieving higher results.
@@
 
-\bibitem[Author2(year)]{02357-1}
-{Shaikh, M.A.;} %MDPI: The label 02357 is repeated. We updated this one, please confirm. % H.K.D it's duplicated with the research paper cited 33, please remove it
- Duan, T.; Chauhan, M.; Srihari, S.N. {In} %MDPI: please add the article title.
- Proceedings of the 2020 17th International Conference on Frontiers in Handwriting Recognition, Dortmund, Germany, 8--10 September 2020.
-
 		\end{thebibliography}

### 2022-10-03 MDPI/sensors-1915564-redo - For Proof/sensors-1915564.tex
Update Paper Final Version

@@
  of Electrical and Electronic Engineering, Hanoi University of Science and Technology, \hl{Vietnam;} %MDPI: Please add the city and post code.
-\hl{ khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct.
+\hl{dung.nguyenviet1@hust.edu.vn, khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct. %H.K.D confirmed
 \\
@@
 	To adapt the rise in skin cancer cases, AI algorithms over the last decade has a great performance.
-Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet~\cite{04861}, Inception \cite{00567}\hl{\mbox{\cite{07261}}}, MobileNets\cite{04861,04381,02244}, \hl{Xception\mbox{\cite{02357}}}, ResNet \cite{03385,05027}, and NasNet \cite{07012}.
+Some typical models that can be mentioned are DenseNet \cite{06993}, EfficientNet~\cite{04861}, Inception \cite{00567,07261}, MobileNets\cite{04861,04381,02244}, \hl{Xception\mbox{\cite{02357}}}, ResNet \cite{03385,05027}, and NasNet \cite{07012}.
 Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.
@@
 	{Skin lesion classification is not a new area, since there are many great performance models constructed, recent years.
-The skin classification approaches can be divided into two main approaches: Deep Learning and Machine Learning.
+The skin classification approaches can be divided into two main approaches: Deep Learning and Machine Learning (\hl{\mbox{as shown in Table \ref{table:related-work-summary}}}).
 Both approaches gain great performance.
 Data Augmentation and Feature Extractor, otherwise are two main supporters that make the model better.
+%H.K.D We provided the citation to Table 1
 		\begin{table}[H]
-\caption{\hl{Related} %MDPI: we updated the format of all tables, please confirm the change. Please cite the table in the text and ensure the first citation of each table appears in numerical order.
- Works Summary.}
+\caption{\hl{Summary of related} %MDPI: we updated the format of all tables, please confirm the change.
+Please cite the table in the text and ensure the first citation of each table appears in numerical order.
+%H.K.D We also changed the table caption
+works.}
 \label{table:related-work-summary}
@@
 There are a total of 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), basal cell carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC).
-The distribution of the data set is shown in the Table \ref{table:data-distribution} below:
+The distribution of the data set is shown in Table \ref{table:data-distribution} below:
 
 	\begin{table}[H]
-		\caption{Data Distribution in HAM10000.}
+		\caption{Data distribution in HAM10000.}
 		\label{table:data-distribution}
@@
 Here, $90$\% and $10$\% of the data is used for training and validating respectively.
-Images \hl{(See Figure \mbox{\ref{fig:data-sample}})} in this data set have the type of $RGB$ and shape of (450, 600).
-However, each backbone needs the different input sizes of images as well as the range of pixel value.
-	\begin{figure}[H]
-		\includegraphics[width=1\linewidth]{Definitions/DataDistribution}
+Images in this data set have the type of $RGB$ and shape of (450, 600).
+However, each backbone needs the different input sizes of images as well as the range of pixel value \hl{(as shown in Figure \mbox{\ref{fig:data-sample}})}.
+	\begin{figure}[H]
+		\includegraphics[width=0.8\linewidth]{Definitions/DataDistribution}
 		\caption{\hl{Example} %MDPI: 1.
@@
 	\begin{figure}[H]
-		\includegraphics[width=0.8\linewidth]{Definitions/MainModel - Model Form}
-		\caption{Overall Model Architecture.}
+		\includegraphics[width=0.9\linewidth]{Definitions/MainModel - Model Form}
+		\caption{Overall model architecture.}
 		\label{fig:main-model}
@@
 	\begin{figure}[H]
-		\includegraphics[width=0.7\linewidth]{Definitions/Model Structure}
-		\caption{\hl{Overall Original} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) % H.K.D confirm
- Model Architecture.
-This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge.
+		\includegraphics[width=0.9\linewidth]{Definitions/Model Structure}
+		\caption{\hl{Proposed} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) % H.K.D confirm. %H.K.D confirmed
+ backbone model architecture.
+This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge \hl{with Soft-Attention}.
 The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed structure model}.}
@@
 	\begin{figure}[H]
-		\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
-		\caption{\hl{Overall mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) H.K.D confirm
- model architecture.
+		\includegraphics[width=0.9\linewidth]{Definitions/Mobile Model Structure}
+		\caption{\hl{Mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) H.K.D confirm
+ backbone model architecture.
 This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile.
@@
 The combination of DenseNet201, InceptionResNetV2, and the Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance.
-Otherwise, Resnet50 also well classifies but with much fewer number of parameters and less depth than based on its f1-score and precision stated.
+Otherwise, Resnet50 also well classifies but with much fewer number of parameters and less depth than based on its F1-score and precision stated.
 Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge models, which have more parameters and depth, is analyzed.
-On the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed, which has fewer parameters \hl{(see Figure \mbox{\ref{table:model-summary}})} and depth.
+On the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed, which has fewer parameters \hl{(as shown in Table \mbox{\ref{table:model-summary}})} and depth.
 
 	\begin{table}[H]
-		\caption{\hl{Size} %MDPI: 1. Please cite the table in the text and ensure the first citation of each table appears in numerical order. 2. We remove the vertical line, please confirm.
- , parameters, and depth of the backbone model used in this paper.}
+		\caption{\hl{Size}, parameters, and depth of the backbone model used in this paper.}%MDPI: 1.
+Please cite the table in the text and ensure the first citation of each table appears in numerical order.
+2.
+We remove the vertical line, please confirm.
+		%V.D.N confirmed
 		\label{table:model-summary}
@@
 Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights.
-Soft-Attention is described in the below equation \eqref{eqn:softatt}.
+Soft-Attention is described in \hl{Equation}
+	\eqref{eqn:softatt}. % V.D.N We update the uppercase of "Equation"
 
@@
  (a constant value) attention maps.
-These $K$ attention maps are aggregated to produce a weight function called $\alpha$.
+These $\textit{K}$ attention maps are aggregated to produce a weight function called $\alpha$.
 This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, which is a learnable scalar.
@@
 		\includegraphics[width=1\linewidth]{Definitions/SoftAttention}
-		\caption{\hl{Soft-Attention~Layer.} %MDPI: Please revise the "*" into a multiplication sign ("\times" U+00D7)
+		\caption{\hl{Soft-Attention layer.} %MDPI: Please revise the "*" into a multiplication sign ("\times" U+00D7) 
 }
@@
 		\includegraphics[width=0.5\linewidth]{Definitions/SoftAttentionBlock}
-		\caption{\hl{Soft-Attention~Module.} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7)
+		\caption{\hl{Soft-Attention module.} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7)
 		%H.K.D We have already changed the the multiplication sign into "x" in the Figure 6
@@
 	\subsubsection{Loss Function}
-	The loss function used in this paper is categorical cross-entropy \hl{\mbox{\cite{8943952}}}.
+	The loss function used in this paper is categorical cross-entropy \hl{\mbox{\cite{8943952}}}. %V.D.N We have provided the citation to paper 8943952.
 	Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$.
 Let $N$, and $C$ be the number of training examples and number of classes respectively.
-The categorical cross-entropy loss is presented in the Equation \eqref{eqn:weightlossfunction}:
+The categorical cross-entropy loss is presented in Equation \eqref{eqn:weightlossfunction}:
 	\begin{equation}
@@
 
-	Otherwise, all of the models are trained with the Adam \hl{Optimizer} %MDPI: The citation of references [37-42] are missing. Please add and renumber the references to appear in numerical order.
+	Otherwise, all of the models are trained with the Adam \hl{optimizer} %MDPI: The citation of references [37-42] are missing.
+Please add and renumber the references to appear in numerical order.
+%H.K.D We have already provide the citations for all paper
  \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 \times 10^6$, and the epsilon is set to $0.1$.
@@
 		\begin{figure}[H]
-\includegraphics[width=0.6\linewidth]{Definitions/Confusion-matrix}
-\caption{Confusion Matrix.}\label{fig:confusion-matrix}
+\includegraphics[width=0.7\linewidth]{Definitions/Confusion-matrix}
+\caption{Confusion matrix.}\label{fig:confusion-matrix}
 		\end{figure}\unskip
 \begin{figure}[H]
-\includegraphics[width=.5\linewidth]{Definitions/AUC}
+\includegraphics[width=.7\linewidth]{Definitions/AUC}
 \caption{\hl{Area} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order. % H.K.D Citation provided
- Under the Curve.}\label{fig:AUC}
+ under the curve.}\label{fig:AUC}
 	\end{figure}
@@
 		\label{eqn:f1}
-		\text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\
+		\text{\textit{F1-score}} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\
 	\end{equation}
@@
 	\hl{Precision} %MDPI: Please confirm should the no indentation be retained
-	% H.K.D I think it would be better if there is no indentation but do not know to do it, could you help me remove it.
+	% V.D.N confirmed
  (Equation \eqref{eqn:pre}) or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative.
-F1-score (Equation \eqref{eqn:f1}), on the other hand, refers to the harmonic mean of precision and recall, which means the higher the f1-score is, the higher both precision and recall are.
-Besides, the expected value of precision, f1-score, and recall-score are also applied because of the multi-class problem.
+F1-score (Equation \eqref{eqn:f1}), on the other hand, refers to the harmonic mean of precision and recall, which means the higher the F1-score is, the higher both precision and recall are.
+Besides, the expected value of precision, F1-score, and recall are also applied because of the multi-class problem.
 
@@
 		\label{eqn:balacc}
-		\text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}
+		\text{\textit{Balanced Accuracy}} = \frac{\text{Sens} + \text{Spec}}{2}
 	\end{equation}
@@
 	\hl{The last} %MDPI: Please confirm should the no indentation be retained
-	% H.K.D I think it would be better if there is no indentation but do not know to do it, could you help me remove it.
- metric is the $AUC$ \hl{(see Figure \mbox{\ref{fig:AUC}})} score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of TP versus the probability of FP.
+	% V.D.N confirmed.
+ metric is the $AUC$ \hl{(as shown in Figure \mbox{\ref{fig:AUC}})} score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of TP versus the probability of FP.
 
@@
 AD stands for augmented data; this indicates that the model is trained with augmented data.
-MD stands for metadata, which indicates that the model is trained with metadata.}
+MD stands for metadata, which indicates that the model is trained with metadata.
+The bold numbers highlight the highest performance.
+These results are calculated from the confusion matrix, the two highest model confusion matrices are DenseNet201 and InceptionResNetV2 (as shown in Figure \hl{\mbox{\ref{fig:densenet201cm} and \ref{fig:irv2cm}}})}
 		\label{table:overall-acc}
@@
 
-	Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to Figures \ref{fig:den f1}--\ref{fig:incep recall}.
-As a result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data has an f1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to the Figure \ref{fig:incep f1}.
-However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depths are equal to or larger than 400 have balanced the f1-scores on class.
+	Moreover, the model trained with augmented data does not only have low accuracy but their F1-score and the recall also are imbalanced according to Figures \ref{fig:den f1}--\ref{fig:incep recall}.
+As a result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data has an F1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to Figure \ref{fig:den f1} and \ref{fig:incep f1}.
+However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depths are equal to or larger than 400 have balanced the F1-scores on class.
 The others still face the imbalanced term.
@@
 \centering
-\includegraphics[width=1.2\linewidth]{Definitions/CM/dn201cm}
+\includegraphics[width=1\linewidth]{Definitions/CM/dn201cm}
 		\end{minipage}
@@
 	% H.K.D Citation Provided
- Confusion Matrix.}\label{fig:densenet201cm}
+ confusion matrix.}\label{fig:densenet201cm}
 		\end{figure}\unskip
@@
 \centering
-\includegraphics[width=1.2\linewidth]{Definitions/CM/irv2cm}
+\includegraphics[width=1\linewidth]{Definitions/CM/irv2cm}
 		\end{minipage}
@@
 % H.K.D Citation Provided
- Confusion Matrix.}\label{fig:irv2cm}
+ confusion matrix.}\label{fig:irv2cm}
 	\end{figure}
@@
 		\includegraphics[width=1\linewidth]{Definitions/den f1}
-		\caption{The comparison between f1 scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
+		\caption{The comparison between F1-scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
 		\label{fig:den f1}
@@
 		\includegraphics[width=1\linewidth]{Definitions/in f1}
-		\caption{The comparison between f1 scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
+		\caption{The comparison between F1-scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
 		\label{fig:incep f1}
@@
 		\includegraphics[width=1\linewidth]{Definitions/den re}
-		\caption{The comparison between recall scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
+		\caption{The comparison between recall of DenseNet201 trained with augmented data and the one trained with metadata and weight loss.}
 		\label{fig:den recall}
@@
 		\includegraphics[width=1\linewidth]{Definitions/in re}
-		\caption{The comparison between recall scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
+		\caption{Comparison between recall of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss.}
 		\label{fig:incep recall}
@@
 	\end{table}
-
-	Table \ref{table:overall-auc} shows the AUC score of the three models—InceptionResNetV2, Densenet201, and ResNet50—which are trained with only augmented data or metadata.
-It is transparent that the InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: both 0.99 as opposed to 0.972 and 0.93, respectively.
-ResNet50 trained with augmented data, on the other hand, has a higher AUC-score: 0.95 as compared to 0.93 of ResNet50 trained with metadata.
-Overall, InceptionResNetV2 trained with metadata reaches the peak with an AUC score of 0.974.
+	Table \ref{table:overall-auc} shows the AUC of the three models—InceptionResNetV2, Densenet201, and ResNet50—which are trained with only augmented data or metadata.
+It is transparent that the InceptionResNetV2 and DenseNet201 have higher AUC trained with metadata: both 0.99 as opposed to 0.972 and 0.93, respectively.
+ResNet50 trained with augmented data, on the other hand, has a higher AUC of 0.95 as compared to 0.93 of ResNet50 trained with metadata.
+Overall, InceptionResNetV2 trained with metadata reaches the peak with an AUC of 0.974.
 The InceptionResNetV2 trained with metadata is also compared with the others to find out the best models trained.
-According to Figure \ref{fig:densevsirv2}, \hl{\mbox{\ref{fig:densenet201cm}, and \ref{fig:irv2cm}}} the InceptionResNetV2 still hit the peak AUC score of 0.99.
-In contrast, ResNet152 otherwise is the worst model with the AUC score of 0.87.
-Other models, on the other hand, have the approximately the same AUC score.
+According to Figure \hl{\mbox{\ref{fig:densenet201cm}, \ref{fig:irv2cm}, and \ref{fig:densevsirv2}}} the InceptionResNetV2 still hit the peak AUC of 0.99.
+In contrast, ResNet152 otherwise is the worst model with the AUC of 0.87.
+Other models, on the other hand, have the approximately the same AUC.
 
 	\begin{table}[H]
-			\caption{AUC (area under the curve) of all models.
+			\caption{AUCs of all models.
 AD stands for augmented data, this indicates that the model is trained with augmented data.
-MD stands for metadata, which indicates that the model is trained with metadata.}
+MD stands for metadata, which indicates that the model is trained with metadata.
+Bold numbers highlight the highest performance}
 		\label{table:overall-auc}
@@
 \midrule
-Proposed Method & 0.9	& 0.86 & \hl{0.86} & \hl{0.81} & \hl{0.99}%MDPI: Please confirm if the bold should be retained. If not necessary, please remove.
+Proposed Method & 0.9	& 0.86 & \hl{\textbf{0.86}} & \hl{\textbf{0.81}} & \hl{\textbf{0.99}}%MDPI: Please confirm if the bold should be retained.
+If not necessary, please remove.
+%V.D.N We confirmed to continue to use bold numbers.
 \\
@@
 } of each class: akiec, bcc, bkl, df, mel, nv and vasc, which are denoted in the abbreviations.
-The last column shows the expected value of the f1-score from each model.
+The last column shows the expected value of the F1-score from each model.
 All models in the first column are the models trained in this research.
@@
 \caption{\hl{Recall%MDPI: We remove the vertical line, please confirm. %H.K.D too beautiful
-} score of each class and the expected value of recall score from each model.}
+} of each class and the expected value of recall from each model.}
 \label{appendix-table:recall-score-summary}
@@
 
-		\subsection[\appendixname~\thesection]{Detailed Mobile Model Perform}
+		\subsection[\appendixname~\thesection]{Detailed Mobile Model Performance}
 		\begin{table}[H]
@@
 
-\bibitem[Author2(year)]{02357-1}
-\hl{Shaikh, M.A.;} %MDPI: The label 02357 is repeated. We updated this one, please confirm. % H.K.D it's duplicated with the research paper cited 33, please remove it
- Duan, T.; Chauhan, M.; Srihari, S.N. \hl{In} %MDPI: please add the article title.
- Proceedings of the 2020 17th International Conference on Frontiers in Handwriting Recognition, Dortmund, Germany, 8--10 September 2020.
-
 		\end{thebibliography}
